### 2020-09-04 main.tex
initial commit.

\documentclass{amsart}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage[alphabetic,y2k,lite]{amsrefs}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{fullpage, mystyle}
\usepackage{tikz-cd}

\newcommand{\torus}{{\mathbb{T}^2}}

\newcommand{\RRR}{{\underline{\mathfrak{R}}}}
\newcommand{\QQQ}{{\underline{\mathfrak{Q}}}}
\newcommand{\CCC}{{\underline{\mathfrak{C}}}}
\newcommand{\PPP}{{\underline{\mathbf{\Phi}}}}
\newcommand{\TTT}{{\underline{\mathbf{\Theta}}}}
\newcommand{\LLL}{{\underline{\mathfrak{L}}}}

\newcommand{\cev}[1]{\overset{\leftarrow}{#1}}

%% for allowing other symbols to be arrow in tikzcd
%% e.g. A \ar[r, symbol=\subseteq] & B
\tikzset{
  symbol/.style={
    draw=none,
    every to/.append style={
      edge node={node [sloped, allow upside down, auto=false]{$#1$}}}
  }
}

\begin{document}

\title{Variation on a Variational Principle}
\author{Alice Kwon}
   \address{TODO SUNY Maritime address}
    \email{TODO email}
    \urladdr{TODO webpage}
\author{Ying Hong Tham}
   \address{Department of Mathematics, Stony Brook University, 
            Stony Brook, NY 11794, USA}
    \email{yinghong.tham@stonybrook.edu}
    \urladdr{http://www.math.sunysb.edu/\textasciitilde yinghong/}

\begin{abstract}
We prove that alternating links in the thickened torus remaini hyperbolic
after certain augmentations.
\end{abstract}
\maketitle

%===============================================================================
\section{Introduction}

\textbf{Definitions, Notations, and Conventions}

Always assume surface $\Sigma$ (our case $\Sigma = \torus$) is oriented.

define cellular decomp of surface

$V,E,F$ are set of vertices, edges, faces.

$\vec{E}$ is the set of oriented edges.
We may identify an oriented edge $\vec{e}$ with the pair $(f_{\vec{e}}, e)$,
where $f_{\vec{e}}$ is the face to the left of $\vec{e}$.

%===============================================================================

\section{Set up?}

Recall circle pattern.

A circle pattern is determined by the radius of the circle $C_f$ associated to each face, $r_f$,
and the angle that each edge subtends in adjacent faces, $\vphi_{\vec{e}}$. (see figure TODO)
Thus determines, and is determined by a point in $\RRR \times \QQQ$, where

\begin{itemize}
	\item $\RRR := \RR_+^F = \{(r_f)_{f\in F} | r_f \in \RR_+\}$
	\item $\QQQ := \RR^{\vec{E}} =
		\{(\vphi_{\vec{e}})_{\vec{e} \in \vec{E}} | \vphi_{\vec{e}} \in \RR\}$
\end{itemize}
but clearly not every point $c\in \RRR \times \QQQ$ determines a circle pattern.

On $\RRR \times \QQQ$, there are several functions to consider:
\begin{itemize}
	\item $\Phi_f = 2 \sum_{\vec{e} \in \del f} \vphi_{\vec{e}}$, measuring the cone angle
		at the center of $C_f$
	\item $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$
	\item $l_{\vec{e}} = r_{f_{\vec{e}}} \sin \vphi_{\vec{e}}$
\end{itemize}

These fit together to give maps to the following spaces:

\begin{itemize}
	\item $\PPP := \RR^F = \{(\Phi_f)_{f\in F} | \Phi_f \in \RR\}$
	\item $\TTT := \RR^E = \{(\theta_e)_{e \in E} | \theta_e \in \RR\}$
	\item $\LLL := \RR^{\vec{E}} = \{(l_{\vec{e}})_{\vec{e} \in E} | l_{\vec{e}} \in \RR\}$
\end{itemize}

Our main argument is to deform "degenerate" circle patterns, where adjacent circles may
be identical or tangent, into ones that don't look so degenerate,
hence it is conveneint to extend the notion of circle pattern:

\begin{definition}
An \emph{extended circle pattern} is $c = ((r_f), (\vphi_{\vec{e}})) \in \RRR \times \QQQ$
such that $l_{\vec{e}} = l_{\cev{e}}$ for all edges $e\in E$. We denote by
$\CCC$ the set of extended circle patterns.
\end{definition}

\begin{tikzcd}
\CCC = \{l_{\vec{e}} = l_{\cev{e}} \} \ar[r,symbol=\subseteq]
	& \RRR \times \QQQ \ar[r] \ar[d]
	&\TTT \\
	& \PPP
\end{tikzcd}

[Check this] The usual notion of circle pattern would be restricted to those $c\in \CCC$
with $\vphi_{\vec{e}} \in (0,\pi)$ and $\theta_e \in (0,\pi)$.
One may consider deforming a circle pattern so as to have some $\theta_e$ approach 0 or $\pi$.
The limit $\theta_e \to \pi$ is easy to picture, one simply gets that the two circles
$C_f, C_{f'}$ of the adjacent faces become tangent. The limit $\theta_e \to 0$
is a bit more complex, as the final shape of $Q_e$ (the quadrangle associated to $e$)
depends also on $\vphi_{\vec{e}}$ (which equals $\pi - \vphi_{\cev{e}}$ in the limit.
If we parametrize circle patterns by $(r_f)$ and $(\theta_e)$ as in TODO \ocite{BS},
the limiting shape would depend on how $r_f$ approaches $r_{f'}$,
some sort of blow up stuff TODO.

We will mostly be working with extended circle patterns that mostly ``look normal",
with all $\vphi_{\vec{e}}$ in some range $(-\veps, \pi + \veps)$.

\begin{definition}
An extended circle pattern is said to be \emph{face non-singular}
if $\Phi_f = 2\pi$ for all faces $f$; it is said to be \emph{vertex non-singular}
if $\sum_{e \ni v} \theta_e = 2\pi$ for all vertices $v$.
Finally it is said to be \emph{non-singular} if it is both.
\end{definition}

non-degenerate circle pattern?

\begin{definition}
Given some extended circle pattern $c \in \CCC$,
we say a face $f$ is \emph{convex} if for all edges $\vec{e} \in \del f$,
we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
We say $f$ is \emph{thin} if exactly two edges $\vec{e}, \vec{e'} \in \del f$
have nonzero $\vphi_{\cdot}$, and furtheremore,
	$0 < \vphi_{\vec{e}} = \pi - \vphi_{\vec{e'}} < \pi/2$.
\end{definition}

TODO figures for convex, thin faces

\begin{definition}
Given an extended circle pattern $c\in \CCC$, an edge $e$ is \emph{short}
if it has length 0, $l_{\vec{e}} = l_{\cev{e}} = 0$;
it is \emph{long} otherwise.
\end{definition}

\begin{definition}
Given an extended circle pattern $c\in \CCC$, a \emph{thick path}
is a sequence of faces $f_0,f_1,\ldots,f_n$
such that $f_i,f_{i+1}$ share a long edge.
A \emph{thick cycle} is a thick path with $f_0 = f_n$.
\end{definition}

%===============================================================================

\section{Main results??}

Our general strategry for obtaining a (non-singular) circle pattern
is to start with an assignment $\underline{\theta} = (\theta_\cdot)$
for which we know an extended circle pattern exists
(say from results of \ocite{BS}),
and a path $\gamma$ in $\TTT$ starting at $\underline{\theta}$.
We then attempt to lift $\gamma$ to a path $\tilde{\gamma}$ in $\CCC$,
so that $\tilde{\gamma}$ remains (face) non-singular
(vertex non-singularity is already determined by $\gamma$).

Note that since $\sum_{e\in E} \theta_e
= 2\pi |E| - \sum_{\vec{e} \in \vec{E}} \vphi_{\vec{e}}
= 2\pi |E| - \sum_{f\in F} \Phi_f$,
we see that maintaining face non-singularity of $\tilde{\gamma}$
forces $\sum \theta_e$ to be constant.
We will show that this is the only obstruction on $\gamma$
to the lifting to such $\tilde{\gamma}$.

To that end, let $L$ be the $(|E|-1)$-plane distribution on $\TTT$
tangent to the level sets of $\sum \theta_v$.
The following proposition proves it(?) up to first order at a point:

\begin{proposition}
\label{p:point_lift}
Let $c \in \CCC$ be an extended circle pattern such that
\begin{itemize}
	\item $\Phi_f = 2\pi$ for all $f\in F$;
	\item all faces are eithe convex or thin;
	\item every pair of faces is connected by a thick path.
\end{itemize}
Let $K_c = \ker (A_*|_c : T_c \CCC \to T_{A(c)} \PPP)$.
Then $B_*(K_c) = L_{B(c)}$.

In other words, for any vector $b = b^e \del_{\theta_e}$
with sum of coefficients 0, one can vary $c$ so that its
first order change in $\theta_\cdot$ is $b$,
and also remains face non-singular up to first order.
\end{proposition}

\begin{lemma}
Let $c \in \CCC$ be as in \prpref{p:point_lift}.
Then $A$ is a submersion in a neighbourhood of $c$.
\end{lemma}

\begin{proposition}
Let $c\in \CCC$ be as in \prpref{p:point_lift}.
TODO full lifting statement.
\end{proposition}

%===============================================================================

%\input{appendix}
\end{document}

### 2020-09-06 main.tex
moved things around, now can edit files separately, avoid clashes

@@
 \begin{abstract}
-We prove that alternating links in the thickened torus remaini hyperbolic
+We prove that alternating links in the thickened torus remain hyperbolic
 after certain augmentations.
@@
 
-%===============================================================================
-\section{Introduction}
+\input{intro}
+\input{notation}
+\input{results}
 
-\textbf{Definitions, Notations, and Conventions}
-
-Always assume surface $\Sigma$ (our case $\Sigma = \torus$) is oriented.
-
-define cellular decomp of surface
-
-$V,E,F$ are set of vertices, edges, faces.
-
-$\vec{E}$ is the set of oriented edges.
-We may identify an oriented edge $\vec{e}$ with the pair $(f_{\vec{e}}, e)$,
-where $f_{\vec{e}}$ is the face to the left of $\vec{e}$.
-
-%===============================================================================
-
-\section{Set up?}
-
-Recall circle pattern.
-
-A circle pattern is determined by the radius of the circle $C_f$ associated to each face, $r_f$,
-and the angle that each edge subtends in adjacent faces, $\vphi_{\vec{e}}$. (see figure TODO)
-Thus determines, and is determined by a point in $\RRR \times \QQQ$, where
-
-\begin{itemize}
-	\item $\RRR := \RR_+^F = \{(r_f)_{f\in F} | r_f \in \RR_+\}$
-	\item $\QQQ := \RR^{\vec{E}} =
-		\{(\vphi_{\vec{e}})_{\vec{e} \in \vec{E}} | \vphi_{\vec{e}} \in \RR\}$
-\end{itemize}
-but clearly not every point $c\in \RRR \times \QQQ$ determines a circle pattern.
-
-On $\RRR \times \QQQ$, there are several functions to consider:
-\begin{itemize}
-	\item $\Phi_f = 2 \sum_{\vec{e} \in \del f} \vphi_{\vec{e}}$, measuring the cone angle
-		at the center of $C_f$
-	\item $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$
-	\item $l_{\vec{e}} = r_{f_{\vec{e}}} \sin \vphi_{\vec{e}}$
-\end{itemize}
-
-These fit together to give maps to the following spaces:
-
-\begin{itemize}
-	\item $\PPP := \RR^F = \{(\Phi_f)_{f\in F} | \Phi_f \in \RR\}$
-	\item $\TTT := \RR^E = \{(\theta_e)_{e \in E} | \theta_e \in \RR\}$
-	\item $\LLL := \RR^{\vec{E}} = \{(l_{\vec{e}})_{\vec{e} \in E} | l_{\vec{e}} \in \RR\}$
-\end{itemize}
-
-Our main argument is to deform "degenerate" circle patterns, where adjacent circles may
-be identical or tangent, into ones that don't look so degenerate,
-hence it is conveneint to extend the notion of circle pattern:
-
-\begin{definition}
-An \emph{extended circle pattern} is $c = ((r_f), (\vphi_{\vec{e}})) \in \RRR \times \QQQ$
-such that $l_{\vec{e}} = l_{\cev{e}}$ for all edges $e\in E$. We denote by
-$\CCC$ the set of extended circle patterns.
-\end{definition}
-
-\begin{tikzcd}
-\CCC = \{l_{\vec{e}} = l_{\cev{e}} \} \ar[r,symbol=\subseteq]
-	& \RRR \times \QQQ \ar[r] \ar[d]
-	&\TTT \\
-	& \PPP
-\end{tikzcd}
-
-[Check this] The usual notion of circle pattern would be restricted to those $c\in \CCC$
-with $\vphi_{\vec{e}} \in (0,\pi)$ and $\theta_e \in (0,\pi)$.
-One may consider deforming a circle pattern so as to have some $\theta_e$ approach 0 or $\pi$.
-The limit $\theta_e \to \pi$ is easy to picture, one simply gets that the two circles
-$C_f, C_{f'}$ of the adjacent faces become tangent. The limit $\theta_e \to 0$
-is a bit more complex, as the final shape of $Q_e$ (the quadrangle associated to $e$)
-depends also on $\vphi_{\vec{e}}$ (which equals $\pi - \vphi_{\cev{e}}$ in the limit.
-If we parametrize circle patterns by $(r_f)$ and $(\theta_e)$ as in TODO \ocite{BS},
-the limiting shape would depend on how $r_f$ approaches $r_{f'}$,
-some sort of blow up stuff TODO.
-
-We will mostly be working with extended circle patterns that mostly ``look normal",
-with all $\vphi_{\vec{e}}$ in some range $(-\veps, \pi + \veps)$.
-
-\begin{definition}
-An extended circle pattern is said to be \emph{face non-singular}
-if $\Phi_f = 2\pi$ for all faces $f$; it is said to be \emph{vertex non-singular}
-if $\sum_{e \ni v} \theta_e = 2\pi$ for all vertices $v$.
-Finally it is said to be \emph{non-singular} if it is both.
-\end{definition}
-
-non-degenerate circle pattern?
-
-\begin{definition}
-Given some extended circle pattern $c \in \CCC$,
-we say a face $f$ is \emph{convex} if for all edges $\vec{e} \in \del f$,
-we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
-We say $f$ is \emph{thin} if exactly two edges $\vec{e}, \vec{e'} \in \del f$
-have nonzero $\vphi_{\cdot}$, and furtheremore,
-	$0 < \vphi_{\vec{e}} = \pi - \vphi_{\vec{e'}} < \pi/2$.
-\end{definition}
-
-TODO figures for convex, thin faces
-
-\begin{definition}
-Given an extended circle pattern $c\in \CCC$, an edge $e$ is \emph{short}
-if it has length 0, $l_{\vec{e}} = l_{\cev{e}} = 0$;
-it is \emph{long} otherwise.
-\end{definition}
-
-\begin{definition}
-Given an extended circle pattern $c\in \CCC$, a \emph{thick path}
-is a sequence of faces $f_0,f_1,\ldots,f_n$
-such that $f_i,f_{i+1}$ share a long edge.
-A \emph{thick cycle} is a thick path with $f_0 = f_n$.
-\end{definition}
-
-%===============================================================================
-
-\section{Main results??}
-
-Our general strategry for obtaining a (non-singular) circle pattern
-is to start with an assignment $\underline{\theta} = (\theta_\cdot)$
-for which we know an extended circle pattern exists
-(say from results of \ocite{BS}),
-and a path $\gamma$ in $\TTT$ starting at $\underline{\theta}$.
-We then attempt to lift $\gamma$ to a path $\tilde{\gamma}$ in $\CCC$,
-so that $\tilde{\gamma}$ remains (face) non-singular
-(vertex non-singularity is already determined by $\gamma$).
-
-Note that since $\sum_{e\in E} \theta_e
-= 2\pi |E| - \sum_{\vec{e} \in \vec{E}} \vphi_{\vec{e}}
-= 2\pi |E| - \sum_{f\in F} \Phi_f$,
-we see that maintaining face non-singularity of $\tilde{\gamma}$
-forces $\sum \theta_e$ to be constant.
-We will show that this is the only obstruction on $\gamma$
-to the lifting to such $\tilde{\gamma}$.
-
-To that end, let $L$ be the $(|E|-1)$-plane distribution on $\TTT$
-tangent to the level sets of $\sum \theta_v$.
-The following proposition proves it(?) up to first order at a point:
-
-\begin{proposition}
-\label{p:point_lift}
-Let $c \in \CCC$ be an extended circle pattern such that
-\begin{itemize}
-	\item $\Phi_f = 2\pi$ for all $f\in F$;
-	\item all faces are eithe convex or thin;
-	\item every pair of faces is connected by a thick path.
-\end{itemize}
-Let $K_c = \ker (A_*|_c : T_c \CCC \to T_{A(c)} \PPP)$.
-Then $B_*(K_c) = L_{B(c)}$.
-
-In other words, for any vector $b = b^e \del_{\theta_e}$
-with sum of coefficients 0, one can vary $c$ so that its
-first order change in $\theta_\cdot$ is $b$,
-and also remains face non-singular up to first order.
-\end{proposition}
-
-\begin{lemma}
-Let $c \in \CCC$ be as in \prpref{p:point_lift}.
-Then $A$ is a submersion in a neighbourhood of $c$.
-\end{lemma}
-
-\begin{proposition}
-Let $c\in \CCC$ be as in \prpref{p:point_lift}.
-TODO full lifting statement.
-\end{proposition}
-
-%===============================================================================
-
-%\input{appendix}
 \end{document}

### 2020-09-06 notation.tex
moved things around, now can edit files separately, avoid clashes

\textbf{Definitions, Notations, and Conventions}

Always assume surface $\Sigma$ (our case $\Sigma = \torus$) is oriented.

define cellular decomp of surface

$V,E,F$ are set of vertices, edges, faces.

$\vec{E}$ is the set of oriented edges.
We may identify an oriented edge $\vec{e}$ with the pair $(f_{\vec{e}}, e)$,
where $f_{\vec{e}}$ is the face to the left of $\vec{e}$.

%===============================================================================

Recall circle pattern.

A circle pattern is determined by the radius of the circle $C_f$ associated to each face, $r_f$,
and the angle that each edge subtends in adjacent faces, $\vphi_{\vec{e}}$. (see figure TODO)
Thus determines, and is determined by a point in $\RRR \times \QQQ$, where

\begin{itemize}
	\item $\RRR := \RR_+^F = \{(r_f)_{f\in F} | r_f \in \RR_+\}$
	\item $\QQQ := \RR^{\vec{E}} =
		\{(\vphi_{\vec{e}})_{\vec{e} \in \vec{E}} | \vphi_{\vec{e}} \in \RR\}$
\end{itemize}
but clearly not every point $c\in \RRR \times \QQQ$ determines a circle pattern.

On $\RRR \times \QQQ$, there are several functions to consider:
\begin{itemize}
	\item $\Phi_f = 2 \sum_{\vec{e} \in \del f} \vphi_{\vec{e}}$, measuring the cone angle
		at the center of $C_f$
	\item $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$
	\item $l_{\vec{e}} = r_{f_{\vec{e}}} \sin \vphi_{\vec{e}}$
\end{itemize}

These fit together to give maps to the following spaces:

\begin{itemize}
	\item $\PPP := \RR^F = \{(\Phi_f)_{f\in F} | \Phi_f \in \RR\}$
	\item $\TTT := \RR^E = \{(\theta_e)_{e \in E} | \theta_e \in \RR\}$
	\item $\LLL := \RR^{\vec{E}} = \{(l_{\vec{e}})_{\vec{e} \in E} | l_{\vec{e}} \in \RR\}$
\end{itemize}

Our main argument is to deform ``degenerate" circle patterns,
where adjacent circles may
be identical or tangent, into ones that don't look so degenerate,
hence it is conveneint to extend the notion of circle pattern:

\begin{definition}
An \emph{extended circle pattern} is
$c = ((r_f), (\vphi_{\vec{e}})) \in \RRR \times \QQQ$
such that $l_{\vec{e}} = l_{\cev{e}}$ for all edges $e\in E$. We denote by
$\CCC$ the set of extended circle patterns.
\end{definition}

\begin{tikzcd}
\CCC = \{l_{\vec{e}} = l_{\cev{e}} \} \ar[r,symbol=\subseteq]
	& \RRR \times \QQQ \ar[r] \ar[d]
	&\TTT \\
	& \PPP
\end{tikzcd}

[Check this] The usual notion of circle pattern would be restricted to those $c\in \CCC$
with $\vphi_{\vec{e}} \in (0,\pi)$ and $\theta_e \in (0,\pi)$.
One may consider deforming a circle pattern so as to have some $\theta_e$ approach 0 or $\pi$.
The limit $\theta_e \to \pi$ is easy to picture, one simply gets that the two circles
$C_f, C_{f'}$ of the adjacent faces become tangent. The limit $\theta_e \to 0$
is a bit more complex, as the final shape of $Q_e$ (the quadrangle associated to $e$)
depends also on $\vphi_{\vec{e}}$ (which equals $\pi - \vphi_{\cev{e}}$ in the limit.
If we parametrize circle patterns by $(r_f)$ and $(\theta_e)$ as in TODO \ocite{BS},
the limiting shape would depend on how $r_f$ approaches $r_{f'}$,
some sort of blow up stuff TODO.

We will mostly be working with extended circle patterns that mostly ``look normal",
with all $\vphi_{\vec{e}}$ in some range $(-\veps, \pi + \veps)$.

\begin{definition}
An extended circle pattern is said to be \emph{face non-singular}
if $\Phi_f = 2\pi$ for all faces $f$; it is said to be \emph{vertex non-singular}
if $\sum_{e \ni v} \theta_e = 2\pi$ for all vertices $v$.
Finally it is said to be \emph{non-singular} if it is both.
\end{definition}

non-degenerate circle pattern?

\begin{definition}
Given some extended circle pattern $c \in \CCC$,
we say a face $f$ is \emph{convex} if for all edges $\vec{e} \in \del f$,
we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
We say $f$ is \emph{thin} if exactly two edges $\vec{e}, \vec{e'} \in \del f$
have nonzero $\vphi_{\bullet}$, and furtheremore,
	$0 < \vphi_{\vec{e}} = \pi - \vphi_{\vec{e'}} < \pi/2$.
\end{definition}

TODO figures for convex, thin faces

\begin{definition}
Given an extended circle pattern $c\in \CCC$, an edge $e$ is \emph{short}
if it has length 0, $l_{\vec{e}} = l_{\cev{e}} = 0$;
it is \emph{long} otherwise.
\end{definition}

\begin{definition}
Given an extended circle pattern $c\in \CCC$, a \emph{thick path}
is a sequence of faces $f_0,f_1,\ldots,f_n$
such that $f_i,f_{i+1}$ share a long edge.
A \emph{thick cycle} is a thick path with $f_0 = f_n$.
\end{definition}

\begin{definition}
A \emph{slit-convex circle pattern} is an extended cirlce pattern
$c \in \CCC$ such that all its faces are either convex or thin.
\end{definition}

\begin{lemma}
$\CCC$ is a manifold near slit-convex circle patterns.
\end{lemma}

\begin{proof}
$d(l_{\vec{e}} - l_{\cev{e}})
= \sin \vphi_{\vec{e}} d r_{f_{\vec{e}}}
+ r_{f_{\vec{e}}} \cos \vphi_{\vec{e}} d \vphi_{\vec{e}}
- \sin \vphi_{\cev{e}} d r_{f_{\cev{e}}}
- r_{f_{\cev{e}}} \cos \vphi_{\cev{e}} d \vphi_{\cev{e}}
$,
and since having only convex of thin faces implies
$\cos \vphi_{\vec{e}} \neq 0$,
we see the differentials are linearly independent at
a slit-convex circle pattern $c$.
\end{proof}

### 2020-09-06 results.tex
moved things around, now can edit files separately, avoid clashes

\section{Main results??}

Our general strategry for obtaining a (non-singular) circle pattern
is to start with an assignment $\underline{\theta} = (\theta_\bullet)$
for which we know an extended circle pattern exists
(say from results of \ocite{BS}),
and a path $\gamma$ in $\TTT$ starting at $\underline{\theta}$.
We then attempt to lift $\gamma$ to a path $\tilde{\gamma}$ in $\CCC$,
so that $\tilde{\gamma}$ remains (face) non-singular
(vertex non-singularity is already determined by $\gamma$).

Note that since $\sum_{e\in E} \theta_e
= 2\pi |E| - \sum_{\vec{e} \in \vec{E}} \vphi_{\vec{e}}
= 2\pi |E| - \sum_{f\in F} \Phi_f$,
we see that maintaining face non-singularity of $\tilde{\gamma}$
forces $\sum \theta_e$ to be constant.
We will show that this is the only obstruction on $\gamma$
to the lifting to such $\tilde{\gamma}$.

To that end, let $L$ be the $(|E|-1)$-plane distribution on $\TTT$
tangent to the level sets of $\sum \theta_v$.
The following proposition proves it(?) up to first order at a point:

\begin{proposition}
\label{p:point_lift}
Let $c \in \CCC$ be an extended circle pattern such that
\begin{itemize}
	\item $\Phi_f = 2\pi$ for all $f\in F$;
	\item all faces are eithe convex or thin;
	\item every pair of faces is connected by a thick path.
\end{itemize}
Let $K_c = \ker (A_*|_c : T_c \CCC \to T_{A(c)} \PPP)$.
Then $B_*(K_c) = L_{B(c)}$.

In other words, for any vector $b = b^e \del_{\theta_e}$
with sum of coefficients 0, one can vary $c$ so that its
first order change in $\theta_\bullet$ is $b$,
and also remains face non-singular up to first order.
\end{proposition}

\begin{lemma}
Let $c \in \CCC$ be as in \prpref{p:point_lift}.
Then $A$ is a submersion in a neighbourhood of $c$.
\end{lemma}

\begin{proposition}
Let $c\in \CCC$ be as in \prpref{p:point_lift}.
TODO full lifting statement.
\end{proposition}

%===============================================================================

### 2020-09-07 results.tex
some progress

@@
 	\item $\Phi_f = 2\pi$ for all $f\in F$;
-	\item all faces are eithe convex or thin;
+	\item all faces are eithe convex or thin,
+		with at least one convex face;
 	\item every pair of faces is connected by a thick path.
@@
 
+Before we prove this, it is convenient to first prove the following:
+
 \begin{lemma}
@@
 \end{lemma}
+
+\begin{proof}
+We construct vectors $\beta_f \in T_c \CCC$ so that
+$A_*(\beta_f) = \ddd{\Phi_f}$.
+The vector
+\begin{equation}
+\beta_f = [ \ddd{r_f} - \sum_{\vec{e} \in \del f} 
+	\frac{\tan \vphi_{\vec{e}}}{r_f} \ddd{\vphi_{\vec{e}}}] \cdot \alpha
+\end{equation}
+doesn't change $l_{\vec{e}}$,
+so is in $T_c \CCC$
+($\alpha$ to be determined).
+Its pushforward under $A$ is simply
+$A_*(\beta_f) = \frac{1}{r_f} \sum_{\vec{e}\in \del f} \tan \vphi_{\vec{e}}
+	\ddd{\Phi_f}$.
+
+If $f$ is a convex face, then the $\tan \vphi_{\vec{e}}$ are all positive,
+so $A_*(\beta_f)$ is a negative multiple of $\ddd{\Phi_f}$;
+we choose $\alpha$ so that $A_*(\beta_f) = \ddd{\Phi_f}$.
+Intuitively, this is like
+pulling the center of $C_f$ up off the plane, increasing $r_f$ and decreasing all
+$\vphi$'s.
+
+If $f$ is thin, the coefficients sum to 0 so that $A_*(\beta_f) = 0$,
+so we need a different approach. First suppose $f$ shares an edge
+$e$ with a convex face $f'$. We can increase $l_e$
+by increasing $\vphi_{\vec{e}},\vphi_{\cev{e}}$
+while holding $r_f,r_{f'}$ constant.
+This will affect both $\Phi_f, \Phi_{f'}$,
+so we use $\beta_{f'}$ to make $\Phi_{f'}$ constant.
+More explicitly, consider
+$\beta_e = \frac{1}{2\cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
++ \frac{1}{2\cos \vphi_{\cev{e}}} \ddd{\vphi_{\cev{e}}}$.
+Then we can take
+$\beta_f = \cos \vphi_{\vec{e}}
+	(\beta_e - \frac{1}{\cos \vphi_{\cev{e}}} \beta_{f'})$.
+We can repeat this procedure with $f'$ set to $f$.
+\end{proof}
+
+\begin{proof}[Proof of \prpref{p:point_lift}]
+proof
+\end{proof}
 

### 2020-09-08 results.tex
more stuff.

--- 2020-09-06 results.tex
@@
-\section{Main results??}
+\section{Main ?? results}
 
@@
 tangent to the level sets of $\sum \theta_v$.
-The following proposition proves it(?) up to first order at a point:
+The following proposition proves it (avoid using `it'?) up to first order at a point:
 
@@
 	\item $\Phi_f = 2\pi$ for all $f\in F$;
-	\item all faces are eithe convex or thin;
+	\item all faces are eithe convex or thin,
+		with at least one convex face;
 	\item every pair of faces is connected by a thick path.
 \end{itemize}
-Let $K_c = \ker (A_*|_c : T_c \CCC \to T_{A(c)} \PPP)$.
-Then $B_*(K_c) = L_{B(c)}$.
+Let $K_c = \ker (\Phi_*|_c : T_c \CCC \to T_{\Phi(c)} \PPP)$.
+Then $\Theta_*(K_c) = L_{\Theta(c)}$.
 
@@
 
+Before we prove this, it is convenient to first prove the following:
+
 \begin{lemma}
 Let $c \in \CCC$ be as in \prpref{p:point_lift}.
-Then $A$ is a submersion in a neighbourhood of $c$.
+Then $\Phi$ is a submersion in a neighbourhood of $c$.
 \end{lemma}
+
+\begin{proof}
+We construct vectors $\beta_f \in T_c \CCC$ so that
+$\Phi_*(\beta_f) = \ddd{\Phi_f}$.
+The vector
+\begin{equation}
+\label{e:alpha_f}
+\alpha_f := \ddd{r_f} - \sum_{\vec{e} \in \del f} 
+	\frac{\tan \vphi_{\vec{e}}}{r_f} \ddd{\vphi_{\vec{e}}}
+	\in T(\RRR \times \QQQ)
+\end{equation}
+doesn't change $l_{\vec{e}}$,
+so is in $T_c \CCC$.
+Intuitively, $\alpha_f$ is like
+pulling the center of $C_f$ up off the plane, increasing $r_f$ and decreasing all
+$\vphi$'s.
+Its pushforward under $\Phi$ is simply
+$\Phi_*(\beta_f) = \frac{1}{r_f} \sum_{\vec{e}\in \del f} \tan \vphi_{\vec{e}}
+	\ddd{\Phi_f}$.
+
+If $f$ is a convex face, then the $\tan \vphi_{\vec{e}}$ are all non-negative,
+being 0 if and only if $e$ is short.
+so $\Phi_*(\alpha_f)$ is a negative multiple of $\ddd{\Phi_f}$;
+we choose $\beta$ so that
+\begin{equation}
+\label{e:beta_f_convex}
+\beta_f := \beta \cdot \alpha_f; \;\;\;
+\Phi_*(\beta_f) = \ddd{\Phi_f}
+\end{equation}
+
+If $f$ is thin, the coefficients sum to 0 so that $\Phi_*(\beta_f) = 0$,
+so we need a different approach. First suppose $f$ shares an edge
+$e$ with a convex face $f'$. We can increase $l_e$
+by increasing $\vphi_{\vec{e}},\vphi_{\cev{e}}$
+while holding $r_f,r_{f'}$ constant.
+This will affect both $\Phi_f, \Phi_{f'}$,
+so we use $\beta_{f'}$ to make $\Phi_{f'}$ constant.
+More explicitly, consider
+\begin{equation}
+\label{e:alpha_e}
+\alpha_e = \frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
++ \frac{1}{2 r_{f'}\cos \vphi_{\cev{e}}} \ddd{\vphi_{\cev{e}}}
+\end{equation}
+Then we can take
+\begin{equation}
+\label{e:beta_f_thin}
+\beta_f = r_f \cos \vphi_{\vec{e}}
+	(\alpha_e - \frac{1}{r_{f'} \cos \vphi_{\cev{e}}} \beta_{f'})
+\end{equation}
+which increases $l_{\vec{e}}, l_{\cev{e}}$ at unit speed,
+$dl_{\vec{e}}(\alpha_e) = dl_{\cev{e}}(\alpha_e) = 1$.
+We can repeat this procedure with $f'$ set to this thin face,
+and $f$ set to another thin face adjacent to it, etc.
+\end{proof}
+
+\begin{proof}[Proof of \prpref{p:point_lift}]
+We construct a vector $u_e \in K_c \subseteq T_c \CCC$ for each long edge $e$
+such that if $\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$,
+\begin{itemize}
+	\item $a^e = 1$;
+	\item $a^{e'} \leq 0$ for all $e' \neq e$;
+	\item $a^{e'} = 0$ for short edges $e'$.
+\end{itemize}
+
+First suppose that $e$ is between two convex faces $f, f'$
+(so $\vec{e} \in \del f, \cev{e} \in \del f'$).
+Observe that $\alpha_e$ from \eqnref{e:alpha_e}
+increases $\Phi_f$ and $\Phi_{f'}$,
+and we can compensate using $\beta_f$ from \eqnref{e:beta_f_convex},
+so we consider
+\[
+w_e = \alpha_e - \frac{1}{\cos \vphi_{\vec{e}}} \beta_f
+	- \frac{1}{\cos \vphi_{\cev{e}}} \beta_{f'} \in K_c
+\]
+%Since $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$,
+%we need to show that the coefficients of $\ddd{\vphi_{\vec{e}}},
+%\ddd{\vphi_{\cev{e}}}$ sum to 0.
+For $\vec{e'} \in \del f \cup \del f' \backslash \{\vec{e},\cev{e}\}$,
+the $\ddd{\vphi_{\vec{e'}}}$ component only appears in $\beta_f$
+or $\beta_{f'}$, which is positive by construciton
+(this requires $f,f'$ to be convex faces);
+thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
+is equal 0 if and only if $e'$ is short.
+Finally, since $w_e \in K_c$, it leaves the sum $\sum_{e\in E} \theta_e$
+constant, so $d\theta_e(w_e) < 0$, so we can take
+\begin{equation}
+\label{e:u_e}
+u_e = (d\theta_e(w_e))^\inv \cdot w_e
+\end{equation}
+
+In general, we consider a thick path of faces $f_0, \ldots, f_n$,
+such that all faces except $f_0$ and $f_n$ are thin.
+
+\end{proof}
 

### 2020-09-08 draft1.tex
more stuff from Alice

\documentclass[11pt]{amsart}
\usepackage{float}
\usepackage{amsfonts, amstext, amsmath, amsthm, amscd, amssymb, upgreek}
\usepackage{graphicx, color,  subfigure, wrapfig, overpic}
\usepackage[all,cmtip]{xy} 
\usepackage{tikz}

\textwidth 6.07in 
\textheight 8.6in 
\oddsidemargin 0.18in
\evensidemargin 0.18in
% \topmargin -0.07in

%%  If the following line is uncommented, we see the labels of theorems, figures, etc. in the margins.
% \usepackage[notref,notcite]{showkeys}
\setlength{\marginparwidth}{0.8in}
\let\oldmarginpar\marginpar
\renewcommand\marginpar[1]{\oldmarginpar[\raggedleft\footnotesize #1]%
{\raggedright\footnotesize #1}}

%This command stops the Math Review numbers appearing in the references! 
\AtBeginDocument{
   \def\MR#1{}
}
\newcommand{\Sp}{\rm{S}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\HH}{\mathbb{H}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\bfloor}[1]{\left\lfloor #1\right\rfloor}
\renewcommand{\P}{\mathcal P}
\newcommand{\A}{\mathcal A}
\newcommand{\W}{\mathcal W}
\newcommand{\vol}{{\rm vol}}
\newcommand{\cut}{{\backslash \backslash}}
\newcommand{\bdy}{\partial}
\newcommand{\voct}{{v_{\rm oct}}}
\newcommand{\vtet}{{v_{\rm tet}}}
\renewcommand{\L}{\mathcal L}
\newcommand{\cp}{\mathcal{C}}
\newcommand{\toF}{{\overset{F}{\longrightarrow}}}
\newcommand{\K}{\upkappa}

\def\co{\colon\thinspace}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{example}[theorem]{Example}

\newtheorem*{namedtheorem}{\theoremname}
\newcommand{\theoremname}{testing}
\newenvironment{named}[1]{\renewcommand{\theoremname}{#1}\begin{namedtheorem}}{\end{namedtheorem}}
\theoremstyle{definition}
\newtheorem{define}[theorem]{Definition}
\newtheorem{question}[theorem]{Question}
\newtheorem{remark}[theorem]{Remark}

\title [Augmented Links in the Thickened Torus] {Augmented Links in the Thickened Torus}

\author[Alice Kwon and Ying Hong Tham]{Alice Kwon and Ying Hong Tham}

\begin{document}
\maketitle

\begin{abstract}
  abstract goes here...
\end{abstract}

\section{Introduction}

Given a twist reduced diagram of a link $L$, {\it augmentation} is a process in which an unknotted circle component is added to one or more twist regions (a single crossing or a string of bigons) of $L$. Due to the added circle component we can remove full twists at the twist region of $L$. If the twist region has an odd number of crossings then all but one crossing is removed, whereas if the twist region has an even number of crossings then all are removed. The newly obtained link diagram is called an {\it augmented link diagram}. See Figure \ref{fig:Augmentations}.

Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in $\Sp^3$ the link $L$ obtained by augmentation $K$ is hyperbolic. In this paper we investigate if this statement holds for links in the thickened torus i.e. if $L$ is a link obtained from augmenting a hyperbolic alternating link $K$ in the thickened torus. In this chapter we find many families of hyperbolic links in the thickened torus which remain hyperbolic after augmentation.

 \begin{figure}
 \centering  
 \begin{tabular}{cc}
 \includegraphics [height=4cm]{augmentation1}&
  \includegraphics [height=4cm]{augmentation2}\\
  (a)&(b)
  \end{tabular}
 \caption{The left shows a pretzel knot before augmentation and the right shows after augmentation}
 \label{fig:augmentationS3}
 \end{figure}

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Augmented Links}
 Champanerkar, Kofman and Purcell have studied alternating links in the thickened torus. They define a link in the thickened torus as a quotient of a biperiodic alternating link as follows,

\begin{define}\cite{CKP2} \label{def:biperiodiclink}
 A \emph{biperiodic alternating link} $\mathcal{L}$ is an infinite link which has a projection onto $\R^2$ which is invariant under an action of a two dimensional lattice $\Lambda$ by translations, such that $L=\mathcal{L}/\Lambda$ is an alternating link in $T^2 \times I$, where $I = (-1,1)$, with the projection on $T^2 \times \{0\}$. We call $L$ a link diagram in $T^2 \times I$.   
\end{define}

\begin{remark}
Since $T^2 \times I \cong \Sp^3 - H$, where $H$ is a Hopf link. The complement $T^2 \times I- L = \Sp^3 - (L \cup H)$.
\end{remark}

Champanerkar, Kofman and Purcell \cite{CKP2} extended the definition of prime links in $\Sp^3$ for links in $T^2 \times I$ called weakly prime.

 \begin{define} \label{def:weaklyprime}
A diagram of a link $L$ is weakly prime if whenever a disk is embedded in the diagram surface meets the diagram transversely in exactly two edges, then the disk contains a simple edge of the diagram and no crossings.
\end{define}

\begin{define}
A \emph{twist region} in a link diagram $L=\mathcal{L}/\Lambda$ in $T^2 \times I$, is the quotient of a twist region in the biperiodic link $\mathcal{L}$. %a string of bigons, or a single crossing in the diagram on the universal cover of $T^2 \times I$ is called a . 
A biperiodic link $\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on the plane that intersects $\mathcal{L}$ transversely in four points, with two points adjacent to one crossing and the other two points adjacent to another crossing, the simple closed
curve bounds a subdiagram consisting of a (possibly empty) collection of bigons
strung end to end between these crossings. We say $L$ is \emph{twist-reduced} if it is the quotient of a twist-reduced biperiodic link. 
\end{define}

Now we can define augmentation for a link in $T^2 \times I$ the same way we define augmentation for links in $\Sp^3$. For a link in $T^2 \times I$, the crossing circles are added to the diagram projected onto $T^2 \times \{0\}$. Let $L$ be a twist reduced diagram in $T^2 \times I$, we define {\it augmentation} as a process in which an unknotted circle component is added to one or more twist regions of $L$. See Figure \ref{fig:Augmentations}

 \begin{figure}
 \centering
 \begin{tabular}{cccc}
 \includegraphics [width=3cm]{fig1}&
 \includegraphics  [width=3cm]{twist-augment}&
  \includegraphics [width=3cm]{fig-2}\\
 % \includegraphics [width=3cm]{fal}\\
  A&B&C
  \end{tabular}
 \caption{A: The top right has an odd number of twists while the bottom left has an even number of twists. B: The picture of the link on the right after augmentation twist regions circled in red. C: The link with the twists removed.}
 \label{fig:Augmentations}
 \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Torihedral Decomposition of Augmented Alternating Links in Thickened Torus}

We show a method of decomposing an augmented link in the thickened torus into two isomorphic torihedra. The idea is to combine methods of Menasco \cite{Menasco} and the use of crossing edges between each crossing of our link and Lackenby's ``cut-slice-flatten" method \cite{lackenby} on the augmentation sites.

\begin{define}\cite{CKP2} \label{def:torihedron}
 A \emph{torihedron} is a cone on the torus, i.e. $T^2 \times [0,1]/(T^2 \times \{1\})$, with a cellular graph $G$ on $T^2 \times \{0\}$. An \emph{ideal torihedron} is a torihedron with the vertices of $G$ and the vertex $T^2 \times \{1\}$ removed. Hence, an ideal torihedron is homeomorphic to $T^2 \times [0,1)$ with a finite set of points (ideal vertices) removed from $T^2 \times \{0\}$ 
\end{define}

\begin{prop}\label{thm:torihedraldecomposition}
Let $L$ be an augmented link in $T^2 \times I$. Let $G(L)$ be a diagram of the link on $T^2 \times \{0\}$. There is a decomposition of the complement, $(T^2 \times I) - L$ into two isomorphic ideal torihedra.
\end{prop}

\textit{Proof}. We will begin by assuming that there are no half twists and then arrange the link diagram of $L$ in the following way: first place the added circle components (augmentation) perpendicular to the projection plane, $T^2 \times \{0\}$ leaving the remaining part of the link parallel to the projection plane. 
We now place a crossing edge on each crossing of the link so that for each crossing edge, one end of the edge lies on a bottom strand while the other end lies on a top strand as in Figure \ref{fig:crossingArc} left.

\begin{figure}
 \centering
 \includegraphics[width=4cm]{crossingArc}
  \includegraphics[width=5cm]{crossingPush}
 \caption{Left: The black strands are part of the link and the red strand is the crossing edge. Right: The blue and red edges represent the split crossing edges and the shaded half disk is bounded by the crossing circle}
 \label{fig:crossingArc}
 \end{figure}

\indent We view the link from the point at infinity from the top. We will push the top strand to the bottom strand, splitting the crossing edge into two identical edges as in Figure \ref{fig:crossingArc} right. We push the link components to infinity and stretch the crossing edge so that we have flattened the link onto $T^2 \times \{0\}$ except for the crossing circles which will remain perpendicular to the projection plane.

\indent Now place a disk on each crossing circle, so that the disk bounded by the crossing circle. We can then cut $T^2 \times I$ along $T^2 \times \{0\}$ and focus on the top half, $T^2 \times [0,1)$. We will follow the same method on the bottom half to obtain the second identical torihedron. The disk we place on each crossing circle is now cut in half. This half disk is now bounded by the projection plane and the semi-cricle arc of the crossing circle. We push down on the crossing circle and split the disk into two identical disks. We then push the arc of each crossing circle to infinity, collapsing them to ideal vertices. We obtain two triangular faces which represent the disk which look like a bow-tie as in Figure \ref{fig:falGluings}.

\begin{figure}
 \centering
 \begin{tabular}{cc}
 \includegraphics [width=8cm]{falGluing1}&
 \includegraphics [width=7cm]{falGluing2}\\
 (a)&(b)
 \end{tabular}
 \caption{The first pictures shows gluing without half-twists the second shows gluing with half-twists}
 \label{fig:falGluings}
 \end{figure}

\indent We repeat the steps for the bottom half of $T^2 \times I$, $T^2 \times [-1,0)$. Then we get two isomorphic torihedra. The graph of each will come from crossing edges and, edges of the disk. Now, if there are half twists we will decompose the complement of the link the same way as if there are no half twists and we will identify the two bow-ties as in Figure \ref{fig:falGluings}. Finally we obtain the complement of the link by gluing the two torihedra with the gluing information given by identifying crossing edges and triangles of the bow-tie. We glue the faces of the torihedra which do not correspond to a bow-tie with a $\pi/n$ twist where $n$ is the number of sides of each face as in Figure \ref{fig:top-bottom} clockwise or counterclockwise. \qed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The following figures is an example which decomposes the link (C) of Figure \ref{fig:Augmentations}.
 \begin{figure}[h]
 \centering
 \includegraphics [height=3cm]{fig-3}
 \includegraphics [height=3cm]{fig-4}
 \caption{Each crossing circle bounds a disk}
 \end{figure}

 \vspace*{-0.5cm}
  \begin{figure}[h]
\centering
 \includegraphics [height=3cm]{fig-5}
 \caption{We split the disk and collapse the arc of each crossing circle to ideal vertices}
 \end{figure}

  \vspace*{-0.5cm}
  \begin{figure}[h]
 \centering
 \includegraphics [height=3cm]{fig-6}
 \caption{Left: The crossing arc is the edge in red. Middle: Picture of splitting the crossing edge. Right: The link component is pushed off to infinity.}
 \end{figure}

 \vspace*{-0.5cm}
 \begin{figure}[h]
 \centering
 \includegraphics [height=3cm]{top-bottom}
 \caption{Left: The top torihedron. Right: The bottom torihdron with rotation for face gluing.}
 \label{fig:top-bottom}
 \end{figure}

\begin{remark}\label{cor:triangulation}
The faces of one torihedron which do not correspond to a bow-tie glue to a corresponding face of the second torihedron to form bipyramids. One can add stellating edges, edges which have vertices corresponding to the different components of the Hopf link that cuts through the center of the face to decompose the bipyramids into tetrahedra. This process is called {\it stellation}. Stellating all the bipyramids of the decomposition obtained from Proposition \ref{thm:torihedraldecomposition} we obtained a triangulation of the complement of $L$ which is made up of {\it horizontal} edges (edges from the graph of the torihedra), {\it vertical} edges (edges from coning vertices of the the graph of the torihedra) and stellating edges. 
\end{remark}

{\it Proof.}  Using the decomposition from Proposition \ref{thm:torihedraldecomposition} we can add a stellation edge whose end points are $T^2 \times \{-1\}$ and $T^2 \times \{1\}$ which cut through faces of $T^2 \times I$ which do not come from the augmentation disks like in \cite{CKP2}. Since each face of the top torihedron gets glued to the bottom torihedron, we obtain bipyramids, and the stellation edge will decompose the bipyramids into tetrahedra. Then the link of the vertex  $T^2 \times \{1\}$ or $T^2 \times \{-1\}$ is the graph of the torihedron $T^2 \times [0,1)$ or $T^2 \times (-1,0]$ respectively. \qed

\section{Hyperbolicity of Augmented Links}

We will use angle structures and a result by Casson-Rivin which shows that if one has angled triangulation manifold is hyperbolic.

\begin{define}
angle structure
\end{define}

\begin{theorem}\cite{ANGLE STRUCTURE PAPER}
casson-Rivin theorem
\end{theorem}

For a hyperbolic link $K$ in $T^2 \times I$, we produce sufficient conditions on augmentations such that the resulting link obtained from augmenting $K$ is hyperbolic. The idea is to start with a graph from the torihedral decomposition of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges \cite{CKP}. Then there is corresponding right-angled circle pattern \cite{B-S}. We then consider the augmented link torihedral decomposition from Proposition \ref{} with a corresponding ``degenerate" circle pattern. We then deform this degenerate circle pattern into a ``proper" circle pattern which will give us a polyhedral decomposition with angles of the torihedra in our torihedral decomposition. Which we can further decompose into tetrahedra with angles satisfying conditions of an angle structure.

\begin{define}
An \emph{angled ideal tetrahedron} is an ideal tetrahedron with an assignment of a dihedral angle
to each edge, such that
\begin{itemize}
\item each dihedral angle is between 0 and $\pi$;
\item for each tetrahedron, opposite edges have equal dihedral angles;
\item the three distinct angles sum to $\pi$.
\end{itemize}
\end{define}

\begin{lemma}
Let $P_n$ be an ideal pyramid whose base is an $n$-gon and suppose,
\begin{itemize}
\item each boundary edge of the original base face is assigned a dihedral angle $\alpha_i$ such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$;
\item we are given a decomposition of the base face into triangles by adding new edges. 
\end{itemize}
One gets an obvious corresponding triangulation of $P_n$, where a new face is added for each new edge. Then there is an assignment of a dihedral angle to each edge of each ideal tetrahedron in this triangulation such that
\begin{itemize}
\item each tetrahedron is an angled ideal tetrahedron;
\item the sum of dihedral angles around each new edge is $\pi$;
\item the dihedral angles of the edges of the original base face are the same as before.
\end{itemize} 
\end{lemma}

{\it Proof.} See Figure \ref{TODO}

\begin{define}
We say an augmentation is \emph{right-augmented} when both strands are (locally) oriented such that they cross the augmentation disk in the same direction, the crossing is positive/ a right-handed half-twist. See Figure \ref{TODO}
We say an augmentation is \emph{left-augmented} if it is not right-augmented.
\end{define}

\begin{define}
Given a face $f$ of the original link diagram the \emph{augmentation sequence} of $f$, denoted $\sigma_f$ is a sequence of symbols $0, L, R$ indexed by vertices of $f$ going counter-clockwise, where, for $v \in \partial f$, the $v$-th element is
\[
\sigma_f^v = 
\begin{cases}
0 \text{ if $v$ is not augmented} \\
L \text{ if $v$ is left-augmented} \\
R \text{ if $v$ is right-augmented}
\end{cases}
\]
\end{define}

\begin{theorem}
Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons. Let $L$ be a link obtained from augmenting $K$ such that:
\begin{enumerate}
\item there exist no sequence of augmentations so that a Left augmentation is adjacent to a Right augmentation;
\item the sequence of augmentations does not contain a subsequence $0, L, L, 0$ and $0, R, R, 0$.
\end{enumerate}  
Then $L$ is hyperbolic.
\end{theorem}

{\it Proof.}

\bibliographystyle{plain}
\bibliography{references-ak}

\end{document}

### 2020-09-09 results.tex
main prop for pointwise statement done, next finish up the neighbourhood version.

@@
 \section{Main ?? results}
+
+TODO: make a list of images of vectors, e.g.
+$\Theta_*(\ddd{\vphi_{\vec{e}}}) = -\ddd{\theta_e}$.
 
@@
 
-In other words, for any vector $b = b^e \del_{\theta_e}$
+In other words, for any vector $a = a^e \del_{\theta_e}$
 with sum of coefficients 0, one can vary $c$ so that its
-first order change in $\theta_\bullet$ is $b$,
+first order change in $\theta_\bullet$ is $a$,
 and also remains face non-singular up to first order.
@@
 
-If $f$ is thin, the coefficients sum to 0 so that $\Phi_*(\beta_f) = 0$,
+If $f$ is thin, we actually have that $\alpha_f \in K_c$,
+since the coefficients sum to 0 so that $\Phi_*(\alpha_f) = 0$,
 so we need a different approach. First suppose $f$ shares an edge
@@
 \begin{proof}[Proof of \prpref{p:point_lift}]
-We construct a vector $u_e \in K_c \subseteq T_c \CCC$ for each long edge $e$
-such that if $\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$,
+We construct a vector $u_e \in K_c \subseteq T_c \CCC$ for each edge $e$
+and show that $\{\Theta_*(u_e)\}_{e\in E}$ spans an
+$|E|-1$ dimensional space,
+thus must be equal $L_{\Theta_c}$.
+
+For long edges $e$, $u_e$ will have the following property:
+if $\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$, then
 \begin{itemize}
@@
 \end{itemize}
+Furthermore, these $u_e$'s collectively satisfy the following
+connectivity property:
+consider the graph $G_\llong$ whose vertex set is the set of long edges,
+and we connect two long edges $e,e'$ by an edge if there is some $e"$ such that
+$a^e, a^{e'}$ are both nonzero in $\Theta_*(u_{e"})$;
+then $G_\llong$ is connected.
 
-First suppose that $e$ is between two convex faces $f, f'$
+In addition, for short edges $e$,
+$u_e$ have the following property: again writing
+$\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$,
+one has
+\begin{itemize}
+	\item $a^e = 1$;
+	\item $a^{e'} = 0$ for other short edges $e'$.
+\end{itemize}
+
+Let us first suppose we have constructed such $u_e$,
+and show that these properties ensure that
+$\{\Theta_*(u_e)\}_{e\in E}$ spans an $|E|-1$ dimensional space.
+This is a simple exercise in linear algebra,
+but we show it for completeness.
+
+Put the $\Theta_*(u_e)$'s into a $E \times E$ matrix,
+denoted $M$,
+so that the $e$-th row corresponds to $u_e$.
+By virtue of $u_e \in K_c$, we have that $(1\; 1\; \cdots \; 1)^T$
+is in the null space of $M$;
+our goal is to show that it spans the null space.
+
+Suppose $b = (b_e)^T$ is in the null space of $M$.
+Reorder $E$, if necessary, so that long edges come before
+short edges.
+Then by the last property of $u_e$'s for long edges,
+the top right block of long-by-short entries are 0.
+Thus the vector $b_\llong := (b_e)_{e \in \llong}^T$ is in the null space
+of the submatrix $M_\llong$ of long-by-long entries.
+
+Let $|b_e|$ be the largest among components of $b_\llong$;
+rescale $b$ so that $b_e = 1$.
+The $e$-th component of $M_\llong b_\llong$
+is $1 - \sum a^{e'} b_{e'}$.
+Since $\sum a^{e'} = 1$, this can 0 if and only if
+for all $e'$ with $a^{e'} < 0$, we have exactly $b_{e'} = 1$.
+By connectedness of $G_\llong$, this implies
+$b_\llong = (1 \; \cdots \; 1)^T$.
+
+Returning to the full $M$, it is now easy to see that
+for a short edge $e$,
+by looking at the $e$-th row of $M$,
+we have $b_e = \sum a^{e'} = 1$,
+so we are done.
+
+%\footnote{
+%This is a well-known argument/result about graph Laplacians:
+%the first two properties of $u_e$'s ensure that
+%$-M_\llong^T$ is essentially a graph Laplacian for $G_\llong$,
+%so has rank = (\#vertices) - (\#components).}
+
+Now we construct the $u_e$'s.
+First suppose that $e$ is a long edge between two convex faces $f, f'$
 (so $\vec{e} \in \del f, \cev{e} \in \del f'$).
@@
 \label{e:u_e}
-u_e = (d\theta_e(w_e))^\inv \cdot w_e
+u_e := (d\theta_e(w_e))^\inv \cdot w_e
 \end{equation}
@@
 In general, we consider a thick path of faces $f_0, \ldots, f_n$,
-such that all faces except $f_0$ and $f_n$ are thin.
+such that all faces except $f_0$ and $f_n$ are thin,
+and $f_i$ are distinct except possibly $f_0 = f_n$.
+\footnote{Picture a slinky linking two rocks.}
+Let $e_i$ be the long edge between $f_i$ and $f_{i+1}$,
+and orient so that $\vec{e_i} \in \del f_i$, $\cev{e_i} \in \del f_{i+1}$.
 
+We will construct $u_{e_i}$ for $i = 1,\ldots,n$.
+
+We want to increase the lengths of $e_i$'s all together.
+Let $E' = \{\vec{e_i}, \cev{e_i} | i=1,\ldots, n\}$.
+Consider
+\[
+x :=
+\sum_{i=0,\ldots,n-1} \alpha_{e_i}
+=
+\sum_{\vec{e} \in E'}
+\frac{1}{2 r_{f_{\vec{e}}} \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
+%\sum_{\substack{i = 0,\ldots, n-1 \\ \vec{e} = \vec{e_i}, \cev{e_i} }}
+%\frac{1}{2 r_{f_0} \cos \vphi_{\vec{e_0}}} \ddd{\vphi_{\vec{e_0}}}
+%+
+%\frac{1}{2 r_{f_n} \cos \vphi_{\cev{e_{n-1}}}} \ddd{\vphi_{\cev{e_{n-1}}}}
+%+
+\]
+with $\alpha_e$ from \eqnref{e:alpha_e}.
+It is clear that $x$ increases all oriented $e_i$ lengths
+$l_{\vec{e}}$ equally fast,
+i.e. $dl_{\vec{e_i}}(x) = dl_{\cev{e_i}}(x) = 1$ for all $i$,
+so $x\in T_c \CCC$.
+It is also clear that for the thin faces $f_i$,
+$x$ makes one of the angles $\vphi_{\cev{e_{i-1}}}, \vphi_{\vec{e_i}}$
+increase and makes the other decrease, both at the same rate,
+thus $d\Phi_{f_i}(x) = 0$.
+
+The vector $x$ increase $\Phi_{f_0}$ and $\Phi_{f_n}$, so it is compensated
+using $\beta_f$'s, so that
+\[
+y := x - \frac{1}{r_{f_0} \cos \vphi_{\vec{e_0}}} \beta_{f_0}
+- \frac{1}{r_{f_n} \cos \vphi_{\cev{e_{n-1}}}} \beta_{f_n}
+\in K_c
+\]
+Before we modify $y$ to give the desired $u_{e_i}$,
+we note that for $\vec{e} \in (\cup \del f_i) \backslash E'$,
+the coefficient of $\ddd{\vphi_{\vec{e}}}$ in $y$ is non-positive,
+and is 0 if and only if $e$ is short;
+so $\Theta_*(y)$ satisfies two of the three properties
+desired in $u_e$.
+
+Recall that for thin face $f$,
+$\alpha_f$ from \eqnref{e:alpha_f} is in $K_c$,
+and we have
+\[
+\Theta_*(\frac{r_{f_i}}{\tan \vphi_{\vec{e_i}}} \alpha_{f_i}) = 
+	\ddd{\theta_{e_i}} - \ddd{\theta_{e_{i-1}}}
+\]
+Write $\bar{\alpha}_{f_i} = \frac{r_{f_i}}{\tan \vphi_{\vec{e_i}}} \alpha_{f_i}$.
+Then it is easy to see that using $\bar{\alpha}_{f_i}$'s, we can
+push the coefficients of $\ddd{\theta_{e_i}}$'s in $\Theta_*(y)$ around
+so only one is nonzero.
+More precisely, if
+$\Theta_*(y) = \sum_e y^e \ddd{\theta_e}$, the image under $\Theta_*$
+of the vector
+\[
+\bar{u}_{e_0} := y - y^{e_{n-1}} \bar{\alpha}_{f_{n-1}}
+- (y^{e_{n-2}} + y^{e_{n-1}}) \bar{\alpha}_{f_{n-2}}
+- \ldots
+\]
+would have $\ddd{\theta_{e_i}}$ coefficients 0 for all $i$ except 0.
+Finally, we can take
+\[
+u_{e_0} := (d\theta_{e_0}(\bar{u}_{e_0}))^\inv \cdot \bar{u}_{e_0};
+\;\;\;
+u_{e_i} = u_{e_{i-1}} + \bar{\alpha}_{f_i}
+\]
+
+We still need to show the collective connectivity property of the $u_e$'s.
+It is easy to see that the long edges of a convex face
+are connected in $G_\llong$
+(for example, $u_{e_0}$ defined above clearly does it for
+$f_0$).
+Furthermore, all the $\Theta_*(u_{e_i})$ share most of the same coefficients,
+so $e_i$ are in the same connected component of $G_\llong$.
+Thus connectivity of $G_\llong$ follows from the
+thick-path-connectivity of faces.
+
+Finally, for short edges $e$, we simply define $u_e$
+as in \eqnref{e:u_e}
+(here we do not worry about whether faces are thin or convex,
+as there is no non-positivity condition of $a^{e'}$ is absent).
 \end{proof}
@@
 Let $c\in \CCC$ be as in \prpref{p:point_lift}.
-TODO full lifting statement.
+Given a path $\gamma: [0,\veps] \to \TTT$
+starting at $\gamma(0) = \Theta(c)$
+and has constant value $(\sum \theta_e) \circ \gamma$,
+there exists a lift $\tilde{\gamma} :[0, \veps] \to \CCC$
+that starts at $\tilde{\gamma}(0) = c$
+and has constant value $\Phi \circ \tilde{\gamma}$.
 \end{proposition}
 
+\begin{proof}
+TODO.
+\end{proof}
+
 %===============================================================================

### 2020-09-12 draft1.tex
circle pattern to polyhedral decomp

@@
 \usepackage{amsfonts, amstext, amsmath, amsthm, amscd, amssymb, upgreek}
+\usepackage{bbm}
 \usepackage{graphicx, color,  subfigure, wrapfig, overpic}
@@
 \usepackage{tikz}
+%\usepackage{mystyle}
 
@@
 \def\co{\colon\thinspace}
+
+\newcommand{\torus}{{\mathbb{T}^2}}
+
+\newcommand{\RRR}{{\underline{\mathfrak{R}}}}
+\newcommand{\QQQ}{{\underline{\mathfrak{Q}}}}
+\newcommand{\CCC}{{\underline{\mathfrak{C}}}}
+\newcommand{\PPP}{{\underline{\mathbf{\Phi}}}}
+\newcommand{\TTT}{{\underline{\mathbf{\Theta}}}}
+\newcommand{\LLL}{{\underline{\mathfrak{L}}}}
+
+\newcommand{\cev}[1]{\overset{\leftarrow}{#1}}
+
+\newcommand{\del}{\partial}
+\newcommand{\ddd}[1]{{\frac{\del}{\del #1}}}
+\newcommand{\vphi}{\varphi}
+\newcommand{\llong}{{\text{long}}}
+\newcommand{\Span}{{\text{span}}}
+\newcommand{\Pol}{{\text{Pol}}}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{From Extended Circle Patterns to polyhedra}
+
+In this section, we describe how to obtain a
+decomposition of a torihedron
+into hyperbolic ideal pyramids
+from a non-singular extended circle pattern.
+
+\begin{lemma}
+Suppose we have the graph of a torihedron.
+Given a non-singular extended circle pattern $c \in \CCC$ on the graph,
+there exists a decomposition of the torihedron
+into base-angled ideal pyramids (TODO make sure it's been defined) so that
+	\begin{itemize}
+		\item each interior edge of the torihedron has dihedral angles sum to $2\pi$;
+		\item each boundary edge $e$ of the torihedron has dihedral angles sum to
+			$\pi - \theta_e$.
+	\end{itemize}
+\end{lemma}
+
+\begin{proof}
+For each directed edge $\vec{e} \in \vec{E}$,
+construct the isosceles triangle $T_{\vec{e}}$
+with equal sides of length $r_{f_{\vec{e}}}$ and
+angle $2\tilde{\vphi_{\vec{e}}}$ subtended between them,
+where $\tilde{\vphi_{\vec{e}}} = \vphi_{\vec{e}}$
+if $\vphi_{\vec{e}}$ if it is acute,
+and = $\pi - \vphi_{\vec{e}}$ otherwise.
+(TODO draw figure?)
+
+Let $f \in F$ be a face.
+If $\vphi_{\vec{e}} \leq \pi/2$ for all $\vec{e} \in \del f$,
+i.e. if $f$ is convex, then 
+the $T_{\vec{e}}$ for $\vec{e}\in \del f$
+fit together into a Euclidean polygon $\Pol_f$.
+If not, suppose $\vphi_{\vec{e}} > \pi/2$
+for $\vec{e} = \vec{e_1}$, 
+and $\leq \pi/2$ for $\vec{e} = \vec{e_2},\ldots \vec{e_k} \in \del f$.
+Then put $T_{\vec{e_2}},\ldots,T_{\vec{e_k}}$ together as above,
+creating a $(k+1)$-gon,
+then subtract $T_{\vec{e_1}}$ from it.
+
+Thus, to each face, we associate $\Pol_f$.
+View the Euclidean plane as the boundary of the upper-half space.
+Then $\Pol_f$ subtends an ideal hyperbolic pyramid $P_f$.
+
+Clearly, these $P_f$'s, as abstract ideal tetrahedra,
+glue together into the torihedron (TODO rephrase).
+%The hyperbolic structure on $P_f$
+%in particular provide dihedral angles to each edge of $P_f$
+%which clearly satisfies the conditions of making $P_f$
+%a base-angled ideal pyramid.
+We need to check that the angles around each edge of
+the torihedron have the appropriate angles.
+For an interior edge, i.e. an edge that dooes not meet the boundary,
+
+have dihedral angles that sum to $2\pi$,
+and boundary angle
+and it is easy to see
+These $P_f$'s clearly glue tog
+
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Hyperbolicity of Augmented Links}
-
-We will use angle structures and a result by Casson-Rivin which shows that if one has angled triangulation manifold is hyperbolic.
+Thurston introduced a method for finding the unique hyperbolic metric for a given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}.
+The idea was to triangulate the interior of $M$ into ideal tetrahedra and give those tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently in $M$.
+The shape parameter of a tetrahedron is described by the cross-ratio of its four vertices on the sphere at infinity.
+Thurston had written down a system of gluing equations with shape parameters whose solutions correspond to the complete hyperbolic metric on the interior of $M$.
+Casson and Rivin separated gluing equations into a linear and non-linear part \cite{Casson-Rivin}.
+Angle structures is the linear part of Thurston's gluing equations, and what we will use to attain hyperbolicity of complements of augmented links in the thickened torus.
 
 \begin{define}
-angle structure
+Let $M$ be an orientable 3–manifold with boundary consisting of tori.
+An angle structure on an ideal triangulation $\tau$ is an assignment of an (internal) dihedral angle to each edge of each tetrahedron, such that opposite
+edges carry the same dihedral angle, and such that
+\begin{itemize}
+\item all angles lie in the range $(0,\pi)$,
+\item around each ideal vertex of a tetrahedron, the dihedral angles sum to $\pi$
+\item around each edge of $M$, the dihedral angles sum to $2\pi$.
+\end{itemize}
 \end{define}
 
-\begin{theorem}\cite{ANGLE STRUCTURE PAPER}
-casson-Rivin theorem
+\begin{theorem}\cite{Casson-Rivin}\label{thm:Casson-Rivin}
+Let $M$ be a 3-manifold admitting an angle structure. Then $M$ is hyperbolic.
 \end{theorem}
@@
 For a hyperbolic link $K$ in $T^2 \times I$, we produce sufficient conditions on augmentations such that the resulting link obtained from augmenting $K$ is hyperbolic.
-The idea is to start with a graph from the torihedral decomposition of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges \cite{CKP}.
-Then there is corresponding right-angled circle pattern \cite{B-S}.
-We then consider the augmented link torihedral decomposition from Proposition \ref{} with a corresponding ``degenerate" circle pattern.
-We then deform this degenerate circle pattern into a ``proper" circle pattern which will give us a polyhedral decomposition with angles of the torihedra in our torihedral decomposition.
+The idea is to start with a graph from the torihedral decomposition of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges \cite{CKP2}.
+Then by results of \cite{BandS} there exist a corresponding right-angled circle pattern.
+We then consider the augmented link $L$ and its torihedral decomposition from Proposition \ref{thm:torihedraldecomposition} with a corresponding ``degenerate" circle pattern.
+We deform this degenerate circle pattern into a ``proper" circle pattern which will give us a polyhedral decomposition of $(T^2 \times I)-L$ with angles of the torihedra in our torihedral decomposition.
 Which we can further decompose into tetrahedra with angles satisfying conditions of an angle structure.
@@
 
+\begin{define}
+A \emph{base-angled ideal pyramid}
+is a pyramid whose base is an $n$-gon, $n \geq 3$,
+and each boundary edge $e_i$ of the base face is assigned a dihedral angle $\alpha_i$
+such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$.
+The vertical edge $e_i'$ that meets $e_i$ and $e_{i+1}$
+is automatically assigned the dihedral angle $\pi - \alpha_i - \alpha_{i+1}$.
+\end{define}
+
+Clearly, the dihedral angles of an ideal hyperbolic pyramid
+make it a base-angled ideal pyramid.
+(TODO probably vice-versa?)
+
 \begin{lemma}
-Let $P_n$ be an ideal pyramid whose base is an $n$-gon and suppose,
-\begin{itemize}
-\item each boundary edge of the original base face is assigned a dihedral angle $\alpha_i$ such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$;
-\item we are given a decomposition of the base face into triangles by adding new edges. 
-\end{itemize}
+%Let $P_n$ be an ideal pyramid whose base is an $n$-gon and suppose,
+%\begin{itemize}
+%\item each boundary edge of the base face is assigned a dihedral angle $\alpha_i$ such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$;
+%\item we are given a decomposition of the base face into triangles by adding new edges. 
+%\end{itemize}
+Let $P_n$ be a base-angled ideal pyramid,
+and suppose we are given a decomposition of the base face into triangles by adding new edges. 
 One gets an obvious corresponding triangulation of $P_n$, where a new face is added for each new edge.
@@
 \begin{define}
-We say an augmentation is \emph{right-augmented} when both strands are (locally) oriented such that they cross the augmentation disk in the same direction, the crossing is positive/ a right-handed half-twist.
+We say an augmentation is \emph{right-augmented} when both strands are (locally) oriented such that they cross the augmentation disk in the same direction, the crossing is positive/a right-handed half-twist.
 See Figure \ref{TODO}
@@
 \begin{theorem}
-Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons. Let $L$ be a link obtained from augmenting $K$ such that:
-\begin{enumerate}
-\item there exist no sequence of augmentations so that a Left augmentation is adjacent to a Right augmentation;
-\item the sequence of augmentations does not contain a subsequence $0, L, L, 0$ and $0, R, R, 0$.
-\end{enumerate}  
+Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons.
+Let $L$ be a link obtained from augmenting $K$ such that there exist no sequence of augmentations where a Left augmentation is adjacent to a Right augmentation.
 Then $L$ is hyperbolic.
@@
 
+Part 1:
+
+by ckp the original link can be decomposed into torihedra with projection graph as torihedra graph with pi/2 edges and this gives circle pattern by bobenko-springborn
+
+Part 2: Our torihedral decomposition has graph and on augmentation we will give 0 and pi angles. Next we add another edge and give blah angle (we have three cases)
+do three cases with pictures
+
+part 3: Use proposition to get circle pattern to get polyhedral decomposition of the link
+
+part 4: get triangulation.
+
 \bibliographystyle{plain}

### 2020-09-12 notation.tex
more stuff.

@@
 \CCC = \{l_{\vec{e}} = l_{\cev{e}} \} \ar[r,symbol=\subseteq]
-	& \RRR \times \QQQ \ar[r] \ar[d]
+	& \RRR \times \QQQ \ar[r, "\Theta"] \ar[d, "\Phi"]
 	&\TTT \\
@@
 
-[Check this] The usual notion of circle pattern would be restricted to those $c\in \CCC$
+[TODO Check this] The usual notion of circle pattern would be restricted to those $c\in \CCC$
 with $\vphi_{\vec{e}} \in (0,\pi)$ and $\theta_e \in (0,\pi)$.
@@
 is a bit more complex, as the final shape of $Q_e$ (the quadrangle associated to $e$)
-depends also on $\vphi_{\vec{e}}$ (which equals $\pi - \vphi_{\cev{e}}$ in the limit.
+may depend on $\vphi_{\vec{e}}$ or $\vphi_{\cev{e}}$.
 If we parametrize circle patterns by $(r_f)$ and $(\theta_e)$ as in TODO \ocite{BS},
-the limiting shape would depend on how $r_f$ approaches $r_{f'}$,
-some sort of blow up stuff TODO.
+the limiting shape would depend on the relationship between 
+$r_f$ and $r_{f'}$.
+As our main result depends on extending \ocite{BS} result
+to such limits and beyond,
+we find it more convenient to describe extended circle patterns by
+$(r_f)$ and $(\vphi_{\vec{e}})$.
 
-We will mostly be working with extended circle patterns that mostly ``look normal",
-with all $\vphi_{\vec{e}}$ in some range $(-\veps, \pi + \veps)$.
+We will mostly be working with extended circle patterns that ``looks normal",
+with all $\vphi_{\vec{e}}$ in the range $[0,\pi)$,
+so we do not dwell on the meaning of negative $\vphi_{\vec{e}}$'s.
+\footnote{
+Intuitively, one can visualize decreasing $\vphi_{\vec{e}}$
+from $\veps$ to $-\veps$
+as moving the black vertices of the quadrangle $Q_e$ past each other,
+thus flipping $Q_e$ along its long axis
+and making it have negative area.
+}
 
@@
 
-non-degenerate circle pattern?
+TODO non-degenerate circle pattern?
 
@@
 
-\begin{definition}
-A \emph{slit-convex circle pattern} is an extended cirlce pattern
-$c \in \CCC$ such that all its faces are either convex or thin.
-\end{definition}
+%\begin{definition}
+%A \emph{slit-convex circle pattern} is an extended cirlce pattern
+%$c \in \CCC$ such that all its faces are either convex or thin.
+%\end{definition}
 
 \begin{lemma}
-$\CCC$ is a manifold near slit-convex circle patterns.
+Let $c$ be an extended circle pattern whose faces are either
+convex or thin.
+Then $\CCC$ is a manifold in a neighborhood of $c$.
 \end{lemma}
@@
 and since having only convex of thin faces implies
-$\cos \vphi_{\vec{e}} \neq 0$,
-we see the differentials are linearly independent at
-a slit-convex circle pattern $c$.
+$\cos \vphi_{\vec{e}} \neq 0$ for all $\vec{e}$,
+we see that the differentials $d(l_{\vec{e}} - l_{\cev{e}})$
+are linearly independent at $c$,
+hence are linearly independent in a neighborhood of $c$.
+Thus, by the implicit function theorem,
+$\CCC$ is a manifold in a neighborhood of $c$.
 \end{proof}

### 2020-09-12 results.tex

@@
 To that end, let $L$ be the $(|E|-1)$-plane distribution on $\TTT$
-tangent to the level sets of $\sum \theta_v$.
+tangent to the level sets of $\sum_{e\in E} \theta_e$.
 The following proposition proves it (avoid using `it'?) up to first order at a point:
@@
 
-In other words, for any vector $a = a^e \del_{\theta_e}$
-with sum of coefficients 0, one can vary $c$ so that its
+In other words, for any vector $a \in T_{\Theta(c)} \TTT$
+with sum of components 0, one can vary $c$ so that its
 first order change in $\theta_\bullet$ is $a$,
@@
 
-Before we prove this, it is convenient to first prove the following:
+Before we prove this, it is convenient to first prove the following,
+which will establish some useful notation:
 
 \begin{lemma}
+\label{l:Phi_full}
 Let $c \in \CCC$ be as in \prpref{p:point_lift}.
@@
 Its pushforward under $\Phi$ is simply
-$\Phi_*(\beta_f) = \frac{1}{r_f} \sum_{\vec{e}\in \del f} \tan \vphi_{\vec{e}}
+$\Phi_*(\alpha_f) =
+	(-\frac{2}{r_f} \sum_{\vec{e}\in \del f} \tan \vphi_{\vec{e}})
 	\ddd{\Phi_f}$.
@@
 If $f$ is a convex face, then the $\tan \vphi_{\vec{e}}$ are all non-negative,
-being 0 if and only if $e$ is short.
-so $\Phi_*(\alpha_f)$ is a negative multiple of $\ddd{\Phi_f}$;
+being 0 if and only if $e$ is short,
+and because $\Phi_f = 2\pi$, atleast three edges are long.
+So $\Phi_*(\alpha_f)$ is a negative multiple of $\ddd{\Phi_f}$;
 we choose $\beta$ so that
@@
 If $f$ is thin, we actually have that $\alpha_f \in K_c$,
-since the coefficients sum to 0 so that $\Phi_*(\alpha_f) = 0$,
-so we need a different approach. First suppose $f$ shares an edge
-$e$ with a convex face $f'$. We can increase $l_e$
-by increasing $\vphi_{\vec{e}},\vphi_{\cev{e}}$
+since the components sum to 0, so we need a different approach.
+First suppose $f$ shares an edge $e$ with a convex face $f'$,
+with $\vec{e} \in \del f$.
+We can increase $l_e$
+by varying $\vphi_{\vec{e}},\vphi_{\cev{e}}$
 while holding $r_f,r_{f'}$ constant.
@@
 \end{equation}
+which increases $l_{\vec{e}}, l_{\cev{e}}$ at half unit speed,
+$dl_{\vec{e}}(\alpha_e) = dl_{\cev{e}}(\alpha_e) = 1/2$.
 Then we can take
@@
 \end{equation}
-which increases $l_{\vec{e}}, l_{\cev{e}}$ at unit speed,
-$dl_{\vec{e}}(\alpha_e) = dl_{\cev{e}}(\alpha_e) = 1$.
 We can repeat this procedure with $f'$ set to this thin face,
@@
 	\item $a^{e'} = 0$ for short edges $e'$.
+	\item $\sum_{e' \in E} a^{e'} = 0$ (follows directly from $u_e \in K_c$)
 \end{itemize}
@@
 	\item $a^{e'} = 0$ for other short edges $e'$.
+	\item $\sum_{e' \in E} a^{e'} = 0$ (follows directly from $u_e \in K_c$)
 \end{itemize}
@@
 The $e$-th component of $M_\llong b_\llong$
-is $1 - \sum a^{e'} b_{e'}$.
-Since $\sum a^{e'} = 1$, this can 0 if and only if
+is $1 - \sum_{e' \neq e} a^{e'} b_{e'}$,
+where $a^{e'}$ are the components of $\Theta_*(u_e)$.
+Since $\sum_{e' \neq e} |a^{e'}| = 1$, this can be 0 if and only if
 for all $e'$ with $a^{e'} < 0$, we have exactly $b_{e'} = 1$.
@@
 and $f_i$ are distinct except possibly $f_0 = f_n$.
-\footnote{Picture a slinky linking two rocks.}
+\footnote{Picture a closed accordian.}
 Let $e_i$ be the long edge between $f_i$ and $f_{i+1}$,
@@
 We want to increase the lengths of $e_i$'s all together.
-Let $E' = \{\vec{e_i}, \cev{e_i} | i=1,\ldots, n\}$.
+Let $E' = \{\vec{e_i}, \cev{e_i} | i=0,1,\ldots,n-1\}$.
 Consider
@@
 $l_{\vec{e}}$ equally fast,
-i.e. $dl_{\vec{e_i}}(x) = dl_{\cev{e_i}}(x) = 1$ for all $i$,
+i.e. $dl_{\vec{e_i}}(x) = dl_{\cev{e_i}}(x) = 1/2$ for all $i$,
 so $x\in T_c \CCC$.
@@
 $x$ makes one of the angles $\vphi_{\cev{e_{i-1}}}, \vphi_{\vec{e_i}}$
-increase and makes the other decrease, both at the same rate,
+increase and the other decrease, both at the same rate,
 thus $d\Phi_{f_i}(x) = 0$.
-
-The vector $x$ increase $\Phi_{f_0}$ and $\Phi_{f_n}$, so it is compensated
-using $\beta_f$'s, so that
+However, the vector $x$ increase $\Phi_{f_0}$ and $\Phi_{f_n}$,
+so it is compensated using $\beta_f$'s, so that
 \[
@@
 we note that for $\vec{e} \in (\cup \del f_i) \backslash E'$,
-the coefficient of $\ddd{\vphi_{\vec{e}}}$ in $y$ is non-positive,
+the $\vphi_{\vec{e}}$-component in $y$ is non-positive,
 and is 0 if and only if $e$ is short;
-so $\Theta_*(y)$ satisfies two of the three properties
-desired in $u_e$.
+so $\Theta_*(-y)$ already satisfies three of the four properties
+desired in $\Theta_*(u_e)$.
 
@@
 Then it is easy to see that using $\bar{\alpha}_{f_i}$'s, we can
-push the coefficients of $\ddd{\theta_{e_i}}$'s in $\Theta_*(y)$ around
+``push around" the $\theta_{e_i}$-components in $\Theta_*(y)$
 so only one is nonzero.
@@
 - \ldots
+- (y^{e_1} + \ldots + y^{e_{n-1}}) \bar{\alpha}_{f_1}
 \]
-would have $\ddd{\theta_{e_i}}$ coefficients 0 for all $i$ except 0.
-Finally, we can take
+would have $\theta_{e_i}$-components 0 for all $i$ except 0;
+for $i=0$, the $\theta_{e_0}$-component is now $y^{e_0} + \ldots + y^{e_{n-1}}$,
+which is nonzero because $\sum_{e'\in E} y^{e'} = 0$
+and $\sum_{e' \in E \backslash E'} y^{e'} > 0$.
+Therefore, we can take
 \[
@@
 $f_0$).
-Furthermore, all the $\Theta_*(u_{e_i})$ share most of the same coefficients,
+Furthermore, all the $\Theta_*(u_{e_i})$ have most components equal,
 so $e_i$ are in the same connected component of $G_\llong$.
@@
 (here we do not worry about whether faces are thin or convex,
-as there is no non-positivity condition of $a^{e'}$ is absent).
+as the non-positivity condition of $a^{e'}$ is absent).
 \end{proof}
@@
 \begin{proposition}
+\label{p:nghd_lift}
 Let $c\in \CCC$ be as in \prpref{p:point_lift}.
-Given a path $\gamma: [0,\veps] \to \TTT$
+Given a smooth path $\gamma: [0,\infty) \to \TTT$
 starting at $\gamma(0) = \Theta(c)$
 and has constant value $(\sum \theta_e) \circ \gamma$,
-there exists a lift $\tilde{\gamma} :[0, \veps] \to \CCC$
+there exists $\veps > 0$ and a lift $\tilde{\gamma} :[0, \veps] \to \CCC$
+of $\gamma|_{[0,\veps]}$ along $\Theta$
 that starts at $\tilde{\gamma}(0) = c$
@@
 \begin{proof}
-TODO.
+By \lemref{l:Phi_full}, $\Phi$ is a submersion at $c$,
+hence is a submersion in a neighborhood $U \in \CCC$ of $c$.
+Thus, the kernels
+$K_{c'} = \ker(\Phi_*|{c'} : T_{c'} \CCC \to T_{\Phi(c')} \PPP)$
+form an $|E|$-plane distribution $K \subset T\CCC|_U$ over $U$.
+By \prpref{p:point_lift}, the bundle map
+$\Theta_*|_K : K \to L$ is full rank at $c$,
+hence it is full in a possibly smaller neighborhood,
+which we redefine $U$ to be.
+
+Since $\sum_{e \in E} \theta_e = 2\pi |E| - \sum_{f\in F} \Phi_f$,
+the fullness of $\Phi_*$ also shows that
+$\sum \theta$ has no critical points in $U$;
+for $s$ in some small interval around $(\sum \theta)(c)$,
+denote, by overloading notation,
+$L_s = (\sum \theta)^\inv (s)$,
+$U_s = U \cap \Theta^\inv(L_s)$.
+We may consider $K$ as a family of $|E|$-plane distributions
+$K_s$ over $U_s$.
+
+The vector $\rho := \sum_{f\in F} r_f \ddd{r_f}$ corresponds to
+scaling all radii by the same factor, and is clearly in $T\CCC$.
+It is obviously mapped to zero under $\Phi_*$ and $\Theta_*$,
+so $\Span\{\rho\} = \ker(\Theta_*|_K) \subset K$.
+Thus, over $U$, we may split
+$K = \Span\{\rho\} \oplus K'$
+(say as orthogonal decomposition w.r.t. some smooth metric on $\CCC$),
+so that $\Theta_*|{c'} : K'|_{c'} \simeq L_{\Theta(c')}$.
+
+In other words, $K'|_{U_s}$ is a horizontal $(|E|-1)$-plane distribution
+that determines an Ehresmann connection of the
+fibre bundle $U_s \to L_s$ (after being appropriately restricted).
+Therefore, a short path $\gamma$ starting at $\Theta(c)$
+with constant $\sum \theta$, i.e. a path in $L_s$, $s ={(\sum \theta)(c)}$,
+can be lifted to a path $\tilde{\gamma}$ in $U_s$,
+so that $\tilde{\gamma}$ is always tangent to $K'$,
+hence $\Phi(\tilde{\gamma})$ is constant.
 \end{proof}
@@
 %===============================================================================
+
+TODO
+Note: no face can have its edges glued together; prevented by fact
+of alternating links

### 2020-09-12 draft1.tex
finish that proof of circle pattern to polyhedra

@@
 \usepackage{graphicx, color,  subfigure, wrapfig, overpic}
-\usepackage[all,cmtip]{xy} 
+%\usepackage[all,cmtip]{xy} 
 \usepackage{tikz}
@@
 
-\indent We repeat the steps for the bottom half of $T^2 \times I$, $T^2 \times [-1,0)$.
-Then we get two isomorphic torihedra.
-The graph of each will come from crossing edges and, edges of the disk.
-Now, if there are half twists we will decompose the complement of the link the same way as if there are no half twists and we will identify the two bow-ties as in Figure \ref{fig:falGluings}.
-Finally we obtain the complement of the link by gluing the two torihedra with the gluing information given by identifying crossing edges and triangles of the bow-tie.
-We glue the faces of the torihedra which do not correspond to a bow-tie with a $\pi/n$ twist where $n$ is the number of sides of each face as in Figure \ref{fig:top-bottom} clockwise or counterclockwise.
-\qed
+\indent We repeat the steps for the bottom half of $T^2 \times I$, $T^2 \times
+[-1,0)$. Then we get two isomorphic torihedra. The graph of each will come from
+crossing edges and, edges of the disk. Now, if there are half twists we will
+decompose the complement of the link the same way as if there are no half twists
+and we will identify the two bow-ties as in Figure \ref{fig:falGluings}. Finally
+we obtain the complement of the link by gluing the two torihedra with the gluing
+information given by identifying crossing edges and triangles of the bow-tie. We
+glue the faces of the torihedra which do not correspond to a bow-tie with a
+$\pi/n$ twist where $n$ is the number of sides of each face as in Figure
+\ref{fig:top-bottom} clockwise or counterclockwise. \qed
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The following figures is an example which decomposes the link (C) of Figure \ref{fig:Augmentations}.
- \begin{figure}[h]
- \centering
- \includegraphics [height=3cm]{fig-3}
- \includegraphics [height=3cm]{fig-4}
- \caption{Each crossing circle bounds a disk}
- \end{figure}
+The following figures is an example which decomposes the link (C) of Figure
+\ref{fig:Augmentations}.  \begin{figure}[h] \centering \includegraphics
+[height=3cm]{fig-3} \includegraphics [height=3cm]{fig-4} \caption{Each crossing
+circle bounds a disk} \end{figure}
 
- \vspace*{-0.5cm}
-  \begin{figure}[h]
-\centering
- \includegraphics [height=3cm]{fig-5}
- \caption{We split the disk and collapse the arc of each crossing circle to ideal vertices}
- \end{figure}
+ \vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
+ [height=3cm]{fig-5} \caption{We split the disk and collapse the arc of each
+ crossing circle to ideal vertices} \end{figure}
 
-  \vspace*{-0.5cm}
-  \begin{figure}[h]
- \centering
- \includegraphics [height=3cm]{fig-6}
- \caption{Left: The crossing arc is the edge in red. Middle: Picture of splitting the crossing edge. Right: The link component is pushed off to infinity.}
- \end{figure}
+	\vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
+	[height=3cm]{fig-6} \caption{Left: The crossing arc is the edge in red.
+	Middle: Picture of splitting the crossing edge. Right: The link component is
+	pushed off to infinity.} \end{figure}
 
- \vspace*{-0.5cm}
- \begin{figure}[h]
- \centering
- \includegraphics [height=3cm]{top-bottom}
- \caption{Left: The top torihedron. Right: The bottom torihdron with rotation for face gluing.}
- \label{fig:top-bottom}
- \end{figure}
+ \vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
+ [height=3cm]{top-bottom} \caption{
+	Left: The top torihedron.
+	Right: The bottom torihdron with rotation for face gluing.} \label{fig:top-bottom} \end{figure}
 
 \begin{remark}\label{cor:triangulation}
-The faces of one torihedron which do not correspond to a bow-tie glue to a corresponding face of the second torihedron to form bipyramids.
-One can add stellating edges, edges which have vertices corresponding to the different components of the Hopf link that cuts through the center of the face to decompose the bipyramids into tetrahedra.
-This process is called {\it stellation}.
-Stellating all the bipyramids of the decomposition obtained from Proposition \ref{thm:torihedraldecomposition} we obtained a triangulation of the complement of $L$ which is made up of {\it horizontal} edges (edges from the graph of the torihedra), {\it vertical} edges (edges from coning vertices of the the graph of the torihedra) and stellating edges.
-\end{remark}
+The faces of one torihedron which do not correspond to a bow-tie glue to a
+corresponding face of the second torihedron to form bipyramids. One can add
+stellating edges, edges which have vertices corresponding to the different
+components of the Hopf link that cuts through the center of the face to
+decompose the bipyramids into tetrahedra. This process is called {\it
+stellation}. Stellating all the bipyramids of the decomposition obtained from
+Proposition \ref{thm:torihedraldecomposition} we obtained a triangulation of the
+complement of $L$ which is made up of {\it horizontal} edges (edges from the
+graph of the torihedra), {\it vertical} edges (edges from coning vertices of the
+the graph of the torihedra) and stellating edges.  \end{remark}
 
-{\it Proof.}  Using the decomposition from Proposition \ref{thm:torihedraldecomposition} we can add a stellation edge whose end points are $T^2 \times \{-1\}$ and $T^2 \times \{1\}$ which cut through faces of $T^2 \times I$ which do not come from the augmentation disks like in \cite{CKP2}.
-Since each face of the top torihedron gets glued to the bottom torihedron, we obtain bipyramids, and the stellation edge will decompose the bipyramids into tetrahedra.
-Then the link of the vertex  $T^2 \times \{1\}$ or $T^2 \times \{-1\}$ is the graph of the torihedron $T^2 \times [0,1)$ or $T^2 \times (-1,0]$ respectively.
-\qed
+{\it Proof.}  Using the decomposition from Proposition
+\ref{thm:torihedraldecomposition} we can add a stellation edge whose end points
+are $T^2 \times \{-1\}$ and $T^2 \times \{1\}$ which cut through faces of $T^2
+\times I$ which do not come from the augmentation disks like in \cite{CKP2}.
+Since each face of the top torihedron gets glued to the bottom torihedron, we
+obtain bipyramids, and the stellation edge will decompose the bipyramids into
+tetrahedra. Then the link of the vertex  $T^2 \times \{1\}$ or $T^2 \times
+\{-1\}$ is the graph of the torihedron $T^2 \times [0,1)$ or $T^2 \times (-1,0]$
+respectively. \qed
 
@@
 with equal sides of length $r_{f_{\vec{e}}}$ and
-angle $2\tilde{\vphi_{\vec{e}}}$ subtended between them,
-where $\tilde{\vphi_{\vec{e}}} = \vphi_{\vec{e}}$
+angle $2\tilde{\vphi}_{\vec{e}}$ subtended between them,
+where $\tilde{\vphi}_{\vec{e}} = \vphi_{\vec{e}}$
 if $\vphi_{\vec{e}}$ if it is acute,
@@
 Let $f \in F$ be a face.
+We construct a Euclidean polygon $\Pol_f$ as follows.
 If $\vphi_{\vec{e}} \leq \pi/2$ for all $\vec{e} \in \del f$,
@@
 the $T_{\vec{e}}$ for $\vec{e}\in \del f$
-fit together into a Euclidean polygon $\Pol_f$.
+fit together into $\Pol_f$.
 If not, suppose $\vphi_{\vec{e}} > \pi/2$
@@
 creating a $(k+1)$-gon,
-then subtract $T_{\vec{e_1}}$ from it.
+then subtract $T_{\vec{e_1}}$ from it to form $\Pol_f$.
 
-Thus, to each face, we associate $\Pol_f$.
+Thus, to each face, we associate the Euclidean polygon $\Pol_f$.
+If $v$ is the vertex of $\Pol_f$ between $e_i$ and $e_{i+1}$,
+then the angle at $v$ is
+$\pi - \vphi_{\vec{e_i}} - \vphi_{\vec{e_{i+1}}}$.
+Then the non-vertex-singularity of $c$ guarantees that
+the sum of angles at $v$ of $\Pol_f$, for faces $f$ containing $v$,
+is $2\pi$.
+%; in other words, $\Pol_f$ glue along edges
+
 View the Euclidean plane as the boundary of the upper-half space.
@@
 the torihedron have the appropriate angles.
-For an interior edge, i.e. an edge that dooes not meet the boundary,
 
-have dihedral angles that sum to $2\pi$,
-and boundary angle
-and it is easy to see
-These $P_f$'s clearly glue tog
+Consider an interior edge $e$ of the pyramidal decomposition
+of the torihedron.
+It corresponds to a vertex $v$ of the graph.
+Note that the dihedral angle of the vertical edge
+at $v$ of $P_f$ is simply the angle at $v$ of $\Pol_f$;
+these sum to $2\pi$ over $f \ni v$.
+
+For a boundary edge $e$, the dihedral angles at $e$ of the $P_f$'s
+containing it are $\vphi_{\vec{e}}$ and $\vphi_{\cev{e}}$,
+which sum to $\theta_e$ by definition.
 

### 2020-09-13 draft1.tex
middle of proving thm; detour to do prop about +- deform theta stuff.

@@
 %\usepackage{mystyle}
+
+\newcommand{\thmref}[1]{Theorem \ref{#1}}
+\newcommand{\prpref}[1]{Proposition \ref{#1}}
 
@@
 }
-\newcommand{\Sp}{\rm{S}}
+\newcommand{\Sp}{{\rm{S}}}
 \newcommand{\C}{\mathbb{C}}
@@
 \newcommand{\Pol}{{\text{Pol}}}
+\newcommand{\toruscomp}[1]{{\torus \times I - #1}}
 
@@
 In this chapter we find many families of hyperbolic links in the thickened torus which remain hyperbolic after augmentation.
-
  \begin{figure}
@@
 
-\begin{prop}\label{thm:torihedraldecomposition}
+\begin{prop}\label{p:tori_decomp}
 Let $L$ be an augmented link in $T^2 \times I$.
-Let $G(L)$ be a diagram of the link on $T^2 \times \{0\}$.
-There is a decomposition of the complement, $(T^2 \times I) - L$ into two isomorphic ideal torihedra.
+%Let $G(L)$ be a diagram of the link on $T^2 \times \{0\}$.
+There is a decomposition of the complement,
+$(T^2 \times I) - L$ into two isomorphic ideal torihedra.
 \end{prop}
 
-\textit{Proof}.
-We will begin by assuming that there are no half twists and then arrange the link diagram of $L$ in the following way: first place the added circle components (augmentation) perpendicular to the projection plane, $T^2 \times \{0\}$ leaving the remaining part of the link parallel to the projection plane.
-We now place a crossing edge on each crossing of the link so that for each crossing edge, one end of the edge lies on a bottom strand while the other end lies on a top strand as in Figure \ref{fig:crossingArc} left.
+\begin{proof}
+We will begin by assuming that there are no half twists and then
+arrange the link diagram of $L$ in the following way: first place the added
+circle components (augmentation) perpendicular to the projection plane, $T^2
+\times \{0\}$ leaving the remaining part of the link parallel to the projection
+plane.  We now place a crossing edge on each crossing of the link so that for
+each crossing edge, one end of the edge lies on a bottom strand while the other
+end lies on a top strand as in Figure \ref{fig:crossingArc} left.
 
-\begin{figure}
- \centering
- \includegraphics[width=4cm]{crossingArc}
-  \includegraphics[width=5cm]{crossingPush}
- \caption{Left: The black strands are part of the link and the red strand is the crossing edge.
-Right: The blue and red edges represent the split crossing edges and the shaded half disk is bounded by the crossing circle}
- \label{fig:crossingArc}
- \end{figure}
+\begin{figure} \centering \includegraphics[width=4cm]{crossingArc}
+\includegraphics[width=5cm]{crossingPush} \caption{Left: The black strands are
+part of the link and the red strand is the crossing edge. Right: The blue and
+red edges represent the split crossing edges and the shaded half disk is bounded
+by the crossing circle} \label{fig:crossingArc} \end{figure}
 
-\indent We view the link from the point at infinity from the top.
-We will push the top strand to the bottom strand, splitting the crossing edge into two identical edges as in Figure \ref{fig:crossingArc} right.
-We push the link components to infinity and stretch the crossing edge so that we have flattened the link onto $T^2 \times \{0\}$ except for the crossing circles which will remain perpendicular to the projection plane.
+\indent We view the link from the point at infinity from the top. We will push
+the top strand to the bottom strand, splitting the crossing edge into two
+identical edges as in Figure \ref{fig:crossingArc} right. We push the link
+components to infinity and stretch the crossing edge so that we have flattened
+the link onto $T^2 \times \{0\}$ except for the crossing circles which will
+remain perpendicular to the projection plane.
 
-\indent Now place a disk on each crossing circle, so that the disk bounded by the crossing circle.
-We can then cut $T^2 \times I$ along $T^2 \times \{0\}$ and focus on the top half, $T^2 \times [0,1)$.
-We will follow the same method on the bottom half to obtain the second identical torihedron.
-The disk we place on each crossing circle is now cut in half.
-This half disk is now bounded by the projection plane and the semi-cricle arc of the crossing circle.
-We push down on the crossing circle and split the disk into two identical disks.
-We then push the arc of each crossing circle to infinity, collapsing them to ideal vertices.
-We obtain two triangular faces which represent the disk which look like a bow-tie as in Figure \ref{fig:falGluings}.
+\indent Now place a disk on each crossing circle, so that the disk bounded by
+the crossing circle. We can then cut $T^2 \times I$ along $T^2 \times \{0\}$ and
+focus on the top half, $T^2 \times [0,1)$. We will follow the same method on the
+bottom half to obtain the second identical torihedron. The disk we place on each
+crossing circle is now cut in half. This half disk is now bounded by the
+projection plane and the semi-cricle arc of the crossing circle. We push down on
+the crossing circle and split the disk into two identical disks. We then push
+the arc of each crossing circle to infinity, collapsing them to ideal vertices.
+We obtain two triangular faces which represent the disk which look like a
+bow-tie as in Figure \ref{fig:falGluings}.
 
@@
 $\pi/n$ twist where $n$ is the number of sides of each face as in Figure
-\ref{fig:top-bottom} clockwise or counterclockwise. \qed
+\ref{fig:top-bottom} clockwise or counterclockwise.
+
+For future reference, we will denote the graph for the top and bottom
+torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively.
+\end{proof}
 
@@
 stellation}. Stellating all the bipyramids of the decomposition obtained from
-Proposition \ref{thm:torihedraldecomposition} we obtained a triangulation of the
+Proposition \ref{p:tori_decomp} we obtained a triangulation of the
 complement of $L$ which is made up of {\it horizontal} edges (edges from the
@@
 {\it Proof.}  Using the decomposition from Proposition
-\ref{thm:torihedraldecomposition} we can add a stellation edge whose end points
+\ref{p:tori_decomp} we can add a stellation edge whose end points
 are $T^2 \times \{-1\}$ and $T^2 \times \{1\}$ which cut through faces of $T^2
@@
 View the Euclidean plane as the boundary of the upper-half space.
-Then $\Pol_f$ subtends an ideal hyperbolic pyramid $P_f$.
+Then $\Pol_f$ supports an ideal hyperbolic pyramid $P_f$.
 
@@
 Then by results of \cite{BandS} there exist a corresponding right-angled circle pattern.
-We then consider the augmented link $L$ and its torihedral decomposition from Proposition \ref{thm:torihedraldecomposition} with a corresponding ``degenerate" circle pattern.
+We then consider the augmented link $L$ and its torihedral decomposition from Proposition \ref{p:tori_decomp} with a corresponding ``degenerate" circle pattern.
 We deform this degenerate circle pattern into a ``proper" circle pattern which will give us a polyhedral decomposition of $(T^2 \times I)-L$ with angles of the torihedra in our torihedral decomposition.
@@
 is a pyramid whose base is an $n$-gon, $n \geq 3$,
-and each boundary edge $e_i$ of the base face is assigned a dihedral angle $\alpha_i$
-such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$.
+and each boundary edge $e_i$ of the base face is assigned a dihedral angle
+$\alpha_i > 0$ such that the sum is $\sum \alpha_i = 2\pi$.
 The vertical edge $e_i'$ that meets $e_i$ and $e_{i+1}$
@@
 Clearly, the dihedral angles of an ideal hyperbolic pyramid
-make it a base-angled ideal pyramid.
+make it a base-angled ideal pyramid
+(with $\alpha_i = \vphi_{e_i}$).
 (TODO probably vice-versa?)
+Also, an angled ideal tetrahedron is simply a base-angled ideal pyramid
+with base a triangle, and with no preferred face.
 
@@
 %\end{itemize}
-Let $P_n$ be a base-angled ideal pyramid,
-and suppose we are given a decomposition of the base face into triangles by adding new edges. 
-One gets an obvious corresponding triangulation of $P_n$, where a new face is added for each new edge.
-Then there is an assignment of a dihedral angle to each edge of each ideal tetrahedron in this triangulation such that
+Let $P_n$ be a base-angled ideal pyramid, and suppose we are given a
+decomposition of the base face into triangles by adding new edges.  One gets an
+obvious corresponding triangulation of $P_n$, where a new face is added for each
+new edge. Then there is an assignment of a dihedral angle to each edge of each
+ideal tetrahedron in this triangulation such that
 \begin{itemize}
@@
 \item the sum of dihedral angles around each new edge is $\pi$;
-\item the dihedral angles of the edges of the original base face are the same as before.
+\item the dihedral angles of the edges of the original base face are the same as
+	before.
 \end{itemize} 
@@
 
-{\it Proof.} See Figure \ref{TODO}
+\begin{proof}
+Induct on $n$; there is nothing to prove for the base case $n=3$.
+
+Suppose the edges are labelled $e_i$,
+which goes between vertices $v_i$ and $v_{i+1}$,
+and suppose $e_i$ is assigned dihedral angle $\alpha_i$.
+Let $e'$ be a new edge addeed to the base face of $P_n$
+such that it separates the base face into a triangle and
+an $(n-1)$-gon;
+suppose the sides of the triangle are
+$e_i, e_{i+1}$, and $e'$.
+The new face corresponding to $e'$ separates $P_n$ into
+an ideal tetrahedron $T$ and an ideal pyramid $P_{n-1}$.
+We assign the dihedral angle of $\pi - \alpha_i - \alpha_{i+1}$
+to $e'$ in $T$, and assign $\alpha_i + \alpha_{i+1}$ to $e'$ in $P_{n-1}$.
+Clearly the condition that the sum of dihedral angles are satisfied
+in $T$ and $P_{n-1}$.
+It remains to check that the dihedral angles assigned to the vertical edges
+are correct.
+For the vertical edge associated $v_j$ for $j \neq i, i+2$,
+there is nothing to check;
+for $j = i$, the dihedral angles are
+$\pi - \alpha_i - (\pi - \alpha_i - \alpha_{i-1})$
+in $T$ and $\pi - \alpha_{i-1} - (\alpha_i + \alpha_{i+1})$ in $P_{n-1}$,
+which sum to $\pi - \alpha_i - \alpha_{i+1}$;
+it is similar for $j = i+2$.
+
+See Figure \ref{TODO}
+\end{proof}
 
@@
 \begin{define}
-Given a face $f$ of the original link diagram the \emph{augmentation sequence} of $f$, denoted $\sigma_f$ is a sequence of symbols $0, L, R$ indexed by vertices of $f$ going counter-clockwise, where, for $v \in \partial f$, the $v$-th element is
+Given a face $f$ of the original link diagram the \emph{augmentation sequence}
+of $f$, denoted $\sigma_f$, is a cyclical sequence of symbols $0, L, R$ indexed
+by vertices of $f$ going counter-clockwise, where, for $v \in \partial f$, the
+$v$-th element is
 \[
@@
 
+\begin{prop}
+Suppose $L$ is obtained from augmenting $K$,
+so that for each face $f$ of the link projection of $K$,
+the augmentation sequence $\sigma_f$ has no $L$ adjacent to $R$.
+Then the TODO CONTINUE HERE
+\end{prop}
+
 \begin{theorem}
-Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons.
-Let $L$ be a link obtained from augmenting $K$ such that there exist no sequence of augmentations where a Left augmentation is adjacent to a Right augmentation.
+Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons. Let
+$L$ be a link obtained from augmenting $K$ such that there exist no sequence of
+augmentations where a Left augmentation is adjacent to a Right augmentation.
 Then $L$ is hyperbolic.
@@
 
-{\it Proof.}
+\begin{proof}
+By ckp [TODO look up precise thm number],
+$\toruscomp{K}$ can be decomposed
+into two torihedra whose graphs are the projection graph of $K$,
+which we denote by $\Gamma$.
+By assigning angles $\pi/2$ to each edge of the torihedra graphs,
+we can invoke \cite[Theorem 3]{BandS} to give us a circle pattern
+on the projection graph.
 
-Part 1:
+By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
+obtained by gluing two torihedra with graph $\Gamma_T(L)$ and $\Gamma_B(L)$.
+Recall that $\Gamma_T(L)$ is obtained from $\Gamma$ by some slight
+modifications, specifically by replacing augmented vertices with bow-ties.
+We assign angles to edges of the bow-ties as in TODO figure,
+and leave untouched edges with the same assignment of $\pi/2$;
+we do the same for $\Gamma_B(L)$.
 
-by ckp the original link can be decomposed into torihedra with projection graph as torihedra graph with pi/2 edges and this gives circle pattern by bobenko-springborn
+We can think of a bow-tie in $\Gamma_T(L)$ as ``thickened edges" in the
+following sense: consider the bow-tie at a crossing $v$,
+and let the edges $e,e'$ of $\Gamma$ at $v$
+be associated to the over-strand of $K$.
+There is a cellular map from each triangle of the bow-tie
+on to $e, e'$ that identifies the $\pi/2$- and 0-labelled edges,
+and collapses the $\pi$-labelled edges onto $v$
+(TODO see same figure).
+It is not hard to see that this map extends to a cellular map
+$\Psi: \Gamma_T(L) \to \Gamma$,
+and in fact extends to the faces as well.
+A similar story applies to $\Gamma_B$.
 
-Part 2: Our torihedral decomposition has graph and on augmentation we will give 0 and pi angles. Next we add another edge and give blah angle (we have three cases)
+Now we construct an extended circle pattern for $\Gamma_T(L)$.
+We will give a more precise description,
+but let us first give the picture.
+Under $\Psi$,
+each face $f$ of $\Gamma_T(L)$ that is not in a bow-tie
+is identified with a face $\bar{f}$ of $\Gamma$,
+so we assign the circle of $\bar{f}$ to $f$;
+each triangle face $f$ in a bow-tie is collapsed to an edge,
+and we assign to $f$ the circle circumscribing the
+face of $\Gamma$ that meets $f$ along the 0-labelled edge.
+This is a ``degenerate" circle pattern that can be thought of as
+the limit of some (singular) circle patterns.
+
+Let us make this more precise,
+describing an extended circle pattern $c$
+on $\Gamma_T(L)$.
+Let the circle pattern for $\Gamma$ be given by
+$\bar{c} = ((r_f),(\vphi_{\vec{e}}))$,
+where recall $r_f$ is the radius of the circle $C_f$
+circumscribing $f$ and $\vphi_{\vec{e}}$
+is half the angle subtended by the edge $e$
+at the center of $C_f$.
+For non-bow-tie faces $f$ of $\Gamma_T(L)$,
+$\Psi$ identifies $f$ with the face $\bar{f}$ of $\Gamma$.
+We set $r_f(c) = r_{\bar{f}}(\bar{c})$.
+For $\vphi$ of its edges,
+if $\vec{e} \in \del f$ is labelled $\pi$,
+we set $\vphi_{\vec{e}} = 0$;
+otherwise, $\Psi$ identifies $\vec{e}$
+with the edge $\vec{e}'$ in $\Gamma$,
+then we set $\vphi_{\vec{e}}(c) = \vphi_{\vec{e}'}(\bar{c})$.
+
+For a triangular face $f$ of a bow tie,
+let $\vec{e}_0, \vec{e}_{\pi/2}, \vec{e}_{\pi}$
+be the edges of $f$ labelled $0,\pi/2, \pi$ respectively.
+We set $r_f(c) = r_{f'}(c)$,
+where $f'$ is the face adjacent to $f$ across $e_0$.
+Then we set
+$\vphi_{\vec{e}_{\pi/2}} = \vphi_{\cev{e}_0} = \pi - \vphi_{\vec{e}_0}$
+and $\vphi_{\vec{e}_{\pi}} = 0$.
+
+It can be easily checked that $c$ satisfies the conditions of
+\prpref{p:nghd_lift}.
+
+with the same procedure for $\Gamma_B(L)$.
+
+Our torihedral decomposition has graph and on augmentation we will give 0 and pi angles. Next we add another edge and give blah angle (we have three cases)
 do three cases with pictures
@@
 
+\end{proof}
+
 \bibliographystyle{plain}
@@
 
+TODO consistent torus symbol, consistent thickened torus symbols
+
 \end{document}

### 2020-09-14 draft1.tex
some progress; the deformation of theta's is lengthy to describe...

@@
 \newcommand{\prpref}[1]{Proposition \ref{#1}}
+\newcommand{\lemref}[1]{Lemma \ref{#1}}
+\newcommand{\comment}[1]{}
 
@@
 \newcommand{\vphi}{\varphi}
+\newcommand{\veps}{\varepsilon}
 \newcommand{\llong}{{\text{long}}}
@@
 \begin{lemma}
+\label{l:circpattern_polyhedra}
 Suppose we have the graph of a torihedron.
 Given a non-singular extended circle pattern $c \in \CCC$ on the graph,
+such that all $\vphi_{\vec{e}} \in (0,\pi)$,
 there exists a decomposition of the torihedron
-into base-angled ideal pyramids (TODO make sure it's been defined) so that
+into base-angled ideal pyramids (TODO make sure it's been defined) such that
 	\begin{itemize}
@@
 \begin{define}
-We say an augmentation is \emph{right-augmented} when both strands are (locally) oriented such that they cross the augmentation disk in the same direction, the crossing is positive/a right-handed half-twist.
-See Figure \ref{TODO}
+We say an augmentation is \emph{right-augmented} if, when both strands are
+(locally) oriented such that they cross the augmentation disk in the same
+direction, the crossing is positive/a right-handed half-twist. See Figure
+\ref{TODO}
 We say an augmentation is \emph{left-augmented} if it is not right-augmented.
@@
 
+We can recover $L$ from the link diagram of $K$
+together with labels at vertices indicating left- or right-augmentation.
+
+\comment{
 \begin{define}
@@
 \end{define}
+}
+
+\comment{
 
@@
 
+\begin{prop}
+Let $\Sigma$ be a closed surface with a cellular decomposition.
+Suppose we have labelled some edges by either $`+'$ or $`-'$,
+such that for each face $f$,
+\begin{itemize}
+	\item no two adjacent edges have the same label,
+	\item the length of consecutive labelled edges is at least 2.
+\end{itemize}
+Then one can further decompose faces along new edges,
+and extend the labelling of edges,
+such that every vertex is adjacent to the same number of
+$`+'$'s and $`-'$'s.
+\end{prop}
+
+\begin{proof}
+Consider a face $f$ and consider a maximal contiguous sequence
+of labelled edges, $e_1,\ldots,e_k$ in $\del f$.
+they span the vertices $v_0,\ldots,v_k$.
+Suppose $e_1$ is labelled $`+'$ (the other case is similar).
+Then $e_2$ is labelled $`-'$, $e_3$ is $`+'$, and so on.
+\end{proof}
+
+\textbf{Case 1}: $k$ is odd. Then we cut $f$ along a new edge
+$\overline{v_0 v_k}$, and label this edge by $`-'$.
+
+\textbf{Case 2}: $k = 2$ and . Then we cut $f$ along a new edge
+\end{proof}
+}
+
+%\begin{theorem}
+%Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons. Let
+%$L$ be a link obtained from augmenting $K$ such that there exist no sequence of
+%augmentations where a Left augmentation is adjacent to a Right augmentation.
+%Then $L$ is hyperbolic.
+%\end{theorem}
 \begin{theorem}
-Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons. Let
-$L$ be a link obtained from augmenting $K$ such that there exist no sequence of
-augmentations where a Left augmentation is adjacent to a Right augmentation.
+Let $K$ be a weakly prime, alternating link whose diagram has no bigons.
+Let $L$ be a link obtained from augmenting $K$ such that
+no edge spans left- and right-augmented vertices.
 Then $L$ is hyperbolic.
@@
 
+(Hmmm... might be misleading, I think $\Psi$ should be a cellular map
+$\Gamma_T(L) \to \Gamma_T(K)$, but the latter happens to be
+same as $\Gamma$, so that's why it's confusing!)
 We can think of a bow-tie in $\Gamma_T(L)$ as ``thickened edges" in the
@@
 \prpref{p:nghd_lift}.
+We would like to apply \lemref{l:circpattern_polyhedra}
+to obtain a polyhedral decomposition of the torihedra,
+but there are edges with $\vphi_{\vec{e}}$
+(specifically, those with $\theta_e = \pi$).
+%We want a deformation of $\theta_{\bullet}$ of $c$
+%that remains vertex non-singular,
+%and gives us an honest ?? circle pattern.
+Hence, we want to find a vector $a = \sum a^e \ddd{\theta_e}$
+in the tangent space of $\Theta(c)$
+that maintains vertex non-singularity,
+i.e.  such that $\sum_{e \ni v} a^e = 0$ for all vertices $v$,
+and for edges $e$ with $\theta_e = \pi$,
+we have $a^e < 0$.
+By \prpref{p:nghd_lift}, there exists $\veps > 0$
+such that the path $\gamma(t) = \Theta(c) + t \cdot a$, $t\in [0,\veps]$,
+in $\TTT$ can be lifted to a path $\tilde{\gamma}$ in $\CCC$.
 
-with the same procedure for $\Gamma_B(L)$.
+To find such $a$, we need to modify $\Gamma_T(L)$ by
+cutting faces along new edges.
+Consider a face $f$ that is not in a bow-tie.
+Suppose the corresponding face $\bar{f}$ of $\Gamma$
+had vertices $v_1,\ldots,v_n$ in counter-clockwise order.
+Suppose it is the case that if a vertex $v_i$ is left-augmented,
+then the augmentation circle intersects $\bar{f}$
+(everything is similar if it is right-augmented circles that intersect
+$\bar{f}$).
+Vertex $v_i$ corresponds to one edge $e_i$ of $\Gamma_T(L)$
+if $v_i$ is not augmented or right-augmented,
+and corresponds to two edges $e_{i,0}, e_{i,\pi}$
+of $\Gamma_T(L)$ if $v_i$ is left-augmented
+($e_{i,0}, e_{i,\pi}$ are edges of a single bow-tie,
+and $e_{i,0}$ has $\theta_{e_{i,0}} = 0$
+and $e_{i,\pi}$ has $\theta_{e_{i,\pi}} = \pi$).
+
+Suppose, after cyclically reindexing, $v_1,\ldots,v_k$
+is a maximally contiguous subsequence of left-augmented vertices
+of $G(K)$ around the face $\bar{f}$;
+the edges around $f$ would start
+$e_{1,0}, e_{1,\pi}, e_{2,0}, e_{2,\pi}, \ldots$.
+We add new edges across $f$ as follows.
+
+First suppose $k=n$; then we do nothing.
+
+Next suppose there is only one such maximal contiguous subsequence.
+If $k = 1$, we add an edge that goes across
+$e_{1,0},e_{1,\pi},e_2$
+(in the sense that the new edge separates the edges of $f$ into two sets
+one of them being those three edges;
+since $n\geq 3$, this edge is new).
+If $k = 2$, we add edge across $e_{1,0},e_{1,\pi}$
+and another edge across $e_{2,0},e_{2,\pi}$
+(these two edges do not form a bigon because we've ruled out $k=n$).
+If $k \geq 3$,
+we add an edge across $e_{1,0},e_{1,\pi},e_{2,0}$
+and another edge across $e_{2,\pi},e_{3,0},\ldots,e_{k,\pi}$
+(again these two edges do not form a bigon).
+
+Finally, if there are multiple such maximal contiguous subsequences,
+we just add edges as above for each contiguous subsequence.
+The only caveat is that if the procedure calls to add a new edge
+that would form a bigon with the existing edges,
+we just don't add it.
+
+TODO CONTINUE HERE do the $+$ and $-$ on the edges.
 

### 2020-09-15 notation.tex
small changes to lemma on manifold point of CCC

@@
 $V,E,F$ are set of vertices, edges, faces.
+No bigon faces.
 
@@
 where $f_{\vec{e}}$ is the face to the left of $\vec{e}$.
+
+When we use $\cev{e}$ to refer to an oriented edge, it refers to
+the oppositely oriented edge to $\vec{e}$.
+If we construct an expression with both $\vec{e}$ and $\cev{e}$,
+it will always be (anti-)symmetrical in the two orientations,
+and we assume that an arbitrary choice has been made.
 
@@
 \begin{definition}
-An \emph{extended circle pattern} is
+Let $\Gamma$ be a graph on the torus.
+An \emph{extended circle pattern} on $\Gamma$ is
 $c = ((r_f), (\vphi_{\vec{e}})) \in \RRR \times \QQQ$
@@
 hence are linearly independent in a neighborhood of $c$.
-Thus, by the implicit function theorem,
-$\CCC$ is a manifold in a neighborhood of $c$.
+%Thus, by the implicit function theorem,
+%$\CCC$ is a manifold in a neighborhood of $c$.
 \end{proof}
+
+\begin{lemma}
+Let $c$ be a face non-singular extended circular pattern
+such that $\vphi_{\vec{e}} \geq 0$ for all $\vec{e}\in\vec{E}$.
+TODO no cycle of thin faces? It's a bit weaker than that...
+Then $\CCC$ is a manifold in a neighborhood of $c$.
+\end{lemma}
+\begin{proof}
+We need to show that the differentials
+$d(l_{\vec{e}} - l_{\cev{e}})
+= \sin \vphi_{\vec{e}} d r_{f_{\vec{e}}}
++ r_{f_{\vec{e}}} \cos \vphi_{\vec{e}} d \vphi_{\vec{e}}
+- \sin \vphi_{\cev{e}} d r_{f_{\cev{e}}}
+- r_{f_{\cev{e}}} \cos \vphi_{\cev{e}} d \vphi_{\cev{e}}
+$
+are linearly independent at $c$.
+If $\vphi_{\vec{e}} \neq \pi/2$,
+then the $d\vphi_{\vec{e}}$ term makes $d(l_{\vec{e}} - l_{\cev{e}})$
+linearly independent from the rest;
+likewise for $\vphi_{\cev{e}} \neq \pi/2$.
+If both equal $\pi/2$,
+then $d(l_{\vec{e}} - l_{\cev{e}}) = d r_{\vec{e}} - d r_{\cev{e}}$.
+consider $f$ with $\vec{e} \in \del f$.
+
+By face non-singularity, $\sum_{\vec{e} \in f} \vphi_{\vec{e}} = \pi$,
+and since there are no bigon faces,
+
+\end{proof}
+
+\subsection{Modifications to Extended Circle Patterns}
+
+Let $\Gamma$ be a graph on the torus, and let $c$ be a
+non-singular extended circle pattern on $\Gamma$.
+There are two simple operations to modify $\Gamma$:
+cutting a face along a new edge,
+and splitting a vertex in two then joining them by a new edge.
+We describe how to associate an extended circle pattern $c'$ to
+the new graph.
+
+Cutting a face: Consider a face $f$,
+and suppose we added a new edge $e'$ so that $f$ is split into
+two faces $f'$ and $f"$, so that
+$\del f' = \{\vec{e_1},\ldots,\vec{e_k}, \vec{e'}\}$,
+and $\del f" = \{\cev{e'}, \vec{e_{k+1}},\ldots \vec{e_n}\}$.
+Then for the new extended circle pattern $c'$,
+we set $r_{f'}(c') = r_{f"}(c') = r_f(c)$,
+$\vphi_{\vec{e'}} = \pi - \vphi_{\vec{e_1}} - \ldots - \vphi_{\vec{e_k}}$,
+$\vphi_{\cev{e'}} = \pi - \vphi_{\vec{e_{k+1}}} - \ldots \vphi_{\vec{e_n}}$,
+and $r_\bullet(c') = r_\bullet(c)$, $\vphi_\bullet(c') = \vphi_\bullet(c)$
+for all other faces, edges.
+It is straightforward to check that $c'$ is non-singular.
+
+Consider a vertex $v$ of the

### 2020-09-20 draft1.tex
progress.

@@
 \newcommand{\torus}{{\mathbb{T}^2}}
+\newcommand{\sT}{{\mathcal{T}}}
 
@@
 \newtheorem{define}[theorem]{Definition}
+\newtheorem{definition}[theorem]{Definition}
 \newtheorem{question}[theorem]{Question}
@@
 
-\begin{define}\cite{CKP2} \label{def:biperiodiclink}
- A \emph{biperiodic alternating link} $\mathcal{L}$ is an infinite link which has a projection onto $\R^2$ which is invariant under an action of a two dimensional lattice $\Lambda$ by translations, such that $L=\mathcal{L}/\Lambda$ is an alternating link in $T^2 \times I$, where $I = (-1,1)$, with the projection on $T^2 \times \{0\}$.
-We call $L$ a link diagram in $T^2 \times I$.
+\begin{define}\cite{CKP2}
+\label{def:biperiodiclink}
+A \emph{biperiodic alternating link} $\mathcal{L}$ is an infinite link
+which has a projection onto
+$\R^2$ which is invariant under an action of a two dimensional lattice $\Lambda$
+by translations, such that $L=\mathcal{L}/\Lambda$ is an alternating link in
+$\torus \times I$, where $I = (-1,1)$, with the projection on $\torus \times \{0\}$.
+We call $L$ a link diagram in $\torus \times I$.   
 \end{define}
@@
 \begin{remark}
-Since $T^2 \times I \cong \Sp^3 - H$, where $H$ is a Hopf link. The complement $T^2 \times I- L = \Sp^3 - (L \cup H)$.
+Since $\torus \times I \cong \Sp^3 - H$, where $H$ is a Hopf link. The complement $\torus \times I- L = \Sp^3 - (L \cup H)$.
 \end{remark}
 
-Champanerkar, Kofman and Purcell \cite{CKP2} extended the definition of prime links in $\Sp^3$ for links in $T^2 \times I$ called weakly prime.
+Champanerkar, Kofman and Purcell \cite{CKP2} extended the definition of prime links in $\Sp^3$ for links in $\torus \times I$ called weakly prime.
 
@@
 \begin{define}
-A \emph{twist region} in a link diagram $L=\mathcal{L}/\Lambda$ in $T^2 \times I$, is the quotient of a twist region in the biperiodic link $\mathcal{L}$.
-%a string of bigons, or a single crossing in the diagram on the universal cover of $T^2 \times I$ is called a .
+A \emph{twist region} in a link diagram $L=\mathcal{L}/\Lambda$ in $\torus \times I$, is the quotient of a twist region in the biperiodic link $\mathcal{L}$.
+%a string of bigons, or a single crossing in the diagram on the universal cover of $\torus \times I$ is called a .
 A biperiodic link $\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on the plane that intersects $\mathcal{L}$ transversely in four points, with two points adjacent to one crossing and the other two points adjacent to another crossing, the simple closed
@@
 
-Now we can define augmentation for a link in $T^2 \times I$ the same way we define augmentation for links in $\Sp^3$.
-For a link in $T^2 \times I$, the crossing circles are added to the diagram projected onto $T^2 \times \{0\}$.
-Let $L$ be a twist reduced diagram in $T^2 \times I$, we define {\it augmentation} as a process in which an unknotted circle component is added to one or more twist regions of $L$.
+Now we can define augmentation for a link in $\torus \times I$ the same way we define augmentation for links in $\Sp^3$.
+For a link in $\torus \times I$, the crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
+Let $L$ be a twist reduced diagram in $\torus \times I$, we define {\it augmentation} as a process in which an unknotted circle component is added to one or more twist regions of $L$.
 See Figure \ref{fig:Augmentations}
@@
 
-We show a method of decomposing an augmented link in the thickened torus into two isomorphic torihedra.
-The idea is to combine methods of Menasco \cite{Menasco} and the use of crossing edges between each crossing of our link and Lackenby's ``cut-slice-flatten" method \cite{lackenby} on the augmentation sites.
+We show a method of decomposing an augmented link in the thickened torus into
+two torihedra. The idea is to combine methods of Menasco
+\cite{Menasco} and the use of crossing edges between each crossing of our link
+and Lackenby's ``cut-slice-flatten" method \cite{lackenby} on the augmentation
+sites.
 
-\begin{define}\cite{CKP2} \label{def:torihedron}
- A \emph{torihedron} is a cone on the torus, i.e.
-$T^2 \times [0,1]/(T^2 \times \{1\})$, with a cellular graph $G$ on $T^2 \times \{0\}$.
-An \emph{ideal torihedron} is a torihedron with the vertices of $G$ and the vertex $T^2 \times \{1\}$ removed.
-Hence, an ideal torihedron is homeomorphic to $T^2 \times [0,1)$ with a finite set of points (ideal vertices) removed from $T^2 \times \{0\}$
+\begin{define}\cite{CKP2}
+\label{def:torihedron}
+A \emph{torihedron} $\sT$ is a cone on the torus, 
+i.e. $\torus \times [0,1]/(\torus \times \{1\})$, with a cellular graph
+$G = G(\sT)$ on $\torus \times \{0\}$.
+An \emph{ideal torihedron} is a torihedron with the
+vertices of $G$ and the vertex $\torus \times \{1\}$ removed. Hence, an ideal
+torihedron is homeomorphic to $\torus \times [0,1)$ with a finite set of points
+(ideal vertices) removed from $\torus \times \{0\}$.
+We refer to the vertex $\torus \times \{1\}$ as the cone point.
 \end{define}
 
+For visualization purposes, we typically draw the graph $G(\sT)$ of a
+torihedron from the perspective of the cone point $\torus \times \{1\}$.
+
+If the faces of $G(\sT)$ are disks,
+then $\sT$ can be decomposed into a union of pyramids,
+obtained by coning each face to the cone point of $\sT$.
+This also gives a decomposition of the corresponding ideal torihedron
+into ideal pyramids.
+We call these the \emph{pyramidal decompositions} of $\sT$ and its
+ideal version.
+
 \begin{prop}\label{p:tori_decomp}
-Let $L$ be an augmented link in $T^2 \times I$.
-%Let $G(L)$ be a diagram of the link on $T^2 \times \{0\}$.
+Let $L$ be an augmented link in $\torus \times I$.
+%Let $G(L)$ be a diagram of the link on $\torus \times \{0\}$.
 There is a decomposition of the complement,
-$(T^2 \times I) - L$ into two isomorphic ideal torihedra.
+$(\torus \times I) - L$ into two ideal torihedra.
 \end{prop}
@@
 arrange the link diagram of $L$ in the following way: first place the added
-circle components (augmentation) perpendicular to the projection plane, $T^2
+circle components (augmentation) perpendicular to the projection plane, $\torus
 \times \{0\}$ leaving the remaining part of the link parallel to the projection
@@
 components to infinity and stretch the crossing edge so that we have flattened
-the link onto $T^2 \times \{0\}$ except for the crossing circles which will
+the link onto $\torus \times \{0\}$ except for the crossing circles which will
 remain perpendicular to the projection plane.
 
-\indent Now place a disk on each crossing circle, so that the disk bounded by
-the crossing circle. We can then cut $T^2 \times I$ along $T^2 \times \{0\}$ and
-focus on the top half, $T^2 \times [0,1)$. We will follow the same method on the
+\indent Now place a disk on each crossing circle, so that the disk is bounded by
+the crossing circle. We can then cut $\torus \times I$ along $\torus \times \{0\}$ and
+focus on the top half, $\torus \times [0,1)$. We will follow the same method on the
 bottom half to obtain the second identical torihedron. The disk we place on each
@@
 
-\indent We repeat the steps for the bottom half of $T^2 \times I$, $T^2 \times
-[-1,0)$. Then we get two isomorphic torihedra. The graph of each will come from
+\indent We repeat the steps for the bottom half of $\torus \times I$, $\torus \times
+(-1,0]$. Then we get two torihedra. The graph of each will come from
 crossing edges and, edges of the disk. Now, if there are half twists we will
@@
 
+\end{proof}
+
 For future reference, we will denote the graph for the top and bottom
-torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively.
-\end{proof}
+torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
+where both graphs are viewed from the cone point of the top torihedron
+$\torus \times \{1\}$.
+Note that if $L = K$ is the non-augmented link,
+$\Gamma_T(L)$ is simply the link projection $K$,
+and in fact $\Gamma_T(L) = \Gamma_B(L)$.
 
@@
 
+\comment{
 \begin{remark}\label{cor:triangulation}
@@
 graph of the torihedra), {\it vertical} edges (edges from coning vertices of the
-the graph of the torihedra) and stellating edges.  \end{remark}
+the graph of the torihedra) and stellating edges.
+\end{remark}
+}
 
-{\it Proof.}  Using the decomposition from Proposition
+\comment{
+\begin{proof}[Proof of Remark 2.7]
+Using the decomposition from Proposition
 \ref{p:tori_decomp} we can add a stellation edge whose end points
-are $T^2 \times \{-1\}$ and $T^2 \times \{1\}$ which cut through faces of $T^2
-\times I$ which do not come from the augmentation disks like in \cite{CKP2}.
+are $\torus \times \{-1\}$ and $\torus \times \{1\}$ which cut through faces of $\torus \times I$ which do not come from the augmentation disks like in \cite{CKP2}.
 Since each face of the top torihedron gets glued to the bottom torihedron, we
 obtain bipyramids, and the stellation edge will decompose the bipyramids into
-tetrahedra. Then the link of the vertex  $T^2 \times \{1\}$ or $T^2 \times
-\{-1\}$ is the graph of the torihedron $T^2 \times [0,1)$ or $T^2 \times (-1,0]$
-respectively. \qed
+tetrahedra. Then the link of the vertex  $\torus \times \{1\}$ or
+$\torus \times \{-1\}$ is the graph of the torihedron
+%$\torus \times [0,1)$ or
+%$\torus \times (-1,0]$ respectively.
+\end{proof}
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{From Extended Circle Patterns to polyhedra}
+TODO refer to BS about theta's
+\begin{definition}
+An \emph{angled torihedron} $(\sT, \theta_\bullet^*)$
+is a torihedron $\sT$ with
+an assignment $\theta_e^* \in (0,\pi)$
+such that for each vertex $v \in G(\sT)$,
+$\sum_{e \ni v} \theta_e^* = (\deg(v) - 2)\pi$.
+We also denote $\theta_e = \pi - \theta_e^*$,
+so $\sum_{e \ni v} \theta_e = 2\pi$;
+we refer to $\theta_e$ as the exterior angle
+and $\theta_e$ as the interior angle.
+\end{definition}
 
-In this section, we describe how to obtain a
-decomposition of a torihedron
-into hyperbolic ideal pyramids
-from a non-singular extended circle pattern.
-
-\begin{lemma}
-\label{l:circpattern_polyhedra}
-Suppose we have the graph of a torihedron.
-Given a non-singular extended circle pattern $c \in \CCC$ on the graph,
-such that all $\vphi_{\vec{e}} \in (0,\pi)$,
-there exists a decomposition of the torihedron
-into base-angled ideal pyramids (TODO make sure it's been defined) such that
-	\begin{itemize}
-		\item each interior edge of the torihedron has dihedral angles sum to $2\pi$;
-		\item each boundary edge $e$ of the torihedron has dihedral angles sum to
-			$\pi - \theta_e$.
-	\end{itemize}
-\end{lemma}
-
-\begin{proof}
-For each directed edge $\vec{e} \in \vec{E}$,
-construct the isosceles triangle $T_{\vec{e}}$
-with equal sides of length $r_{f_{\vec{e}}}$ and
-angle $2\tilde{\vphi}_{\vec{e}}$ subtended between them,
-where $\tilde{\vphi}_{\vec{e}} = \vphi_{\vec{e}}$
-if $\vphi_{\vec{e}}$ if it is acute,
-and = $\pi - \vphi_{\vec{e}}$ otherwise.
-(TODO draw figure?)
-
-Let $f \in F$ be a face.
-We construct a Euclidean polygon $\Pol_f$ as follows.
-If $\vphi_{\vec{e}} \leq \pi/2$ for all $\vec{e} \in \del f$,
-i.e. if $f$ is convex, then 
-the $T_{\vec{e}}$ for $\vec{e}\in \del f$
-fit together into $\Pol_f$.
-If not, suppose $\vphi_{\vec{e}} > \pi/2$
-for $\vec{e} = \vec{e_1}$, 
-and $\leq \pi/2$ for $\vec{e} = \vec{e_2},\ldots \vec{e_k} \in \del f$.
-Then put $T_{\vec{e_2}},\ldots,T_{\vec{e_k}}$ together as above,
-creating a $(k+1)$-gon,
-then subtract $T_{\vec{e_1}}$ from it to form $\Pol_f$.
-
-Thus, to each face, we associate the Euclidean polygon $\Pol_f$.
-If $v$ is the vertex of $\Pol_f$ between $e_i$ and $e_{i+1}$,
-then the angle at $v$ is
-$\pi - \vphi_{\vec{e_i}} - \vphi_{\vec{e_{i+1}}}$.
-Then the non-vertex-singularity of $c$ guarantees that
-the sum of angles at $v$ of $\Pol_f$, for faces $f$ containing $v$,
-is $2\pi$.
-%; in other words, $\Pol_f$ glue along edges
-
-View the Euclidean plane as the boundary of the upper-half space.
-Then $\Pol_f$ supports an ideal hyperbolic pyramid $P_f$.
-
-Clearly, these $P_f$'s, as abstract ideal tetrahedra,
-glue together into the torihedron (TODO rephrase).
-%The hyperbolic structure on $P_f$
-%in particular provide dihedral angles to each edge of $P_f$
-%which clearly satisfies the conditions of making $P_f$
-%a base-angled ideal pyramid.
-We need to check that the angles around each edge of
-the torihedron have the appropriate angles.
-
-Consider an interior edge $e$ of the pyramidal decomposition
-of the torihedron.
-It corresponds to a vertex $v$ of the graph.
-Note that the dihedral angle of the vertical edge
-at $v$ of $P_f$ is simply the angle at $v$ of $\Pol_f$;
-these sum to $2\pi$ over $f \ni v$.
-
-For a boundary edge $e$, the dihedral angles at $e$ of the $P_f$'s
-containing it are $\vphi_{\vec{e}}$ and $\vphi_{\cev{e}}$,
-which sum to $\theta_e$ by definition.
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Hyperbolicity of Augmented Links}
-Thurston introduced a method for finding the unique hyperbolic metric for a given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}.
-The idea was to triangulate the interior of $M$ into ideal tetrahedra and give those tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently in $M$.
-The shape parameter of a tetrahedron is described by the cross-ratio of its four vertices on the sphere at infinity.
-Thurston had written down a system of gluing equations with shape parameters whose solutions correspond to the complete hyperbolic metric on the interior of $M$.
-Casson and Rivin separated gluing equations into a linear and non-linear part \cite{Casson-Rivin}.
-Angle structures is the linear part of Thurston's gluing equations, and what we will use to attain hyperbolicity of complements of augmented links in the thickened torus.
-
-\begin{define}
-Let $M$ be an orientable 3–manifold with boundary consisting of tori.
-An angle structure on an ideal triangulation $\tau$ is an assignment of an (internal) dihedral angle to each edge of each tetrahedron, such that opposite
-edges carry the same dihedral angle, and such that
-\begin{itemize}
-\item all angles lie in the range $(0,\pi)$,
-\item around each ideal vertex of a tetrahedron, the dihedral angles sum to $\pi$
-\item around each edge of $M$, the dihedral angles sum to $2\pi$.
-\end{itemize}
-\end{define}
-
-\begin{theorem}\cite{Casson-Rivin}\label{thm:Casson-Rivin}
-Let $M$ be a 3-manifold admitting an angle structure. Then $M$ is hyperbolic.
-\end{theorem}
-
-For a hyperbolic link $K$ in $T^2 \times I$, we produce sufficient conditions on augmentations such that the resulting link obtained from augmenting $K$ is hyperbolic.
-The idea is to start with a graph from the torihedral decomposition of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges \cite{CKP2}.
-Then by results of \cite{BandS} there exist a corresponding right-angled circle pattern.
-We then consider the augmented link $L$ and its torihedral decomposition from Proposition \ref{p:tori_decomp} with a corresponding ``degenerate" circle pattern.
-We deform this degenerate circle pattern into a ``proper" circle pattern which will give us a polyhedral decomposition of $(T^2 \times I)-L$ with angles of the torihedra in our torihedral decomposition.
-Which we can further decompose into tetrahedra with angles satisfying conditions of an angle structure.
+One may ask for the pyramidal decomposition of a torihedron
+to ``respect" angles. The following definitions make sense of this.
 
@@
 with base a triangle, and with no preferred face.
+
+\begin{definition}
+%TODO: this definition should come after base-angled pyramid
+An \emph{angle splitting} of an angled torihedron $(\sT,\theta_\bullet^*)$
+is a splitting of $\theta_e^* = \vphi_{\vec{e}} + \vphi_{\cev{e}}$
+for each edge $e$,
+such that for each face $f$,
+$\sum_{\vec{e} \in \del f} \vphi_{\vec{e}}^* = \pi$.
+
+Equivalently, an angle splitting is a decomposition of
+$\sT$ into base-angled pyramids,
+one for each faceTODO such that
+for each boundary edge $e$ of $\sT$,
+the dihedral angles from the two adjacent pyramids
+add to $\theta_e^*$.
+\end{definition}
+
+TODO check the feasible flow stuff.
 
@@
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Hyperbolicity of Augmented Links}
+Thurston introduced a method for finding the unique hyperbolic metric for a given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}.
+The idea was to triangulate the interior of $M$ into ideal tetrahedra and give those tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently in $M$.
+The shape parameter of a tetrahedron is described by the cross-ratio of its four vertices on the sphere at infinity.
+Thurston had written down a system of gluing equations with shape parameters whose solutions correspond to the complete hyperbolic metric on the interior of $M$.
+Casson and Rivin separated gluing equations into a linear and non-linear part \cite{Casson-Rivin}.
+Angle structures is the linear part of Thurston's gluing equations, and what we will use to attain hyperbolicity of complements of augmented links in the thickened torus.
+
+\begin{define}
+Let $M$ be an orientable 3–manifold with boundary consisting of tori.
+An angle structure on an ideal triangulation $\tau$ is an assignment of an (internal) dihedral angle to each edge of each tetrahedron, such that opposite
+edges carry the same dihedral angle, and such that
+\begin{itemize}
+\item all angles lie in the range $(0,\pi)$,
+\item around each ideal vertex of a tetrahedron, the dihedral angles sum to $\pi$
+\item around each edge of $M$, the dihedral angles sum to $2\pi$.
+\end{itemize}
+\end{define}
+
+\begin{theorem}\cite{Casson-Rivin}\label{thm:Casson-Rivin}
+Let $M$ be a 3-manifold admitting an angle structure. Then $M$ is hyperbolic.
+\end{theorem}
+
+For a hyperbolic link $K$ in $\torus \times I$, we produce sufficient conditions
+on augmentations such that the resulting link obtained from augmenting $K$ is
+hyperbolic. The idea is to start with a graph from the torihedral decomposition
+of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges
+\cite{CKP2}. Then by results of \cite{BandS} there exist a corresponding
+right-angled circle pattern. We then consider the augmented link $L$ and its
+torihedral decomposition from Proposition \ref{p:tori_decomp} with a
+corresponding ``degenerate" circle pattern. We deform this degenerate circle
+pattern into a ``proper" circle pattern which will give us a polyhedral
+decomposition of $(\torus \times I)-L$ with angles of the torihedra in our
+torihedral decomposition. Which we can further decompose into tetrahedra with
+angles satisfying conditions of an angle structure.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{From Extended Circle Patterns to polyhedra}
+
+In this section, we describe how to obtain a
+decomposition of a torihedron
+into hyperbolic ideal pyramids
+from a non-singular extended circle pattern.
+
+\begin{lemma}
+\label{l:circpattern_polyhedra}
+Suppose we have the graph of a torihedron.
+Given a non-singular extended circle pattern $c \in \CCC$ on the graph,
+such that all $\vphi_{\vec{e}} \in (0,\pi)$,
+there exists a decomposition of the torihedron
+into base-angled ideal pyramids (TODO make sure it's been defined) such that
+	\begin{itemize}
+		\item each interior edge of the torihedron has dihedral angles sum to $2\pi$;
+		\item each boundary edge $e$ of the torihedron has dihedral angles sum to
+			$\pi - \theta_e$.
+	\end{itemize}
+\end{lemma}
+
+\begin{proof}
+For each directed edge $\vec{e} \in \vec{E}$,
+construct the isosceles triangle $T_{\vec{e}}$
+with equal sides of length $r_{f_{\vec{e}}}$ and
+angle $2\tilde{\vphi}_{\vec{e}}$ subtended between them,
+where $\tilde{\vphi}_{\vec{e}} = \vphi_{\vec{e}}$
+if $\vphi_{\vec{e}}$ if it is acute,
+and = $\pi - \vphi_{\vec{e}}$ otherwise.
+(TODO draw figure?)
+
+Let $f \in F$ be a face.
+We construct a Euclidean polygon $\Pol_f$ as follows.
+If $\vphi_{\vec{e}} \leq \pi/2$ for all $\vec{e} \in \del f$,
+i.e. if $f$ is convex, then 
+the $T_{\vec{e}}$ for $\vec{e}\in \del f$
+fit together into $\Pol_f$.
+If not, suppose $\vphi_{\vec{e}} > \pi/2$
+for $\vec{e} = \vec{e_1}$, 
+and $\leq \pi/2$ for $\vec{e} = \vec{e_2},\ldots \vec{e_k} \in \del f$.
+Then put $T_{\vec{e_2}},\ldots,T_{\vec{e_k}}$ together as above,
+creating a $(k+1)$-gon,
+then subtract $T_{\vec{e_1}}$ from it to form $\Pol_f$.
+
+Thus, to each face, we associate the Euclidean polygon $\Pol_f$.
+If $v$ is the vertex of $\Pol_f$ between $e_i$ and $e_{i+1}$,
+then the angle at $v$ is
+$\pi - \vphi_{\vec{e_i}} - \vphi_{\vec{e_{i+1}}}$.
+Then the non-vertex-singularity of $c$ guarantees that
+the sum of angles at $v$ of $\Pol_f$, for faces $f$ containing $v$,
+is $2\pi$.
+%; in other words, $\Pol_f$ glue along edges
+
+View the Euclidean plane as the boundary of the upper-half space.
+Then $\Pol_f$ supports an ideal hyperbolic pyramid $P_f$.
+
+Clearly, these $P_f$'s, as abstract ideal tetrahedra,
+glue together into the torihedron (TODO rephrase).
+%The hyperbolic structure on $P_f$
+%in particular provide dihedral angles to each edge of $P_f$
+%which clearly satisfies the conditions of making $P_f$
+%a base-angled ideal pyramid.
+We need to check that the angles around each edge of
+the torihedron have the appropriate angles.
+
+Consider an interior edge $e$ of the pyramidal decomposition
+of the torihedron.
+It corresponds to a vertex $v$ of the graph.
+Note that the dihedral angle of the vertical edge
+at $v$ of $P_f$ is simply the angle at $v$ of $\Pol_f$;
+these sum to $2\pi$ over $f \ni v$.
+
+For a boundary edge $e$, the dihedral angles at $e$ of the $P_f$'s
+containing it are $\vphi_{\vec{e}}$ and $\vphi_{\cev{e}}$,
+which sum to $\theta_e$ by definition.
+
+\end{proof}
+
 \bibliographystyle{plain}

### 2020-09-20 draft1.tex
adding figures

@@
 \newcommand{\lemref}[1]{Lemma \ref{#1}}
+\newcommand{\figref}[1]{Figure \ref{#1}}
 \newcommand{\comment}[1]{}
@@
 
+The proof is essentially given in \figref{f:ideal_pyramid_arg} below
+
+\begin{figure}
+\label{f:ideal_pyramid_arg}
+\includegraphics[height=8cm]{more_pictures/angle_split.png}
+\end{figure}
 Suppose the edges are labelled $e_i$,
@@
 
-See Figure \ref{TODO}
 \end{proof}
@@
 (locally) oriented such that they cross the augmentation disk in the same
-direction, the crossing is positive/a right-handed half-twist. See Figure
-\ref{TODO}
+direction, the crossing is positive/a right-handed half-twist.
+See \figref{right_left_aug.png}.
 We say an augmentation is \emph{left-augmented} if it is not right-augmented.
+\begin{figure}
+\label{f:right_left_aug}
+\includegraphics{more_pictures/right_left_aug.png}
+\end{figure}
 \end{define}
@@
 modifications, specifically by replacing augmented vertices with bow-ties.
-We assign angles to edges of the bow-ties as in TODO figure,
+We assign angles to edges of the bow-ties as in
+\figref{f:bowtie_angles},
 and leave untouched edges with the same assignment of $\pi/2$;
 we do the same for $\Gamma_B(L)$.
+
+\begin{figure}
+\label{f:bowtie_angles}
+\includegraphics{more_pictures/horizontal_bowtie.png}
+\end{figure}
 
@@
 
+See \figref{f:adding_edges}
+
+\begin{figure}
+\label{f:adding_edges}
+\includegraphics[width=5cm]{more_pictures/one_edge.png}
+\includegraphics[width=5cm]{more_pictures/two_edge.png}
+\includegraphics[width=5cm]{more_pictures/two_edge_many.png}
+\end{figure}
+
 TODO CONTINUE HERE do the $+$ and $-$ on the edges.
@@
 and = $\pi - \vphi_{\vec{e}}$ otherwise.
-(TODO draw figure?)
+
+\begin{figure}
+\includegraphics[width=8cm]{more_pictures/kite.png}
+\end{figure}
+\begin{figure}
+\includegraphics[width=5cm]{more_pictures/positive_angle.png}
+\includegraphics[width=5cm]{more_pictures/negative_angle.png}
+\end{figure}
 

### 2020-09-21 draft1.tex
some progress

@@
 (-1,0]$. Then we get two torihedra. The graph of each will come from
-crossing edges and, edges of the disk. Now, if there are half twists we will
+crossing edges and edges of the disk. Now, if there are half twists we will
 decompose the complement of the link the same way as if there are no half twists
-and we will identify the two bow-ties as in Figure \ref{fig:falGluings}. Finally
+and we will identify the two bow-ties as in Figure \ref{fig:falGluings}.
+Finally,
 we obtain the complement of the link by gluing the two torihedra with the gluing
@@
 glue the faces of the torihedra which do not correspond to a bow-tie with a
-$\pi/n$ twist where $n$ is the number of sides of each face as in Figure
+$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
 \ref{fig:top-bottom} clockwise or counterclockwise.
-
-\end{proof}
 
@@
 $\Gamma_T(L)$ is simply the link projection $K$,
-and in fact $\Gamma_T(L) = \Gamma_B(L)$.
+and in fact $\Gamma_T(K) = \Gamma_B(K)$.
+
+\end{proof}
 
@@
 is a torihedron $\sT$ with
-an assignment $\theta_e^* \in (0,\pi)$
+an assignment $\theta_e^* \in [0,\pi]$
 such that for each vertex $v \in G(\sT)$,
@@
 and $\theta_e$ as the interior angle.
+
+We say $(\sT, \theta_\bullet^*)$ is \emph{degenerate}
+if $\theta_e^* = 0$ for some edge;
+we say it is \emph{non-degenerate} otherwise.
 \end{definition}
@@
 \begin{itemize}
-\item each dihedral angle is between 0 and $\pi$;
+\item each dihedral angle is in $[0, \pi]$;
 \item for each tetrahedron, opposite edges have equal dihedral angles;
@@
 \end{itemize}
+
+We say a angled ideal tetrahedron is \emph{degenerate} if
+one dihedral angle is 0; we say it is \emph{non-degenerate} otherwise.
 \end{define}
@@
 and each boundary edge $e_i$ of the base face is assigned a dihedral angle
-$\alpha_i > 0$ such that the sum is $\sum \alpha_i = 2\pi$.
+$\alpha_i \geq 0$ such that the sum is $\sum \alpha_i = 2\pi$.
 The vertical edge $e_i'$ that meets $e_i$ and $e_{i+1}$
 is automatically assigned the dihedral angle $\pi - \alpha_i - \alpha_{i+1}$.
+
+We say a base-angled ideal pyramid is \emph{degenerate} if
+$\alpha_i = 0$ for some $i$; we say it is \emph{non-degenerate} otherwise.
 \end{define}
@@
 make it a base-angled ideal pyramid
-(with $\alpha_i = \vphi_{e_i}$).
-(TODO probably vice-versa?)
+(with $\alpha_i = \vphi_{e_i}$);
+it is not hard to see that the converse is true:
+simply consider a circumsribed polygon such that the side $e_i$
+subtends an angle of $2\alpha_i$ at the center,
+and take the ideal hyperbolic pyramid over it in upper-half space.
 Also, an angled ideal tetrahedron is simply a base-angled ideal pyramid
@@
 $\sT$ into base-angled pyramids,
-one for each faceTODO such that
+one for each face of $G(\sT)$, such that
 for each boundary edge $e$ of $\sT$,
@@
 \end{definition}
+
+TODO same as [BS] ``coherent angle system'' or something.
 
@@
 to $e'$ in $T$, and assign $\alpha_i + \alpha_{i+1}$ to $e'$ in $P_{n-1}$.
-Clearly the condition that the sum of dihedral angles are satisfied
+Clearly the sum of dihedral angles condition is satisfied
 in $T$ and $P_{n-1}$.
@@
 are correct.
-For the vertical edge associated $v_j$ for $j \neq i, i+2$,
+For the vertical edge associated to $v_j$ for $j \neq i, i+2$,
 there is nothing to check;
@@
 \begin{define}
-Let $M$ be an orientable 3–manifold with boundary consisting of tori.
-An angle structure on an ideal triangulation $\tau$ is an assignment of an (internal) dihedral angle to each edge of each tetrahedron, such that opposite
-edges carry the same dihedral angle, and such that
+Let $M$ be an orientable 3-manifold with boundary consisting of tori. An angle
+structure on an ideal triangulation $\tau$ of $M$ is an assignment of a dihedral
+angle to each edge of each tetrahedron, such that
 \begin{itemize}
-\item all angles lie in the range $(0,\pi)$,
-\item around each ideal vertex of a tetrahedron, the dihedral angles sum to $\pi$
-\item around each edge of $M$, the dihedral angles sum to $2\pi$.
+\item each tetrahedron is a non-degenerate angled ideal tetrahedron,
+\item around each edge of $\tau$, the dihedral angles sum to $2\pi$.
 \end{itemize}
@@
 \end{prop}
+}
 
+\comment{
 \begin{prop}
@@
 \end{proof}
+
 }
@@
 Let $K$ be a weakly prime, alternating link whose diagram has no bigons.
-Let $L$ be a link obtained from augmenting $K$ such that
-no edge spans left- and right-augmented vertices.
+Let $L$ be a link obtained from augmenting $K$.
+%such that
+%no edge spans left- and right-augmented vertices.
 Then $L$ is hyperbolic.
@@
 \begin{proof}
-By ckp [TODO look up precise thm number],
+By \cite[Theorem 7.5]{CKP2},
+(as discussed in \prpref{p:tori_decomp},)
+$\toruscomp{K}$ can be decomposed
+into two torihedra $\sT_T$ and $\sT_B$,
+whose graphs are $\Gamma_T(K), \Gamma_B(K)$;
+viewed from the top cone point $\torus \times \{1\}$,
+they are both the same as the projection graph of $K$.
+%which we denote by $\Gamma$.
+We make them non-degenerate angled torihedra by assigning $\theta^* = \pi/2$
+for all edges.
+
+We obtain an angle-splitting by applying the
+Feasible Flow theorem TODO as follows:
+Consider the directed graph whose vertex set is
+$E \cup F \cup \{\otimes\}$,
+where $E, F$ are the set of edges, faces in $\Gamma_T(K)$,
+and $\otimes$ is some abstract vertex.
+There is a directed edge
+\begin{itemize}
+\item $\otimes \to f$ for each face $f\in F$, with capacity interval
+	$[\pi, \infty)$,
+\item $f \to e$ for each edge $e \in \del f$,
+	with capacity interval $[\veps, \infty)$
+	for some $\veps>0$ to be set later,
+\item $e \to \otimes$ for each edge $e$, with capacity interval
+	$(-\infty, \pi/2]$.
+\end{itemize}
+By TODO lemma about $2|F'| \leq |E'|$,
+and taking $\veps < \pi / |\text{max face size}|$,
+the feasible flow condition is satisfied,
+so a feasible flow exists.
+Since $2|F| = |E|$, the capacity interval restrictions
+on the flow at $\otimes$ is sharp, so out-edges at $\otimes$
+have flow $\pi$ and in-edges at $\otimes$ have flow $\pi/2$.
+Then the flow $f \to e$ gives us $\vphi_{\vec{e}}$,
+where $f$ is the face to the left of $\vec{e}$.
+(we adapted this argument from \cite{BandS}).
+
+By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
+obtained by gluing two torihedra $\sT_T(L),\sT_B(L)$
+with graphs $\Gamma_T(L),\Gamma_B(L)$.
+We make them degenerate angled torihedra by assigning $\theta^*$'s
+to edges of the bow-ties as in \figref{f:bowtie_angles},
+and assign $\pi/2$ to all other edges.
+
+\begin{figure}
+\label{f:bowtie_angles}
+\includegraphics[width=5cm]{more_pictures/horizontal_bowtie.png}
+\end{figure}
+
+Furthermore, we can obtain an angle-splitting of $\sT_T(L)$
+(and similarly $\sT_B(L)$) by modifying the angle-splitting
+for $\sT_T(K)$.
+
+Hmm
+
+\end{proof}
+
+\begin{proof}
+By \cite[Theorem 7.5]{CKP2},
 $\toruscomp{K}$ can be decomposed
@@
 
-\begin{figure}
-\label{f:bowtie_angles}
-\includegraphics{more_pictures/horizontal_bowtie.png}
-\end{figure}
+%\begin{figure}
+%\label{f:bowtie_angles}
+%\includegraphics[width=5cm]{more_pictures/horizontal_bowtie.png}
+%\end{figure}
 

### 2020-09-22 draft1.tex
done proof of main theorem. many TODO eg feasible flow thm

@@
 \begin{lemma}
+\label{l:pyramid_decomp}
 %Let $P_n$ be an ideal pyramid whose base is an $n$-gon and suppose,
@@
 \end{figure}
-Suppose the edges are labelled $e_i$,
+Suppose the edges are labeled $e_i$,
 which goes between vertices $v_i$ and $v_{i+1}$,
@@
 
-\comment{
-\begin{define}
-Given a face $f$ of the original link diagram the \emph{augmentation sequence}
-of $f$, denoted $\sigma_f$, is a cyclical sequence of symbols $0, L, R$ indexed
-by vertices of $f$ going counter-clockwise, where, for $v \in \partial f$, the
-$v$-th element is
-\[
-\sigma_f^v = 
-\begin{cases}
-0 \text{ if $v$ is not augmented} \\
-L \text{ if $v$ is left-augmented} \\
-R \text{ if $v$ is right-augmented}
-\end{cases}
-\]
-\end{define}
-}
-
-\comment{
-
-\begin{prop}
-Suppose $L$ is obtained from augmenting $K$,
-so that for each face $f$ of the link projection of $K$,
-the augmentation sequence $\sigma_f$ has no $L$ adjacent to $R$.
-Then the TODO CONTINUE HERE
-\end{prop}
-}
-
-\comment{
-\begin{prop}
-Let $\Sigma$ be a closed surface with a cellular decomposition.
-Suppose we have labelled some edges by either $`+'$ or $`-'$,
-such that for each face $f$,
-\begin{itemize}
-	\item no two adjacent edges have the same label,
-	\item the length of consecutive labelled edges is at least 2.
-\end{itemize}
-Then one can further decompose faces along new edges,
-and extend the labelling of edges,
-such that every vertex is adjacent to the same number of
-$`+'$'s and $`-'$'s.
-\end{prop}
-
-\begin{proof}
-Consider a face $f$ and consider a maximal contiguous sequence
-of labelled edges, $e_1,\ldots,e_k$ in $\del f$.
-they span the vertices $v_0,\ldots,v_k$.
-Suppose $e_1$ is labelled $`+'$ (the other case is similar).
-Then $e_2$ is labelled $`-'$, $e_3$ is $`+'$, and so on.
-\end{proof}
-
-\textbf{Case 1}: $k$ is odd. Then we cut $f$ along a new edge
-$\overline{v_0 v_k}$, and label this edge by $`-'$.
-
-\textbf{Case 2}: $k = 2$ and . Then we cut $f$ along a new edge
-\end{proof}
-
-}
-
-%\begin{theorem}
-%Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons. Let
-%$L$ be a link obtained from augmenting $K$ such that there exist no sequence of
-%augmentations where a Left augmentation is adjacent to a Right augmentation.
-%Then $L$ is hyperbolic.
-%\end{theorem}
 \begin{theorem}
@@
 Let $L$ be a link obtained from augmenting $K$.
-%such that
-%no edge spans left- and right-augmented vertices.
 Then $L$ is hyperbolic.
@@
 and assign $\pi/2$ to all other edges.
+It is easy to check that upon gluing,
+each edge has sum of dihedral angles ($\theta^*$) equals $2\pi$.
 
@@
 (and similarly $\sT_B(L)$) by modifying the angle-splitting
-for $\sT_T(K)$.
+for $\sT_T(K)$;
+this is shown in \figref{TODO}.
 
-Hmm
+Now we have a decomposition of the two torihedra into
+degenerate base-angled pyramids.
+However, we need the pyramids to be non-degenerate,
+so we first need to modify the angles and graph on the torihedra
+to make all $\theta^*$ nonzero.
 
-\end{proof}
-
-\begin{proof}
-By \cite[Theorem 7.5]{CKP2},
-$\toruscomp{K}$ can be decomposed
-into two torihedra whose graphs are the projection graph of $K$,
-which we denote by $\Gamma$.
-By assigning angles $\pi/2$ to each edge of the torihedra graphs,
-we can invoke \cite[Theorem 3]{BandS} to give us a circle pattern
-on the projection graph.
-
-By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
-obtained by gluing two torihedra with graph $\Gamma_T(L)$ and $\Gamma_B(L)$.
-Recall that $\Gamma_T(L)$ is obtained from $\Gamma$ by some slight
-modifications, specifically by replacing augmented vertices with bow-ties.
-We assign angles to edges of the bow-ties as in
-\figref{f:bowtie_angles},
-and leave untouched edges with the same assignment of $\pi/2$;
-we do the same for $\Gamma_B(L)$.
-
-%\begin{figure}
-%\label{f:bowtie_angles}
-%\includegraphics[width=5cm]{more_pictures/horizontal_bowtie.png}
-%\end{figure}
-
-(Hmmm... might be misleading, I think $\Psi$ should be a cellular map
-$\Gamma_T(L) \to \Gamma_T(K)$, but the latter happens to be
-same as $\Gamma$, so that's why it's confusing!)
-We can think of a bow-tie in $\Gamma_T(L)$ as ``thickened edges" in the
-following sense: consider the bow-tie at a crossing $v$,
-and let the edges $e,e'$ of $\Gamma$ at $v$
-be associated to the over-strand of $K$.
-There is a cellular map from each triangle of the bow-tie
-on to $e, e'$ that identifies the $\pi/2$- and 0-labelled edges,
-and collapses the $\pi$-labelled edges onto $v$
-(TODO see same figure).
-It is not hard to see that this map extends to a cellular map
-$\Psi: \Gamma_T(L) \to \Gamma$,
-and in fact extends to the faces as well.
-A similar story applies to $\Gamma_B$.
-
-Now we construct an extended circle pattern for $\Gamma_T(L)$.
-We will give a more precise description,
-but let us first give the picture.
-Under $\Psi$,
-each face $f$ of $\Gamma_T(L)$ that is not in a bow-tie
-is identified with a face $\bar{f}$ of $\Gamma$,
-so we assign the circle of $\bar{f}$ to $f$;
-each triangle face $f$ in a bow-tie is collapsed to an edge,
-and we assign to $f$ the circle circumscribing the
-face of $\Gamma$ that meets $f$ along the 0-labelled edge.
-This is a ``degenerate" circle pattern that can be thought of as
-the limit of some (singular) circle patterns.
-
-Let us make this more precise,
-describing an extended circle pattern $c$
-on $\Gamma_T(L)$.
-Let the circle pattern for $\Gamma$ be given by
-$\bar{c} = ((r_f),(\vphi_{\vec{e}}))$,
-where recall $r_f$ is the radius of the circle $C_f$
-circumscribing $f$ and $\vphi_{\vec{e}}$
-is half the angle subtended by the edge $e$
-at the center of $C_f$.
-For non-bow-tie faces $f$ of $\Gamma_T(L)$,
-$\Psi$ identifies $f$ with the face $\bar{f}$ of $\Gamma$.
-We set $r_f(c) = r_{\bar{f}}(\bar{c})$.
-For $\vphi$ of its edges,
-if $\vec{e} \in \del f$ is labelled $\pi$,
-we set $\vphi_{\vec{e}} = 0$;
-otherwise, $\Psi$ identifies $\vec{e}$
-with the edge $\vec{e}'$ in $\Gamma$,
-then we set $\vphi_{\vec{e}}(c) = \vphi_{\vec{e}'}(\bar{c})$.
-
-For a triangular face $f$ of a bow tie,
-let $\vec{e}_0, \vec{e}_{\pi/2}, \vec{e}_{\pi}$
-be the edges of $f$ labelled $0,\pi/2, \pi$ respectively.
-We set $r_f(c) = r_{f'}(c)$,
-where $f'$ is the face adjacent to $f$ across $e_0$.
-Then we set
-$\vphi_{\vec{e}_{\pi/2}} = \vphi_{\cev{e}_0} = \pi - \vphi_{\vec{e}_0}$
-and $\vphi_{\vec{e}_{\pi}} = 0$.
-
-It can be easily checked that $c$ satisfies the conditions of
-\prpref{p:nghd_lift}.
-We would like to apply \lemref{l:circpattern_polyhedra}
-to obtain a polyhedral decomposition of the torihedra,
-but there are edges with $\vphi_{\vec{e}}$
-(specifically, those with $\theta_e = \pi$).
-%We want a deformation of $\theta_{\bullet}$ of $c$
-%that remains vertex non-singular,
-%and gives us an honest ?? circle pattern.
-Hence, we want to find a vector $a = \sum a^e \ddd{\theta_e}$
-in the tangent space of $\Theta(c)$
-that maintains vertex non-singularity,
-i.e.  such that $\sum_{e \ni v} a^e = 0$ for all vertices $v$,
-and for edges $e$ with $\theta_e = \pi$,
-we have $a^e < 0$.
-By \prpref{p:nghd_lift}, there exists $\veps > 0$
-such that the path $\gamma(t) = \Theta(c) + t \cdot a$, $t\in [0,\veps]$,
-in $\TTT$ can be lifted to a path $\tilde{\gamma}$ in $\CCC$.
-
-To find such $a$, we need to modify $\Gamma_T(L)$ by
-cutting faces along new edges.
-Consider a face $f$ that is not in a bow-tie.
-Suppose the corresponding face $\bar{f}$ of $\Gamma$
+Consider a face $f$ of $\Gamma_T(L)$ that is not in a bow-tie.
+Suppose the corresponding face $\bar{f}$ of $\Gamma$,
+the projection graph (which is equal to $\Gamma_T(K)$),
 had vertices $v_1,\ldots,v_n$ in counter-clockwise order.
-Suppose it is the case that if a vertex $v_i$ is left-augmented,
+We label the edges of $f$ by $e_{i,0}$, $e_{i,\pi}$, or $e_i$,
+depending on whether the $\theta^*$ is $0$, $\pi$, or $\pi/2$ respectively,
+with $i$ non-decreasing from 1 to $n$,
+adjacent edges having the same $i$ if and only if they
+belong to the same bow-tie.
+For sake of concreteness,
+suppose that if a vertex $v_i$ is right-augmented,
 then the augmentation circle intersects $\bar{f}$
-(everything is similar if it is right-augmented circles that intersect
-$\bar{f}$).
-Vertex $v_i$ corresponds to one edge $e_i$ of $\Gamma_T(L)$
-if $v_i$ is not augmented or right-augmented,
-and corresponds to two edges $e_{i,0}, e_{i,\pi}$
-of $\Gamma_T(L)$ if $v_i$ is left-augmented
-($e_{i,0}, e_{i,\pi}$ are edges of a single bow-tie,
-and $e_{i,0}$ has $\theta_{e_{i,0}} = 0$
-and $e_{i,\pi}$ has $\theta_{e_{i,\pi}} = \pi$).
+(everything is similar if it is left-augmented vertices' circles
+that intersect $\bar{f}$).
+In other words, locally, $f$ meets two of the edges of the bow-tie
+corresponding to a right-augmented vertex $v_i$
+(which would be labeled $e_{i,0}, e_{i,\pi}$ in counter-clockwise order),
+but only meets one of the edges of the bow-tie corresponding to
+a left-augmented vertex.
 
@@
 We add new edges across $f$ as follows.
+(See \figref{f:adding_edges}; the + and - signs will be explained later.)
 
@@
 since $n\geq 3$, this edge is new).
-If $k = 2$, we add edge across $e_{1,0},e_{1,\pi}$
-and another edge across $e_{2,0},e_{2,\pi}$
+%If $k = 2$, we add edge across $e_{1,0},e_{1,\pi}$
+%and another edge across $e_{2,0},e_{2,\pi}$
+%(these two edges do not form a bigon because we've ruled out $k=n$).
+%(these two edges do not form a bigon because we've ruled out $k=n$).
+If $k \geq 2$,
+we add an edge across $e_{1,0},e_{1,\pi}$
+and another edge across $e_{2,0},e_{2,\pi},e_{3,0},\ldots,e_{k,\pi}$
 (these two edges do not form a bigon because we've ruled out $k=n$).
-If $k \geq 3$,
-we add an edge across $e_{1,0},e_{1,\pi},e_{2,0}$
-and another edge across $e_{2,\pi},e_{3,0},\ldots,e_{k,\pi}$
-(again these two edges do not form a bigon).
+%(again these two edges do not form a bigon).
 
@@
 
-See \figref{f:adding_edges}
+This way we obtain a new graph $\Gamma_T(L)'$, which defines a
+new torihedron $\sT_T(L)'$.
+We make it angled using the angles from $\sT_T(L)$ for old edges,
+and putting $\pi$ for all new edges.
 
@@
 \includegraphics[width=5cm]{more_pictures/one_edge.png}
-\includegraphics[width=5cm]{more_pictures/two_edge.png}
+%\includegraphics[width=5cm]{more_pictures/two_edge.png}
 \includegraphics[width=5cm]{more_pictures/two_edge_many.png}
@@
 
-TODO CONTINUE HERE do the $+$ and $-$ on the edges.
+Now we deform the $\theta^*$ based on \figref{f:adding_edges},
+increasing/decreasing by some small $\veps' > 0$ if the edge
+is labeled $+/-$.
+Note some edges may be labeled twice, in which case we perform
+both increasing/decreasing (e.g. if it is labeled $+$ and $-$,
+the $\theta^*$ is not changed).
+It is easy to see that the sum of $\theta^*$ around a vertex
+remains unchanged.
+Furthermore, all the edges with $\theta^*$ originally equal 0,
+i.e. all $e_{i,0}$'s,
+now have positive $\theta^*$,
+(it receives only one label $+$,
+because the other face it meets is a bow-tie).
 
-Our torihedral decomposition has graph and on augmentation we will give 0 and pi angles. Next we add another edge and give blah angle (we have three cases)
-do three cases with pictures
+Thus, we may now apply the feasible flow theorem in a similar manner,
+and obtain an angle-splitting for $\sT_T(L)'$.
+Alternatively, we can directly get an angle-splitting for $\sT_T(L)'$
+using the angle-splitting for $\sT_T(L)$.
+We reuse the $+/-$ assignments from \figref{f:adding_edges}.
+For $e = e_{i,0}$, we increase $\vphi_{\vec{e}}, \vphi_{\cev{e}}$
+by $\veps'/2$ each; for $e = e_{i,\pi}$,
+we decrease them by $\veps'/2$ each.
+For other edges, we increase/decrease $\vphi_{\vec{e}}$ by $\veps'$,
+where $\vec{e}$ is the oriented edge corresponding to the side
+on which the $+/-$ sign appears in \figref{f:adding_edges};
+so for example, if an edge $e$ receives both $+$ and $-$,
+then one of $\vphi_{\vec{e}},\vphi_{\cev{e}}$ increases
+while the other decreases, thus $\theta_e^*$ remains constant.
 
-part 3: Use proposition to get circle pattern to get polyhedral decomposition of the link
+Now we address $\sT_B(L)$.
+In the gluing of $\sT_T(L)$ to $\sT_B(L)$,
+non-bow-tie faces of $\Gamma_T(L)$ are identified with
+non-bow-tie faces of $\Gamma_B(L)$.
+Under this identification, we add the same edges to $\Gamma_B(L)$,
+thus obtaining the new torihedron $\sT_B(L)'$ with graph
+$\Gamma_B(L)'$.
+We perform the same deformations of $\theta^*$'s (or $\vphi$'s).
 
-part 4: get triangulation.
+We need to check that upon gluing $\sT_T(L)'$ to $\sT_B(L)'$,
+the sum of dihedral angles around each edge is still $2\pi$.
+This was clearly true before deforming, as the new edges of
+$\Gamma_T(L)'$ only gets identified with the unique
+corresponding edge of $\Gamma_B(L)'$, and they are both labeled
+with $\theta^* = \pi$.
+To see that the deformation does not change these sums,
+note that in the identification of faces of $\Gamma_T(L)'$
+to $\Gamma_B(L)'$,
+an edge with $\theta^*=0$ is identified with an edge with
+$\theta^*=\pi$,
+so an increase in the former would be conterbalanced by
+a decrease in the latter.
+It is also easy to see this is the case for the other edges.
+TODO hmm more detail?
 
+Finally, for each face of $\Gamma_T(L)'$ that has more than three sides,
+we arbitrarily decompose it into triangles
+and apply \lemref{l:pyramid_decomp}
+to obtain a triangulation of $sT_T(L)'$ into non-degenerate angled tetrahedra;
+perform the corresponding decomposition for faces of
+$\Gamma_B(L)'$ and obtain a triangulation of $\sT_B(L)'$
+into non-degenerate angled tetrahedra.
+Upon gluing, this gives an angle structure on the triangulation
+of $\toruscomp{L}$
 \end{proof}
@@
 
-TODO consistent torus symbol, consistent thickened torus symbols
-
 \end{document}

### 2020-09-23 draft1.tex
added lemma, TODO finish proof

@@
 
+\begin{lemma}
+\label{l:2fe}
+Let $G$ be a 4-valent graph on $\torus$ with no bigons or self-loops,
+and whose faces can be checkerboard colored.
+Then for any subset $F' \subseteq F$ of faces,
+\[
+	2|F'| \leq |E'|
+\]
+where $E' = \cup_{f \in F'} \del f$ is the set of edges
+that meets some face of $F'$.
+\end{lemma}
+
+\begin{proof}
+We induct on $|F'|$ (over all possible such graphs $G$);
+for $F' = \emptyset$, there is nothing to prove.
+
+Call a vertex or edge \emph{interior} if it does not meet
+$F'' = F \backslash F'$.
+Suppose there is an interior vertex $v$.
+Make the modification as in \figref{TODO}.
+This decreases $|F'|$ by one and $|E'|$ by 2.
+However, this process may produce bigons;
+if it does, perform the modification as in \figref{TODO}
+simultaneously on all bigons,
+repeatedly until there are no more bigons.
+%each bigon eliminated decreases $|F'|$ by one and $|E'|$ by 2,
+
+TODO finish proof..
+
+We must check that this process terminates with a graph
+which satisfies the hypotheses set out in the lemma.
+It is clear that checkboard colorability is maintained,
+obviously there will not be any bigons.
+After the modification of the internal vertex,
+at most two bigons are created;
+in any case, the bigons belong to one color of the 
+It is clear that when a bigon is eliminated,
+the only faces which it is adjacent to will have a reduced number of edges.
+\end{proof}
+
 \begin{theorem}
@@
 \end{itemize}
-By TODO lemma about $2|F'| \leq |E'|$,
+By \lemref{l:2fe}about $2|F'| \leq |E'|$,
 and taking $\veps < \pi / |\text{max face size}|$,

### 2020-09-24 draft1.tex
done with that proof and put in feasible flow thm.

--- 2020-09-22 draft1.tex
@@
 
+\begin{lemma}
+\label{l:2fe}
+Let $G$ be a 4-valent graph on $\torus$ with no bigons or self-loops.
+%and whose faces can be checkerboard colored.
+Then for any subset $F' \subseteq F$ of faces,
+\[
+	2\chi(F') \leq |E'|
+\]
+where $E' = \cup_{f \in F'} \del f$ is the set of edges
+that meets some face of $F'$,
+and $\chi(F') = \sum_{f\in F'} \chi(f)$ is the sum
+of the Euler characteristics of faces in $F'$.
+\end{lemma}
+
+\begin{proof}
+We induct on $\chi(F')$ (over all possible such graphs $G$);
+for $F' = \emptyset$, there is nothing to prove.
+
+Call a vertex or edge \emph{interior} if it does not meet
+$F'' = F \backslash F'$.
+Suppose there is an interior vertex $v$.
+Make the modification as in \figref{TODO}
+(later we will choose which way to ``resolve'' the vertex).
+This decreases $chi(F')$ by one and $|E'|$ by 2.
+However, this process may produce bigons;
+if it does, repeatedly eliminate bigons by either
+performing the modification as in \figref{TODO}
+if the two vertices of the bigon are distinct,
+or remove the bigon completely if the two vertices
+of the bigon are the same.
+Each of these steps also decreases $chi(F')$ by one and $|E'|$ by 2
+(note in the second case, after removing the bigon,
+the operation merges two distinct faces or joins a face to itself;
+this adds an $S^1$, thus does not change the (total) euler characteristic
+of the two faces or the one face).
+
+We must check that this process terminates with a graph
+which satisfies the hypotheses set out in the lemma.
+It is clear that %checkboard colorability and
+4-valency is maintained
+at each step, and obviously there will not be any bigons at the end.
+We need to ensure that eliminating bigons does not
+create self-loop edges.
+Here we sepcify how to choose which way to resolve the internal
+vertex $v$. If among the four faces touching $v$,
+one of them has greater than three sides (Case 1),
+then resolve $v$ so that this face is not merged;
+if all four faces are triangles (Case 2),
+simply resolve in an arbitrary manner.
+After the modification of the internal vertex,
+at most two bigons are created;
+eliminate those two bigons.
+Now we find that all bigons will be connected end-to-end
+(i.e. forming a single twist region) -
+this is because in Case 1, only one bigon was present after smoothing
+$v$, which would result in at most two bigons that would be connected;
+and if we were in Case 2, we find that the face between those
+eliminated bigons (coming from merging the two triangles across $v$)
+will become a bigon too,
+thus connecting the potential bigons on either ends.
+
+Thus, one can eliminate bigons in an order so that
+they belong in one twist region;
+in particular, the (not necessarily distinct) faces on either side
+are not bigons,
+so eliminating the bigon does not produce a self-loop edge.
+
+Now suppose $G$ has no interior vertices.
+We perform some reductions.
+Remove all $f\in F'$ that have non-positive Euler characteristic,
+since having them only makes the inequality easier to prove.
+Now consider some $f\in F'$.
+If it has at least two boundary (i.e. non-interior) edges,
+we can remove $f$ from $F'$,
+which decreases $chi(F')$ by 1 and $|E'|$ by at least 2.
+Thus we remove all such $f$.
+
+Now suppose $f\in F'$ has three contiguous interior edges
+$e_1,e_2,e_3$.
+(e.g. if $f$ has at least four sides).
+Let $v_1, v_2$ be the vertices between these three interior edges.
+Since $v_1$ is not inteior,
+the face across $v_1$ from $f$ is not in $F'$;
+likewise with $v_2$.
+But this shows that the face across $e_2$ from $f$
+has two boundary edges, contradicting our reduction.
+%This would lead to the situation in \figref{TODO},
+%showing that there is a face with at least
+%two boundary edges, contradicting our reduction.
+
+Thus, we now have a graph whose faces are triangles,
+and each face has exactly one boundary edge.
+Now the problem is solved with a simple counting argument:
+each $f$ corresponds to one boundary edge and two interior edges,
+but since the interior edges are shared by two faces,
+they should count as half an edge; so
+\[
+ |E'| = \sum_{f\in F'} 1 + 1/2 + 1/2 = 2|F'| = 2\chi(F')
+\]
+and we are done.
+\end{proof}
+
+The following theorem is quoted from \cite{BS}
+(TODO cite original too)
+
+\begin{theorem}[Feasible Flow Theorem]
+\label{t:feasible_flow}
+Let $(N,X)$ be a directed graph,
+with a \emph{lower capacity bound} $a_x$
+and \emph{upper capacity bound} $b_x$
+for each directed edge $x \in X$,
+with $-\infty \leq a_x \leq b_x \leq \infty$.
+A \emph{feasible flow} is a function $\vphi : X \to \RR$
+such that Kirchhof's current law is satisfied
+(i.e. flow in = flow out at every vertex).
+
+A feasible flow exists if and only if,
+for every proper nonempty subset $N' \subset N$,
+\[
+\sum_{x \in ex(N')} b_x \geq \sum_{x \in in(N')} a_x
+\]
+where $ex(N'), in(N')$ refer to edges leaving,
+entering $N'$, respectively.
+\end{theorem}
+
 \begin{theorem}
@@
 We obtain an angle-splitting by applying the
-Feasible Flow theorem TODO as follows:
+Feasible Flow theorem (\thmref{t:feasible_flow}) as follows:
 Consider the directed graph whose vertex set is
@@
 \end{itemize}
-By TODO lemma about $2|F'| \leq |E'|$,
+By \lemref{l:2fe}, $2|F'| = 2\chi(F') \leq |E'|$,
 and taking $\veps < \pi / |\text{max face size}|$,

### 2020-09-24 circlepatterns.tex
added reference for feasible flow

--- 2020-09-22 draft1.tex
@@
-\documentclass[11pt]{amsart}
-\usepackage{float}
-\usepackage{amsfonts, amstext, amsmath, amsthm, amscd, amssymb, upgreek}
-\usepackage{bbm}
-\usepackage{graphicx, color,  subfigure, wrapfig, overpic}
-%\usepackage[all,cmtip]{xy} 
-\usepackage{tikz}
-%\usepackage{mystyle}
-
-\newcommand{\thmref}[1]{Theorem \ref{#1}}
-\newcommand{\prpref}[1]{Proposition \ref{#1}}
-\newcommand{\lemref}[1]{Lemma \ref{#1}}
-\newcommand{\figref}[1]{Figure \ref{#1}}
-\newcommand{\comment}[1]{}
-
-\textwidth 6.07in 
-\textheight 8.6in 
-\oddsidemargin 0.18in
-\evensidemargin 0.18in
-% \topmargin -0.07in
-
-%%  If the following line is uncommented, we see the labels of theorems, figures, etc. in the margins.
-% \usepackage[notref,notcite]{showkeys}
-\setlength{\marginparwidth}{0.8in}
-\let\oldmarginpar\marginpar
-\renewcommand\marginpar[1]{\oldmarginpar[\raggedleft\footnotesize #1]%
-{\raggedright\footnotesize #1}}
-
-%This command stops the Math Review numbers appearing in the references! 
-\AtBeginDocument{
-   \def\MR#1{}
-}
-\newcommand{\Sp}{{\rm{S}}}
-\newcommand{\C}{\mathbb{C}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\Q}{\mathbb{Q}}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\CC}{\mathbb{C}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\HH}{\mathbb{H}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\bfloor}[1]{\left\lfloor #1\right\rfloor}
-\renewcommand{\P}{\mathcal P}
-\newcommand{\A}{\mathcal A}
-\newcommand{\W}{\mathcal W}
-\newcommand{\vol}{{\rm vol}}
-\newcommand{\cut}{{\backslash \backslash}}
-\newcommand{\bdy}{\partial}
-\newcommand{\voct}{{v_{\rm oct}}}
-\newcommand{\vtet}{{v_{\rm tet}}}
-\renewcommand{\L}{\mathcal L}
-\newcommand{\cp}{\mathcal{C}}
-\newcommand{\toF}{{\overset{F}{\longrightarrow}}}
-\newcommand{\K}{\upkappa}
-
-\def\co{\colon\thinspace}
-
-\newcommand{\torus}{{\mathbb{T}^2}}
-\newcommand{\sT}{{\mathcal{T}}}
-
-\newcommand{\RRR}{{\underline{\mathfrak{R}}}}
-\newcommand{\QQQ}{{\underline{\mathfrak{Q}}}}
-\newcommand{\CCC}{{\underline{\mathfrak{C}}}}
-\newcommand{\PPP}{{\underline{\mathbf{\Phi}}}}
-\newcommand{\TTT}{{\underline{\mathbf{\Theta}}}}
-\newcommand{\LLL}{{\underline{\mathfrak{L}}}}
-
-\newcommand{\cev}[1]{\overset{\leftarrow}{#1}}
-
-\newcommand{\del}{\partial}
-\newcommand{\ddd}[1]{{\frac{\del}{\del #1}}}
-\newcommand{\vphi}{\varphi}
-\newcommand{\veps}{\varepsilon}
-\newcommand{\llong}{{\text{long}}}
-\newcommand{\Span}{{\text{span}}}
-\newcommand{\Pol}{{\text{Pol}}}
-\newcommand{\toruscomp}[1]{{\torus \times I - #1}}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{example}[theorem]{Example}
-
-\newtheorem*{namedtheorem}{\theoremname}
-\newcommand{\theoremname}{testing}
-\newenvironment{named}[1]{\renewcommand{\theoremname}{#1}\begin{namedtheorem}}{\end{namedtheorem}}
-\theoremstyle{definition}
-\newtheorem{define}[theorem]{Definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{question}[theorem]{Question}
-\newtheorem{remark}[theorem]{Remark}
-
-\title [Augmented Links in the Thickened Torus] {Augmented Links in the Thickened Torus}
-
-\author[Alice Kwon and Ying Hong Tham]{Alice Kwon and Ying Hong Tham}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-  abstract goes here...
-\end{abstract}
-
-\section{Introduction}
-
-Given a twist reduced diagram of a link $L$, {\it augmentation} is a process in which an unknotted circle component is added to one or more twist regions (a single crossing or a string of bigons) of $L$.
-Due to the added circle component we can remove full twists at the twist region of $L$.
-If the twist region has an odd number of crossings then all but one crossing is removed, whereas if the twist region has an even number of crossings then all are removed.
-The newly obtained link diagram is called an {\it augmented link diagram}.
-See Figure \ref{fig:Augmentations}.
-
-Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in $\Sp^3$ the link $L$ obtained by augmentation $K$ is hyperbolic.
-In this paper we investigate if this statement holds for links in the thickened torus i.e.
-if $L$ is a link obtained from augmenting a hyperbolic alternating link $K$ in the thickened torus.
-In this chapter we find many families of hyperbolic links in the thickened torus which remain hyperbolic after augmentation.
- \begin{figure}
- \centering  
- \begin{tabular}{cc}
- \includegraphics [height=4cm]{augmentation1}&
-  \includegraphics [height=4cm]{augmentation2}\\
-  (a)&(b)
-  \end{tabular}
- \caption{The left shows a pretzel knot before augmentation and the right shows after augmentation}
- \label{fig:augmentationS3}
- \end{figure}
-
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Augmented Links}
- Champanerkar, Kofman and Purcell have studied alternating links in the thickened torus. They define a link in the thickened torus as a quotient of a biperiodic alternating link as follows,
-
-\begin{define}\cite{CKP2}
-\label{def:biperiodiclink}
-A \emph{biperiodic alternating link} $\mathcal{L}$ is an infinite link
-which has a projection onto
-$\R^2$ which is invariant under an action of a two dimensional lattice $\Lambda$
-by translations, such that $L=\mathcal{L}/\Lambda$ is an alternating link in
-$\torus \times I$, where $I = (-1,1)$, with the projection on $\torus \times \{0\}$.
-We call $L$ a link diagram in $\torus \times I$.   
-\end{define}
-
-\begin{remark}
-Since $\torus \times I \cong \Sp^3 - H$, where $H$ is a Hopf link. The complement $\torus \times I- L = \Sp^3 - (L \cup H)$.
-\end{remark}
-
-Champanerkar, Kofman and Purcell \cite{CKP2} extended the definition of prime links in $\Sp^3$ for links in $\torus \times I$ called weakly prime.
-
- \begin{define} \label{def:weaklyprime}
-A diagram of a link $L$ is weakly prime if whenever a disk is embedded in the diagram surface meets the diagram transversely in exactly two edges, then the disk contains a simple edge of the diagram and no crossings.
-\end{define}
-
-\begin{define}
-A \emph{twist region} in a link diagram $L=\mathcal{L}/\Lambda$ in $\torus \times I$, is the quotient of a twist region in the biperiodic link $\mathcal{L}$.
-%a string of bigons, or a single crossing in the diagram on the universal cover of $\torus \times I$ is called a .
-A biperiodic link $\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on the plane that intersects $\mathcal{L}$ transversely in four points, with two points adjacent to one crossing and the other two points adjacent to another crossing, the simple closed
-curve bounds a subdiagram consisting of a (possibly empty) collection of bigons
-strung end to end between these crossings. We say $L$ is \emph{twist-reduced} if it is the quotient of a twist-reduced biperiodic link. 
-\end{define}
-
-Now we can define augmentation for a link in $\torus \times I$ the same way we define augmentation for links in $\Sp^3$.
-For a link in $\torus \times I$, the crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
-Let $L$ be a twist reduced diagram in $\torus \times I$, we define {\it augmentation} as a process in which an unknotted circle component is added to one or more twist regions of $L$.
-See Figure \ref{fig:Augmentations}
-
- \begin{figure}
- \centering
- \begin{tabular}{cccc}
- \includegraphics [width=3cm]{fig1}&
- \includegraphics  [width=3cm]{twist-augment}&
-  \includegraphics [width=3cm]{fig-2}\\
- % \includegraphics [width=3cm]{fal}\\
-  A&B&C
-  \end{tabular}
- \caption{A: The top right has an odd number of twists while the bottom left has an even number of twists.
-B: The picture of the link on the right after augmentation twist regions circled in red.
-C: The link with the twists removed.}
- \label{fig:Augmentations}
- \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Torihedral Decomposition of Augmented Alternating Links in Thickened Torus}
-
-We show a method of decomposing an augmented link in the thickened torus into
-two torihedra. The idea is to combine methods of Menasco
-\cite{Menasco} and the use of crossing edges between each crossing of our link
-and Lackenby's ``cut-slice-flatten" method \cite{lackenby} on the augmentation
-sites.
-
-\begin{define}\cite{CKP2}
-\label{def:torihedron}
-A \emph{torihedron} $\sT$ is a cone on the torus, 
-i.e. $\torus \times [0,1]/(\torus \times \{1\})$, with a cellular graph
-$G = G(\sT)$ on $\torus \times \{0\}$.
-An \emph{ideal torihedron} is a torihedron with the
-vertices of $G$ and the vertex $\torus \times \{1\}$ removed. Hence, an ideal
-torihedron is homeomorphic to $\torus \times [0,1)$ with a finite set of points
-(ideal vertices) removed from $\torus \times \{0\}$.
-We refer to the vertex $\torus \times \{1\}$ as the cone point.
-\end{define}
-
-For visualization purposes, we typically draw the graph $G(\sT)$ of a
-torihedron from the perspective of the cone point $\torus \times \{1\}$.
-
-If the faces of $G(\sT)$ are disks,
-then $\sT$ can be decomposed into a union of pyramids,
-obtained by coning each face to the cone point of $\sT$.
-This also gives a decomposition of the corresponding ideal torihedron
-into ideal pyramids.
-We call these the \emph{pyramidal decompositions} of $\sT$ and its
-ideal version.
-
-\begin{prop}\label{p:tori_decomp}
-Let $L$ be an augmented link in $\torus \times I$.
-%Let $G(L)$ be a diagram of the link on $\torus \times \{0\}$.
-There is a decomposition of the complement,
-$(\torus \times I) - L$ into two ideal torihedra.
-\end{prop}
-
-\begin{proof}
-We will begin by assuming that there are no half twists and then
-arrange the link diagram of $L$ in the following way: first place the added
-circle components (augmentation) perpendicular to the projection plane, $\torus
-\times \{0\}$ leaving the remaining part of the link parallel to the projection
-plane.  We now place a crossing edge on each crossing of the link so that for
-each crossing edge, one end of the edge lies on a bottom strand while the other
-end lies on a top strand as in Figure \ref{fig:crossingArc} left.
-
-\begin{figure} \centering \includegraphics[width=4cm]{crossingArc}
-\includegraphics[width=5cm]{crossingPush} \caption{Left: The black strands are
-part of the link and the red strand is the crossing edge. Right: The blue and
-red edges represent the split crossing edges and the shaded half disk is bounded
-by the crossing circle} \label{fig:crossingArc} \end{figure}
-
-\indent We view the link from the point at infinity from the top. We will push
-the top strand to the bottom strand, splitting the crossing edge into two
-identical edges as in Figure \ref{fig:crossingArc} right. We push the link
-components to infinity and stretch the crossing edge so that we have flattened
-the link onto $\torus \times \{0\}$ except for the crossing circles which will
-remain perpendicular to the projection plane.
-
-\indent Now place a disk on each crossing circle, so that the disk is bounded by
-the crossing circle. We can then cut $\torus \times I$ along $\torus \times \{0\}$ and
-focus on the top half, $\torus \times [0,1)$. We will follow the same method on the
-bottom half to obtain the second identical torihedron. The disk we place on each
-crossing circle is now cut in half. This half disk is now bounded by the
-projection plane and the semi-cricle arc of the crossing circle. We push down on
-the crossing circle and split the disk into two identical disks. We then push
-the arc of each crossing circle to infinity, collapsing them to ideal vertices.
-We obtain two triangular faces which represent the disk which look like a
-bow-tie as in Figure \ref{fig:falGluings}.
-
-\begin{figure}
- \centering
- \begin{tabular}{cc}
- \includegraphics [width=8cm]{falGluing1}&
- \includegraphics [width=7cm]{falGluing2}\\
- (a)&(b)
- \end{tabular}
- \caption{The first pictures shows gluing without half-twists the second shows gluing with half-twists}
- \label{fig:falGluings}
- \end{figure}
-
-\indent We repeat the steps for the bottom half of $\torus \times I$, $\torus \times
-(-1,0]$. Then we get two torihedra. The graph of each will come from
-crossing edges and edges of the disk. Now, if there are half twists we will
-decompose the complement of the link the same way as if there are no half twists
-and we will identify the two bow-ties as in Figure \ref{fig:falGluings}.
-Finally,
-we obtain the complement of the link by gluing the two torihedra with the gluing
-information given by identifying crossing edges and triangles of the bow-tie. We
-glue the faces of the torihedra which do not correspond to a bow-tie with a
-$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
-\ref{fig:top-bottom} clockwise or counterclockwise.
-
-For future reference, we will denote the graph for the top and bottom
-torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
-where both graphs are viewed from the cone point of the top torihedron
-$\torus \times \{1\}$.
-Note that if $L = K$ is the non-augmented link,
-$\Gamma_T(L)$ is simply the link projection $K$,
-and in fact $\Gamma_T(K) = \Gamma_B(K)$.
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The following figures is an example which decomposes the link (C) of Figure
-\ref{fig:Augmentations}.  \begin{figure}[h] \centering \includegraphics
-[height=3cm]{fig-3} \includegraphics [height=3cm]{fig-4} \caption{Each crossing
-circle bounds a disk} \end{figure}
-
- \vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
- [height=3cm]{fig-5} \caption{We split the disk and collapse the arc of each
- crossing circle to ideal vertices} \end{figure}
-
-	\vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
-	[height=3cm]{fig-6} \caption{Left: The crossing arc is the edge in red.
-	Middle: Picture of splitting the crossing edge. Right: The link component is
-	pushed off to infinity.} \end{figure}
-
- \vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
- [height=3cm]{top-bottom} \caption{
-	Left: The top torihedron.
-	Right: The bottom torihdron with rotation for face gluing.} \label{fig:top-bottom} \end{figure}
-
-\comment{
-\begin{remark}\label{cor:triangulation}
-The faces of one torihedron which do not correspond to a bow-tie glue to a
-corresponding face of the second torihedron to form bipyramids. One can add
-stellating edges, edges which have vertices corresponding to the different
-components of the Hopf link that cuts through the center of the face to
-decompose the bipyramids into tetrahedra. This process is called {\it
-stellation}. Stellating all the bipyramids of the decomposition obtained from
-Proposition \ref{p:tori_decomp} we obtained a triangulation of the
-complement of $L$ which is made up of {\it horizontal} edges (edges from the
-graph of the torihedra), {\it vertical} edges (edges from coning vertices of the
-the graph of the torihedra) and stellating edges.
-\end{remark}
-}
-
-\comment{
-\begin{proof}[Proof of Remark 2.7]
-Using the decomposition from Proposition
-\ref{p:tori_decomp} we can add a stellation edge whose end points
-are $\torus \times \{-1\}$ and $\torus \times \{1\}$ which cut through faces of $\torus \times I$ which do not come from the augmentation disks like in \cite{CKP2}.
-Since each face of the top torihedron gets glued to the bottom torihedron, we
-obtain bipyramids, and the stellation edge will decompose the bipyramids into
-tetrahedra. Then the link of the vertex  $\torus \times \{1\}$ or
-$\torus \times \{-1\}$ is the graph of the torihedron
-%$\torus \times [0,1)$ or
-%$\torus \times (-1,0]$ respectively.
-\end{proof}
-}
-
-TODO refer to BS about theta's
-\begin{definition}
-An \emph{angled torihedron} $(\sT, \theta_\bullet^*)$
-is a torihedron $\sT$ with
-an assignment $\theta_e^* \in [0,\pi]$
-such that for each vertex $v \in G(\sT)$,
-$\sum_{e \ni v} \theta_e^* = (\deg(v) - 2)\pi$.
-We also denote $\theta_e = \pi - \theta_e^*$,
-so $\sum_{e \ni v} \theta_e = 2\pi$;
-we refer to $\theta_e$ as the exterior angle
-and $\theta_e$ as the interior angle.
-
-We say $(\sT, \theta_\bullet^*)$ is \emph{degenerate}
-if $\theta_e^* = 0$ for some edge;
-we say it is \emph{non-degenerate} otherwise.
-\end{definition}
-
-One may ask for the pyramidal decomposition of a torihedron
-to ``respect" angles. The following definitions make sense of this.
-
-\begin{define}
-An \emph{angled ideal tetrahedron} is an ideal tetrahedron with an assignment of a dihedral angle
-to each edge, such that
-\begin{itemize}
-\item each dihedral angle is in $[0, \pi]$;
-\item for each tetrahedron, opposite edges have equal dihedral angles;
-\item the three distinct angles sum to $\pi$.
-\end{itemize}
-
-We say a angled ideal tetrahedron is \emph{degenerate} if
-one dihedral angle is 0; we say it is \emph{non-degenerate} otherwise.
-\end{define}
-
-\begin{define}
-A \emph{base-angled ideal pyramid}
-is a pyramid whose base is an $n$-gon, $n \geq 3$,
-and each boundary edge $e_i$ of the base face is assigned a dihedral angle
-$\alpha_i \geq 0$ such that the sum is $\sum \alpha_i = 2\pi$.
-The vertical edge $e_i'$ that meets $e_i$ and $e_{i+1}$
-is automatically assigned the dihedral angle $\pi - \alpha_i - \alpha_{i+1}$.
-
-We say a base-angled ideal pyramid is \emph{degenerate} if
-$\alpha_i = 0$ for some $i$; we say it is \emph{non-degenerate} otherwise.
-\end{define}
-
-Clearly, the dihedral angles of an ideal hyperbolic pyramid
-make it a base-angled ideal pyramid
-(with $\alpha_i = \vphi_{e_i}$);
-it is not hard to see that the converse is true:
-simply consider a circumsribed polygon such that the side $e_i$
-subtends an angle of $2\alpha_i$ at the center,
-and take the ideal hyperbolic pyramid over it in upper-half space.
-Also, an angled ideal tetrahedron is simply a base-angled ideal pyramid
-with base a triangle, and with no preferred face.
-
-\begin{definition}
-%TODO: this definition should come after base-angled pyramid
-An \emph{angle splitting} of an angled torihedron $(\sT,\theta_\bullet^*)$
-is a splitting of $\theta_e^* = \vphi_{\vec{e}} + \vphi_{\cev{e}}$
-for each edge $e$,
-such that for each face $f$,
-$\sum_{\vec{e} \in \del f} \vphi_{\vec{e}}^* = \pi$.
-
-Equivalently, an angle splitting is a decomposition of
-$\sT$ into base-angled pyramids,
-one for each face of $G(\sT)$, such that
-for each boundary edge $e$ of $\sT$,
-the dihedral angles from the two adjacent pyramids
-add to $\theta_e^*$.
-\end{definition}
-
-TODO same as [BS] ``coherent angle system'' or something.
-
-TODO check the feasible flow stuff.
-
-\begin{lemma}
-\label{l:pyramid_decomp}
-%Let $P_n$ be an ideal pyramid whose base is an $n$-gon and suppose,
-%\begin{itemize}
-%\item each boundary edge of the base face is assigned a dihedral angle $\alpha_i$ such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$;
-%\item we are given a decomposition of the base face into triangles by adding new edges. 
-%\end{itemize}
-Let $P_n$ be a base-angled ideal pyramid, and suppose we are given a
-decomposition of the base face into triangles by adding new edges.  One gets an
-obvious corresponding triangulation of $P_n$, where a new face is added for each
-new edge. Then there is an assignment of a dihedral angle to each edge of each
-ideal tetrahedron in this triangulation such that
-\begin{itemize}
-\item each tetrahedron is an angled ideal tetrahedron;
-\item the sum of dihedral angles around each new edge is $\pi$;
-\item the dihedral angles of the edges of the original base face are the same as
-	before.
-\end{itemize} 
-\end{lemma}
-
-\begin{proof}
-Induct on $n$; there is nothing to prove for the base case $n=3$.
-
-The proof is essentially given in \figref{f:ideal_pyramid_arg} below
-
-\begin{figure}
-\label{f:ideal_pyramid_arg}
-\includegraphics[height=8cm]{more_pictures/angle_split.png}
-\end{figure}
-Suppose the edges are labeled $e_i$,
-which goes between vertices $v_i$ and $v_{i+1}$,
-and suppose $e_i$ is assigned dihedral angle $\alpha_i$.
-Let $e'$ be a new edge addeed to the base face of $P_n$
-such that it separates the base face into a triangle and
-an $(n-1)$-gon;
-suppose the sides of the triangle are
-$e_i, e_{i+1}$, and $e'$.
-The new face corresponding to $e'$ separates $P_n$ into
-an ideal tetrahedron $T$ and an ideal pyramid $P_{n-1}$.
-We assign the dihedral angle of $\pi - \alpha_i - \alpha_{i+1}$
-to $e'$ in $T$, and assign $\alpha_i + \alpha_{i+1}$ to $e'$ in $P_{n-1}$.
-Clearly the sum of dihedral angles condition is satisfied
-in $T$ and $P_{n-1}$.
-It remains to check that the dihedral angles assigned to the vertical edges
-are correct.
-For the vertical edge associated to $v_j$ for $j \neq i, i+2$,
-there is nothing to check;
-for $j = i$, the dihedral angles are
-$\pi - \alpha_i - (\pi - \alpha_i - \alpha_{i-1})$
-in $T$ and $\pi - \alpha_{i-1} - (\alpha_i + \alpha_{i+1})$ in $P_{n-1}$,
-which sum to $\pi - \alpha_i - \alpha_{i+1}$;
-it is similar for $j = i+2$.
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Hyperbolicity of Augmented Links}
-Thurston introduced a method for finding the unique hyperbolic metric for a given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}.
-The idea was to triangulate the interior of $M$ into ideal tetrahedra and give those tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently in $M$.
-The shape parameter of a tetrahedron is described by the cross-ratio of its four vertices on the sphere at infinity.
-Thurston had written down a system of gluing equations with shape parameters whose solutions correspond to the complete hyperbolic metric on the interior of $M$.
-Casson and Rivin separated gluing equations into a linear and non-linear part \cite{Casson-Rivin}.
-Angle structures is the linear part of Thurston's gluing equations, and what we will use to attain hyperbolicity of complements of augmented links in the thickened torus.
-
-\begin{define}
-Let $M$ be an orientable 3-manifold with boundary consisting of tori. An angle
-structure on an ideal triangulation $\tau$ of $M$ is an assignment of a dihedral
-angle to each edge of each tetrahedron, such that
-\begin{itemize}
-\item each tetrahedron is a non-degenerate angled ideal tetrahedron,
-\item around each edge of $\tau$, the dihedral angles sum to $2\pi$.
-\end{itemize}
-\end{define}
-
-\begin{theorem}\cite{Casson-Rivin}\label{thm:Casson-Rivin}
-Let $M$ be a 3-manifold admitting an angle structure. Then $M$ is hyperbolic.
-\end{theorem}
-
-For a hyperbolic link $K$ in $\torus \times I$, we produce sufficient conditions
-on augmentations such that the resulting link obtained from augmenting $K$ is
-hyperbolic. The idea is to start with a graph from the torihedral decomposition
-of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges
-\cite{CKP2}. Then by results of \cite{BandS} there exist a corresponding
-right-angled circle pattern. We then consider the augmented link $L$ and its
-torihedral decomposition from Proposition \ref{p:tori_decomp} with a
-corresponding ``degenerate" circle pattern. We deform this degenerate circle
-pattern into a ``proper" circle pattern which will give us a polyhedral
-decomposition of $(\torus \times I)-L$ with angles of the torihedra in our
-torihedral decomposition. Which we can further decompose into tetrahedra with
-angles satisfying conditions of an angle structure.
-
-\begin{define}
-We say an augmentation is \emph{right-augmented} if, when both strands are
-(locally) oriented such that they cross the augmentation disk in the same
-direction, the crossing is positive/a right-handed half-twist.
-See \figref{right_left_aug.png}.
-We say an augmentation is \emph{left-augmented} if it is not right-augmented.
-\begin{figure}
-\label{f:right_left_aug}
-\includegraphics{more_pictures/right_left_aug.png}
-\end{figure}
-\end{define}
-
-We can recover $L$ from the link diagram of $K$
-together with labels at vertices indicating left- or right-augmentation.
-
-\begin{theorem}
-Let $K$ be a weakly prime, alternating link whose diagram has no bigons.
-Let $L$ be a link obtained from augmenting $K$.
-Then $L$ is hyperbolic.
-\end{theorem}
-
-\begin{proof}
-By \cite[Theorem 7.5]{CKP2},
-(as discussed in \prpref{p:tori_decomp},)
-$\toruscomp{K}$ can be decomposed
-into two torihedra $\sT_T$ and $\sT_B$,
-whose graphs are $\Gamma_T(K), \Gamma_B(K)$;
-viewed from the top cone point $\torus \times \{1\}$,
-they are both the same as the projection graph of $K$.
-%which we denote by $\Gamma$.
-We make them non-degenerate angled torihedra by assigning $\theta^* = \pi/2$
-for all edges.
-
-We obtain an angle-splitting by applying the
-Feasible Flow theorem TODO as follows:
-Consider the directed graph whose vertex set is
-$E \cup F \cup \{\otimes\}$,
-where $E, F$ are the set of edges, faces in $\Gamma_T(K)$,
-and $\otimes$ is some abstract vertex.
-There is a directed edge
-\begin{itemize}
-\item $\otimes \to f$ for each face $f\in F$, with capacity interval
-	$[\pi, \infty)$,
-\item $f \to e$ for each edge $e \in \del f$,
-	with capacity interval $[\veps, \infty)$
-	for some $\veps>0$ to be set later,
-\item $e \to \otimes$ for each edge $e$, with capacity interval
-	$(-\infty, \pi/2]$.
-\end{itemize}
-By TODO lemma about $2|F'| \leq |E'|$,
-and taking $\veps < \pi / |\text{max face size}|$,
-the feasible flow condition is satisfied,
-so a feasible flow exists.
-Since $2|F| = |E|$, the capacity interval restrictions
-on the flow at $\otimes$ is sharp, so out-edges at $\otimes$
-have flow $\pi$ and in-edges at $\otimes$ have flow $\pi/2$.
-Then the flow $f \to e$ gives us $\vphi_{\vec{e}}$,
-where $f$ is the face to the left of $\vec{e}$.
-(we adapted this argument from \cite{BandS}).
-
-By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
-obtained by gluing two torihedra $\sT_T(L),\sT_B(L)$
-with graphs $\Gamma_T(L),\Gamma_B(L)$.
-We make them degenerate angled torihedra by assigning $\theta^*$'s
-to edges of the bow-ties as in \figref{f:bowtie_angles},
-and assign $\pi/2$ to all other edges.
-It is easy to check that upon gluing,
-each edge has sum of dihedral angles ($\theta^*$) equals $2\pi$.
-
-\begin{figure}
-\label{f:bowtie_angles}
-\includegraphics[width=5cm]{more_pictures/horizontal_bowtie.png}
-\end{figure}
-
-Furthermore, we can obtain an angle-splitting of $\sT_T(L)$
-(and similarly $\sT_B(L)$) by modifying the angle-splitting
-for $\sT_T(K)$;
-this is shown in \figref{TODO}.
-
-Now we have a decomposition of the two torihedra into
-degenerate base-angled pyramids.
-However, we need the pyramids to be non-degenerate,
-so we first need to modify the angles and graph on the torihedra
-to make all $\theta^*$ nonzero.
-
-Consider a face $f$ of $\Gamma_T(L)$ that is not in a bow-tie.
-Suppose the corresponding face $\bar{f}$ of $\Gamma$,
-the projection graph (which is equal to $\Gamma_T(K)$),
-had vertices $v_1,\ldots,v_n$ in counter-clockwise order.
-We label the edges of $f$ by $e_{i,0}$, $e_{i,\pi}$, or $e_i$,
-depending on whether the $\theta^*$ is $0$, $\pi$, or $\pi/2$ respectively,
-with $i$ non-decreasing from 1 to $n$,
-adjacent edges having the same $i$ if and only if they
-belong to the same bow-tie.
-For sake of concreteness,
-suppose that if a vertex $v_i$ is right-augmented,
-then the augmentation circle intersects $\bar{f}$
-(everything is similar if it is left-augmented vertices' circles
-that intersect $\bar{f}$).
-In other words, locally, $f$ meets two of the edges of the bow-tie
-corresponding to a right-augmented vertex $v_i$
-(which would be labeled $e_{i,0}, e_{i,\pi}$ in counter-clockwise order),
-but only meets one of the edges of the bow-tie corresponding to
-a left-augmented vertex.
-
-Suppose, after cyclically reindexing, $v_1,\ldots,v_k$
-is a maximally contiguous subsequence of left-augmented vertices
-of $G(K)$ around the face $\bar{f}$;
-the edges around $f$ would start
-$e_{1,0}, e_{1,\pi}, e_{2,0}, e_{2,\pi}, \ldots$.
-We add new edges across $f$ as follows.
-(See \figref{f:adding_edges}; the + and - signs will be explained later.)
-
-First suppose $k=n$; then we do nothing.
-
-Next suppose there is only one such maximal contiguous subsequence.
-If $k = 1$, we add an edge that goes across
-$e_{1,0},e_{1,\pi},e_2$
-(in the sense that the new edge separates the edges of $f$ into two sets
-one of them being those three edges;
-since $n\geq 3$, this edge is new).
-%If $k = 2$, we add edge across $e_{1,0},e_{1,\pi}$
-%and another edge across $e_{2,0},e_{2,\pi}$
-%(these two edges do not form a bigon because we've ruled out $k=n$).
-%(these two edges do not form a bigon because we've ruled out $k=n$).
-If $k \geq 2$,
-we add an edge across $e_{1,0},e_{1,\pi}$
-and another edge across $e_{2,0},e_{2,\pi},e_{3,0},\ldots,e_{k,\pi}$
-(these two edges do not form a bigon because we've ruled out $k=n$).
-%(again these two edges do not form a bigon).
-
-Finally, if there are multiple such maximal contiguous subsequences,
-we just add edges as above for each contiguous subsequence.
-The only caveat is that if the procedure calls to add a new edge
-that would form a bigon with the existing edges,
-we just don't add it.
-
-This way we obtain a new graph $\Gamma_T(L)'$, which defines a
-new torihedron $\sT_T(L)'$.
-We make it angled using the angles from $\sT_T(L)$ for old edges,
-and putting $\pi$ for all new edges.
-
-\begin{figure}
-\label{f:adding_edges}
-\includegraphics[width=5cm]{more_pictures/one_edge.png}
-%\includegraphics[width=5cm]{more_pictures/two_edge.png}
-\includegraphics[width=5cm]{more_pictures/two_edge_many.png}
-\end{figure}
-
-Now we deform the $\theta^*$ based on \figref{f:adding_edges},
-increasing/decreasing by some small $\veps' > 0$ if the edge
-is labeled $+/-$.
-Note some edges may be labeled twice, in which case we perform
-both increasing/decreasing (e.g. if it is labeled $+$ and $-$,
-the $\theta^*$ is not changed).
-It is easy to see that the sum of $\theta^*$ around a vertex
-remains unchanged.
-Furthermore, all the edges with $\theta^*$ originally equal 0,
-i.e. all $e_{i,0}$'s,
-now have positive $\theta^*$,
-(it receives only one label $+$,
-because the other face it meets is a bow-tie).
-
-Thus, we may now apply the feasible flow theorem in a similar manner,
-and obtain an angle-splitting for $\sT_T(L)'$.
-Alternatively, we can directly get an angle-splitting for $\sT_T(L)'$
-using the angle-splitting for $\sT_T(L)$.
-We reuse the $+/-$ assignments from \figref{f:adding_edges}.
-For $e = e_{i,0}$, we increase $\vphi_{\vec{e}}, \vphi_{\cev{e}}$
-by $\veps'/2$ each; for $e = e_{i,\pi}$,
-we decrease them by $\veps'/2$ each.
-For other edges, we increase/decrease $\vphi_{\vec{e}}$ by $\veps'$,
-where $\vec{e}$ is the oriented edge corresponding to the side
-on which the $+/-$ sign appears in \figref{f:adding_edges};
-so for example, if an edge $e$ receives both $+$ and $-$,
-then one of $\vphi_{\vec{e}},\vphi_{\cev{e}}$ increases
-while the other decreases, thus $\theta_e^*$ remains constant.
-
-Now we address $\sT_B(L)$.
-In the gluing of $\sT_T(L)$ to $\sT_B(L)$,
-non-bow-tie faces of $\Gamma_T(L)$ are identified with
-non-bow-tie faces of $\Gamma_B(L)$.
-Under this identification, we add the same edges to $\Gamma_B(L)$,
-thus obtaining the new torihedron $\sT_B(L)'$ with graph
-$\Gamma_B(L)'$.
-We perform the same deformations of $\theta^*$'s (or $\vphi$'s).
-
-We need to check that upon gluing $\sT_T(L)'$ to $\sT_B(L)'$,
-the sum of dihedral angles around each edge is still $2\pi$.
-This was clearly true before deforming, as the new edges of
-$\Gamma_T(L)'$ only gets identified with the unique
-corresponding edge of $\Gamma_B(L)'$, and they are both labeled
-with $\theta^* = \pi$.
-To see that the deformation does not change these sums,
-note that in the identification of faces of $\Gamma_T(L)'$
-to $\Gamma_B(L)'$,
-an edge with $\theta^*=0$ is identified with an edge with
-$\theta^*=\pi$,
-so an increase in the former would be conterbalanced by
-a decrease in the latter.
-It is also easy to see this is the case for the other edges.
-TODO hmm more detail?
-
-Finally, for each face of $\Gamma_T(L)'$ that has more than three sides,
-we arbitrarily decompose it into triangles
-and apply \lemref{l:pyramid_decomp}
-to obtain a triangulation of $sT_T(L)'$ into non-degenerate angled tetrahedra;
-perform the corresponding decomposition for faces of
-$\Gamma_B(L)'$ and obtain a triangulation of $\sT_B(L)'$
-into non-degenerate angled tetrahedra.
-Upon gluing, this gives an angle structure on the triangulation
-of $\toruscomp{L}$
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{From Extended Circle Patterns to polyhedra}
@@
 \end{proof}
-
-\bibliographystyle{plain}
-\bibliography{references-ak}
-
-\end{document}

### 2020-09-24 draft1.tex
added reference for feasible flow

@@
 
-The following theorem is quoted from \cite{BS}
-(TODO cite original too)
+The following theorem is quoted from \cite{BandS}
+(see also \cite{FF})
 
@@
 A \emph{feasible flow} is a function $\vphi : X \to \RR$
-such that Kirchhof's current law is satisfied
+such that $\vphi_x \in [a_x, b_x]$ and
+Kirchhof's current law is satisfied
 (i.e. flow in = flow out at every vertex).
@@
 and apply \lemref{l:pyramid_decomp}
-to obtain a triangulation of $sT_T(L)'$ into non-degenerate angled tetrahedra;
+to obtain a triangulation of $\sT_T(L)'$ into non-degenerate angled tetrahedra;
 perform the corresponding decomposition for faces of
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{From Extended Circle Patterns to polyhedra}
-
-In this section, we describe how to obtain a
-decomposition of a torihedron
-into hyperbolic ideal pyramids
-from a non-singular extended circle pattern.
-
-\begin{lemma}
-\label{l:circpattern_polyhedra}
-Suppose we have the graph of a torihedron.
-Given a non-singular extended circle pattern $c \in \CCC$ on the graph,
-such that all $\vphi_{\vec{e}} \in (0,\pi)$,
-there exists a decomposition of the torihedron
-into base-angled ideal pyramids (TODO make sure it's been defined) such that
-	\begin{itemize}
-		\item each interior edge of the torihedron has dihedral angles sum to $2\pi$;
-		\item each boundary edge $e$ of the torihedron has dihedral angles sum to
-			$\pi - \theta_e$.
-	\end{itemize}
-\end{lemma}
-
-\begin{proof}
-For each directed edge $\vec{e} \in \vec{E}$,
-construct the isosceles triangle $T_{\vec{e}}$
-with equal sides of length $r_{f_{\vec{e}}}$ and
-angle $2\tilde{\vphi}_{\vec{e}}$ subtended between them,
-where $\tilde{\vphi}_{\vec{e}} = \vphi_{\vec{e}}$
-if $\vphi_{\vec{e}}$ if it is acute,
-and = $\pi - \vphi_{\vec{e}}$ otherwise.
-
-\begin{figure}
-\includegraphics[width=8cm]{more_pictures/kite.png}
-\end{figure}
-\begin{figure}
-\includegraphics[width=5cm]{more_pictures/positive_angle.png}
-\includegraphics[width=5cm]{more_pictures/negative_angle.png}
-\end{figure}
-
-Let $f \in F$ be a face.
-We construct a Euclidean polygon $\Pol_f$ as follows.
-If $\vphi_{\vec{e}} \leq \pi/2$ for all $\vec{e} \in \del f$,
-i.e. if $f$ is convex, then 
-the $T_{\vec{e}}$ for $\vec{e}\in \del f$
-fit together into $\Pol_f$.
-If not, suppose $\vphi_{\vec{e}} > \pi/2$
-for $\vec{e} = \vec{e_1}$, 
-and $\leq \pi/2$ for $\vec{e} = \vec{e_2},\ldots \vec{e_k} \in \del f$.
-Then put $T_{\vec{e_2}},\ldots,T_{\vec{e_k}}$ together as above,
-creating a $(k+1)$-gon,
-then subtract $T_{\vec{e_1}}$ from it to form $\Pol_f$.
-
-Thus, to each face, we associate the Euclidean polygon $\Pol_f$.
-If $v$ is the vertex of $\Pol_f$ between $e_i$ and $e_{i+1}$,
-then the angle at $v$ is
-$\pi - \vphi_{\vec{e_i}} - \vphi_{\vec{e_{i+1}}}$.
-Then the non-vertex-singularity of $c$ guarantees that
-the sum of angles at $v$ of $\Pol_f$, for faces $f$ containing $v$,
-is $2\pi$.
-%; in other words, $\Pol_f$ glue along edges
-
-View the Euclidean plane as the boundary of the upper-half space.
-Then $\Pol_f$ supports an ideal hyperbolic pyramid $P_f$.
-
-Clearly, these $P_f$'s, as abstract ideal tetrahedra,
-glue together into the torihedron (TODO rephrase).
-%The hyperbolic structure on $P_f$
-%in particular provide dihedral angles to each edge of $P_f$
-%which clearly satisfies the conditions of making $P_f$
-%a base-angled ideal pyramid.
-We need to check that the angles around each edge of
-the torihedron have the appropriate angles.
-
-Consider an interior edge $e$ of the pyramidal decomposition
-of the torihedron.
-It corresponds to a vertex $v$ of the graph.
-Note that the dihedral angle of the vertical edge
-at $v$ of $P_f$ is simply the angle at $v$ of $\Pol_f$;
-these sum to $2\pi$ over $f \ni v$.
-
-For a boundary edge $e$, the dihedral angles at $e$ of the $P_f$'s
-containing it are $\vphi_{\vec{e}}$ and $\vphi_{\cev{e}}$,
-which sum to $\theta_e$ by definition.
-
-\end{proof}
+\input{circlepatterns}
 

### 2020-09-25 draft1.tex

@@
 
-Given a twist reduced diagram of a link $L$, {\it augmentation} is a process in which an unknotted circle component is added to one or more twist regions (a single crossing or a string of bigons) of $L$.
-Due to the added circle component we can remove full twists at the twist region of $L$.
-If the twist region has an odd number of crossings then all but one crossing is removed, whereas if the twist region has an even number of crossings then all are removed.
-The newly obtained link diagram is called an {\it augmented link diagram}.
-See Figure \ref{fig:Augmentations}.
+Given a twist reduced diagram of a link $L$, \emph{augmentating} is a process in
+which an unknotted circle component (augmentation) is added to one or
+more twist regions (a
+single crossing or a string of bigons) of $L$. Due to the added circle component
+we can remove full twists at the twist region of $L$. If the twist region has an
+odd number of crossings then all but one crossing is removed, whereas if the
+twist region has an even number of crossings then all are removed. The newly
+obtained link diagram is called an {\it augmented link diagram}. See Figure
+\ref{fig:Augmentations}.
 
-Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in $\Sp^3$ the link $L$ obtained by augmentation $K$ is hyperbolic.
-In this paper we investigate if this statement holds for links in the thickened torus i.e.
-if $L$ is a link obtained from augmenting a hyperbolic alternating link $K$ in the thickened torus.
-In this chapter we find many families of hyperbolic links in the thickened torus which remain hyperbolic after augmentation.
+Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in
+$\Sp^3$ the link $L$ obtained by augmentation $K$ is hyperbolic. In this paper
+we investigate if this statement holds for links in the thickened torus i.e. if
+$L$ is a link obtained from augmenting a hyperbolic alternating link $K$ in the
+thickened torus TODO Alice write.
  \begin{figure}
@@
 
-TODO check the feasible flow stuff.
+TODO remark on what splitting means in terms of ideal hyperbolic
 
@@
 
-For a hyperbolic link $K$ in $\torus \times I$, we produce sufficient conditions
-on augmentations such that the resulting link obtained from augmenting $K$ is
+For a hyperbolic link $K$ in $\torus \times I$, we show
+that the resulting link obtained from augmenting $K$ is
 hyperbolic. The idea is to start with a graph from the torihedral decomposition
 of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges
-\cite{CKP2}. Then by results of \cite{BandS} there exist a corresponding
-right-angled circle pattern. We then consider the augmented link $L$ and its
-torihedral decomposition from Proposition \ref{p:tori_decomp} with a
-corresponding ``degenerate" circle pattern. We deform this degenerate circle
-pattern into a ``proper" circle pattern which will give us a polyhedral
-decomposition of $(\torus \times I)-L$ with angles of the torihedra in our
-torihedral decomposition. Which we can further decompose into tetrahedra with
-angles satisfying conditions of an angle structure.
+\cite{CKP2},
+the angled torihedra can be further decomposed into base-angled pyramids.
+By \prpref{p:tori_decomp},
+there is a torihedral decomposition of the complement of the augmented link $L$.
+Using those angles,
+we then assign angles to edges of these torihedra
+and decompose them into base-angled pyramids.
+These pyramids can be further decomposed into tetrahedra,
+thus obtaining an angle structure on a triangulation.
 
@@
 \label{f:right_left_aug}
-\includegraphics{more_pictures/right_left_aug.png}
+\includegraphics[width=5cm]{more_pictures/right_left_aug.png}
 \end{figure}
@@
 (later we will choose which way to ``resolve'' the vertex).
-This decreases $chi(F')$ by one and $|E'|$ by 2.
+This decreases $\chi(F')$ by one and $|E'|$ by 2.
 However, this process may produce bigons;
 if it does, repeatedly eliminate bigons by either
-performing the modification as in \figref{TODO}
+(1) performing the modification as in \figref{TODO}
 if the two vertices of the bigon are distinct,
-or remove the bigon completely if the two vertices
+or (2) remove the bigon completely if the two vertices
 of the bigon are the same.
-Each of these steps also decreases $chi(F')$ by one and $|E'|$ by 2
+Each of these steps also decreases $\chi(F')$ by one and $|E'|$ by 2
 (note in the second case, after removing the bigon,
@@
 4-valency is maintained
-at each step, and obviously there will not be any bigons at the end.
+at each step, and there will not be any bigons at the end.
 We need to ensure that eliminating bigons does not
@@
 We perform some reductions.
-Remove all $f\in F'$ that have non-positive Euler characteristic,
-since having them only makes the inequality easier to prove.
+We remove all $f$ from $F'$ that have non-positive Euler characteristic,
+as doing so will not decrease $\chi(F')$ and will not increase $|E'|$.
 Now consider some $f\in F'$.
@@
 we can remove $f$ from $F'$,
-which decreases $chi(F')$ by 1 and $|E'|$ by at least 2.
+which decreases $\chi(F')$ by 1 and $|E'|$ by at least 2.
 Thus we remove all such $f$.
@@
 each $f$ corresponds to one boundary edge and two interior edges,
-but since the interior edges are shared by two faces,
+but, since the interior edges are shared by two faces,
 they should count as half an edge; so
@@
 \]
-and we are done.
+and we get the desired result.
 \end{proof}
@@
 into two torihedra $\sT_T$ and $\sT_B$,
-whose graphs are $\Gamma_T(K), \Gamma_B(K)$;
+whose graphs are $\Gamma_T(K), \Gamma_B(K)$ respectively;
 viewed from the top cone point $\torus \times \{1\}$,
@@
 
-Thus, we may now apply the feasible flow theorem in a similar manner,
-and obtain an angle-splitting for $\sT_T(L)'$.
-Alternatively, we can directly get an angle-splitting for $\sT_T(L)'$
+%Thus, we could attempt to apply the feasible flow theorem in a similar manner,
+%and obtain an angle-splitting for $\sT_T(L)'$, but 
+TODO rephrase nicely.
+We can directly get an angle-splitting for $\sT_T(L)'$
 using the angle-splitting for $\sT_T(L)$.

### 2020-09-26 draft1.tex
added abstract, some intro and some TODOs

@@
 \newcommand{\lemref}[1]{Lemma \ref{#1}}
-\newcommand{\figref}[1]{Figure \ref{#1}}
+%\newcommand{\ref}[1]{Figure \ref{#1}}
 \newcommand{\comment}[1]{}
@@
 \begin{abstract}
-  abstract goes here...
+For a hyperbolic link $K$ in the thickened torus, there is a decomposition of the complement
+of a link $L$, obtained from augmenting $K$, into torihedra. Then we further decompose 
+the torihedra into angled pyramids and finally angled tetrahedra. These fit into an angled structure 
+on a triangulation of the link complement, and thus by \cite{Casson-Rivin}, this shows
+that $L$ is hyperbolic.  
 \end{abstract}
@@
 
-Given a twist reduced diagram of a link $L$, \emph{augmentating} is a process in
+Given a twist reduced diagram of a link $K$, \emph{augmentating} is a process in
 which an unknotted circle component (augmentation) is added to one or
 more twist regions (a
-single crossing or a string of bigons) of $L$. Due to the added circle component
-we can remove full twists at the twist region of $L$. If the twist region has an
+single crossing or a string of bigons) of $K$. Due to the added circle component
+we can remove full twists at the twist region of $K$. If the twist region has an
 odd number of crossings then all but one crossing is removed, whereas if the
 twist region has an even number of crossings then all are removed. The newly
-obtained link diagram is called an {\it augmented link diagram}. See Figure
-\ref{fig:Augmentations}.
+obtained link is called an \emph{augmented link} and the newly obtained diagram 
+is called an \emph{augmented link diagram}. See Figure \ref{fig:Augmentations}.
 
@@
 $L$ is a link obtained from augmenting a hyperbolic alternating link $K$ in the
-thickened torus TODO Alice write.
+thickened torus. We define augmenting similarly for links in the thickened torus 
+with their associated link diagram on $\torus \times \{0\}.$
+
+Menasco \cite{Menasco} showed there are decompositions of the complements of 
+alternating links in $\Sp^3$ into two polyhedra, a top polyhedron and a bottom polyhedron. 
+For alternating links, $K$ in the thickened torus Champanerkar, Kofman and Purcell \cite{CKP2}
+showed that there is a decomposition of the complement of $K$ into objects called torihedra, which we think of 
+as counterparts of Menasco's decomposition of links in $\Sp^3$ into polyhedra, for links in the thickened 
+torus. Just like Menasco's decomposition, one can obtain a top and bottom torihedron. In section 2 we show that for augmented links in the thickened torus 
+one can also obtain a decomposition of the complement into a top and bottom torihedron.
+
  \begin{figure}
@@
 \section{Augmented Links}
- Champanerkar, Kofman and Purcell have studied alternating links in the thickened torus. They define a link in the thickened torus as a quotient of a biperiodic alternating link as follows,
+ Champanerkar, Kofman and Purcell have studied alternating links in the thickened torus \cite{CKP2}.
+They define a link in the thickened torus as a quotient of a biperiodic alternating link as follows,
 
-\begin{define}\cite{CKP2}
+\begin{define}
 \label{def:biperiodiclink}
@@
 
-\begin{figure} \centering \includegraphics[width=4cm]{crossingArc}
-\includegraphics[width=5cm]{crossingPush} \caption{Left: The black strands are
+\begin{figure} 
+\centering 
+\includegraphics[width=4cm]{crossingArc}
+\includegraphics[width=5cm]{crossingPush} 
+\caption{Left: The black strands are
 part of the link and the red strand is the crossing edge. Right: The blue and
 red edges represent the split crossing edges and the shaded half disk is bounded
-by the crossing circle} \label{fig:crossingArc} \end{figure}
+by the crossing circle} 
+\label{fig:crossingArc} 
+\end{figure}
 
@@
 The following figures is an example which decomposes the link (C) of Figure
-\ref{fig:Augmentations}.  \begin{figure}[h] \centering \includegraphics
-[height=3cm]{fig-3} \includegraphics [height=3cm]{fig-4} \caption{Each crossing
+\ref{fig:Augmentations}. 
+ \begin{figure}[h] 
+ \centering
+ \includegraphics
+[height=3cm]{fig-3}
+ \includegraphics [height=3cm]{fig-4}
+  \caption{Each crossing
 circle bounds a disk} \end{figure}
 
- \vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
- [height=3cm]{fig-5} \caption{We split the disk and collapse the arc of each
- crossing circle to ideal vertices} \end{figure}
+ \vspace*{-0.5cm} 
+ \begin{figure}[h] 
+ \centering 
+ \includegraphics
+ [height=3cm]{fig-5} 
+ \caption{We split the disk and collapse the arc of each
+ crossing circle to ideal vertices} 
+ \end{figure}
 
-	\vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
-	[height=3cm]{fig-6} \caption{Left: The crossing arc is the edge in red.
+\vspace*{-0.5cm} 
+\begin{figure}[h] 
+\centering 
+\includegraphics[height=3cm]{fig-6} 
+\caption{Left: The crossing arc is the edge in red.
 Middle: Picture of splitting the crossing edge. Right: The link component is
-	pushed off to infinity.} \end{figure}
+pushed off to infinity.} 
+\end{figure}
 
- \vspace*{-0.5cm} \begin{figure}[h] \centering \includegraphics
- [height=3cm]{top-bottom} \caption{
-	Left: The top torihedron.
-	Right: The bottom torihdron with rotation for face gluing.} \label{fig:top-bottom} \end{figure}
+ \vspace*{-0.5cm} 
+ \begin{figure}[h] 
+ \centering 
+ \includegraphics
+ [height=3cm]{top-bottom} 
+ \caption{Left: The top torihedron. Right: The bottom torihdron with rotation for face gluing.} 
+ \label{fig:top-bottom} \end{figure}
 
@@
 
-The proof is essentially given in \figref{f:ideal_pyramid_arg} below
+The proof is essentially given in Figure \ref{f:ideal_pyramid_arg}.
 
 \begin{figure}
+\includegraphics[height=8cm]{more_pictures/angle_split.png}
+\caption{Angle-splitting on a polygonal face of the graph}
 \label{f:ideal_pyramid_arg}
-\includegraphics[height=8cm]{more_pictures/angle_split.png}
 \end{figure}
+
 Suppose the edges are labeled $e_i$,
@@
 (locally) oriented such that they cross the augmentation disk in the same
-direction, the crossing is positive/a right-handed half-twist.
-See \figref{right_left_aug.png}.
+direction, the crossing is positive a right-handed half-twist.
+See Figure \ref{f:right_left_aug}.
 We say an augmentation is \emph{left-augmented} if it is not right-augmented.
+\end{define}
+
 \begin{figure}
+\includegraphics[width=5cm]{more_pictures/right_left_aug.png}
+\caption{R: right augmentation, L: left augmentation}
 \label{f:right_left_aug}
-\includegraphics[width=5cm]{more_pictures/right_left_aug.png}
 \end{figure}
-\end{define}
 
@@
 
+\begin{figure}
+\includegraphics[width=11cm]{bigon_crush}
+\caption{Resolving internal vertex; eliminating bigons via ``crushing"}
+\label{f:bigon_crush}
+\end{figure}
+
 \begin{proof}
@@
 Suppose there is an interior vertex $v$.
-Make the modification as in \figref{TODO}
+Make the modification as in Figure \ref{f:bigon_crush}
 (later we will choose which way to ``resolve'' the vertex).
@@
 if it does, repeatedly eliminate bigons by either
-(1) performing the modification as in \figref{TODO}
+(1) performing the modification as in Figure \ref{f:bigon_crush}
 if the two vertices of the bigon are distinct,
@@
 has two boundary edges, contradicting our reduction.
-%This would lead to the situation in \figref{TODO},
+%This would lead to the situation in \ref{},
 %showing that there is a face with at least
@@
 
+\begin{figure}
+\includegraphics[width=7cm]{more_pictures/horizontal_bowtie.png}
+\caption{Angle assignments on a bow-tie corresponding to an augmentation site}
+\label{f:bowtie_angles}
+\end{figure}
+
 By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
@@
 We make them degenerate angled torihedra by assigning $\theta^*$'s
-to edges of the bow-ties as in \figref{f:bowtie_angles},
+to edges of the bow-ties as in Figure \ref{f:bowtie_angles},
 and assign $\pi/2$ to all other edges.
@@
 
-\begin{figure}
-\label{f:bowtie_angles}
-\includegraphics[width=5cm]{more_pictures/horizontal_bowtie.png}
-\end{figure}
-
 Furthermore, we can obtain an angle-splitting of $\sT_T(L)$
@@
 for $\sT_T(K)$;
-this is shown in \figref{TODO}.
+this is shown in Figure \ref{f:bowtie_angles2}.
+
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width = 5cm]{before_bowtie_angles}&
+\includegraphics[width = 5cm]{bowtie_angles}\\
+(a)&(b)
+\end{tabular}
+\caption{(a) Angles before augmentation (b) Angle splitting for bowtie corresponding to augmentation}
+\label{f:bowtie_angles2}
+\end{figure}
 
@@
 We add new edges across $f$ as follows.
-(See \figref{f:adding_edges}; the + and - signs will be explained later.)
+(See Figure \ref{f:adding_edges}; the + and - signs will be explained later.)
 
@@
 \begin{figure}
-\label{f:adding_edges}
 \includegraphics[width=5cm]{more_pictures/one_edge.png}
@@
 \includegraphics[width=5cm]{more_pictures/two_edge_many.png}
+\caption{Red edge indicates an added edge to the graph to appropriately assign +/- labels which indicate 
+increasing/decreasing angles on the edge respectively.}
+\label{f:adding_edges}
 \end{figure}
 
-Now we deform the $\theta^*$ based on \figref{f:adding_edges},
+Now we deform the $\theta^*$ based on Figure \ref{f:adding_edges},
 increasing/decreasing by some small $\veps' > 0$ if the edge
@@
 using the angle-splitting for $\sT_T(L)$.
-We reuse the $+/-$ assignments from \figref{f:adding_edges}.
+We reuse the $+/-$ assignments from Figure \ref{f:adding_edges}.
 For $e = e_{i,0}$, we increase $\vphi_{\vec{e}}, \vphi_{\cev{e}}$
@@
 where $\vec{e}$ is the oriented edge corresponding to the side
-on which the $+/-$ sign appears in \figref{f:adding_edges};
+on which the $+/-$ sign appears in Figure \ref{f:adding_edges};
 so for example, if an edge $e$ receives both $+$ and $-$,

### 2020-09-27 notation.tex
ok.

@@
 
-We will mostly be working with extended circle patterns that ``looks normal",
+We will mostly be working with extended circle patterns that ``look normal",
 with all $\vphi_{\vec{e}}$ in the range $[0,\pi)$,
@@
 \begin{definition}
-Given some extended circle pattern $c \in \CCC$,
-we say a face $f$ is \emph{convex} if for all edges $\vec{e} \in \del f$,
+Let $f$ be a non-singular face (i.e. $\Phi_f = 2\pi$),
+such that for all edges $\vec{e} \in \del f$,
+$\vphi_{\vec{e}} \in [0,\pi)$.
+We say $f$ is \emph{thin} if
+exactly two edges of $f$ have nonzero $\vphi_\bullet$;
+we say it is \emph{thick} otherwise.
+We say it is \emph{convex} if for all edges $\vec{e} \in \del f$,
 we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
-We say $f$ is \emph{thin} if exactly two edges $\vec{e}, \vec{e'} \in \del f$
-have nonzero $\vphi_{\bullet}$, and furtheremore,
-	$0 < \vphi_{\vec{e}} = \pi - \vphi_{\vec{e'}} < \pi/2$.
 \end{definition}
 
-TODO figures for convex, thin faces
+%\begin{definition}
+%Given some extended circle pattern $c \in \CCC$,
+%we say a face $f$ is \emph{convex} if for all edges $\vec{e} \in \del f$,
+%we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
+%We say $f$ is \emph{thin} if exactly two edges $\vec{e}, \vec{e'} \in \del f$
+%have nonzero $\vphi_{\bullet}$, and furtheremore,
+%	$0 < \vphi_{\vec{e}} = \pi - \vphi_{\vec{e'}} < \pi/2$.
+%\end{definition}
+
+%TODO figures for convex, thin faces
 
@@
 Given an extended circle pattern $c\in \CCC$, an edge $e$ is \emph{short}
-if it has length 0, $l_{\vec{e}} = l_{\cev{e}} = 0$;
+if it has length 0, $l_e = 0$;
 it is \emph{long} otherwise.
@@
 \begin{definition}
-Given an extended circle pattern $c\in \CCC$, a \emph{thick path}
+Given an extended circle pattern $c\in \CCC$, a \emph{wide path}
 is a sequence of faces $f_0,f_1,\ldots,f_n$
 such that $f_i,f_{i+1}$ share a long edge.
-A \emph{thick cycle} is a thick path with $f_0 = f_n$.
+A \emph{wide cycle} is a wide path with $f_0 = f_n$.
 \end{definition}
 
-%\begin{definition}
-%A \emph{slit-convex circle pattern} is an extended cirlce pattern
-%$c \in \CCC$ such that all its faces are either convex or thin.
-%\end{definition}
-
 \begin{lemma}
-Let $c$ be an extended circle pattern whose faces are either
-convex or thin.
-Then $\CCC$ is a manifold in a neighborhood of $c$.
-\end{lemma}
-
-\begin{proof}
-$d(l_{\vec{e}} - l_{\cev{e}})
-= \sin \vphi_{\vec{e}} d r_{f_{\vec{e}}}
-+ r_{f_{\vec{e}}} \cos \vphi_{\vec{e}} d \vphi_{\vec{e}}
-- \sin \vphi_{\cev{e}} d r_{f_{\cev{e}}}
-- r_{f_{\cev{e}}} \cos \vphi_{\cev{e}} d \vphi_{\cev{e}}
-$,
-and since having only convex of thin faces implies
-$\cos \vphi_{\vec{e}} \neq 0$ for all $\vec{e}$,
-we see that the differentials $d(l_{\vec{e}} - l_{\cev{e}})$
-are linearly independent at $c$,
-hence are linearly independent in a neighborhood of $c$.
-%Thus, by the implicit function theorem,
-%$\CCC$ is a manifold in a neighborhood of $c$.
-\end{proof}
-
-\begin{lemma}
+\label{l:manifold_point}
 Let $c$ be a face non-singular extended circular pattern
 such that $\vphi_{\vec{e}} \geq 0$ for all $\vec{e}\in\vec{E}$.
-TODO no cycle of thin faces? It's a bit weaker than that...
+Furthermore, suppose that there is no cycle of edges
+$e_0, e_1, \ldots, e_n = e_0$ such that
+$e_i, e_{i+1}$ belong to the same face,
+and $\vphi_{\vec{e_i}} = \vphi_{\cev{e_i}} = \pi/2$.
 Then $\CCC$ is a manifold in a neighborhood of $c$.
@@
 then the $d\vphi_{\vec{e}}$ term makes $d(l_{\vec{e}} - l_{\cev{e}})$
-linearly independent from the rest;
+linearly independent from the rest
+(no other differential $d(l_{\vec{e'}} - l_{\cev{e'}})$
+contains such component);
 likewise for $\vphi_{\cev{e}} \neq \pi/2$.
-If both equal $\pi/2$,
-then $d(l_{\vec{e}} - l_{\cev{e}}) = d r_{\vec{e}} - d r_{\cev{e}}$.
-consider $f$ with $\vec{e} \in \del f$.
 
-By face non-singularity, $\sum_{\vec{e} \in f} \vphi_{\vec{e}} = \pi$,
-and since there are no bigon faces,
-
+Now consider the set $E'$ of edges $e$ that have
+$\vphi_{\vec{e}} = \vphi_{\cev{e}} = \pi/2$.
+Consider a maximal sequence of faces $f_0,\ldots,f_n$
+with no repetitions and $f_i,f_{i+1}$ share
+an edge $e_i \in E'$.
+By the condition on no cycles,
+$f_0 \neq f_n$.
+By face non-singularity, any face can meet at most two
+edges from $E'$, thus if $e\in E'$,
+it is contained in a unique such string of faces/edges.
+Thus the differentials
+$d(l_{\vec{e_i}} - l_{\cev{e_i}}) = dr_{f_i} - dr_{f_{i+1}}$
+are linearly independent.
 \end{proof}
@@
 
-Consider a vertex $v$ of the
+Consider a vertex $v$ of the TODO

### 2020-09-27 results.tex
progress.
ok.

@@
 tangent to the level sets of $\sum_{e\in E} \theta_e$.
-The following proposition proves it (avoid using `it'?) up to first order at a point:
+The following proposition proves it (TODO avoid using `it'?) up to first order at a point:
 
@@
 \label{p:point_lift}
-Let $c \in \CCC$ be an extended circle pattern such that
-\begin{itemize}
-	\item $\Phi_f = 2\pi$ for all $f\in F$;
-	\item all faces are eithe convex or thin,
-		with at least one convex face;
-	\item every pair of faces is connected by a thick path.
-\end{itemize}
+Let $c \in \CCC$ be a
+non-singular extended circle pattern on a graph
+with no bigons or self-loops such that
+there is no wide cycle of thin faces.
+%\begin{itemize}
+	%\item $\Phi_f = 2\pi$ for all $f\in F$;
+	%\item there is no wide cycle of thin faces.
+	%\item all faces are eithe convex or thin,
+		%with at least one convex face;
+	%\item every pair of faces is connected by a wide path.
+%\end{itemize}
 Let $K_c = \ker (\Phi_*|_c : T_c \CCC \to T_{\Phi(c)} \PPP)$.
@@
 being 0 if and only if $e$ is short,
-and because $\Phi_f = 2\pi$, atleast three edges are long.
+and because $\Phi_f = 2\pi$, at least three edges are long.
 So $\Phi_*(\alpha_f)$ is a negative multiple of $\ddd{\Phi_f}$;
@@
 \end{equation}
+
+If $f$ is thick but not convex,
+let $\vec{e}$ be an edge with largest $\vphi_{\vec{e}}$,
+so that $\vphi_{\vec{e}} \geq \pi/2$.
+If $\vphi_{\vec{e}} = \pi/2$,
+we can
 
@@
 
-In general, we consider a thick path of faces $f_0, \ldots, f_n$,
+In general, we consider a wide path of faces $f_0, \ldots, f_n$,
 such that all faces except $f_0$ and $f_n$ are thin,
@@
 Thus connectivity of $G_\llong$ follows from the
-thick-path-connectivity of faces.
+wide-path-connectivity of faces.
 
@@
 of alternating links
+
+TODO just use Feasible Flow Theorem (see BS)

### 2020-09-27 notation.tex
small change

@@
 
-We will mostly be working with extended circle patterns that ``look normal",
+We will mostly be working with extended circle patterns that ``look normal'',
 with all $\vphi_{\vec{e}}$ in the range $[0,\pi)$,
@@
 and suppose we added a new edge $e'$ so that $f$ is split into
-two faces $f'$ and $f"$, so that
+two faces $f'$ and $f''$, so that
 $\del f' = \{\vec{e_1},\ldots,\vec{e_k}, \vec{e'}\}$,
-and $\del f" = \{\cev{e'}, \vec{e_{k+1}},\ldots \vec{e_n}\}$.
+and $\del f'' = \{\cev{e'}, \vec{e_{k+1}},\ldots \vec{e_n}\}$.
 Then for the new extended circle pattern $c'$,
-we set $r_{f'}(c') = r_{f"}(c') = r_f(c)$,
+we set $r_{f'}(c') = r_{f''}(c') = r_f(c)$,
 $\vphi_{\vec{e'}} = \pi - \vphi_{\vec{e_1}} - \ldots - \vphi_{\vec{e_k}}$,

### 2020-09-27 results.tex
small change

@@
 for which we know an extended circle pattern exists
-(say from results of \ocite{BS}),
+(say from results of \cite{BandS}),
 and a path $\gamma$ in $\TTT$ starting at $\underline{\theta}$.
@@
 so that $\vphi_{\vec{e}} \geq \pi/2$.
+If $\vphi_{\vec{e}} > \pi/2$,
+then since $\tan$ is convex, and $f$ has at least two other
+long edges,
+we see that $\Phi_*(\alpha_f) = -\sum \frac{\tan \vphi_{\vec{e'}}}{r_f} > 0$,
+so we can define $\beta_f$ as in \eqnref{e:beta_f_convex}.
 If $\vphi_{\vec{e}} = \pi/2$,
-we can
+we can take
+\[
+\beta_f = \frac{1}{2} \ddd{\vphi_{\vec{e}}}
+\]
 
@@
 since the components sum to 0, so we need a different approach.
-First suppose $f$ shares an edge $e$ with a convex face $f'$,
+First suppose $f$ shares an edge $e$ with a thick face $f'$,
 with $\vec{e} \in \del f$.
-We can increase $l_e$
-by varying $\vphi_{\vec{e}},\vphi_{\cev{e}}$
-while holding $r_f,r_{f'}$ constant.
+If $\vphi_{\vec{e}} = \pi/2$, we can take
+$\beta_f = \frac{1}{2} \ddd{\vphi_{\vec{e}}}$ as before.
+Otherwise, we can increase $l_{\vec{e}}$
+by varying $\vphi_{\vec{e}}$
+while holding $r_f$ constant,
+and we can increase $l_{\cev{e}}$
+by increasing $r_{f'}$.
 This will affect both $\Phi_f, \Phi_{f'}$,
 so we use $\beta_{f'}$ to make $\Phi_{f'}$ constant.
-More explicitly, consider
-\begin{equation}
-\label{e:alpha_e}
-\alpha_e = \frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
-+ \frac{1}{2 r_{f'}\cos \vphi_{\cev{e}}} \ddd{\vphi_{\cev{e}}}
-\end{equation}
-which increases $l_{\vec{e}}, l_{\cev{e}}$ at half unit speed,
-$dl_{\vec{e}}(\alpha_e) = dl_{\cev{e}}(\alpha_e) = 1/2$.
-Then we can take
-\begin{equation}
-\label{e:beta_f_thin}
-\beta_f = r_f \cos \vphi_{\vec{e}}
-	(\alpha_e - \frac{1}{r_{f'} \cos \vphi_{\cev{e}}} \beta_{f'})
-\end{equation}
+%More explicitly, consider
+%\begin{equation}
+%\label{e:alpha_e}
+%\alpha_e = \frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
+%+ \frac{1}{2 r_{f'}\cos \vphi_{\cev{e}}} \ddd{\vphi_{\cev{e}}}
+%\end{equation}
+%which increases $l_{\vec{e}}, l_{\cev{e}}$ at half unit speed,
+%$dl_{\vec{e}}(\alpha_e) = dl_{\cev{e}}(\alpha_e) = 1/2$.
+%Then we can take
+%\begin{equation}
+%\label{e:beta_f_thin}
+%\beta_f = r_f \cos \vphi_{\vec{e}}
+	%(\alpha_e - \frac{1}{r_{f'} \cos \vphi_{\cev{e}}} \beta_{f'})
+%\end{equation}
 We can repeat this procedure with $f'$ set to this thin face,
 and $f$ set to another thin face adjacent to it, etc.
+\end{proof}
+
+\begin{proof}
+NEW PROOF NEW PROOF NEW PROOF NEW PROOF NEW PROOF NEW PROOF
+
 \end{proof}

### 2020-09-27 results.tex
small changes.

@@
 while holding $r_f$ constant,
-and we can increase $l_{\cev{e}}$
+and increase $l_{\cev{e}}$
 by increasing $r_{f'}$.
@@
 NEW PROOF NEW PROOF NEW PROOF NEW PROOF NEW PROOF NEW PROOF 
+We construct a vector $u_e \in K_c \subseteq T_c \CCC$ for each edge $e$
+and show that $\{\Theta_*(u_e)\}_{e\in E}$ spans an
+$|E|-1$ dimensional space,
+thus must be equal $L_{\Theta_c}$.
+$u_e$ will have the following property:
+if $\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$, then
+\begin{itemize}
+	\item $a^e = 1$;
+	\item $a^{e'} \leq 0$ for all $e' \neq e$;
+	%\item $a^{e'} = 0$ for short edges $e'$ (hmm...)
+	\item $\sum_{e' \in E} a^{e'} = 0$ (follows directly from $u_e \in K_c$)
+\end{itemize}
+
+To illustrate the main idea of the construction,
+first suppose that $e$ is an edge between two convex faces $f, f'$
+(so $\vec{e} \in \del f, \cev{e} \in \del f'$).
+Observe that %$\alpha_e$ from \eqnref{e:alpha_e}
+\begin{equation}
+\label{e:alpha_e}
+\alpha_e = \frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
++ \frac{1}{2 r_{f'}\cos \vphi_{\cev{e}}} \ddd{\vphi_{\cev{e}}}
+\end{equation}
+increases $\Phi_f$ and $\Phi_{f'}$.
+We can compensate using $\beta_f$ from \eqnref{e:beta_f_convex},
+so we consider
+\[
+w_e = \alpha_e - \frac{1}{\cos \vphi_{\vec{e}}} \beta_f
+	- \frac{1}{\cos \vphi_{\cev{e}}} \beta_{f'} \in K_c
+\]
+%Since $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$,
+%we need to show that the coefficients of $\ddd{\vphi_{\vec{e}}},
+%\ddd{\vphi_{\cev{e}}}$ sum to 0.
+For $\vec{e'} \in \del f \cup \del f' \backslash \{\vec{e},\cev{e}\}$,
+the $\ddd{\vphi_{\vec{e'}}}$ component only appears in $\beta_f$
+or $\beta_{f'}$, which is positive by construciton
+(this requires $f,f'$ to be convex faces);
+thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
+is equal 0 if and only if $e'$ is short.
+Finally, since $w_e \in K_c$, it leaves the sum $\sum_{e\in E} \theta_e$
+constant, so $d\theta_e(w_e) < 0$, so we can take
+\begin{equation}
+\label{e:u_e}
+u_e := (d\theta_e(w_e))^\inv \cdot w_e
+\end{equation}
 

### 2020-09-28 notation.tex
new new proof

@@
 A circle pattern is determined by the radius of the circle $C_f$ associated to each face, $r_f$,
-and the angle that each edge subtends in adjacent faces, $\vphi_{\vec{e}}$. (see figure TODO)
+and the angle that each edge subtends in adjacent faces, $\vphi_{\vec{e}}$.
+(See \figref{f:circle_pattern})
+\begin{figure}
+\includegraphics[width=5cm]{circle_pattern}
+\caption{Circle pattern in terms of radii $r_f$ and angles $\vphi_{\vec{e}}$}
+\label{f:circle_pattern}
+\end{figure}
 Thus determines, and is determined by a point in $\RRR \times \QQQ$, where
@@
 	\item $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$
-	\item $l_{\vec{e}} = r_{f_{\vec{e}}} \sin \vphi_{\vec{e}}$
+	\item $l_{\vec{e}} = 2 r_{f_{\vec{e}}} \sin \vphi_{\vec{e}}$
 \end{itemize}
@@
 $d(l_{\vec{e}} - l_{\cev{e}})
-= \sin \vphi_{\vec{e}} d r_{f_{\vec{e}}}
-+ r_{f_{\vec{e}}} \cos \vphi_{\vec{e}} d \vphi_{\vec{e}}
-- \sin \vphi_{\cev{e}} d r_{f_{\cev{e}}}
-- r_{f_{\cev{e}}} \cos \vphi_{\cev{e}} d \vphi_{\cev{e}}
+= 2\sin \vphi_{\vec{e}} d r_{f_{\vec{e}}}
++ 2r_{f_{\vec{e}}} \cos \vphi_{\vec{e}} d \vphi_{\vec{e}}
+- 2\sin \vphi_{\cev{e}} d r_{f_{\cev{e}}}
+- 2r_{f_{\cev{e}}} \cos \vphi_{\cev{e}} d \vphi_{\cev{e}}
 $
@@
 Thus the differentials
-$d(l_{\vec{e_i}} - l_{\cev{e_i}}) = dr_{f_i} - dr_{f_{i+1}}$
+$d(l_{\vec{e_i}} - l_{\cev{e_i}}) = 2dr_{f_i} - 2dr_{f_{i+1}}$
 are linearly independent.

### 2020-09-28 results.tex
new new proof

@@
 \end{equation}
-increases $\Phi_f$ and $\Phi_{f'}$.
+increases both $l_{\vec{e}}$ and $l_{\cev{e}}$ at the same rate,
+and has the side effect of
+increasing $\Phi_f$ and $\Phi_{f'}$.
 We can compensate using $\beta_f$ from \eqnref{e:beta_f_convex},
@@
 or $\beta_{f'}$, which is positive by construciton
-(this requires $f,f'$ to be convex faces);
+(because $f,f'$ are convex faces);
 thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
@@
 \end{equation}
+
+Next we consider the presence of thick faces that are not convex,
+but still assume there are no thin faces.
+Then a thick face as at most one edge with $\vphi_{\vec{e}} \geq \pi/2$.
+Suppose $\vec{e} \in \del f$, and $f$ is not convex.
+We want to increase $l_{\vec{e}}$ as before.
+If $f$ has no edges with $\vphi_\bullet = \pi/2$,
+then we consider
+\begin{equation}
+\gamma_f = \ddd{\vphi_{\vec{e}}} - \ddd{\vphi_{\vec{e'}}}
+\end{equation}
+where $e'$ is some other edge of $f$, such that
+$\max \{\vphi_{\vec{e}}, \vphi_{\vec{e'}}\} > \pi/2$.
+Because $\cos \vphi_{\vec{e}} \neq 0 \cos \vphi_{\vec{e'}}$,
+$\gamma_f$ affects both $l_{\vec{e}}$ and $l_{\vec{e'}}$
+(increasing or decreasing both simultaneously)
+while keeping $\Phi_f$ constant.
+This allows us to ``transfer'' the effect of increasing $l_{\vec{e}}$
+to $l_{\vec{e'}}$, in the following sense:
+if $e'$ is adjacent to another face $f''$ that is convex,
+then
+
+END NEW PROOF END NEW PROOF END NEW PROOF END NEW PROOF END NEW PROOF
+
+Let us first construct several other auxiliary vectors
+that are not necessarily in $T_c \CCC$.
+Generally they keep $\Phi_f$'s constant,
+but have an effect on the lengths of oriented edges $l_{\vec{e}}$.
+The $u_e$'s will be built from a combination of these.
+
+Let $f$ be a convex face, and $\vec{e} \in \del f$. Define
+\begin{equation}
+\label{e:eta_e}
+\eta_{\vec{e}} =
+\frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
+- \frac{1}{r_f \cos \vphi_{\vec{e}}} \beta_f
+\end{equation}
+$\eta_{\vec{e}}$ keeps $\Phi_f$ constant, but increases $l_{\vec{e}}$
+at unit speed, i.e. $dl_{\vec{e}}(\eta_{\vec{e}}) = 1$.
+
+Let $f$ be a thick but not convex face.
+There is exactly one edge $\vec{e} \in \del f$
+with $\vphi_{\vec{e}} \geq \pi/2$.
+If $\vphi_{\vec{e}} > \pi/2$, we will define
+$\eta_{\vec{e}}$ as in \eqnref{e:eta_e}.
+If $\vphi_{\vec{e}} = \pi/2$,
+we will define
+\begin{equation}
+\label{e:eta_e_2}
+\eta_{\vec{e}} = \frac{1}{2}\ddd{r_f}
++ (\sum_{\vec{e'} \neq \vec{e}}
+	\frac{\sin \vphi_{\vec{e'}}}{2 r_f \cos \vphi_{\vec{e'}}})
+	\ddd{\vphi_{\vec{e'}}}
+- \sum_{\vec{e'} \neq \vec{e}}
+	\frac{\sin \vphi_{\vec{e'}}}{2 r_f \cos \vphi_{\vec{e'}}}
+	\ddd{\vphi_{\vec{e'}}}
+\end{equation}
+Then it is easy to see that
+$dl_{\vec{e}}(\eta_{\vec{e}}) = 1$
+while
+$dl_{\vec{e'}}(\eta_{\vec{e}}) = 0$
+for all other $\vec{e'} \neq \vec{e}$,
+and $\eta_{\vec{e}}$ keeps $\Phi_f$ constant.
+
+Now let $\vec{e'} \in \del f$ be another edge.
+We define
+\begin{equation}
+\label{e:gamma_e}
+\gamma_{\vec{e'}} = \frac{1}{2 r_f \cos{\vphi_{\vec{e'}}}}
+	(\ddd{\vphi_{\vec{e'}}} - \ddd{\vphi_{\vec{e}}})
+\end{equation}
+Then $dl_{\vec{e'}} = 1$,
+$dl_{\vec{e}} = -\frac{\cos \vphi_{\vec{e}}}{\cos \vphi_{\vec{e'}}} \geq 0$,
+and keeps $\Phi_f$ constant.
+
+Finally, let $f$ be a thin face.
+If $\vec{e} \in \del f$ is a short edge,
+i.e. $\vphi_{\vec{e}} = 0$,
+then we define $\eta_{\vec{e}}$ as in \eqnref{e:eta_e}.
+If $\vec{e}$ is long, and $\vphi_{\vec{e}} \neq \pi/2$,
+we define $\gamma_{\vec{e}}$ as in \eqnref{e:gamma_e};
+if $\vphi_{\vec{e}} = \pi/2$, we define
+\begin{equation}
+\label{e:xi_e}
+\xi_{\vec{e}} = \frac{1}{2}\ddd{r_f}
+\end{equation}
+Clearly $dl_{\vec{e}}(\xi_{\vec{e}}) = dl_{\vec{e'}}(\xi_{\vec{e}}) = 1$
+for the other edge $e'$ with $\vphi_{\vec{e'}} = \pi/2$.
+%where $\vec{e'} \in \del f$ is the unique other long edge.
+
+In summary,
+$\eta_{\vec{e}}, \gamma_{\vec{e}}, \xi_{\vec{e}}$
+always increases $l_{\vec{e}}$ at unit speed,
+and keeps $\Phi_{f_{\vec{e}}}$ constant.
+$\eta_{\vec{e}}$ does not affect the lenghts of other edges
+in the face $f_{\vec{e}}$,
+but the other two might affect another edge
+- this other edge $\vec{e'}$ is unique,
+and $l_{\vec{e}}, l_{\vec{e'}}$ either both increase
+or decrease.
+Furthermore, $l_{\vec{e'}} \geq l_{\vec{e'}}$.
+
+For any oriented edge $\vec{e}$,
+there is exactly one such vector defined for it;
+call that vector $\zeta_{\vec{e}}$.
+
+Now we can put these vectors together to construct the desired $u_e$'s.
+To illustrate the main idea of the construction,
+first suppose that $e$ is an edge between two convex faces $f,f'$.
+Then we can consider
+\[
+w_e = \eta_{\vec{e}} + \eta_{\cev{e}}
+\]
+Since $dl_{\vec{e}}(w_e) = dl_{\cev{e}}(w_e) = 1$,
+and $dl_{\vec{e'}}(w_e) = 0$ for all other edges,
+$w_e \in T_c \CCC$;
+furthermore, $\eta_\bullet$ does not affect $\Phi_\bullet$,
+so $w_e \in K_c$.
+For $\vec{e'} \in \del f \cup \del f' \backslash \{\vec{e},\cev{e}\}$,
+the $\ddd{\vphi_{\vec{e'}}}$ component only appears in $\beta_f$
+or $\beta_{f'}$, which is positive by construciton
+(because $f,f'$ are convex faces);
+thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
+is equal 0 if and only if $e'$ is short.
+Finally, since $w_e \in K_c$, it leaves the sum $\sum_{e\in E} \theta_e$
+constant, so $d\theta_e(w_e) < 0$, so we can take
+\begin{equation}
+\label{e:u_e}
+u_e := (d\theta_e(w_e))^\inv \cdot w_e
+\end{equation}
+
+Now consider an arbitrary edge $e$ between faces $f,f'$.
+We build $u_e$ inductively, beginning with
+$w_e = \zeta_{\vec{e}} + \zeta_{\cev{e}}$,
+$F' = \{f, f'\}$, and $E' = \{e\}$.
+If $w_e$ also affects $l_{\vec{e'}}$ for some edge
+$\vec{e'} \in \del F' \backslash\{\vec{e''},\cev{e''} | e''\in E'\}$,
+we add an appriopriate positive multiple
+of $\zeta_{\cev{e'}}$ to $w_e$,
+add $f_{\cev{e'}}$ to $F'$,
+and add $e'$ to $E'$.
+Recall that when $\zeta_{\vec{e'}}$ affects
+the length of another edge $e''$,
+we always have $l_{\vec{e''}} \geq l_{\vec{e'}}$.
+Thus by the condition of non-existence of wide cycles of thin faces,
+this process must terminate.
+
+Now we need to check that
 

### 2020-09-28 results.tex
almost finished proof

@@
 thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
-is equal 0 if and only if $e'$ is short.
+is equal to 0 if and only if $e'$ is short.
 Finally, since $w_e \in K_c$, it leaves the sum $\sum_{e\in E} \theta_e$
@@
 
-Now we need to check that
+Now we need to check that $w_e$ has the right properties.
+First we assume that there are no thin faces.
+Then there is a sequence of thick faces
+$f_0 = f, f_1, \ldots, f_n$
+with edges $e_0 = e, e_1, \ldots, e_n$ between them
+(similar for $f_0 = f'$).
+Observe that the coefficient of $\ddd{\vphi_{\vec{e}}}$
+is positive in either $\eta_{\vec{e}}$ or $\gamma_{\vec{e}}$,
+so $d\theta_e(\Theta_*(w_e)) < 0$.
+Now consider $e_i$ for some $i$,
+and let $\vec{e_i} \in \del f_{i-1}, \cev{e_i} \in \del f_i$.
+Observe that since the $\gamma$ term from the previous edge
+affects the length of $e_i$,
+we must have $\vphi_{\vec{e_i}} > \pi/2$,
+and thus $\vphi_{\cev{e_i}} < \pi/2$.
+Then we see that $\Theta_*(w_e) > 0$
+by the following claim:
+consider an obtuse triangle
+with $\vphi_{\vec{e_i}}$,
+The coefficient of
 

### 2020-10-05 results.tex
almost done.

@@
 The $u_e$'s will be built from a combination of these.
+All discussion of changes will refer to changes in the first order.
 
@@
 \eta_{\vec{e}} = \frac{1}{2}\ddd{r_f}
-+ (\sum_{\vec{e'} \neq \vec{e}}
-	\frac{\sin \vphi_{\vec{e'}}}{2 r_f \cos \vphi_{\vec{e'}}})
-	\ddd{\vphi_{\vec{e'}}}
++ \big(\sum_{\vec{e'} \neq \vec{e}}
+	\frac{\sin \vphi_{\vec{e'}}}{2 r_f \cos \vphi_{\vec{e'}}}\big)
+	\ddd{\vphi_{\vec{e}}}
 - \sum_{\vec{e'} \neq \vec{e}}
@@
 $w_e \in T_c \CCC$;
-furthermore, $\eta_\bullet$ does not affect $\Phi_\bullet$,
+furthermore, $\eta_-$ does not affect $\Phi_-$,
 so $w_e \in K_c$.
@@
 this process must terminate.
+It is not hard to see that when an $\eta_-$ term appears,
+the process terminates (for that direction);
+a $\gamma_-$ term begets either another $\gamma_-$ or $\eta_-$ term;
+a $\xi_-$ term begets either
+a $\xi_-, \gamma_-$, or $\eta_-$ term.
+In other words, in the end we get some sum
+(ignoring possible positive coefficients)
+\[
+w_e = (\xi_- + \xi_- + \cdots + \gamma_- + \gamma_- + \cdots + \eta_-)
++ (\xi_- + \xi_- + \cdots + \gamma_- + \gamma_- + \cdots + \eta_-)
+\]
+where in each parenthesis,
+the first term affects the next term and so on.
 
-Now we need to check that $w_e$ has the right properties.
-First we assume that there are no thin faces.
-Then there is a sequence of thick faces
-$f_0 = f, f_1, \ldots, f_n$
-with edges $e_0 = e, e_1, \ldots, e_n$ between them
-(similar for $f_0 = f'$).
+Assume that there are no thin faces.
+We check that $w_e$ has the desired properties.
+By construction, $w_e \in T_c \CCC$.
 Observe that the coefficient of $\ddd{\vphi_{\vec{e}}}$
@@
 so $d\theta_e(\Theta_*(w_e)) < 0$.
-Now consider $e_i$ for some $i$,
-and let $\vec{e_i} \in \del f_{i-1}, \cev{e_i} \in \del f_i$.
-Observe that since the $\gamma$ term from the previous edge
-affects the length of $e_i$,
-we must have $\vphi_{\vec{e_i}} > \pi/2$,
-and thus $\vphi_{\cev{e_i}} < \pi/2$.
-Then we see that $\Theta_*(w_e) > 0$
-by the following claim:
-consider an obtuse triangle
-with $\vphi_{\vec{e_i}}$,
-The coefficient of
+There is a maximal sequence of thick faces
+$f_0 = f, f_1, \ldots, f_n$
+and a sequence of edges $e_0 = e, e_1, \ldots, e_n$,
+where for $i\neq 0$, $e_i$ is between $f_{i-1}$ and $f_i$,
+and $l_{e_i}$ increases under $w_e$;
+we label oriented edges so $\vec{e_i} \in \del f_i$,
+$\cev{e_i} \in \del f_{i+1}$.
+(Similar discussion for $f_0 = f'$).
+Consider one of the edges $e_i$, $i\neq 0$.
+Since $l_{e_i}$ increases, the $\zeta_{\vec{e}_{i-1}}$ term
+from the previous edge $e_{i-1}$ must have been
+$\gamma_{\vec{e}_{i-1}}$;
+in particular, $\vphi_{\cev{e_i}} > \pi/2$,
+$w_e$ decreases $\vphi_{\cev{e_i}}$,
+and keeps $r_{f_{i-1}}$ constant.
+The edge $e_i$ also contributes some $\zeta_{\vec{e_i}}$
+term to $w_e$;
+it increases $\vphi_{\vec{e_i}}$ and either increases
+or keeps constant $r_{f_i}$.
+Then $\theta_{e_i}$ increases, i.e. $d\theta_{e_i}(\Theta_*(w_e)) > 0$,
+by the following simple exercise in elementary Euclidean geometry.
+Suppose an obtuse triangle $\triangle ABC$, $\angle B > \pi/2$,
+and we decrease $\angle B$, increase $\angle C$,
+keep length of $\overline{AB}$ constant,
+and either increase or keeps constant the length of $\overline{AC}$;
+then $\angle A$ increases.
+This can be proved by observing that the changes we are forcing
+on the triangle can be broken in two:
+the first is increase $\angle B$ and keeping lengths
+$\overline{AB}, \overline{AC}$ constant,
+and the second is keeping $\angle B$ and length $\overline{AB}$ constant,
+and increasing length $\overline{AC}$;
+each of these increases $\angle A$.
+We apply this to our situation with $B,C$ being the centers of
+the centers of circles $C_{f_{i-1}}, C_{f_i}$
+of the faces $f_{i-1}, f_i$.
+
+Now we consider the preence of thin faces.
+If all the $\zeta_-$ terms added to $w_e$
+are $\eta_-$ or $\gamma_-$,
+then all arguments in the previous paragraph applies.
+The only situation in which $\xi_-$ is used
+is when either $\zeta_{\vec{e}}$ or $\zeta_{\cev{e}}$ is $\xi_-$.
 

### 2020-10-05 results.tex
hopefully done proof

@@
 \begin{proof}
-NEW PROOF NEW PROOF NEW PROOF NEW PROOF NEW PROOF NEW PROOF 
 We construct a vector $u_e \in K_c \subseteq T_c \CCC$ for each edge $e$
@@
 thus must be equal $L_{\Theta_c}$.
-$u_e$ will have the following property:
+The vectors $u_e$ will have the following property:
 if $\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$, then
@@
 
-To illustrate the main idea of the construction,
-first suppose that $e$ is an edge between two convex faces $f, f'$
-(so $\vec{e} \in \del f, \cev{e} \in \del f'$).
-Observe that %$\alpha_e$ from \eqnref{e:alpha_e}
-\begin{equation}
-\label{e:alpha_e}
-\alpha_e = \frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
-+ \frac{1}{2 r_{f'}\cos \vphi_{\cev{e}}} \ddd{\vphi_{\cev{e}}}
-\end{equation}
-increases both $l_{\vec{e}}$ and $l_{\cev{e}}$ at the same rate,
-and has the side effect of
-increasing $\Phi_f$ and $\Phi_{f'}$.
-We can compensate using $\beta_f$ from \eqnref{e:beta_f_convex},
-so we consider
-\[
-w_e = \alpha_e - \frac{1}{\cos \vphi_{\vec{e}}} \beta_f
-	- \frac{1}{\cos \vphi_{\cev{e}}} \beta_{f'} \in K_c
-\]
-%Since $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$,
-%we need to show that the coefficients of $\ddd{\vphi_{\vec{e}}},
-%\ddd{\vphi_{\cev{e}}}$ sum to 0.
-For $\vec{e'} \in \del f \cup \del f' \backslash \{\vec{e},\cev{e}\}$,
-the $\ddd{\vphi_{\vec{e'}}}$ component only appears in $\beta_f$
-or $\beta_{f'}$, which is positive by construciton
-(because $f,f'$ are convex faces);
-thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
-is equal to 0 if and only if $e'$ is short.
-Finally, since $w_e \in K_c$, it leaves the sum $\sum_{e\in E} \theta_e$
-constant, so $d\theta_e(w_e) < 0$, so we can take
-\begin{equation}
-\label{e:u_e}
-u_e := (d\theta_e(w_e))^\inv \cdot w_e
-\end{equation}
+Furthermore, these $u_e$'s collectively satisfy the following
+connectivity property:
+consider the graph $G$ whose vertex set is the set of edges $E$,
+and we connect two long edges $e,e'$ by an edge if there is some $e''$ such that
+$a^e, a^{e'}$ are both nonzero in $\Theta_*(u_{e''})$;
+then $G$ is connected.
 
-Next we consider the presence of thick faces that are not convex,
-but still assume there are no thin faces.
-Then a thick face as at most one edge with $\vphi_{\vec{e}} \geq \pi/2$.
-Suppose $\vec{e} \in \del f$, and $f$ is not convex.
-We want to increase $l_{\vec{e}}$ as before.
-If $f$ has no edges with $\vphi_\bullet = \pi/2$,
-then we consider
-\begin{equation}
-\gamma_f = \ddd{\vphi_{\vec{e}}} - \ddd{\vphi_{\vec{e'}}}
-\end{equation}
-where $e'$ is some other edge of $f$, such that
-$\max \{\vphi_{\vec{e}}, \vphi_{\vec{e'}}\} > \pi/2$.
-Because $\cos \vphi_{\vec{e}} \neq 0 \cos \vphi_{\vec{e'}}$,
-$\gamma_f$ affects both $l_{\vec{e}}$ and $l_{\vec{e'}}$
-(increasing or decreasing both simultaneously)
-while keeping $\Phi_f$ constant.
-This allows us to ``transfer'' the effect of increasing $l_{\vec{e}}$
-to $l_{\vec{e'}}$, in the following sense:
-if $e'$ is adjacent to another face $f''$ that is convex,
-then
+Let us first suppose we have constructed such $u_e$,
+and show that these properties ensure that
+$\{\Theta_*(u_e)\}_{e\in E}$ spans an $|E|-1$ dimensional space.
+This is a simple exercise in linear algebra,
+but we show it for completeness.
 
-END NEW PROOF END NEW PROOF END NEW PROOF END NEW PROOF END NEW PROOF
+Put the $\Theta_*(u_e)$'s into a $E \times E$ matrix,
+denoted $M$,
+so that the $e$-th row corresponds to $\Theta_*(u_e)$.
+By virtue of $u_e \in K_c$, we have that $(1\; 1\; \cdots \; 1)^T$
+is in the null space of $M$;
+our goal is to show that it spans the null space.
 
-Let us first construct several other auxiliary vectors
+Suppose $b = (b_e)^T$ is in the null space of $M$.
+Let $|b_e|$ be the largest among components of $b$;
+rescale $b$ so that $b_e = 1$.
+The $e$-th component of $M b$
+is $1 - \sum_{e' \neq e} a^{e'} b_{e'}$,
+where $a^{e'}$ are the components of $\Theta_*(u_e)$.
+Since $\sum_{e' \neq e} |a^{e'}| = 1$, this can be 0 if and only if
+for all $e'$ with $a^{e'} < 0$, we have exactly $b_{e'} = 1$.
+We then repeat this argument on the other $e'$
+that appear in $\Theta_*(u_e)$.
+By connectedness of $G$, this implies
+$b = (1 \; \cdots \; 1)^T$,
+thus $M$ has rank $|E|-1$.
+
+Before constructing the $u_e$'s,
+let us first construct several other auxiliary vectors
 that are not necessarily in $T_c \CCC$.
@@
 each of these increases $\angle A$.
-We apply this to our situation with $B,C$ being the centers of
+We apply this to our situation with $B,C$ being
 the centers of circles $C_{f_{i-1}}, C_{f_i}$
 of the faces $f_{i-1}, f_i$.
+As before, we simply rescale $w_e$ appropriately to obtain $u_e$.
 
-Now we consider the preence of thin faces.
+Now we consider the presence of thin faces.
 If all the $\zeta_-$ terms added to $w_e$
@@
 is when either $\zeta_{\vec{e}}$ or $\zeta_{\cev{e}}$ is $\xi_-$.
-
-\end{proof}
-
-\begin{proof}[Proof of \prpref{p:point_lift}]
-We construct a vector $u_e \in K_c \subseteq T_c \CCC$ for each edge $e$
-and show that $\{\Theta_*(u_e)\}_{e\in E}$ spans an
-$|E|-1$ dimensional space,
-thus must be equal $L_{\Theta_c}$.
-
-For long edges $e$, $u_e$ will have the following property:
-if $\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$, then
-\begin{itemize}
-	\item $a^e = 1$;
-	\item $a^{e'} \leq 0$ for all $e' \neq e$;
-	\item $a^{e'} = 0$ for short edges $e'$.
-	\item $\sum_{e' \in E} a^{e'} = 0$ (follows directly from $u_e \in K_c$)
-\end{itemize}
-Furthermore, these $u_e$'s collectively satisfy the following
-connectivity property:
-consider the graph $G_\llong$ whose vertex set is the set of long edges,
-and we connect two long edges $e,e'$ by an edge if there is some $e"$ such that
-$a^e, a^{e'}$ are both nonzero in $\Theta_*(u_{e"})$;
-then $G_\llong$ is connected.
-
-In addition, for short edges $e$,
-$u_e$ have the following property: again writing
-$\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$,
-one has
-\begin{itemize}
-	\item $a^e = 1$;
-	\item $a^{e'} = 0$ for other short edges $e'$.
-	\item $\sum_{e' \in E} a^{e'} = 0$ (follows directly from $u_e \in K_c$)
-\end{itemize}
-
-Let us first suppose we have constructed such $u_e$,
-and show that these properties ensure that
-$\{\Theta_*(u_e)\}_{e\in E}$ spans an $|E|-1$ dimensional space.
-This is a simple exercise in linear algebra,
-but we show it for completeness.
-
-Put the $\Theta_*(u_e)$'s into a $E \times E$ matrix,
-denoted $M$,
-so that the $e$-th row corresponds to $u_e$.
-By virtue of $u_e \in K_c$, we have that $(1\; 1\; \cdots \; 1)^T$
-is in the null space of $M$;
-our goal is to show that it spans the null space.
-
-Suppose $b = (b_e)^T$ is in the null space of $M$.
-Reorder $E$, if necessary, so that long edges come before
-short edges.
-Then by the last property of $u_e$'s for long edges,
-the top right block of long-by-short entries are 0.
-Thus the vector $b_\llong := (b_e)_{e \in \llong}^T$ is in the null space
-of the submatrix $M_\llong$ of long-by-long entries.
-
-Let $|b_e|$ be the largest among components of $b_\llong$;
-rescale $b$ so that $b_e = 1$.
-The $e$-th component of $M_\llong b_\llong$
-is $1 - \sum_{e' \neq e} a^{e'} b_{e'}$,
-where $a^{e'}$ are the components of $\Theta_*(u_e)$.
-Since $\sum_{e' \neq e} |a^{e'}| = 1$, this can be 0 if and only if
-for all $e'$ with $a^{e'} < 0$, we have exactly $b_{e'} = 1$.
-By connectedness of $G_\llong$, this implies
-$b_\llong = (1 \; \cdots \; 1)^T$.
-
-Returning to the full $M$, it is now easy to see that
-for a short edge $e$,
-by looking at the $e$-th row of $M$,
-we have $b_e = \sum a^{e'} = 1$,
-so we are done.
-
-%\footnote{
-%This is a well-known argument/result about graph Laplacians:
-%the first two properties of $u_e$'s ensure that
-%$-M_\llong^T$ is essentially a graph Laplacian for $G_\llong$,
-%so has rank = (\#vertices) - (\#components).}
-
-Now we construct the $u_e$'s.
-First suppose that $e$ is a long edge between two convex faces $f, f'$
-(so $\vec{e} \in \del f, \cev{e} \in \del f'$).
-Observe that $\alpha_e$ from \eqnref{e:alpha_e}
-increases $\Phi_f$ and $\Phi_{f'}$,
-and we can compensate using $\beta_f$ from \eqnref{e:beta_f_convex},
-so we consider
-\[
-w_e = \alpha_e - \frac{1}{\cos \vphi_{\vec{e}}} \beta_f
-	- \frac{1}{\cos \vphi_{\cev{e}}} \beta_{f'} \in K_c
-\]
-%Since $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$,
-%we need to show that the coefficients of $\ddd{\vphi_{\vec{e}}},
-%\ddd{\vphi_{\cev{e}}}$ sum to 0.
-For $\vec{e'} \in \del f \cup \del f' \backslash \{\vec{e},\cev{e}\}$,
-the $\ddd{\vphi_{\vec{e'}}}$ component only appears in $\beta_f$
-or $\beta_{f'}$, which is positive by construciton
-(this requires $f,f'$ to be convex faces);
-thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
-is equal to 0 if and only if $e'$ is short.
-Finally, since $w_e \in K_c$, it leaves the sum $\sum_{e\in E} \theta_e$
-constant, so $d\theta_e(w_e) < 0$, so we can take
-\begin{equation}
-\label{e:u_e}
-u_e := (d\theta_e(w_e))^\inv \cdot w_e
-\end{equation}
-
-In general, we consider a wide path of faces $f_0, \ldots, f_n$,
-such that all faces except $f_0$ and $f_n$ are thin,
-and $f_i$ are distinct except possibly $f_0 = f_n$.
-\footnote{Picture a closed accordian.}
-Let $e_i$ be the long edge between $f_i$ and $f_{i+1}$,
-and orient so that $\vec{e_i} \in \del f_i$, $\cev{e_i} \in \del f_{i+1}$.
-
-We will construct $u_{e_i}$ for $i = 1,\ldots,n$.
-
-We want to increase the lengths of $e_i$'s all together.
-Let $E' = \{\vec{e_i}, \cev{e_i} | i=0,1,\ldots,n-1\}$.
-Consider
-\[
-x :=
-\sum_{i=0,\ldots,n-1} \alpha_{e_i}
-=
-\sum_{\vec{e} \in E'}
-\frac{1}{2 r_{f_{\vec{e}}} \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
-%\sum_{\substack{i = 0,\ldots, n-1 \\ \vec{e} = \vec{e_i}, \cev{e_i} }}
-%\frac{1}{2 r_{f_0} \cos \vphi_{\vec{e_0}}} \ddd{\vphi_{\vec{e_0}}}
-%+
-%\frac{1}{2 r_{f_n} \cos \vphi_{\cev{e_{n-1}}}} \ddd{\vphi_{\cev{e_{n-1}}}}
-%+
-\]
-with $\alpha_e$ from \eqnref{e:alpha_e}.
-It is clear that $x$ increases all oriented $e_i$ lengths
-$l_{\vec{e}}$ equally fast,
-i.e. $dl_{\vec{e_i}}(x) = dl_{\cev{e_i}}(x) = 1/2$ for all $i$,
-so $x\in T_c \CCC$.
-It is also clear that for the thin faces $f_i$,
-$x$ makes one of the angles $\vphi_{\cev{e_{i-1}}}, \vphi_{\vec{e_i}}$
-increase and the other decrease, both at the same rate,
-thus $d\Phi_{f_i}(x) = 0$.
-However, the vector $x$ increase $\Phi_{f_0}$ and $\Phi_{f_n}$,
-so it is compensated using $\beta_f$'s, so that
-\[
-y := x - \frac{1}{r_{f_0} \cos \vphi_{\vec{e_0}}} \beta_{f_0}
-- \frac{1}{r_{f_n} \cos \vphi_{\cev{e_{n-1}}}} \beta_{f_n}
-\in K_c
-\]
-Before we modify $y$ to give the desired $u_{e_i}$,
-we note that for $\vec{e} \in (\cup \del f_i) \backslash E'$,
-the $\vphi_{\vec{e}}$-component in $y$ is non-positive,
-and is 0 if and only if $e$ is short;
-so $\Theta_*(-y)$ already satisfies three of the four properties
-desired in $\Theta_*(u_e)$.
-
-Recall that for thin face $f$,
-$\alpha_f$ from \eqnref{e:alpha_f} is in $K_c$,
-and we have
-\[
-\Theta_*(\frac{r_{f_i}}{\tan \vphi_{\vec{e_i}}} \alpha_{f_i}) = 
-	\ddd{\theta_{e_i}} - \ddd{\theta_{e_{i-1}}}
-\]
-Write $\bar{\alpha}_{f_i} = \frac{r_{f_i}}{\tan \vphi_{\vec{e_i}}} \alpha_{f_i}$.
-Then it is easy to see that using $\bar{\alpha}_{f_i}$'s, we can
-``push around" the $\theta_{e_i}$-components in $\Theta_*(y)$
-so only one is nonzero.
-More precisely, if
-$\Theta_*(y) = \sum_e y^e \ddd{\theta_e}$, the image under $\Theta_*$
-of the vector
-\[
-\bar{u}_{e_0} := y - y^{e_{n-1}} \bar{\alpha}_{f_{n-1}}
-- (y^{e_{n-2}} + y^{e_{n-1}}) \bar{\alpha}_{f_{n-2}}
-- \ldots
-- (y^{e_1} + \ldots + y^{e_{n-1}}) \bar{\alpha}_{f_1}
-\]
-would have $\theta_{e_i}$-components 0 for all $i$ except 0;
-for $i=0$, the $\theta_{e_0}$-component is now $y^{e_0} + \ldots + y^{e_{n-1}}$,
-which is nonzero because $\sum_{e'\in E} y^{e'} = 0$
-and $\sum_{e' \in E \backslash E'} y^{e'} > 0$.
-Therefore, we can take
-\[
-u_{e_0} := (d\theta_{e_0}(\bar{u}_{e_0}))^\inv \cdot \bar{u}_{e_0};
-\;\;\;
-u_{e_i} = u_{e_{i-1}} + \bar{\alpha}_{f_i}
-\]
-
-We still need to show the collective connectivity property of the $u_e$'s.
-It is easy to see that the long edges of a convex face
-are connected in $G_\llong$
-(for example, $u_{e_0}$ defined above clearly does it for
-$f_0$).
-Furthermore, all the $\Theta_*(u_{e_i})$ have most components equal,
-so $e_i$ are in the same connected component of $G_\llong$.
-Thus connectivity of $G_\llong$ follows from the
-wide-path-connectivity of faces.
-
-Finally, for short edges $e$, we simply define $u_e$
-as in \eqnref{e:u_e}
-(here we do not worry about whether faces are thin or convex,
-as the non-positivity condition of $a^{e'}$ is absent).
+Without loss of generality, $\zeta_{\vec{e}} = \xi_{\vec{e}}$,
+so that $\vec{e} \in \del f$, $f$ is a thin face with nonzero
+angles equal to $\pi/2$;
+let $\vec{e'}$ be the other edge with $\vphi$ angle $\pi/2$.
+Suppose the next face, the one adjacent to $e'$, is not thin.
+We simply add $\alpha \cdot (\ddd{\vec{e}} - \ddd{\vec{e'}})$
+to $w_e$,
+where $\alpha > 0$ is chosen small enough so that, in combination
+with the next $w_e$ term $\zeta_{\cev{e'}}$,
+$\theta_{e'}$ increases;
+for example, if the next term is $\zeta_{\cev{e'}} = \gamma_{\cev{e'}}$,
+then we choose $\alpha < \frac{1}{2r \cos \vphi_{\cev{e'}}}$,
+the coefficient of $\ddd{\vphi_{\cev{e'}}}$ in $\gamma_{\cev{e'}}$.
+If the next face is also thin,
+we add the same term, and so on, until we reach a non-thin face.
+It is straighforward to check that $\theta_e$ decreases,
+and all other affected $\theta_-$'s increase.
 \end{proof}

### 2020-10-05 circlepatterns.tex
done! hopefully...

@@
-\section{From Extended Circle Patterns to polyhedra}
+\section{Appendix}
 
+We provide an alternative method via circle patterns to obtain
+an angle-splitting of the torihedral decomposition
+in \secref{s:auglinks}.
+This guarantees that the resulting angle structure
+on the final triangulation
+also satisfies Thurston's gluing equations.
+Thus, one can obtian lower bounds on volume
+from these angles.
+
+Let $\Gamma$ be a graph on the torus $\torus$,
+and let $V,E,F$ be the set of vertices, edges, faces, respectively.
+Generally we assume that graphs do not have bigon faces
+nor self-loop edges.
+
+$\vec{E}$ is the set of oriented edges.
+We may identify an oriented edge $\vec{e}$ with the pair $(f_{\vec{e}}, e)$,
+where $f_{\vec{e}}$ is the face to the left of $\vec{e}$.
+
+When we use $\cev{e}$ to refer to an oriented edge, it refers to
+the oppositely oriented edge to $\vec{e}$.
+If we construct an expression with both $\vec{e}$ and $\cev{e}$,
+it will always be (anti-)symmetrical in the two orientations,
+and we assume that an arbitrary choice has been made.
+
+%===============================================================================
+
+Recall that a cirlce pattern for a graph $\Gamma$ is an arrangement of circles
+in $\torus$ such that each circle circumscribes a face of $\Gamma$.
+A circle pattern is determined by the radius of the circle $C_f$ associated to each face, $r_f$,
+and the angle that each edge subtends in adjacent faces, $\vphi_{\vec{e}}$.
+(See \figref{f:circle_pattern})
+\begin{figure}
+\includegraphics[width=8cm]{circle_pattern}
+\caption{Circle pattern in terms of radii $r_f$ and angles $\vphi_{\vec{e}}$}
+\label{f:circle_pattern}
+\end{figure}
+Thus determines, and is determined by a point in $\RRR \times \QQQ$, where
+
+\begin{itemize}
+	\item $\RRR := \RR_+^F = \{(r_f)_{f\in F} | r_f \in \RR_+\}$
+	\item $\QQQ := \RR^{\vec{E}} =
+		\{(\vphi_{\vec{e}})_{\vec{e} \in \vec{E}} | \vphi_{\vec{e}} \in \RR\}$
+\end{itemize}
+but clearly not every point $c\in \RRR \times \QQQ$ determines a circle pattern.
+This larger space allows us to consider
+``degenerate" circle patterns, where adjacent circles may
+be identical or tangent.
+
+On $\RRR \times \QQQ$, there are several functions to consider:
+\begin{itemize}
+	\item $\Phi_f = 2 \sum_{\vec{e} \in \del f} \vphi_{\vec{e}}$, measuring the cone angle
+		at the center of $C_f$
+	\item $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$
+	\item $l_{\vec{e}} = 2 r_{f_{\vec{e}}} \sin \vphi_{\vec{e}}$
+\end{itemize}
+
+These fit together to give maps to the following spaces:
+
+\begin{itemize}
+	\item $\PPP := \RR^F = \{(\Phi_f)_{f\in F} | \Phi_f \in \RR\}$
+	\item $\TTT := \RR^E = \{(\theta_e)_{e \in E} | \theta_e \in \RR\}$
+	\item $\LLL := \RR^{\vec{E}} = \{(l_{\vec{e}})_{\vec{e} \in E} | l_{\vec{e}} \in \RR\}$
+\end{itemize}
+
+\begin{define}
+Let $\Gamma$ be a graph on the torus.
+An \emph{extended circle pattern} on $\Gamma$ is
+$c = ((r_f), (\vphi_{\vec{e}})) \in \RRR \times \QQQ$
+such that $l_{\vec{e}} = l_{\cev{e}}$ for all edges $e\in E$. We denote by
+$\CCC$ the set of extended circle patterns.
+\end{define}
+
+\begin{tikzcd}
+\CCC = \{l_{\vec{e}} = l_{\cev{e}} \} \ar[r, "\subset"]
+	& \RRR \times \QQQ \ar[r, "\Theta"] \ar[d, "\Phi"]
+	& \TTT \\
+	& \PPP
+\end{tikzcd}
+
+The notion of circle pattern that is considered in \cite{BandS}
+would be restricted to those $c\in \CCC$
+with $\vphi_{\vec{e}} \in (0,\pi)$ and $\theta_e \in (0,\pi)$.
+They parametrize circle patterns by $(r_f)$ and $(\theta_e)$
+(or $(\theta_e^*)$),
+and call $(\vphi_{\vec{e}})$ a coherent angle system.
+One may consider deforming a circle pattern so as to have
+some $\theta_e$ approach 0 or $\pi$.
+The limit $\theta_e \to \pi$ is easy to picture, one simply gets that the two circles
+$C_f, C_{f'}$ of the adjacent faces become tangent. The limit $\theta_e \to 0$
+is a bit more complex, as the final shape of $Q_e$ (the quadrangle associated to $e$)
+may depend on $\vphi_{\vec{e}}$ or $\vphi_{\cev{e}}$.
+If we parametrize circle patterns by $(r_f)$ and $(\theta_e)$ as in \cite{BandS},
+the limiting shape would depend on the relationship between 
+$r_f$ and $r_{f'}$.
+As our main result depends on extending \cite{BandS} result
+to such limits and beyond,
+we find it more convenient to describe extended circle patterns by
+$(r_f)$ and $(\vphi_{\vec{e}})$.
+
+We will mostly be working with extended circle patterns that ``look normal'',
+with all $\vphi_{\vec{e}}$ in the range $[0,\pi)$,
+so we do not dwell on the meaning of negative $\vphi_{\vec{e}}$'s.
+\footnote{
+Intuitively, one can visualize decreasing $\vphi_{\vec{e}}$
+from $\veps$ to $-\veps$
+as moving the black vertices of the quadrangle $Q_e$ past each other,
+thus flipping $Q_e$ along its long axis
+and making it have negative area.
+}
+
+\begin{define}
+An extended circle pattern is said to be \emph{face non-singular}
+if $\Phi_f = 2\pi$ for all faces $f$; it is said to be \emph{vertex non-singular}
+if $\sum_{e \ni v} \theta_e = 2\pi$ for all vertices $v$.
+Finally it is said to be \emph{non-singular} if it is both.
+\end{define}
+
+\begin{define}
+Let $f$ be a non-singular face (i.e. $\Phi_f = 2\pi$),
+such that for all edges $\vec{e} \in \del f$,
+$\vphi_{\vec{e}} \in [0,\pi)$.
+We say $f$ is \emph{thin} if
+exactly two edges of $f$ have nonzero $\vphi_\bullet$;
+we say it is \emph{thick} otherwise.
+We say it is \emph{convex} if for all edges $\vec{e} \in \del f$,
+we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
+\end{define}
+
+%\begin{define}
+%Given some extended circle pattern $c \in \CCC$,
+%we say a face $f$ is \emph{convex} if for all edges $\vec{e} \in \del f$,
+%we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
+%We say $f$ is \emph{thin} if exactly two edges $\vec{e}, \vec{e'} \in \del f$
+%have nonzero $\vphi_{\bullet}$, and furtheremore,
+%	$0 < \vphi_{\vec{e}} = \pi - \vphi_{\vec{e'}} < \pi/2$.
+%\end{define}
+
+%figures for convex, thin faces
+
+\begin{define}
+Given an extended circle pattern $c\in \CCC$, an edge $e$ is \emph{short}
+if it has length 0, $l_e = 0$;
+it is \emph{long} otherwise.
+\end{define}
+
+\begin{define}
+Given an extended circle pattern $c\in \CCC$, a \emph{wide path}
+is a sequence of faces $f_0,f_1,\ldots,f_n$
+such that $f_i,f_{i+1}$ share a long edge.
+A \emph{wide cycle} is a wide path with $f_0 = f_n$.
+\end{define}
+
+\begin{lemma}
+\label{l:manifold_point}
+Let $c$ be a face non-singular extended circular pattern
+such that $\vphi_{\vec{e}} \geq 0$ for all $\vec{e}\in\vec{E}$.
+Furthermore, suppose that there is no cycle of edges
+$e_0, e_1, \ldots, e_n = e_0$ such that
+$e_i, e_{i+1}$ belong to the same face,
+and $\vphi_{\vec{e_i}} = \vphi_{\cev{e_i}} = \pi/2$.
+Then $\CCC$ is a manifold in a neighborhood of $c$.
+\end{lemma}
+\begin{proof}
+We need to show that the differentials
+$d(l_{\vec{e}} - l_{\cev{e}})
+= 2\sin \vphi_{\vec{e}} d r_{f_{\vec{e}}}
++ 2r_{f_{\vec{e}}} \cos \vphi_{\vec{e}} d \vphi_{\vec{e}}
+- 2\sin \vphi_{\cev{e}} d r_{f_{\cev{e}}}
+- 2r_{f_{\cev{e}}} \cos \vphi_{\cev{e}} d \vphi_{\cev{e}}
+$
+are linearly independent at $c$.
+If $\vphi_{\vec{e}} \neq \pi/2$,
+then the $d\vphi_{\vec{e}}$ term makes $d(l_{\vec{e}} - l_{\cev{e}})$
+linearly independent from the rest
+(no other differential $d(l_{\vec{e'}} - l_{\cev{e'}})$
+contains such component);
+likewise for $\vphi_{\cev{e}} \neq \pi/2$.
+
+Now consider the set $E'$ of edges $e$ that have
+$\vphi_{\vec{e}} = \vphi_{\cev{e}} = \pi/2$.
+Consider a maximal sequence of faces $f_0,\ldots,f_n$
+with no repetitions and $f_i,f_{i+1}$ share
+an edge $e_i \in E'$.
+By the condition on no cycles,
+$f_0 \neq f_n$.
+By face non-singularity, any face can meet at most two
+edges from $E'$, thus if $e\in E'$,
+it is contained in a unique such string of faces/edges.
+Thus the differentials
+$d(l_{\vec{e_i}} - l_{\cev{e_i}}) = 2dr_{f_i} - 2dr_{f_{i+1}}$
+are linearly independent.
+\end{proof}
+
+\subsection{From Extended Circle Patterns to Hyperbolic Polyhedra}
 In this section, we describe how to obtain a
-decomposition of a torihedron
-into hyperbolic ideal pyramids
+decomposition of a torihedron into hyperbolic ideal pyramids
 from a non-singular extended circle pattern.
@@
 there exists a decomposition of the torihedron
-into base-angled ideal pyramids (TODO make sure it's been defined) such that
+into base-angled ideal pyramids such that
 	\begin{itemize}
@@
 Clearly, these $P_f$'s, as abstract ideal tetrahedra,
-glue together into the torihedron (TODO rephrase).
+glue together into the torihedron.
 %The hyperbolic structure on $P_f$
@@
 \end{proof}
+
+\subsection{Deforming Extended Circle Patterns}
+
+Our general strategry for obtaining a (non-singular) circle pattern
+is to start with an assignment $\underline{\theta} = (\theta_\bullet)$
+for which we know an extended circle pattern exists
+(say from results of \cite{BandS}),
+and a path $\gamma$ in $\TTT$ starting at $\underline{\theta}$.
+We then attempt to lift $\gamma$ to a path $\tilde{\gamma}$ in $\CCC$,
+so that $\tilde{\gamma}$ remains (face) non-singular
+(vertex non-singularity is already determined by $\gamma$).
+
+Note that since $\sum_{e\in E} \theta_e
+= 2\pi |E| - \sum_{\vec{e} \in \vec{E}} \vphi_{\vec{e}}
+= 2\pi |E| - \sum_{f\in F} \Phi_f$,
+we see that maintaining face non-singularity of $\tilde{\gamma}$
+forces $\sum \theta_e$ to be constant.
+We will show that this is the only obstruction on $\gamma$
+to the lifting to such $\tilde{\gamma}$.
+
+To that end, let $L$ be the $(|E|-1)$-plane distribution on $\TTT$
+tangent to the level sets of $\sum_{e\in E} \theta_e$.
+The following proposition proves that we can deform
+some circle patterns up to first order at a point:
+
+\begin{prop}
+\label{p:point_lift}
+Let $c \in \CCC$ be a
+non-singular extended circle pattern on a graph
+with no bigons or self-loops such that
+there is no wide cycle of thin faces,
+and each edge meets two distinct faces.
+Let $K_c = \ker (\Phi_*|_c : T_c \CCC \to T_{\Phi(c)} \PPP)$.
+Then $\Theta_*(K_c) = L_{\Theta(c)}$.
+
+In other words, for any vector $a \in T_{\Theta(c)} \TTT$
+with sum of components 0, one can vary $c$ so that its
+first order change in $\theta_\bullet$ is $a$,
+and also remains face non-singular up to first order.
+\end{prop}
+
+Before we prove this, it is convenient to first prove the following,
+which will establish some useful notation:
+
+\begin{lemma}
+\label{l:Phi_full}
+Let $c \in \CCC$ be as in \prpref{p:point_lift}.
+Then $\Phi$ is a submersion in a neighbourhood of $c$.
+\end{lemma}
+
+\begin{proof}
+We construct vectors $\beta_f \in T_c \CCC$ so that
+$\Phi_*(\beta_f) = \ddd{\Phi_f}$.
+The vector
+\begin{equation}
+\label{e:alpha_f}
+\alpha_f := \ddd{r_f} - \sum_{\vec{e} \in \del f} 
+	\frac{\tan \vphi_{\vec{e}}}{r_f} \ddd{\vphi_{\vec{e}}}
+	\in T(\RRR \times \QQQ)
+\end{equation}
+doesn't change $l_{\vec{e}}$,
+so is in $T_c \CCC$.
+Intuitively, $\alpha_f$ is like
+pulling the center of $C_f$ up off the plane, increasing $r_f$ and decreasing all
+$\vphi$'s.
+Its pushforward under $\Phi$ is simply
+$\Phi_*(\alpha_f) =
+	(-\frac{2}{r_f} \sum_{\vec{e}\in \del f} \tan \vphi_{\vec{e}})
+	\ddd{\Phi_f}$.
+
+If $f$ is a convex face, then the $\tan \vphi_{\vec{e}}$ are all non-negative,
+being 0 if and only if $e$ is short,
+and because $\Phi_f = 2\pi$, at least three edges are long.
+So $\Phi_*(\alpha_f)$ is a negative multiple of $\ddd{\Phi_f}$;
+we choose $\beta$ so that
+\begin{equation}
+\label{e:beta_f_convex}
+\beta_f := \beta \cdot \alpha_f; \;\;\;
+\Phi_*(\beta_f) = \ddd{\Phi_f}
+\end{equation}
+
+If $f$ is thick but not convex,
+let $\vec{e}$ be an edge with largest $\vphi_{\vec{e}}$,
+so that $\vphi_{\vec{e}} \geq \pi/2$.
+If $\vphi_{\vec{e}} > \pi/2$,
+then since $\tan$ is convex, and $f$ has at least two other
+long edges,
+we see that $\Phi_*(\alpha_f) = -\sum \frac{\tan \vphi_{\vec{e'}}}{r_f} > 0$,
+so we can define $\beta_f$ as in \eqnref{e:beta_f_convex}.
+If $\vphi_{\vec{e}} = \pi/2$,
+we can take
+\[
+\beta_f = \frac{1}{2} \ddd{\vphi_{\vec{e}}}
+\]
+
+If $f$ is thin, we actually have that $\alpha_f \in K_c$,
+since the components sum to 0, so we need a different approach.
+First suppose $f$ shares an edge $e$ with a thick face $f'$,
+with $\vec{e} \in \del f$.
+If $\vphi_{\vec{e}} = \pi/2$, we can take
+$\beta_f = \frac{1}{2} \ddd{\vphi_{\vec{e}}}$ as before.
+Otherwise, we can increase $l_{\vec{e}}$
+by varying $\vphi_{\vec{e}}$
+while holding $r_f$ constant,
+and increase $l_{\cev{e}}$
+by increasing $r_{f'}$.
+This will affect both $\Phi_f, \Phi_{f'}$,
+so we use $\beta_{f'}$ to make $\Phi_{f'}$ constant.
+%More explicitly, consider
+%\begin{equation}
+%\label{e:alpha_e}
+%\alpha_e = \frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
+%+ \frac{1}{2 r_{f'}\cos \vphi_{\cev{e}}} \ddd{\vphi_{\cev{e}}}
+%\end{equation}
+%which increases $l_{\vec{e}}, l_{\cev{e}}$ at half unit speed,
+%$dl_{\vec{e}}(\alpha_e) = dl_{\cev{e}}(\alpha_e) = 1/2$.
+%Then we can take
+%\begin{equation}
+%\label{e:beta_f_thin}
+%\beta_f = r_f \cos \vphi_{\vec{e}}
+	%(\alpha_e - \frac{1}{r_{f'} \cos \vphi_{\cev{e}}} \beta_{f'})
+%\end{equation}
+We can repeat this procedure with $f'$ set to this thin face,
+and $f$ set to another thin face adjacent to it, etc.
+\end{proof}
+
+\begin{proof}
+We construct a vector $u_e \in K_c \subseteq T_c \CCC$ for each edge $e$
+and show that $\{\Theta_*(u_e)\}_{e\in E}$ spans an
+$|E|-1$ dimensional space,
+thus must be equal $L_{\Theta_c}$.
+The vectors $u_e$ will have the following property:
+if $\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$, then
+\begin{itemize}
+	\item $a^e = 1$;
+	\item $a^{e'} \leq 0$ for all $e' \neq e$;
+	%\item $a^{e'} = 0$ for short edges $e'$ (hmm...)
+	\item $\sum_{e' \in E} a^{e'} = 0$ (follows directly from $u_e \in K_c$)
+\end{itemize}
+
+Furthermore, these $u_e$'s collectively satisfy the following
+connectivity property:
+consider the graph $G$ whose vertex set is the set of edges $E$,
+and we connect two long edges $e,e'$ by an edge if there is some $e''$ such that
+$a^e, a^{e'}$ are both nonzero in $\Theta_*(u_{e''})$;
+then $G$ is connected.
+
+Let us first suppose we have constructed such $u_e$,
+and show that these properties ensure that
+$\{\Theta_*(u_e)\}_{e\in E}$ spans an $|E|-1$ dimensional space.
+This is a simple exercise in linear algebra,
+but we show it for completeness.
+
+Put the $\Theta_*(u_e)$'s into a $E \times E$ matrix,
+denoted $M$,
+so that the $e$-th row corresponds to $\Theta_*(u_e)$.
+By virtue of $u_e \in K_c$, we have that $(1\; 1\; \cdots \; 1)^T$
+is in the null space of $M$;
+our goal is to show that it spans the null space.
+
+Suppose $b = (b_e)^T$ is in the null space of $M$.
+Let $|b_e|$ be the largest among components of $b$;
+rescale $b$ so that $b_e = 1$.
+The $e$-th component of $M b$
+is $1 - \sum_{e' \neq e} a^{e'} b_{e'}$,
+where $a^{e'}$ are the components of $\Theta_*(u_e)$.
+Since $\sum_{e' \neq e} |a^{e'}| = 1$, this can be 0 if and only if
+for all $e'$ with $a^{e'} < 0$, we have exactly $b_{e'} = 1$.
+We then repeat this argument on the other $e'$
+that appear in $\Theta_*(u_e)$.
+By connectedness of $G$, this implies
+$b = (1 \; \cdots \; 1)^T$,
+thus $M$ has rank $|E|-1$.
+
+Before constructing the $u_e$'s,
+let us first construct several other auxiliary vectors
+that are not necessarily in $T_c \CCC$.
+Generally they keep $\Phi_f$'s constant,
+but have an effect on the lengths of oriented edges $l_{\vec{e}}$.
+The $u_e$'s will be built from a combination of these.
+All discussion of changes will refer to changes in the first order.
+
+Let $f$ be a convex face, and $\vec{e} \in \del f$. Define
+\begin{equation}
+\label{e:eta_e}
+\eta_{\vec{e}} =
+\frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
+- \frac{1}{r_f \cos \vphi_{\vec{e}}} \beta_f
+\end{equation}
+$\eta_{\vec{e}}$ keeps $\Phi_f$ constant, but increases $l_{\vec{e}}$
+at unit speed, i.e. $dl_{\vec{e}}(\eta_{\vec{e}}) = 1$.
+
+Let $f$ be a thick but not convex face.
+There is exactly one edge $\vec{e} \in \del f$
+with $\vphi_{\vec{e}} \geq \pi/2$.
+If $\vphi_{\vec{e}} > \pi/2$, we will define
+$\eta_{\vec{e}}$ as in \eqnref{e:eta_e}.
+If $\vphi_{\vec{e}} = \pi/2$,
+we will define
+\begin{equation}
+\label{e:eta_e_2}
+\eta_{\vec{e}} = \frac{1}{2}\ddd{r_f}
++ \big(\sum_{\vec{e'} \neq \vec{e}}
+	\frac{\sin \vphi_{\vec{e'}}}{2 r_f \cos \vphi_{\vec{e'}}}\big)
+	\ddd{\vphi_{\vec{e}}}
+- \sum_{\vec{e'} \neq \vec{e}}
+	\frac{\sin \vphi_{\vec{e'}}}{2 r_f \cos \vphi_{\vec{e'}}}
+	\ddd{\vphi_{\vec{e'}}}
+\end{equation}
+Then it is easy to see that
+$dl_{\vec{e}}(\eta_{\vec{e}}) = 1$
+while
+$dl_{\vec{e'}}(\eta_{\vec{e}}) = 0$
+for all other $\vec{e'} \neq \vec{e}$,
+and $\eta_{\vec{e}}$ keeps $\Phi_f$ constant.
+
+Now let $\vec{e'} \in \del f$ be another edge.
+We define
+\begin{equation}
+\label{e:gamma_e}
+\gamma_{\vec{e'}} = \frac{1}{2 r_f \cos{\vphi_{\vec{e'}}}}
+	(\ddd{\vphi_{\vec{e'}}} - \ddd{\vphi_{\vec{e}}})
+\end{equation}
+Then $dl_{\vec{e'}} = 1$,
+$dl_{\vec{e}} = -\frac{\cos \vphi_{\vec{e}}}{\cos \vphi_{\vec{e'}}} \geq 0$,
+and keeps $\Phi_f$ constant.
+
+Finally, let $f$ be a thin face.
+If $\vec{e} \in \del f$ is a short edge,
+i.e. $\vphi_{\vec{e}} = 0$,
+then we define $\eta_{\vec{e}}$ as in \eqnref{e:eta_e}.
+If $\vec{e}$ is long, and $\vphi_{\vec{e}} \neq \pi/2$,
+we define $\gamma_{\vec{e}}$ as in \eqnref{e:gamma_e};
+if $\vphi_{\vec{e}} = \pi/2$, we define
+\begin{equation}
+\label{e:xi_e}
+\xi_{\vec{e}} = \frac{1}{2}\ddd{r_f}
+\end{equation}
+Clearly $dl_{\vec{e}}(\xi_{\vec{e}}) = dl_{\vec{e'}}(\xi_{\vec{e}}) = 1$
+for the other edge $e'$ with $\vphi_{\vec{e'}} = \pi/2$.
+%where $\vec{e'} \in \del f$ is the unique other long edge.
+
+In summary,
+$\eta_{\vec{e}}, \gamma_{\vec{e}}, \xi_{\vec{e}}$
+always increases $l_{\vec{e}}$ at unit speed,
+and keeps $\Phi_{f_{\vec{e}}}$ constant.
+$\eta_{\vec{e}}$ does not affect the lenghts of other edges
+in the face $f_{\vec{e}}$,
+but the other two might affect another edge
+- this other edge $\vec{e'}$ is unique,
+and $l_{\vec{e}}, l_{\vec{e'}}$ either both increase
+or decrease.
+Furthermore, $l_{\vec{e'}} \geq l_{\vec{e'}}$.
+
+For any oriented edge $\vec{e}$,
+there is exactly one such vector defined for it;
+call that vector $\zeta_{\vec{e}}$.
+
+Now we can put these vectors together to construct the desired $u_e$'s.
+To illustrate the main idea of the construction,
+first suppose that $e$ is an edge between two convex faces $f,f'$.
+Then we can consider
+\[
+w_e = \eta_{\vec{e}} + \eta_{\cev{e}}
+\]
+Since $dl_{\vec{e}}(w_e) = dl_{\cev{e}}(w_e) = 1$,
+and $dl_{\vec{e'}}(w_e) = 0$ for all other edges,
+$w_e \in T_c \CCC$;
+furthermore, $\eta_-$ does not affect $\Phi_-$,
+so $w_e \in K_c$.
+For $\vec{e'} \in \del f \cup \del f' \backslash \{\vec{e},\cev{e}\}$,
+the $\ddd{\vphi_{\vec{e'}}}$ component only appears in $\beta_f$
+or $\beta_{f'}$, which is positive by construciton
+(because $f,f'$ are convex faces);
+thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
+is equal to 0 if and only if $e'$ is short.
+Finally, since $w_e \in K_c$, it leaves the sum $\sum_{e\in E} \theta_e$
+constant, so $d\theta_e(w_e) < 0$, so we can take
+\begin{equation}
+\label{e:u_e}
+u_e := (d\theta_e(w_e))^\inv \cdot w_e
+\end{equation}
+
+Now consider an arbitrary edge $e$ between faces $f,f'$.
+We build $u_e$ inductively, beginning with
+$w_e = \zeta_{\vec{e}} + \zeta_{\cev{e}}$,
+$F' = \{f, f'\}$, and $E' = \{e\}$.
+If $w_e$ also affects $l_{\vec{e'}}$ for some edge
+$\vec{e'} \in \del F' \backslash\{\vec{e''},\cev{e''} | e''\in E'\}$,
+we add an appriopriate positive multiple
+of $\zeta_{\cev{e'}}$ to $w_e$,
+add $f_{\cev{e'}}$ to $F'$,
+and add $e'$ to $E'$.
+Recall that when $\zeta_{\vec{e'}}$ affects
+the length of another edge $e''$,
+we always have $l_{\vec{e''}} \geq l_{\vec{e'}}$.
+Thus by the condition of non-existence of wide cycles of thin faces,
+this process must terminate.
+It is not hard to see that when an $\eta_-$ term appears,
+the process terminates (for that direction);
+a $\gamma_-$ term begets either another $\gamma_-$ or $\eta_-$ term;
+a $\xi_-$ term begets either
+a $\xi_-, \gamma_-$, or $\eta_-$ term.
+In other words, in the end we get some sum
+(ignoring possible positive coefficients)
+\[
+w_e = (\xi_- + \xi_- + \cdots + \gamma_- + \gamma_- + \cdots + \eta_-)
++ (\xi_- + \xi_- + \cdots + \gamma_- + \gamma_- + \cdots + \eta_-)
+\]
+where in each parenthesis,
+the first term affects the next term and so on.
+
+Assume that there are no thin faces.
+We check that $w_e$ has the desired properties.
+By construction, $w_e \in T_c \CCC$.
+Observe that the coefficient of $\ddd{\vphi_{\vec{e}}}$
+is positive in either $\eta_{\vec{e}}$ or $\gamma_{\vec{e}}$,
+so $d\theta_e(\Theta_*(w_e)) < 0$.
+There is a maximal sequence of thick faces
+$f_0 = f, f_1, \ldots, f_n$
+and a sequence of edges $e_0 = e, e_1, \ldots, e_n$,
+where for $i\neq 0$, $e_i$ is between $f_{i-1}$ and $f_i$,
+and $l_{e_i}$ increases under $w_e$;
+we label oriented edges so $\vec{e_i} \in \del f_i$,
+$\cev{e_i} \in \del f_{i+1}$.
+(Similar discussion for $f_0 = f'$).
+Consider one of the edges $e_i$, $i\neq 0$.
+Since $l_{e_i}$ increases, the $\zeta_{\vec{e}_{i-1}}$ term
+from the previous edge $e_{i-1}$ must have been
+$\gamma_{\vec{e}_{i-1}}$;
+in particular, $\vphi_{\cev{e_i}} > \pi/2$,
+$w_e$ decreases $\vphi_{\cev{e_i}}$,
+and keeps $r_{f_{i-1}}$ constant.
+The edge $e_i$ also contributes some $\zeta_{\vec{e_i}}$
+term to $w_e$;
+it increases $\vphi_{\vec{e_i}}$ and either increases
+or keeps constant $r_{f_i}$.
+Then $\theta_{e_i}$ increases, i.e. $d\theta_{e_i}(\Theta_*(w_e)) > 0$,
+by the following simple exercise in elementary Euclidean geometry.
+Suppose an obtuse triangle $\triangle ABC$, $\angle B > \pi/2$,
+and we decrease $\angle B$, increase $\angle C$,
+keep length of $\overline{AB}$ constant,
+and either increase or keeps constant the length of $\overline{AC}$;
+then $\angle A$ increases.
+This can be proved by observing that the changes we are forcing
+on the triangle can be broken in two:
+the first is increase $\angle B$ and keeping lengths
+$\overline{AB}, \overline{AC}$ constant,
+and the second is keeping $\angle B$ and length $\overline{AB}$ constant,
+and increasing length $\overline{AC}$;
+each of these increases $\angle A$.
+We apply this to our situation with $B,C$ being
+the centers of circles $C_{f_{i-1}}, C_{f_i}$
+of the faces $f_{i-1}, f_i$.
+As before, we simply rescale $w_e$ appropriately to obtain $u_e$.
+
+Now we consider the presence of thin faces.
+If all the $\zeta_-$ terms added to $w_e$
+are $\eta_-$ or $\gamma_-$,
+then all arguments in the previous paragraph applies.
+The only situation in which $\xi_-$ is used
+is when either $\zeta_{\vec{e}}$ or $\zeta_{\cev{e}}$ is $\xi_-$.
+Without loss of generality, $\zeta_{\vec{e}} = \xi_{\vec{e}}$,
+so that $\vec{e} \in \del f$, $f$ is a thin face with nonzero
+angles equal to $\pi/2$;
+let $\vec{e'}$ be the other edge with $\vphi$ angle $\pi/2$.
+Suppose the next face, the one adjacent to $e'$, is not thin.
+We simply add $\alpha \cdot (\ddd{\vec{e}} - \ddd{\vec{e'}})$
+to $w_e$,
+where $\alpha > 0$ is chosen small enough so that, in combination
+with the next $w_e$ term $\zeta_{\cev{e'}}$,
+$\theta_{e'}$ increases;
+for example, if the next term is $\zeta_{\cev{e'}} = \gamma_{\cev{e'}}$,
+then we choose $\alpha < \frac{1}{2r \cos \vphi_{\cev{e'}}}$,
+the coefficient of $\ddd{\vphi_{\cev{e'}}}$ in $\gamma_{\cev{e'}}$.
+If the next face is also thin,
+we add the same term, and so on, until we reach a non-thin face.
+It is straighforward to check that $\theta_e$ decreases,
+and all other affected $\theta_-$'s increase.
+\end{proof}
+
+\begin{prop}
+\label{p:nghd_lift}
+Let $c\in \CCC$ be as in \prpref{p:point_lift}.
+Given a smooth path $\gamma: [0,\infty) \to \TTT$
+starting at $\gamma(0) = \Theta(c)$
+and has constant value $(\sum \theta_e) \circ \gamma$,
+there exists $\veps > 0$ and a lift $\tilde{\gamma} :[0, \veps] \to \CCC$
+of $\gamma|_{[0,\veps]}$ along $\Theta$
+that starts at $\tilde{\gamma}(0) = c$
+and has constant value $\Phi \circ \tilde{\gamma}$.
+\end{prop}
+
+\begin{proof}
+By \lemref{l:Phi_full}, $\Phi$ is a submersion at $c$,
+hence is a submersion in a neighborhood $U \in \CCC$ of $c$.
+Thus, the kernels
+$K_{c'} = \ker(\Phi_*|{c'} : T_{c'} \CCC \to T_{\Phi(c')} \PPP)$
+form an $|E|$-plane distribution $K \subset T\CCC|_U$ over $U$.
+By \prpref{p:point_lift}, the bundle map
+$\Theta_*|_K : K \to L$ is full rank at $c$,
+hence it is full in a possibly smaller neighborhood,
+which we redefine $U$ to be.
+
+Since $\sum_{e \in E} \theta_e = 2\pi |E| - \sum_{f\in F} \Phi_f$,
+the fullness of $\Phi_*$ also shows that
+$\sum \theta$ has no critical points in $U$;
+for $s$ in some small interval around $(\sum \theta)(c)$,
+denote, by overloading notation,
+$L_s = (\sum \theta)^\inv (s)$,
+$U_s = U \cap \Theta^\inv(L_s)$.
+We may consider $K$ as a family of $|E|$-plane distributions
+$K_s$ over $U_s$.
+
+The vector $\rho := \sum_{f\in F} r_f \ddd{r_f}$ corresponds to
+scaling all radii by the same factor, and is clearly in $T\CCC$.
+It is obviously mapped to zero under $\Phi_*$ and $\Theta_*$,
+so $\Span\{\rho\} = \ker(\Theta_*|_K) \subset K$.
+Thus, over $U$, we may split
+$K = \Span\{\rho\} \oplus K'$
+(say as orthogonal decomposition w.r.t. some smooth metric on $\CCC$),
+so that $\Theta_*|{c'} : K'|_{c'} \simeq L_{\Theta(c')}$.
+
+In other words, $K'|_{U_s}$ is a horizontal $(|E|-1)$-plane distribution
+that determines an Ehresmann connection of the
+fibre bundle $U_s \to L_s$ (after being appropriately restricted).
+Therefore, a short path $\gamma$ starting at $\Theta(c)$
+with constant $\sum \theta$, i.e. a path in $L_s$, $s ={(\sum \theta)(c)}$,
+can be lifted to a path $\tilde{\gamma}$ in $U_s$,
+so that $\tilde{\gamma}$ is always tangent to $K'$,
+hence $\Phi(\tilde{\gamma})$ is constant.
+\end{proof}
+
+Finally let us say a few words in relation to the proof of hyperbolicity
+of augmented links, i.e. the proof of
+\thmref{t:auglink_hyp}.
+Using Theorem 4 from \cite{BandS},
+we obtain an angle-splitting for the $\pi/2$-angled
+torihedra in the torihedral decomposition
+of the original link $K$.
+This allows us to get a ``degenerate'' circle pattern
+for $\Gamma_T(L)$:
+an edge with label $\theta_e^* = \pi$
+separates a triangular face $t$ from a bowtie with a face $f$
+which corresponds to a face in the original graph $\Gamma_T(K)$;
+we will take the circumcircle of $t$ to be the same
+as that of $f$;
+an edge with $\theta_e^* = 0$
+then separates two circles that are tangent.
+Now we apply \prpref{p:nghd_lift},
+possibly adding some edges and
+using the $+$'s and $-$'s as in \figref{f:adding_edges},
+to obtain an extended circle pattern on $\Gamma_T(L)$
+that has all $\theta^* > 0$.
+By \lemref{l:circpattern_polyhedra},
+we obtain a decompositiion of the torihedron $\sT_T$
+into ideal hyperbolic pyramids.
+We do the same for the bottom torihedron $\sT_B$.
+Finally, as before, we can cut up these hyperbolic ideal pyramids
+into ideal tetrahedra,
+thus obtaining a hyperbolic triangulation of the link complement
+$\toruscomp{L}$.

### 2020-10-05 draft1.tex
done! hopefully...

@@
 \usepackage{graphicx, color,  subfigure, wrapfig, overpic}
+\usepackage{fullpage}
 %\usepackage[all,cmtip]{xy} 
-\usepackage{tikz}
+%\usepackage{tikz}
+\usepackage{tikz-cd}
 %\usepackage{mystyle}
@@
 \newcommand{\lemref}[1]{Lemma \ref{#1}}
+\newcommand{\figref}[1]{Figure \ref{#1}}
+\newcommand{\secref}[1]{Section \ref{#1}}
+\newcommand{\eqnref}[1]{(\ref{#1})}
 %\newcommand{\ref}[1]{Figure \ref{#1}}
 \newcommand{\comment}[1]{}
+\newcommand{\inv}{{-1}} % annoying to type {-1} when taking inverse
 
@@
 \section{Introduction}
+\label{s:intro}
 
@@
 For alternating links, $K$ in the thickened torus Champanerkar, Kofman and Purcell \cite{CKP2}
-showed that there is a decomposition of the complement of $K$ into objects called torihedra, which we think of 
+showed that there is a decomposition of the complement of $K$ into objects called torihedra,
+which we think of 
 as counterparts of Menasco's decomposition of links in $\Sp^3$ into polyhedra, for links in the thickened 
-torus. Just like Menasco's decomposition, one can obtain a top and bottom torihedron. In section 2 we show that for augmented links in the thickened torus 
+torus. Just like Menasco's decomposition, one can obtain a top and bottom torihedron.
+In \secref{s:auglinks} we show that for augmented links in the thickened torus 
 one can also obtain a decomposition of the complement into a top and bottom torihedron.
+In \secref{s:hyperbolicity}, we prove that augmented alternating links in the thickened torus
+are hyperbolic.
+In the Appendix, we provide an alternative proof to hyperbolicity of these links
+via circle patterns, which one could use obtain lower bounds for volume.
 
@@
 \section{Augmented Links}
- Champanerkar, Kofman and Purcell have studied alternating links in the thickened torus \cite{CKP2}.
-They define a link in the thickened torus as a quotient of a biperiodic alternating link as follows,
+\label{s:auglinks}
+
+Champanerkar, Kofman and Purcell have studied alternating links in the thickened torus \cite{CKP2}. They define a link in the thickened torus as a quotient of a biperiodic alternating link as follows,
 
@@
 \ref{fig:Augmentations}.
+
 \begin{figure}[h] 
 \centering
- \includegraphics
-[height=3cm]{fig-3}
- \includegraphics [height=3cm]{fig-4}
-  \caption{Each crossing
-circle bounds a disk} \end{figure}
+\includegraphics[height=3cm]{fig-3}
+\includegraphics[height=3cm]{fig-4}
+	\caption{Each crossing circle bounds a disk}
+\end{figure}
 
- \vspace*{-0.5cm} 
+%\vspace{-0.5cm} 
 \begin{figure}[h] 
 \centering 
- \includegraphics
- [height=3cm]{fig-5} 
+\includegraphics[height=3cm]{fig-5} 
 	\caption{We split the disk and collapse the arc of each
@@
 
-\vspace*{-0.5cm} 
 \begin{figure}[h] 
@@
 
- \vspace*{-0.5cm} 
 \begin{figure}[h] 
 \centering 
- \includegraphics
- [height=3cm]{top-bottom} 
+\includegraphics[height=3cm]{top-bottom} 
 	\caption{Left: The top torihedron. Right: The bottom torihdron with rotation for face gluing.} 
- \label{fig:top-bottom} \end{figure}
+\label{fig:top-bottom}
+\end{figure}
 
-\comment{
-\begin{remark}\label{cor:triangulation}
-The faces of one torihedron which do not correspond to a bow-tie glue to a
-corresponding face of the second torihedron to form bipyramids. One can add
-stellating edges, edges which have vertices corresponding to the different
-components of the Hopf link that cuts through the center of the face to
-decompose the bipyramids into tetrahedra. This process is called {\it
-stellation}. Stellating all the bipyramids of the decomposition obtained from
-Proposition \ref{p:tori_decomp} we obtained a triangulation of the
-complement of $L$ which is made up of {\it horizontal} edges (edges from the
-graph of the torihedra), {\it vertical} edges (edges from coning vertices of the
-the graph of the torihedra) and stellating edges.
-\end{remark}
-}
-
-\comment{
-\begin{proof}[Proof of Remark 2.7]
-Using the decomposition from Proposition
-\ref{p:tori_decomp} we can add a stellation edge whose end points
-are $\torus \times \{-1\}$ and $\torus \times \{1\}$ which cut through faces of $\torus \times I$ which do not come from the augmentation disks like in \cite{CKP2}.
-Since each face of the top torihedron gets glued to the bottom torihedron, we
-obtain bipyramids, and the stellation edge will decompose the bipyramids into
-tetrahedra. Then the link of the vertex  $\torus \times \{1\}$ or
-$\torus \times \{-1\}$ is the graph of the torihedron
-%$\torus \times [0,1)$ or
-%$\torus \times (-1,0]$ respectively.
-\end{proof}
-}
-
-TODO refer to BS about theta's
 \begin{definition}
@@
 
-TODO same as [BS] ``coherent angle system'' or something.
+\begin{remark}
+These $\theta$'s are related to the $\theta$'s in
+\cite{BandS},
+and the $\vphi$'s are related to their ``coherent angle system''.
+\end{remark}
 
-TODO remark on what splitting means in terms of ideal hyperbolic
+%TODO remark on what splitting means in terms of ideal hyperbolic
 
@@
 \section{Hyperbolicity of Augmented Links}
-Thurston introduced a method for finding the unique hyperbolic metric for a given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}.
-The idea was to triangulate the interior of $M$ into ideal tetrahedra and give those tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently in $M$.
-The shape parameter of a tetrahedron is described by the cross-ratio of its four vertices on the sphere at infinity.
-Thurston had written down a system of gluing equations with shape parameters whose solutions correspond to the complete hyperbolic metric on the interior of $M$.
-Casson and Rivin separated gluing equations into a linear and non-linear part \cite{Casson-Rivin}.
-Angle structures is the linear part of Thurston's gluing equations, and what we will use to attain hyperbolicity of complements of augmented links in the thickened torus.
+\label{s:hyperbolicity}
+Thurston introduced a method for finding the unique hyperbolic metric for a
+given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}. The idea
+was to triangulate the interior of $M$ into ideal tetrahedra and give those
+tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently
+in $M$. The shape parameter of a tetrahedron is described by the cross-ratio of
+its four vertices on the sphere at infinity. Thurston had written down a system
+of gluing equations with shape parameters whose solutions correspond to the
+complete hyperbolic metric on the interior of $M$. Casson and Rivin separated
+gluing equations into a linear and non-linear part \cite{Casson-Rivin}. Angle
+structures is the linear part of Thurston's gluing equations, and what we will
+use to attain hyperbolicity of complements of augmented links in the thickened
+torus.
 
@@
 thus obtaining an angle structure on a triangulation.
+In the Appendix, we show that this triangulation
+also has an angle structure that
+satisfies Thurston's gluing equations.
 
@@
 \begin{theorem}
+\label{t:auglink_hyp}
 Let $K$ be a weakly prime, alternating link whose diagram has no bigons.
@@
 %and obtain an angle-splitting for $\sT_T(L)'$, but 
-TODO rephrase nicely.
+%TODO rephrase nicely.
 We can directly get an angle-splitting for $\sT_T(L)'$
@@
 It is also easy to see this is the case for the other edges.
-TODO hmm more detail?
+%TODO hmm more detail?
 

### 2020-10-05 notation.tex
done! hopefully...

@@
 \begin{figure}
-\includegraphics[width=5cm]{circle_pattern}
+\includegraphics[width=8cm]{circle_pattern}
 \caption{Circle pattern in terms of radii $r_f$ and angles $\vphi_{\vec{e}}$}
@@
 
-[TODO Check this] The usual notion of circle pattern would be restricted to those $c\in \CCC$
+The notion of circle pattern that is considered in \cite{BandS}
+would be restricted to those $c\in \CCC$
 with $\vphi_{\vec{e}} \in (0,\pi)$ and $\theta_e \in (0,\pi)$.
-One may consider deforming a circle pattern so as to have some $\theta_e$ approach 0 or $\pi$.
+They parametrize circle patterns by $(r_f)$ and $(\theta_e)$
+(or $(\theta_e^*)$),
+and call $(\vphi_{\vec{e}})$ a coherent angle system.
+One may consider deforming a circle pattern so as to have
+some $\theta_e$ approach 0 or $\pi$.
 The limit $\theta_e \to \pi$ is easy to picture, one simply gets that the two circles
@@
 may depend on $\vphi_{\vec{e}}$ or $\vphi_{\cev{e}}$.
-If we parametrize circle patterns by $(r_f)$ and $(\theta_e)$ as in TODO \ocite{BS},
+If we parametrize circle patterns by $(r_f)$ and $(\theta_e)$ as in \cite{BandS},
 the limiting shape would depend on the relationship between 
@@
 
-TODO non-degenerate circle pattern?
-
 \begin{definition}
@@
 
-%TODO figures for convex, thin faces
+%figures for convex, thin faces
 
@@
 \end{proof}
-
-\subsection{Modifications to Extended Circle Patterns}
-
-Let $\Gamma$ be a graph on the torus, and let $c$ be a
-non-singular extended circle pattern on $\Gamma$.
-There are two simple operations to modify $\Gamma$:
-cutting a face along a new edge,
-and splitting a vertex in two then joining them by a new edge.
-We describe how to associate an extended circle pattern $c'$ to
-the new graph.
-
-Cutting a face: Consider a face $f$,
-and suppose we added a new edge $e'$ so that $f$ is split into
-two faces $f'$ and $f''$, so that
-$\del f' = \{\vec{e_1},\ldots,\vec{e_k}, \vec{e'}\}$,
-and $\del f'' = \{\cev{e'}, \vec{e_{k+1}},\ldots \vec{e_n}\}$.
-Then for the new extended circle pattern $c'$,
-we set $r_{f'}(c') = r_{f''}(c') = r_f(c)$,
-$\vphi_{\vec{e'}} = \pi - \vphi_{\vec{e_1}} - \ldots - \vphi_{\vec{e_k}}$,
-$\vphi_{\cev{e'}} = \pi - \vphi_{\vec{e_{k+1}}} - \ldots \vphi_{\vec{e_n}}$,
-and $r_\bullet(c') = r_\bullet(c)$, $\vphi_\bullet(c') = \vphi_\bullet(c)$
-for all other faces, edges.
-It is straightforward to check that $c'$ is non-singular.
-
-Consider a vertex $v$ of the TODO

### 2020-10-05 results.tex
done! hopefully...

@@
 
-TODO: make a list of images of vectors, e.g.
-$\Theta_*(\ddd{\vphi_{\vec{e}}}) = -\ddd{\theta_e}$.
+%TODO: make a list of images of vectors, e.g.
+%$\Theta_*(\ddd{\vphi_{\vec{e}}}) = -\ddd{\theta_e}$.
 
@@
 tangent to the level sets of $\sum_{e\in E} \theta_e$.
-The following proposition proves it (TODO avoid using `it'?) up to first order at a point:
+The following proposition proves that we can deform
+some circle patterns up to first order at a point:
 
@@
 with no bigons or self-loops such that
-there is no wide cycle of thin faces.
-%\begin{itemize}
-	%\item $\Phi_f = 2\pi$ for all $f\in F$;
-	%\item there is no wide cycle of thin faces.
-	%\item all faces are eithe convex or thin,
-		%with at least one convex face;
-	%\item every pair of faces is connected by a wide path.
-%\end{itemize}
+there is no wide cycle of thin faces,
+and each edge meets two distinct faces.
 Let $K_c = \ker (\Phi_*|_c : T_c \CCC \to T_{\Phi(c)} \PPP)$.
@@
 \end{proof}
-
-%===============================================================================
-
-TODO
-Note: no face can have its edges glued together; prevented by fact
-of alternating links
-
-TODO just use Feasible Flow Theorem (see BS)

### 2020-10-05 draft1.tex
changed title
added remark on allowing twist regions

@@
 \newcommand{\secref}[1]{Section \ref{#1}}
+\newcommand{\remref}[1]{Remark \ref{#1}}
 \newcommand{\eqnref}[1]{(\ref{#1})}
@@
 
-\title [Augmented Links in the Thickened Torus] {Augmented Links in the Thickened Torus}
+\title{Hyperbolicity of Augmented Links in the Thickened Torus}
 
@@
 each edge has sum of dihedral angles ($\theta^*$) equals $2\pi$.
+(This holds true even if they were glued assuming
+some augmentations had no half-twist; see \remref{r:nohalftwist}.)
 
@@
 new torihedron $\sT_T(L)'$.
-We make it angled using the angles from $\sT_T(L)$ for old edges,
+We make $\sT_T(L)'$ angled using the angles from $\sT_T(L)$ for old edges,
 and putting $\pi$ for all new edges.
@@
 It is also easy to see this is the case for the other edges.
-%TODO hmm more detail?
+(Once again, a similar argument applies if $\sT_(L)'$
+and $\sT_B(L)'$ are glued assuming
+some augmentations had no half-twist; see \remref{r:nohalftwist}.)
 
@@
 
+\begin{remark}
+\label{r:nohalftwist}
+If the original link $K$ had some twist regions with at least one bigon,
+we may consider augmentations $L$ where all such twist regions
+are augmented.
+Then, as pointed out in proof of \thmref{t:auglink_hyp} above,
+the proof still works for $L$, showing that $L$ is also hyperbolic.
+\end{remark}
+
 \input{circlepatterns}

### 2020-10-05 draft1.tex
made minor grammatical corrections

@@
 \begin{abstract}
-For a hyperbolic link $K$ in the thickened torus, there is a decomposition of the complement
-of a link $L$, obtained from augmenting $K$, into torihedra. Then we further decompose 
+For a hyperbolic link $K$ in the thickened torus, We show there is a decomposition of the complement
+of a link $L$, obtained from augmenting $K$, into torihedra. We further decompose 
 the torihedra into angled pyramids and finally angled tetrahedra. These fit into an angled structure 
@@
 Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in
-$\Sp^3$ the link $L$ obtained by augmentation $K$ is hyperbolic. In this paper
+$\Sp^3$ the link $L$ obtained by augmentating $K$ is hyperbolic. In this paper
 we investigate if this statement holds for links in the thickened torus i.e. if
@@
 which we think of 
-as counterparts of Menasco's decomposition of links in $\Sp^3$ into polyhedra, for links in the thickened 
-torus. Just like Menasco's decomposition, one can obtain a top and bottom torihedron.
+as counterparts to Menasco's decomposition of links in $\Sp^3$ into polyhedra, for links in the thickened 
+torus. Just like Menasco's decomposition, one can obtain a top and a bottom torihedron.
 In \secref{s:auglinks} we show that for augmented links in the thickened torus 
@@
 In the Appendix, we provide an alternative proof to hyperbolicity of these links
-via circle patterns, which one could use obtain lower bounds for volume.
+via circle patterns, which one could use to obtain lower bounds for volume.
 
@@
 For a link in $\torus \times I$, the crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
-Let $L$ be a twist reduced diagram in $\torus \times I$, we define {\it augmentation} as a process in which an unknotted circle component is added to one or more twist regions of $L$.
+Let $L$ be a twist reduced diagram in $\torus \times I$, we define {\it augmentating} as a process in which an unknotted circle component is added to one or more twist regions of $L$.
 See Figure \ref{fig:Augmentations}
@@
 We show a method of decomposing an augmented link in the thickened torus into
-two torihedra. The idea is to combine methods of Menasco
+two objects called torihedra. The idea is to combine methods of Menasco
 \cite{Menasco} and the use of crossing edges between each crossing of our link
@@
 \begin{proof}
-We will begin by assuming that there are no half twists and then
-arrange the link diagram of $L$ in the following way: first place the added
-circle components (augmentation) perpendicular to the projection plane, $\torus
+We will begin by assuming that there are no half twists. 
+Arrange the link diagram of $L$ in the following way: first place the added
+circle components perpendicular to the projection plane, $\torus
 \times \{0\}$ leaving the remaining part of the link parallel to the projection
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The following figures is an example which decomposes the link (C) of Figure
+The Figures \ref{fig:step_one} to \ref{fig:top-bottom} is an example which decomposes the link (C) of Figure
 \ref{fig:Augmentations}.
@@
 	\caption{Each crossing circle bounds a disk}
+	\label{fig:step_one}
 \end{figure}
@@
  crossing circle to ideal vertices}
+	\label{fig:step_two}
 \end{figure}
@@
 pushed off to infinity.}
+	\label{fig:step_three}
 \end{figure}
@@
 in $T$ and $P_{n-1}$.
-It remains to check that the dihedral angles assigned to the vertical edges
-are correct.
+	It remains to check that the dihedral angles assigned to the vertical (non-base)
+	edges are correct.
 For the vertical edge associated to $v_j$ for $j \neq i, i+2$,
@@
 hyperbolic. The idea is to start with a graph from the torihedral decomposition
-of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges
+of the link $K$ which will give us a graph on each torihedron with an angle
+assignment of
+$\pi/2$ for edge
 \cite{CKP2},
@@
 create self-loop edges.
-Here we sepcify how to choose which way to resolve the internal
+Here we specify how to choose which way to resolve the internal
 vertex $v$. If among the four faces touching $v$,
@@
 
-Thus, one can eliminate bigons in an order so that
+Therefore, one can eliminate bigons in an order so that
 they belong in one twist region;
@@
 $E \cup F \cup \{\otimes\}$,
-where $E, F$ are the set of edges, faces in $\Gamma_T(K)$,
+where $E, F$ are the set of edges, faces of $\Gamma_T(K)$ respectively,
 and $\otimes$ is some abstract vertex.
@@
 we may consider augmentations $L$ where all such twist regions
-are augmented.
+are augmented, i.e. $L$ may have augmentations without half-twists.
 Then, as pointed out in proof of \thmref{t:auglink_hyp} above,

### 2020-10-05 circlepatterns.tex
added a remark at end
captions last two figs

@@
 
-The notion of circle pattern that is considered in \cite{BandS}
+The notion of a circle pattern that is considered in \cite{BandS}
 would be restricted to those $c\in \CCC$
@@
 \includegraphics[width=8cm]{more_pictures/kite.png}
+	\caption{The kite of two circles intersecting in a ``normal" circle pattern.}
 \end{figure}
@@
 \includegraphics[width=5cm]{more_pictures/negative_angle.png}
+	\caption{Kites of a degenerate circle pattern.}
 \end{figure}
@@
 $\toruscomp{L}$.
+
+\begin{remark}
+It is not clear to us how to extend the proof of
+Theorem 3 \cite{BandS} to allow $\theta \geq \pi$,
+as we no longer have convexity of $S_{\text{Euc}}$.
+\end{remark}

### 2020-10-06 circlepatterns.tex
fixed captions for figures

@@
 \begin{figure}
-\includegraphics[width=8cm]{more_pictures/kite.png}
-	\caption{The kite of two circles intersecting in a ``normal" circle pattern.}
+\includegraphics[width=6cm]{more_pictures/kite.png}
+	\caption{The quadrangle associated to the edge $e$ between two
+		convex faces.}
 \end{figure}
 \begin{figure}
-\includegraphics[width=5cm]{more_pictures/positive_angle.png}
-\includegraphics[width=5cm]{more_pictures/negative_angle.png}
-	\caption{Kites of a degenerate circle pattern.}
+\includegraphics[height=5cm]{more_pictures/positive_angle.png}
+\includegraphics[height=5cm]{more_pictures/negative_angle.png}
+	\caption{Left: Quadrangle when $\theta_e$ is small and positive;
+		Right: Quadrangle when $\theta_e$ is small and negative,
+		so it takes up ``negative area'' (see proof of
+		\lemref{l:circpattern_polyhedra}).}
 \end{figure}

### 2020-10-09 circlepatterns.tex
minor fixes

@@
 
-Our general strategry for obtaining a (non-singular) circle pattern
+Our general strategy for obtaining a (non-singular) circle pattern
 is to start with an assignment $\underline{\theta} = (\theta_\bullet)$
@@
 Let $c \in \CCC$ be as in \prpref{p:point_lift}.
-Then $\Phi$ is a submersion in a neighbourhood of $c$.
+Then $\Phi$ is a submersion in a neighborhood of $c$.
 \end{lemma}

### 2020-10-09 draft1.tex
minor fixes

@@
  \begin{define} \label{def:weaklyprime}
-A diagram of a link $L$ is weakly prime if whenever a disk is embedded in the diagram surface meets the diagram transversely in exactly two edges, then the disk contains a simple edge of the diagram and no crossings.
+	 A diagram of a link $L$ is \emph{weakly prime} if whenever a disk is embedded in the diagram surface meets the diagram transversely in exactly two edges, then the disk contains a simple edge of the diagram and no crossings.
 \end{define}
@@
 We show a method of decomposing an augmented link in the thickened torus into
-two objects called torihedra. The idea is to combine methods of Menasco
+objects called torihedra. The idea is to combine methods of Menasco
 \cite{Menasco} and the use of crossing edges between each crossing of our link
@@
  \end{tabular}
- \caption{The first pictures shows gluing without half-twists the second shows gluing with half-twists}
+	\caption{(a) Gluing of bow-ties without half-twists
+	(b) Gluing with half-twists}
  \label{fig:falGluings}
@@
 \includegraphics[height=3cm]{fig-4}
-	\caption{Each crossing circle bounds a disk}
+	\caption{Each crossing circle bounds a twice-punctured disk}
 	\label{fig:step_one}
@@
 (locally) oriented such that they cross the augmentation disk in the same
-direction, the crossing is positive a right-handed half-twist.
+direction, the crossing is a positive right-handed half-twist.
 See Figure \ref{f:right_left_aug}.
@@
 Let $v_1, v_2$ be the vertices between these three interior edges.
-Since $v_1$ is not inteior,
+Since $v_1$ is not interior,
 the face across $v_1$ from $f$ is not in $F'$;

### 2020-10-19 draft1.tex
small changes

--- 2020-10-05 draft1.tex
@@
 
-Given a twist reduced diagram of a link $K$, \emph{augmentating} is a process in
+Given a twist reduced diagram of a link $K$, \emph{augmenting} is a process in
 which an unknotted circle component (augmentation) is added to one or
 more twist regions (a
-single crossing or a string of bigons) of $K$. Due to the added circle component
-we can remove full twists at the twist region of $K$. If the twist region has an
+single crossing or a string of bigons) of $K$. The added circle component
+allows us to remove full twists at the twist region of $K$. If the twist region has an
 odd number of crossings then all but one crossing is removed, whereas if the
@@
 Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in
-$\Sp^3$ the link $L$ obtained by augmentating $K$ is hyperbolic. In this paper
+$\Sp^3$ the link $L$ obtained by augmenting $K$ is hyperbolic. In this paper
 we investigate if this statement holds for links in the thickened torus i.e. if
@@
 alternating links in $\Sp^3$ into two polyhedra, a top polyhedron and a bottom polyhedron. 
-For alternating links, $K$ in the thickened torus Champanerkar, Kofman and Purcell \cite{CKP2}
+For alternating links $K$ in the thickened torus, Champanerkar, Kofman and Purcell \cite{CKP2}
 showed that there is a decomposition of the complement of $K$ into objects called torihedra,
@@
 as counterparts to Menasco's decomposition of links in $\Sp^3$ into polyhedra, for links in the thickened 
-torus. Just like Menasco's decomposition, one can obtain a top and a bottom torihedron.
+torus. Just like Menasco's decomposition, one obtains a top and a bottom torihedron.
 In \secref{s:auglinks} we show that for augmented links in the thickened torus 
 one can also obtain a decomposition of the complement into a top and bottom torihedron.
-In \secref{s:hyperbolicity}, we prove that augmented alternating links in the thickened torus
+In \secref{s:hyperbolicity}, we prove that many augmented alternating links in the thickened torus
 are hyperbolic.
@@
 \begin{define}
-A \emph{twist region} in a link diagram $L=\mathcal{L}/\Lambda$ in $\torus \times I$, is the quotient of a twist region in the biperiodic link $\mathcal{L}$.
-%a string of bigons, or a single crossing in the diagram on the universal cover of $\torus \times I$ is called a .
-A biperiodic link $\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on the plane that intersects $\mathcal{L}$ transversely in four points, with two points adjacent to one crossing and the other two points adjacent to another crossing, the simple closed
-curve bounds a subdiagram consisting of a (possibly empty) collection of bigons
-strung end to end between these crossings. We say $L$ is \emph{twist-reduced} if it is the quotient of a twist-reduced biperiodic link. 
-\end{define}
+A \emph{twist region} in a link diagram $L=\mathcal{L}/\Lambda$ in $\torus
+\times I$, is the quotient of a twist region in the biperiodic link
+$\mathcal{L}$. %a string of bigons, or a single crossing in the diagram on the
+universal cover of $\torus \times I$ is called a .  A biperiodic link
+$\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on
+the plane that intersects $\mathcal{L}$ transversely in four points, with two
+points adjacent to one crossing and the other two points adjacent to another
+crossing, the simple closed curve bounds a subdiagram consisting of a (possibly
+empty) collection of bigons strung end to end between these crossings. We say
+$L$ is \emph{twist-reduced} if it is the quotient of a twist-reduced biperiodic
+link.  \end{define}
 
-Now we can define augmentation for a link in $\torus \times I$ the same way we define augmentation for links in $\Sp^3$.
-For a link in $\torus \times I$, the crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
-Let $L$ be a twist reduced diagram in $\torus \times I$, we define {\it augmentating} as a process in which an unknotted circle component is added to one or more twist regions of $L$.
-See Figure \ref{fig:Augmentations}
+Now we can define augmentation for a link in $\torus \times I$ the same way we
+define augmentation for links in $\Sp^3$. For a link in $\torus \times I$, the
+crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
+Let $L$ be a twist reduced diagram in $\torus \times I$, we define
+\emph{augmenting} as a process in which an unknotted circle component is added
+to one or more twist regions of $L$. See Figure \ref{fig:Augmentations}
 
@@
 \begin{tabular}{cccc}
- \includegraphics [width=3cm]{fig1}&
- \includegraphics  [width=3cm]{twist-augment}&
-  \includegraphics [width=3cm]{fig-2}\\
+\includegraphics[width=3cm]{fig1}&
+\includegraphics[width=3cm]{twist-augment}&
+\includegraphics[width=3cm]{fig-2}\\
  % \includegraphics [width=3cm]{fal}\\
@@
 \end{tabular}
- \caption{A: The top right has an odd number of twists while the bottom left has an even number of twists.
-B: The picture of the link on the right after augmentation twist regions circled in red.
-C: The link with the twists removed.}
+	 \caption{A: The top right has an odd number of twists while the bottom left has
+	 an even number of twists. B: The picture of the link on the right after
+	 augmentation twist regions circled in red. C: The link with the twists
+	 removed.}
 \label{fig:Augmentations}
@@
 
-We show a method of decomposing an augmented link in the thickened torus into
-two objects called torihedra. The idea is to combine methods of Menasco
+We present a method of decomposing an augmented link in the thickened torus into
+objects called ``torihedra'' as defined below. The idea is to combine methods of Menasco
 \cite{Menasco} and the use of crossing edges between each crossing of our link

### 2020-10-19 circlepatterns.tex
small changes

@@
 \label{l:circpattern_polyhedra}
-Suppose we have the graph of a torihedron.
-Given a non-singular extended circle pattern $c \in \CCC$ on the graph,
+Let $\sT$ be a torihedron, with graph $\Gamma = \Gamma(\sT)$.
+Given a non-singular extended circle pattern $c \in \CCC$ on $\Gamma$,
 such that all $\vphi_{\vec{e}} \in (0,\pi)$,
-there exists a decomposition of the torihedron
+there exists a decomposition of $\sT$
 into base-angled ideal pyramids such that

### 2020-10-19 draft1.tex
small changes

@@
 One may ask for the pyramidal decomposition of a torihedron
-to ``respect" angles. The following definitions make sense of this.
+to ``respect" angles. The following definitions,
+in particular an ``angle splitting'', make sense of this.
 
@@
 Consider the directed graph whose vertex set is
-$E \cup F \cup \{\otimes\}$,
+$E \cup F \cup \{*\}$,
 where $E, F$ are the set of edges, faces of $\Gamma_T(K)$ respectively,
-and $\otimes$ is some abstract vertex.
-There is a directed edge
+%and $*$ is some abstract vertex.
+and there is a directed edge
 \begin{itemize}
-\item $\otimes \to f$ for each face $f\in F$, with capacity interval
+\item $* \to f$ for each face $f\in F$, with capacity interval
 	$[\pi, \infty)$,
@@
 	for some $\veps>0$ to be set later,
-\item $e \to \otimes$ for each edge $e$, with capacity interval
+\item $e \to *$ for each edge $e$, with capacity interval
 	$(-\infty, \pi/2]$.
@@
 Since $2|F| = |E|$, the capacity interval restrictions
-on the flow at $\otimes$ is sharp, so out-edges at $\otimes$
-have flow $\pi$ and in-edges at $\otimes$ have flow $\pi/2$.
+on the flow at $*$ is sharp, so out-edges at $*$
+have flow $\pi$ and in-edges at $*$ have flow $\pi/2$.
 Then the flow $f \to e$ gives us $\vphi_{\vec{e}}$,
 where $f$ is the face to the left of $\vec{e}$.
-(we adapted this argument from \cite{BandS}).
+(We adapted this argument from \cite{BandS}).
 
@@
 We add new edges across $f$ as follows.
-(See Figure \ref{f:adding_edges}; the + and - signs will be explained later.)
+(See Figure \ref{f:adding_edges};
+ignore the + and - signs for now.)
 
@@
 $e_{1,0},e_{1,\pi},e_2$
-(in the sense that the new edge separates the edges of $f$ into two sets
+(in the sense that the new edge separates the edges of $f$ into two sets,
 one of them being those three edges;
@@
 that would form a bigon with the existing edges,
-we just don't add it.
+we just do not add it.
 

### 2020-10-20 circlepatterns.tex
small changes. final draft hopefullly

@@
 let us first construct several other auxiliary vectors
-that are not necessarily in $T_c \CCC$.
+that are not in $T_c \CCC$.
 Generally they keep $\Phi_f$'s constant,
@@
 or decrease.
-Furthermore, $l_{\vec{e'}} \geq l_{\vec{e'}}$.
+Furthermore, $l_{\vec{e'}} \geq l_{\vec{e}}$.
 
@@
 by the following simple exercise in elementary Euclidean geometry.
-Suppose an obtuse triangle $\triangle ABC$, $\angle B > \pi/2$,
+Suppose we have an obtuse triangle $\triangle ABC$, $\angle B > \pi/2$,
 and we decrease $\angle B$, increase $\angle C$,
@@
 and increasing length $\overline{AC}$;
-each of these increases $\angle A$.
+each of these steps increases $\angle A$.
 We apply this to our situation with $B,C$ being

### 2020-10-20 draft1.tex
made figure 9 smaller
small change

@@
  \begin{tabular}{cc}
- \includegraphics [height=4cm]{augmentation1}&
-  \includegraphics [height=4cm]{augmentation2}\\
+ \includegraphics [height=4cm]{augmentation1.png}&
+  \includegraphics [height=4cm]{augmentation2.png}\\
   (a)&(b)
@@
 \begin{tabular}{cccc}
-\includegraphics[width=3cm]{fig1}&
-\includegraphics[width=3cm]{twist-augment}&
-\includegraphics[width=3cm]{fig-2}\\
+\includegraphics[width=3cm]{fig1.png}&
+\includegraphics[width=3cm]{twist-augment.png}&
+\includegraphics[width=3cm]{fig-2.png}\\
  % \includegraphics [width=3cm]{fal}\\
@@
 \centering 
-\includegraphics[width=4cm]{crossingArc}
-\includegraphics[width=5cm]{crossingPush} 
+\includegraphics[width=4cm]{crossingArc.png}
+\includegraphics[width=5cm]{crossingPush.png}
 \caption{Left: The black strands are
@@
  \begin{tabular}{cc}
- \includegraphics [width=8cm]{falGluing1}&
- \includegraphics [width=7cm]{falGluing2}\\
+ \includegraphics [width=8cm]{falGluing1.png}&
+ \includegraphics [width=7cm]{falGluing2.png}\\
  (a)&(b)
@@
 \centering
-\includegraphics[height=3cm]{fig-3}
-\includegraphics[height=3cm]{fig-4}
+\includegraphics[height=3cm]{fig-3.png}
+\includegraphics[height=3cm]{fig-4.png}
 	\caption{Each crossing circle bounds a twice-punctured disk}
@@
 \centering 
-\includegraphics[height=3cm]{fig-5} 
+\includegraphics[height=3cm]{fig-5.png} 
 	\caption{We split the disk and collapse the arc of each
@@
 \centering 
-\includegraphics[height=3cm]{fig-6} 
+\includegraphics[height=3cm]{fig-6.png} 
 \caption{Left: The crossing arc is the edge in red.
@@
 \centering 
-\includegraphics[height=3cm]{top-bottom} 
+\includegraphics[height=3cm]{top-bottom.png} 
 	\caption{Left: The top torihedron. Right: The bottom torihdron with rotation for face gluing.} 
@@
 \begin{figure}
-\includegraphics[height=8cm]{more_pictures/angle_split.png}
+\includegraphics[height=5cm]{more_pictures/angle_split.png}
 \caption{Angle-splitting on a polygonal face of the graph}
@@
 \begin{figure}
-\includegraphics[width=11cm]{bigon_crush}
+\includegraphics[width=11cm]{bigon_crush.png}
 \caption{Resolving internal vertex; eliminating bigons via ``crushing"}
@@
 \begin{tabular}{cc}
-\includegraphics[width = 5cm]{before_bowtie_angles}&
-\includegraphics[width = 5cm]{bowtie_angles}\\
+\includegraphics[width = 5cm]{before_bowtie_angles.png}&
+\includegraphics[width = 5cm]{bowtie_angles.png}\\
 (a)&(b)
@@
 
-\input{circlepatterns}
+\section{Appendix}
+
+We provide an alternative method via circle patterns to obtain
+an angle-splitting of the torihedral decomposition
+in \secref{s:auglinks}.
+This guarantees that the resulting angle structure
+on the final triangulation
+also satisfies Thurston's gluing equations.
+Thus, one can obtian lower bounds on volume
+from these angles.
+
+Let $\Gamma$ be a graph on the torus $\torus$,
+and let $V,E,F$ be the set of vertices, edges, faces, respectively.
+Generally we assume that graphs do not have bigon faces
+nor self-loop edges.
+
+$\vec{E}$ is the set of oriented edges.
+We may identify an oriented edge $\vec{e}$ with the pair $(f_{\vec{e}}, e)$,
+where $f_{\vec{e}}$ is the face to the left of $\vec{e}$.
+
+When we use $\cev{e}$ to refer to an oriented edge, it refers to
+the oppositely oriented edge to $\vec{e}$.
+If we construct an expression with both $\vec{e}$ and $\cev{e}$,
+it will always be (anti-)symmetrical in the two orientations,
+and we assume that an arbitrary choice has been made.
+
+%===============================================================================
+
+Recall that a cirlce pattern for a graph $\Gamma$ is an arrangement of circles
+in $\torus$ such that each circle circumscribes a face of $\Gamma$.
+A circle pattern is determined by the radius of the circle $C_f$ associated to each face, $r_f$,
+and the angle that each edge subtends in adjacent faces, $\vphi_{\vec{e}}$.
+(See \figref{f:circle_pattern})
+\begin{figure}
+\includegraphics[width=8cm]{circle_pattern.png}
+\caption{Circle pattern in terms of radii $r_f$ and angles $\vphi_{\vec{e}}$}
+\label{f:circle_pattern}
+\end{figure}
+Thus determines, and is determined by a point in $\RRR \times \QQQ$, where
+
+\begin{itemize}
+	\item $\RRR := \RR_+^F = \{(r_f)_{f\in F} | r_f \in \RR_+\}$
+	\item $\QQQ := \RR^{\vec{E}} =
+		\{(\vphi_{\vec{e}})_{\vec{e} \in \vec{E}} | \vphi_{\vec{e}} \in \RR\}$
+\end{itemize}
+but clearly not every point $c\in \RRR \times \QQQ$ determines a circle pattern.
+This larger space allows us to consider
+``degenerate" circle patterns, where adjacent circles may
+be identical or tangent.
+
+On $\RRR \times \QQQ$, there are several functions to consider:
+\begin{itemize}
+	\item $\Phi_f = 2 \sum_{\vec{e} \in \del f} \vphi_{\vec{e}}$, measuring the cone angle
+		at the center of $C_f$
+	\item $\theta_e = \pi - \vphi_{\vec{e}} - \vphi_{\cev{e}}$
+	\item $l_{\vec{e}} = 2 r_{f_{\vec{e}}} \sin \vphi_{\vec{e}}$
+\end{itemize}
+
+These fit together to give maps to the following spaces:
+
+\begin{itemize}
+	\item $\PPP := \RR^F = \{(\Phi_f)_{f\in F} | \Phi_f \in \RR\}$
+	\item $\TTT := \RR^E = \{(\theta_e)_{e \in E} | \theta_e \in \RR\}$
+	\item $\LLL := \RR^{\vec{E}} = \{(l_{\vec{e}})_{\vec{e} \in E} | l_{\vec{e}} \in \RR\}$
+\end{itemize}
+
+\begin{define}
+Let $\Gamma$ be a graph on the torus.
+An \emph{extended circle pattern} on $\Gamma$ is
+$c = ((r_f), (\vphi_{\vec{e}})) \in \RRR \times \QQQ$
+such that $l_{\vec{e}} = l_{\cev{e}}$ for all edges $e\in E$. We denote by
+$\CCC$ the set of extended circle patterns.
+\end{define}
+
+\begin{tikzcd}
+\CCC = \{l_{\vec{e}} = l_{\cev{e}} \} \ar[r, "\subset"]
+	& \RRR \times \QQQ \ar[r, "\Theta"] \ar[d, "\Phi"]
+	& \TTT \\
+	& \PPP
+\end{tikzcd}
+
+The notion of a circle pattern that is considered in \cite{BandS}
+would be restricted to those $c\in \CCC$
+with $\vphi_{\vec{e}} \in (0,\pi)$ and $\theta_e \in (0,\pi)$.
+They parametrize circle patterns by $(r_f)$ and $(\theta_e)$
+(or $(\theta_e^*)$),
+and call $(\vphi_{\vec{e}})$ a coherent angle system.
+One may consider deforming a circle pattern so as to have
+some $\theta_e$ approach 0 or $\pi$.
+The limit $\theta_e \to \pi$ is easy to picture, one simply gets that the two circles
+$C_f, C_{f'}$ of the adjacent faces become tangent. The limit $\theta_e \to 0$
+is a bit more complex, as the final shape of $Q_e$ (the quadrangle associated to $e$)
+may depend on $\vphi_{\vec{e}}$ or $\vphi_{\cev{e}}$.
+If we parametrize circle patterns by $(r_f)$ and $(\theta_e)$ as in \cite{BandS},
+the limiting shape would depend on the relationship between 
+$r_f$ and $r_{f'}$.
+As our main result depends on extending \cite{BandS} result
+to such limits and beyond,
+we find it more convenient to describe extended circle patterns by
+$(r_f)$ and $(\vphi_{\vec{e}})$.
+
+We will mostly be working with extended circle patterns that ``look normal'',
+with all $\vphi_{\vec{e}}$ in the range $[0,\pi)$,
+so we do not dwell on the meaning of negative $\vphi_{\vec{e}}$'s.
+\footnote{
+Intuitively, one can visualize decreasing $\vphi_{\vec{e}}$
+from $\veps$ to $-\veps$
+as moving the black vertices of the quadrangle $Q_e$ past each other,
+thus flipping $Q_e$ along its long axis
+and making it have negative area.
+}
+
+\begin{define}
+An extended circle pattern is said to be \emph{face non-singular}
+if $\Phi_f = 2\pi$ for all faces $f$; it is said to be \emph{vertex non-singular}
+if $\sum_{e \ni v} \theta_e = 2\pi$ for all vertices $v$.
+Finally it is said to be \emph{non-singular} if it is both.
+\end{define}
+
+\begin{define}
+Let $f$ be a non-singular face (i.e. $\Phi_f = 2\pi$),
+such that for all edges $\vec{e} \in \del f$,
+$\vphi_{\vec{e}} \in [0,\pi)$.
+We say $f$ is \emph{thin} if
+exactly two edges of $f$ have nonzero $\vphi_\bullet$;
+we say it is \emph{thick} otherwise.
+We say it is \emph{convex} if for all edges $\vec{e} \in \del f$,
+we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
+\end{define}
+
+%\begin{define}
+%Given some extended circle pattern $c \in \CCC$,
+%we say a face $f$ is \emph{convex} if for all edges $\vec{e} \in \del f$,
+%we have $\vphi_{\vec{e}} \in [0,\pi/2)$.
+%We say $f$ is \emph{thin} if exactly two edges $\vec{e}, \vec{e'} \in \del f$
+%have nonzero $\vphi_{\bullet}$, and furtheremore,
+%	$0 < \vphi_{\vec{e}} = \pi - \vphi_{\vec{e'}} < \pi/2$.
+%\end{define}
+
+%figures for convex, thin faces
+
+\begin{define}
+Given an extended circle pattern $c\in \CCC$, an edge $e$ is \emph{short}
+if it has length 0, $l_e = 0$;
+it is \emph{long} otherwise.
+\end{define}
+
+\begin{define}
+Given an extended circle pattern $c\in \CCC$, a \emph{wide path}
+is a sequence of faces $f_0,f_1,\ldots,f_n$
+such that $f_i,f_{i+1}$ share a long edge.
+A \emph{wide cycle} is a wide path with $f_0 = f_n$.
+\end{define}
+
+\begin{lemma}
+\label{l:manifold_point}
+Let $c$ be a face non-singular extended circular pattern
+such that $\vphi_{\vec{e}} \geq 0$ for all $\vec{e}\in\vec{E}$.
+Furthermore, suppose that there is no cycle of edges
+$e_0, e_1, \ldots, e_n = e_0$ such that
+$e_i, e_{i+1}$ belong to the same face,
+and $\vphi_{\vec{e_i}} = \vphi_{\cev{e_i}} = \pi/2$.
+Then $\CCC$ is a manifold in a neighborhood of $c$.
+\end{lemma}
+\begin{proof}
+We need to show that the differentials
+$d(l_{\vec{e}} - l_{\cev{e}})
+= 2\sin \vphi_{\vec{e}} d r_{f_{\vec{e}}}
++ 2r_{f_{\vec{e}}} \cos \vphi_{\vec{e}} d \vphi_{\vec{e}}
+- 2\sin \vphi_{\cev{e}} d r_{f_{\cev{e}}}
+- 2r_{f_{\cev{e}}} \cos \vphi_{\cev{e}} d \vphi_{\cev{e}}
+$
+are linearly independent at $c$.
+If $\vphi_{\vec{e}} \neq \pi/2$,
+then the $d\vphi_{\vec{e}}$ term makes $d(l_{\vec{e}} - l_{\cev{e}})$
+linearly independent from the rest
+(no other differential $d(l_{\vec{e'}} - l_{\cev{e'}})$
+contains such component);
+likewise for $\vphi_{\cev{e}} \neq \pi/2$.
+
+Now consider the set $E'$ of edges $e$ that have
+$\vphi_{\vec{e}} = \vphi_{\cev{e}} = \pi/2$.
+Consider a maximal sequence of faces $f_0,\ldots,f_n$
+with no repetitions and $f_i,f_{i+1}$ share
+an edge $e_i \in E'$.
+By the condition on no cycles,
+$f_0 \neq f_n$.
+By face non-singularity, any face can meet at most two
+edges from $E'$, thus if $e\in E'$,
+it is contained in a unique such string of faces/edges.
+Thus the differentials
+$d(l_{\vec{e_i}} - l_{\cev{e_i}}) = 2dr_{f_i} - 2dr_{f_{i+1}}$
+are linearly independent.
+\end{proof}
+
+\subsection{From Extended Circle Patterns to Hyperbolic Polyhedra}
+In this section, we describe how to obtain a
+decomposition of a torihedron into hyperbolic ideal pyramids
+from a non-singular extended circle pattern.
+
+\begin{lemma}
+\label{l:circpattern_polyhedra}
+Let $\sT$ be a torihedron, with graph $\Gamma = \Gamma(\sT)$.
+Given a non-singular extended circle pattern $c \in \CCC$ on $\Gamma$,
+such that all $\vphi_{\vec{e}} \in (0,\pi)$,
+there exists a decomposition of $\sT$
+into base-angled ideal pyramids such that
+	\begin{itemize}
+		\item each interior edge of the torihedron has dihedral angles sum to $2\pi$;
+		\item each boundary edge $e$ of the torihedron has dihedral angles sum to
+			$\pi - \theta_e$.
+	\end{itemize}
+\end{lemma}
+
+\begin{proof}
+For each directed edge $\vec{e} \in \vec{E}$,
+construct the isosceles triangle $T_{\vec{e}}$
+with equal sides of length $r_{f_{\vec{e}}}$ and
+angle $2\tilde{\vphi}_{\vec{e}}$ subtended between them,
+where $\tilde{\vphi}_{\vec{e}} = \vphi_{\vec{e}}$
+if $\vphi_{\vec{e}}$ if it is acute,
+and = $\pi - \vphi_{\vec{e}}$ otherwise.
+
+\begin{figure}
+\includegraphics[width=6cm]{more_pictures/kite.png}
+	\caption{The quadrangle associated to the edge $e$ between two
+		convex faces.}
+\end{figure}
+\begin{figure}
+\includegraphics[height=5cm]{more_pictures/positive_angle.png}
+\includegraphics[height=5cm]{more_pictures/negative_angle.png}
+	\caption{Left: Quadrangle when $\theta_e$ is small and positive;
+		Right: Quadrangle when $\theta_e$ is small and negative,
+		so it takes up ``negative area'' (see proof of
+		\lemref{l:circpattern_polyhedra}).}
+\end{figure}
+
+Let $f \in F$ be a face.
+We construct a Euclidean polygon $\Pol_f$ as follows.
+If $\vphi_{\vec{e}} \leq \pi/2$ for all $\vec{e} \in \del f$,
+i.e. if $f$ is convex, then 
+the $T_{\vec{e}}$ for $\vec{e}\in \del f$
+fit together into $\Pol_f$.
+If not, suppose $\vphi_{\vec{e}} > \pi/2$
+for $\vec{e} = \vec{e_1}$, 
+and $\leq \pi/2$ for $\vec{e} = \vec{e_2},\ldots \vec{e_k} \in \del f$.
+Then put $T_{\vec{e_2}},\ldots,T_{\vec{e_k}}$ together as above,
+creating a $(k+1)$-gon,
+then subtract $T_{\vec{e_1}}$ from it to form $\Pol_f$.
+
+Thus, to each face, we associate the Euclidean polygon $\Pol_f$.
+If $v$ is the vertex of $\Pol_f$ between $e_i$ and $e_{i+1}$,
+then the angle at $v$ is
+$\pi - \vphi_{\vec{e_i}} - \vphi_{\vec{e_{i+1}}}$.
+Then the non-vertex-singularity of $c$ guarantees that
+the sum of angles at $v$ of $\Pol_f$, for faces $f$ containing $v$,
+is $2\pi$.
+%; in other words, $\Pol_f$ glue along edges
+
+View the Euclidean plane as the boundary of the upper-half space.
+Then $\Pol_f$ supports an ideal hyperbolic pyramid $P_f$.
+
+Clearly, these $P_f$'s, as abstract ideal tetrahedra,
+glue together into the torihedron.
+%The hyperbolic structure on $P_f$
+%in particular provide dihedral angles to each edge of $P_f$
+%which clearly satisfies the conditions of making $P_f$
+%a base-angled ideal pyramid.
+We need to check that the angles around each edge of
+the torihedron have the appropriate angles.
+
+Consider an interior edge $e$ of the pyramidal decomposition
+of the torihedron.
+It corresponds to a vertex $v$ of the graph.
+Note that the dihedral angle of the vertical edge
+at $v$ of $P_f$ is simply the angle at $v$ of $\Pol_f$;
+these sum to $2\pi$ over $f \ni v$.
+
+For a boundary edge $e$, the dihedral angles at $e$ of the $P_f$'s
+containing it are $\vphi_{\vec{e}}$ and $\vphi_{\cev{e}}$,
+which sum to $\theta_e$ by definition.
+
+\end{proof}
+
+\subsection{Deforming Extended Circle Patterns}
+
+Our general strategy for obtaining a (non-singular) circle pattern
+is to start with an assignment $\underline{\theta} = (\theta_\bullet)$
+for which we know an extended circle pattern exists
+(say from results of \cite{BandS}),
+and a path $\gamma$ in $\TTT$ starting at $\underline{\theta}$.
+We then attempt to lift $\gamma$ to a path $\tilde{\gamma}$ in $\CCC$,
+so that $\tilde{\gamma}$ remains (face) non-singular
+(vertex non-singularity is already determined by $\gamma$).
+
+Note that since $\sum_{e\in E} \theta_e
+= 2\pi |E| - \sum_{\vec{e} \in \vec{E}} \vphi_{\vec{e}}
+= 2\pi |E| - \sum_{f\in F} \Phi_f$,
+we see that maintaining face non-singularity of $\tilde{\gamma}$
+forces $\sum \theta_e$ to be constant.
+We will show that this is the only obstruction on $\gamma$
+to the lifting to such $\tilde{\gamma}$.
+
+To that end, let $L$ be the $(|E|-1)$-plane distribution on $\TTT$
+tangent to the level sets of $\sum_{e\in E} \theta_e$.
+The following proposition proves that we can deform
+some circle patterns up to first order at a point:
+
+\begin{prop}
+\label{p:point_lift}
+Let $c \in \CCC$ be a
+non-singular extended circle pattern on a graph
+with no bigons or self-loops such that
+there is no wide cycle of thin faces,
+and each edge meets two distinct faces.
+Let $K_c = \ker (\Phi_*|_c : T_c \CCC \to T_{\Phi(c)} \PPP)$.
+Then $\Theta_*(K_c) = L_{\Theta(c)}$.
+
+In other words, for any vector $a \in T_{\Theta(c)} \TTT$
+with sum of components 0, one can vary $c$ so that its
+first order change in $\theta_\bullet$ is $a$,
+and also remains face non-singular up to first order.
+\end{prop}
+
+Before we prove this, it is convenient to first prove the following,
+which will establish some useful notation:
+
+\begin{lemma}
+\label{l:Phi_full}
+Let $c \in \CCC$ be as in \prpref{p:point_lift}.
+Then $\Phi$ is a submersion in a neighborhood of $c$.
+\end{lemma}
+
+\begin{proof}
+We construct vectors $\beta_f \in T_c \CCC$ so that
+$\Phi_*(\beta_f) = \ddd{\Phi_f}$.
+The vector
+\begin{equation}
+\label{e:alpha_f}
+\alpha_f := \ddd{r_f} - \sum_{\vec{e} \in \del f} 
+	\frac{\tan \vphi_{\vec{e}}}{r_f} \ddd{\vphi_{\vec{e}}}
+	\in T(\RRR \times \QQQ)
+\end{equation}
+doesn't change $l_{\vec{e}}$,
+so is in $T_c \CCC$.
+Intuitively, $\alpha_f$ is like
+pulling the center of $C_f$ up off the plane, increasing $r_f$ and decreasing all
+$\vphi$'s.
+Its pushforward under $\Phi$ is simply
+$\Phi_*(\alpha_f) =
+	(-\frac{2}{r_f} \sum_{\vec{e}\in \del f} \tan \vphi_{\vec{e}})
+	\ddd{\Phi_f}$.
+
+If $f$ is a convex face, then the $\tan \vphi_{\vec{e}}$ are all non-negative,
+being 0 if and only if $e$ is short,
+and because $\Phi_f = 2\pi$, at least three edges are long.
+So $\Phi_*(\alpha_f)$ is a negative multiple of $\ddd{\Phi_f}$;
+we choose $\beta$ so that
+\begin{equation}
+\label{e:beta_f_convex}
+\beta_f := \beta \cdot \alpha_f; \;\;\;
+\Phi_*(\beta_f) = \ddd{\Phi_f}
+\end{equation}
+
+If $f$ is thick but not convex,
+let $\vec{e}$ be an edge with largest $\vphi_{\vec{e}}$,
+so that $\vphi_{\vec{e}} \geq \pi/2$.
+If $\vphi_{\vec{e}} > \pi/2$,
+then since $\tan$ is convex, and $f$ has at least two other
+long edges,
+we see that $\Phi_*(\alpha_f) = -\sum \frac{\tan \vphi_{\vec{e'}}}{r_f} > 0$,
+so we can define $\beta_f$ as in \eqnref{e:beta_f_convex}.
+If $\vphi_{\vec{e}} = \pi/2$,
+we can take
+\[
+\beta_f = \frac{1}{2} \ddd{\vphi_{\vec{e}}}
+\]
+
+If $f$ is thin, we actually have that $\alpha_f \in K_c$,
+since the components sum to 0, so we need a different approach.
+First suppose $f$ shares an edge $e$ with a thick face $f'$,
+with $\vec{e} \in \del f$.
+If $\vphi_{\vec{e}} = \pi/2$, we can take
+$\beta_f = \frac{1}{2} \ddd{\vphi_{\vec{e}}}$ as before.
+Otherwise, we can increase $l_{\vec{e}}$
+by varying $\vphi_{\vec{e}}$
+while holding $r_f$ constant,
+and increase $l_{\cev{e}}$
+by increasing $r_{f'}$.
+This will affect both $\Phi_f, \Phi_{f'}$,
+so we use $\beta_{f'}$ to make $\Phi_{f'}$ constant.
+%More explicitly, consider
+%\begin{equation}
+%\label{e:alpha_e}
+%\alpha_e = \frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
+%+ \frac{1}{2 r_{f'}\cos \vphi_{\cev{e}}} \ddd{\vphi_{\cev{e}}}
+%\end{equation}
+%which increases $l_{\vec{e}}, l_{\cev{e}}$ at half unit speed,
+%$dl_{\vec{e}}(\alpha_e) = dl_{\cev{e}}(\alpha_e) = 1/2$.
+%Then we can take
+%\begin{equation}
+%\label{e:beta_f_thin}
+%\beta_f = r_f \cos \vphi_{\vec{e}}
+	%(\alpha_e - \frac{1}{r_{f'} \cos \vphi_{\cev{e}}} \beta_{f'})
+%\end{equation}
+We can repeat this procedure with $f'$ set to this thin face,
+and $f$ set to another thin face adjacent to it, etc.
+\end{proof}
+
+\begin{proof}
+We construct a vector $u_e \in K_c \subseteq T_c \CCC$ for each edge $e$
+and show that $\{\Theta_*(u_e)\}_{e\in E}$ spans an
+$|E|-1$ dimensional space,
+thus must be equal $L_{\Theta_c}$.
+The vectors $u_e$ will have the following property:
+if $\Theta_*(u_e) = \sum_{e' \in E} a^{e'} \ddd{\theta_{e'}}$, then
+\begin{itemize}
+	\item $a^e = 1$;
+	\item $a^{e'} \leq 0$ for all $e' \neq e$;
+	%\item $a^{e'} = 0$ for short edges $e'$ (hmm...)
+	\item $\sum_{e' \in E} a^{e'} = 0$ (follows directly from $u_e \in K_c$)
+\end{itemize}
+
+Furthermore, these $u_e$'s collectively satisfy the following
+connectivity property:
+consider the graph $G$ whose vertex set is the set of edges $E$,
+and we connect two long edges $e,e'$ by an edge if there is some $e''$ such that
+$a^e, a^{e'}$ are both nonzero in $\Theta_*(u_{e''})$;
+then $G$ is connected.
+
+Let us first suppose we have constructed such $u_e$,
+and show that these properties ensure that
+$\{\Theta_*(u_e)\}_{e\in E}$ spans an $|E|-1$ dimensional space.
+This is a simple exercise in linear algebra,
+but we show it for completeness.
+
+Put the $\Theta_*(u_e)$'s into a $E \times E$ matrix,
+denoted $M$,
+so that the $e$-th row corresponds to $\Theta_*(u_e)$.
+By virtue of $u_e \in K_c$, we have that $(1\; 1\; \cdots \; 1)^T$
+is in the null space of $M$;
+our goal is to show that it spans the null space.
+
+Suppose $b = (b_e)^T$ is in the null space of $M$.
+Let $|b_e|$ be the largest among components of $b$;
+rescale $b$ so that $b_e = 1$.
+The $e$-th component of $M b$
+is $1 - \sum_{e' \neq e} a^{e'} b_{e'}$,
+where $a^{e'}$ are the components of $\Theta_*(u_e)$.
+Since $\sum_{e' \neq e} |a^{e'}| = 1$, this can be 0 if and only if
+for all $e'$ with $a^{e'} < 0$, we have exactly $b_{e'} = 1$.
+We then repeat this argument on the other $e'$
+that appear in $\Theta_*(u_e)$.
+By connectedness of $G$, this implies
+$b = (1 \; \cdots \; 1)^T$,
+thus $M$ has rank $|E|-1$.
+
+Before constructing the $u_e$'s,
+let us first construct several other auxiliary vectors
+that are not in $T_c \CCC$.
+Generally they keep $\Phi_f$'s constant,
+but have an effect on the lengths of oriented edges $l_{\vec{e}}$.
+The $u_e$'s will be built from a combination of these.
+All discussion of changes will refer to changes in the first order.
+
+Let $f$ be a convex face, and $\vec{e} \in \del f$. Define
+\begin{equation}
+\label{e:eta_e}
+\eta_{\vec{e}} =
+\frac{1}{2 r_f \cos \vphi_{\vec{e}}} \ddd{\vphi_{\vec{e}}}
+- \frac{1}{r_f \cos \vphi_{\vec{e}}} \beta_f
+\end{equation}
+$\eta_{\vec{e}}$ keeps $\Phi_f$ constant, but increases $l_{\vec{e}}$
+at unit speed, i.e. $dl_{\vec{e}}(\eta_{\vec{e}}) = 1$.
+
+Let $f$ be a thick but not convex face.
+There is exactly one edge $\vec{e} \in \del f$
+with $\vphi_{\vec{e}} \geq \pi/2$.
+If $\vphi_{\vec{e}} > \pi/2$, we will define
+$\eta_{\vec{e}}$ as in \eqnref{e:eta_e}.
+If $\vphi_{\vec{e}} = \pi/2$,
+we will define
+\begin{equation}
+\label{e:eta_e_2}
+\eta_{\vec{e}} = \frac{1}{2}\ddd{r_f}
++ \big(\sum_{\vec{e'} \neq \vec{e}}
+	\frac{\sin \vphi_{\vec{e'}}}{2 r_f \cos \vphi_{\vec{e'}}}\big)
+	\ddd{\vphi_{\vec{e}}}
+- \sum_{\vec{e'} \neq \vec{e}}
+	\frac{\sin \vphi_{\vec{e'}}}{2 r_f \cos \vphi_{\vec{e'}}}
+	\ddd{\vphi_{\vec{e'}}}
+\end{equation}
+Then it is easy to see that
+$dl_{\vec{e}}(\eta_{\vec{e}}) = 1$
+while
+$dl_{\vec{e'}}(\eta_{\vec{e}}) = 0$
+for all other $\vec{e'} \neq \vec{e}$,
+and $\eta_{\vec{e}}$ keeps $\Phi_f$ constant.
+
+Now let $\vec{e'} \in \del f$ be another edge.
+We define
+\begin{equation}
+\label{e:gamma_e}
+\gamma_{\vec{e'}} = \frac{1}{2 r_f \cos{\vphi_{\vec{e'}}}}
+	(\ddd{\vphi_{\vec{e'}}} - \ddd{\vphi_{\vec{e}}})
+\end{equation}
+Then $dl_{\vec{e'}} = 1$,
+$dl_{\vec{e}} = -\frac{\cos \vphi_{\vec{e}}}{\cos \vphi_{\vec{e'}}} \geq 0$,
+and keeps $\Phi_f$ constant.
+
+Finally, let $f$ be a thin face.
+If $\vec{e} \in \del f$ is a short edge,
+i.e. $\vphi_{\vec{e}} = 0$,
+then we define $\eta_{\vec{e}}$ as in \eqnref{e:eta_e}.
+If $\vec{e}$ is long, and $\vphi_{\vec{e}} \neq \pi/2$,
+we define $\gamma_{\vec{e}}$ as in \eqnref{e:gamma_e};
+if $\vphi_{\vec{e}} = \pi/2$, we define
+\begin{equation}
+\label{e:xi_e}
+\xi_{\vec{e}} = \frac{1}{2}\ddd{r_f}
+\end{equation}
+Clearly $dl_{\vec{e}}(\xi_{\vec{e}}) = dl_{\vec{e'}}(\xi_{\vec{e}}) = 1$
+for the other edge $e'$ with $\vphi_{\vec{e'}} = \pi/2$.
+%where $\vec{e'} \in \del f$ is the unique other long edge.
+
+In summary,
+$\eta_{\vec{e}}, \gamma_{\vec{e}}, \xi_{\vec{e}}$
+always increases $l_{\vec{e}}$ at unit speed,
+and keeps $\Phi_{f_{\vec{e}}}$ constant.
+$\eta_{\vec{e}}$ does not affect the lenghts of other edges
+in the face $f_{\vec{e}}$,
+but the other two might affect another edge
+- this other edge $\vec{e'}$ is unique,
+and $l_{\vec{e}}, l_{\vec{e'}}$ either both increase
+or decrease.
+Furthermore, $l_{\vec{e'}} \geq l_{\vec{e}}$.
+
+For any oriented edge $\vec{e}$,
+there is exactly one such vector defined for it;
+call that vector $\zeta_{\vec{e}}$.
+
+Now we can put these vectors together to construct the desired $u_e$'s.
+To illustrate the main idea of the construction,
+first suppose that $e$ is an edge between two convex faces $f,f'$.
+Then we can consider
+\[
+w_e = \eta_{\vec{e}} + \eta_{\cev{e}}
+\]
+Since $dl_{\vec{e}}(w_e) = dl_{\cev{e}}(w_e) = 1$,
+and $dl_{\vec{e'}}(w_e) = 0$ for all other edges,
+$w_e \in T_c \CCC$;
+furthermore, $\eta_-$ does not affect $\Phi_-$,
+so $w_e \in K_c$.
+For $\vec{e'} \in \del f \cup \del f' \backslash \{\vec{e},\cev{e}\}$,
+the $\ddd{\vphi_{\vec{e'}}}$ component only appears in $\beta_f$
+or $\beta_{f'}$, which is positive by construciton
+(because $f,f'$ are convex faces);
+thus, $d\theta_{e'}(w_e) \geq 0$ for such $e'$, and
+is equal to 0 if and only if $e'$ is short.
+Finally, since $w_e \in K_c$, it leaves the sum $\sum_{e\in E} \theta_e$
+constant, so $d\theta_e(w_e) < 0$, so we can take
+\begin{equation}
+\label{e:u_e}
+u_e := (d\theta_e(w_e))^\inv \cdot w_e
+\end{equation}
+
+Now consider an arbitrary edge $e$ between faces $f,f'$.
+We build $u_e$ inductively, beginning with
+$w_e = \zeta_{\vec{e}} + \zeta_{\cev{e}}$,
+$F' = \{f, f'\}$, and $E' = \{e\}$.
+If $w_e$ also affects $l_{\vec{e'}}$ for some edge
+$\vec{e'} \in \del F' \backslash\{\vec{e''},\cev{e''} | e''\in E'\}$,
+we add an appriopriate positive multiple
+of $\zeta_{\cev{e'}}$ to $w_e$,
+add $f_{\cev{e'}}$ to $F'$,
+and add $e'$ to $E'$.
+Recall that when $\zeta_{\vec{e'}}$ affects
+the length of another edge $e''$,
+we always have $l_{\vec{e''}} \geq l_{\vec{e'}}$.
+Thus by the condition of non-existence of wide cycles of thin faces,
+this process must terminate.
+It is not hard to see that when an $\eta_-$ term appears,
+the process terminates (for that direction);
+a $\gamma_-$ term begets either another $\gamma_-$ or $\eta_-$ term;
+a $\xi_-$ term begets either
+a $\xi_-, \gamma_-$, or $\eta_-$ term.
+In other words, in the end we get some sum
+(ignoring possible positive coefficients)
+\[
+w_e = (\xi_- + \xi_- + \cdots + \gamma_- + \gamma_- + \cdots + \eta_-)
++ (\xi_- + \xi_- + \cdots + \gamma_- + \gamma_- + \cdots + \eta_-)
+\]
+where in each parenthesis,
+the first term affects the next term and so on.
+
+Assume that there are no thin faces.
+We check that $w_e$ has the desired properties.
+By construction, $w_e \in T_c \CCC$.
+Observe that the coefficient of $\ddd{\vphi_{\vec{e}}}$
+is positive in either $\eta_{\vec{e}}$ or $\gamma_{\vec{e}}$,
+so $d\theta_e(\Theta_*(w_e)) < 0$.
+There is a maximal sequence of thick faces
+$f_0 = f, f_1, \ldots, f_n$
+and a sequence of edges $e_0 = e, e_1, \ldots, e_n$,
+where for $i\neq 0$, $e_i$ is between $f_{i-1}$ and $f_i$,
+and $l_{e_i}$ increases under $w_e$;
+we label oriented edges so $\vec{e_i} \in \del f_i$,
+$\cev{e_i} \in \del f_{i+1}$.
+(Similar discussion for $f_0 = f'$).
+Consider one of the edges $e_i$, $i\neq 0$.
+Since $l_{e_i}$ increases, the $\zeta_{\vec{e}_{i-1}}$ term
+from the previous edge $e_{i-1}$ must have been
+$\gamma_{\vec{e}_{i-1}}$;
+in particular, $\vphi_{\cev{e_i}} > \pi/2$,
+$w_e$ decreases $\vphi_{\cev{e_i}}$,
+and keeps $r_{f_{i-1}}$ constant.
+The edge $e_i$ also contributes some $\zeta_{\vec{e_i}}$
+term to $w_e$;
+it increases $\vphi_{\vec{e_i}}$ and either increases
+or keeps constant $r_{f_i}$.
+Then $\theta_{e_i}$ increases, i.e. $d\theta_{e_i}(\Theta_*(w_e)) > 0$,
+by the following simple exercise in elementary Euclidean geometry.
+Suppose we have an obtuse triangle $\triangle ABC$, $\angle B > \pi/2$,
+and we decrease $\angle B$, increase $\angle C$,
+keep length of $\overline{AB}$ constant,
+and either increase or keeps constant the length of $\overline{AC}$;
+then $\angle A$ increases.
+This can be proved by observing that the changes we are forcing
+on the triangle can be broken in two:
+the first is increase $\angle B$ and keeping lengths
+$\overline{AB}, \overline{AC}$ constant,
+and the second is keeping $\angle B$ and length $\overline{AB}$ constant,
+and increasing length $\overline{AC}$;
+each of these steps increases $\angle A$.
+We apply this to our situation with $B,C$ being
+the centers of circles $C_{f_{i-1}}, C_{f_i}$
+of the faces $f_{i-1}, f_i$.
+As before, we simply rescale $w_e$ appropriately to obtain $u_e$.
+
+Now we consider the presence of thin faces.
+If all the $\zeta_-$ terms added to $w_e$
+are $\eta_-$ or $\gamma_-$,
+then all arguments in the previous paragraph applies.
+The only situation in which $\xi_-$ is used
+is when either $\zeta_{\vec{e}}$ or $\zeta_{\cev{e}}$ is $\xi_-$.
+Without loss of generality, $\zeta_{\vec{e}} = \xi_{\vec{e}}$,
+so that $\vec{e} \in \del f$, $f$ is a thin face with nonzero
+angles equal to $\pi/2$;
+let $\vec{e'}$ be the other edge with $\vphi$ angle $\pi/2$.
+Suppose the next face, the one adjacent to $e'$, is not thin.
+We simply add $\alpha \cdot (\ddd{\vec{e}} - \ddd{\vec{e'}})$
+to $w_e$,
+where $\alpha > 0$ is chosen small enough so that, in combination
+with the next $w_e$ term $\zeta_{\cev{e'}}$,
+$\theta_{e'}$ increases;
+for example, if the next term is $\zeta_{\cev{e'}} = \gamma_{\cev{e'}}$,
+then we choose $\alpha < \frac{1}{2r \cos \vphi_{\cev{e'}}}$,
+the coefficient of $\ddd{\vphi_{\cev{e'}}}$ in $\gamma_{\cev{e'}}$.
+If the next face is also thin,
+we add the same term, and so on, until we reach a non-thin face.
+It is straighforward to check that $\theta_e$ decreases,
+and all other affected $\theta_-$'s increase.
+\end{proof}
+
+\begin{prop}
+\label{p:nghd_lift}
+Let $c\in \CCC$ be as in \prpref{p:point_lift}.
+Given a smooth path $\gamma: [0,\infty) \to \TTT$
+starting at $\gamma(0) = \Theta(c)$
+and has constant value $(\sum \theta_e) \circ \gamma$,
+there exists $\veps > 0$ and a lift $\tilde{\gamma} :[0, \veps] \to \CCC$
+of $\gamma|_{[0,\veps]}$ along $\Theta$
+that starts at $\tilde{\gamma}(0) = c$
+and has constant value $\Phi \circ \tilde{\gamma}$.
+\end{prop}
+
+\begin{proof}
+By \lemref{l:Phi_full}, $\Phi$ is a submersion at $c$,
+hence is a submersion in a neighborhood $U \in \CCC$ of $c$.
+Thus, the kernels
+$K_{c'} = \ker(\Phi_*|{c'} : T_{c'} \CCC \to T_{\Phi(c')} \PPP)$
+form an $|E|$-plane distribution $K \subset T\CCC|_U$ over $U$.
+By \prpref{p:point_lift}, the bundle map
+$\Theta_*|_K : K \to L$ is full rank at $c$,
+hence it is full in a possibly smaller neighborhood,
+which we redefine $U$ to be.
+
+Since $\sum_{e \in E} \theta_e = 2\pi |E| - \sum_{f\in F} \Phi_f$,
+the fullness of $\Phi_*$ also shows that
+$\sum \theta$ has no critical points in $U$;
+for $s$ in some small interval around $(\sum \theta)(c)$,
+denote, by overloading notation,
+$L_s = (\sum \theta)^\inv (s)$,
+$U_s = U \cap \Theta^\inv(L_s)$.
+We may consider $K$ as a family of $|E|$-plane distributions
+$K_s$ over $U_s$.
+
+The vector $\rho := \sum_{f\in F} r_f \ddd{r_f}$ corresponds to
+scaling all radii by the same factor, and is clearly in $T\CCC$.
+It is obviously mapped to zero under $\Phi_*$ and $\Theta_*$,
+so $\Span\{\rho\} = \ker(\Theta_*|_K) \subset K$.
+Thus, over $U$, we may split
+$K = \Span\{\rho\} \oplus K'$
+(say as orthogonal decomposition w.r.t. some smooth metric on $\CCC$),
+so that $\Theta_*|{c'} : K'|_{c'} \simeq L_{\Theta(c')}$.
+
+In other words, $K'|_{U_s}$ is a horizontal $(|E|-1)$-plane distribution
+that determines an Ehresmann connection of the
+fibre bundle $U_s \to L_s$ (after being appropriately restricted).
+Therefore, a short path $\gamma$ starting at $\Theta(c)$
+with constant $\sum \theta$, i.e. a path in $L_s$, $s ={(\sum \theta)(c)}$,
+can be lifted to a path $\tilde{\gamma}$ in $U_s$,
+so that $\tilde{\gamma}$ is always tangent to $K'$,
+hence $\Phi(\tilde{\gamma})$ is constant.
+\end{proof}
+
+Finally let us say a few words in relation to the proof of hyperbolicity
+of augmented links, i.e. the proof of
+\thmref{t:auglink_hyp}.
+Using Theorem 4 from \cite{BandS},
+we obtain an angle-splitting for the $\pi/2$-angled
+torihedra in the torihedral decomposition
+of the original link $K$.
+This allows us to get a ``degenerate'' circle pattern
+for $\Gamma_T(L)$:
+an edge with label $\theta_e^* = \pi$
+separates a triangular face $t$ from a bowtie with a face $f$
+which corresponds to a face in the original graph $\Gamma_T(K)$;
+we will take the circumcircle of $t$ to be the same
+as that of $f$;
+an edge with $\theta_e^* = 0$
+then separates two circles that are tangent.
+Now we apply \prpref{p:nghd_lift},
+possibly adding some edges and
+using the $+$'s and $-$'s as in \figref{f:adding_edges},
+to obtain an extended circle pattern on $\Gamma_T(L)$
+that has all $\theta^* > 0$.
+By \lemref{l:circpattern_polyhedra},
+we obtain a decompositiion of the torihedron $\sT_T$
+into ideal hyperbolic pyramids.
+We do the same for the bottom torihedron $\sT_B$.
+Finally, as before, we can cut up these hyperbolic ideal pyramids
+into ideal tetrahedra,
+thus obtaining a hyperbolic triangulation of the link complement
+$\toruscomp{L}$.
+
+\begin{remark}
+It is not clear to us how to extend the proof of
+Theorem 3 \cite{BandS} to allow $\theta \geq \pi$,
+as we no longer have convexity of $S_{\text{Euc}}$.
+\end{remark}
 

### 2021-08-13 main.tex
some progress
main prop for pointwise statement done, next finish up the neighbourhood version.
testing branching
added references, cut out appendix

@@
-\documentclass{amsart}
-\usepackage{amssymb,amsfonts,amsmath}
-\usepackage[alphabetic,y2k,lite]{amsrefs}
+\documentclass[11pt]{amsart}
+\usepackage{float}
+\usepackage{amsfonts, amstext, amsmath, amsthm, amscd, amssymb, upgreek}
 \usepackage{bbm}
-\usepackage{graphicx}
-\usepackage{fullpage, mystyle}
+\usepackage{graphicx, color,  subfigure, wrapfig, overpic}
+\usepackage{fullpage}
+%\usepackage[all,cmtip]{xy} 
+%\usepackage{tikz}
 \usepackage{tikz-cd}
+%\usepackage{mystyle}
+
+\newcommand{\thmref}[1]{Theorem \ref{#1}}
+\newcommand{\prpref}[1]{Proposition \ref{#1}}
+\newcommand{\lemref}[1]{Lemma \ref{#1}}
+\newcommand{\figref}[1]{Figure \ref{#1}}
+\newcommand{\secref}[1]{Section \ref{#1}}
+\newcommand{\remref}[1]{Remark \ref{#1}}
+\newcommand{\eqnref}[1]{(\ref{#1})}
+%\newcommand{\ref}[1]{Figure \ref{#1}}
+\newcommand{\comment}[1]{}
+\newcommand{\inv}{{-1}} % annoying to type {-1} when taking inverse
+
+\textwidth 6.07in 
+\textheight 8.6in 
+\oddsidemargin 0.18in
+\evensidemargin 0.18in
+% \topmargin -0.07in
+
+%%  If the following line is uncommented, we see the labels of theorems, figures, etc. in the margins.
+% \usepackage[notref,notcite]{showkeys}
+\setlength{\marginparwidth}{0.8in}
+\let\oldmarginpar\marginpar
+\renewcommand\marginpar[1]{\oldmarginpar[\raggedleft\footnotesize #1]%
+{\raggedright\footnotesize #1}}
+
+%This command stops the Math Review numbers appearing in the references! 
+\AtBeginDocument{
+   \def\MR#1{}
+}
+\newcommand{\Sp}{{\rm{S}}}
+\newcommand{\C}{\mathbb{C}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\Q}{\mathbb{Q}}
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\N}{\mathbb{N}}
+\newcommand{\CC}{\mathbb{C}}
+\newcommand{\RR}{\mathbb{R}}
+\newcommand{\HH}{\mathbb{H}}
+\newcommand{\ZZ}{\mathbb{Z}}
+\newcommand{\bfloor}[1]{\left\lfloor #1\right\rfloor}
+\renewcommand{\P}{\mathcal P}
+\newcommand{\A}{\mathcal A}
+\newcommand{\W}{\mathcal W}
+\newcommand{\vol}{{\rm vol}}
+\newcommand{\cut}{{\backslash \backslash}}
+\newcommand{\bdy}{\partial}
+\newcommand{\voct}{{v_{\rm oct}}}
+\newcommand{\vtet}{{v_{\rm tet}}}
+\renewcommand{\L}{\mathcal L}
+\newcommand{\cp}{\mathcal{C}}
+\newcommand{\toF}{{\overset{F}{\longrightarrow}}}
+\newcommand{\K}{\upkappa}
+
+\def\co{\colon\thinspace}
 
 \newcommand{\torus}{{\mathbb{T}^2}}
+\newcommand{\sT}{{\mathcal{T}}}
 
@@
 
-%% for allowing other symbols to be arrow in tikzcd
-%% e.g. A \ar[r, symbol=\subseteq] & B
-\tikzset{
-  symbol/.style={
-    draw=none,
-    every to/.append style={
-      edge node={node [sloped, allow upside down, auto=false]{$#1$}}}
-  }
-}
+\newcommand{\del}{\partial}
+\newcommand{\ddd}[1]{{\frac{\del}{\del #1}}}
+\newcommand{\vphi}{\varphi}
+\newcommand{\veps}{\varepsilon}
+\newcommand{\llong}{{\text{long}}}
+\newcommand{\Span}{{\text{span}}}
+\newcommand{\Pol}{{\text{Pol}}}
+\newcommand{\toruscomp}[1]{{\torus \times I - #1}}
+
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{prop}[theorem]{Proposition}
+\newtheorem{claim}[theorem]{Claim}
+\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{example}[theorem]{Example}
+
+\newtheorem*{namedtheorem}{\theoremname}
+\newcommand{\theoremname}{testing}
+\newenvironment{named}[1]{\renewcommand{\theoremname}{#1}\begin{namedtheorem}}{\end{namedtheorem}}
+\theoremstyle{definition}
+\newtheorem{define}[theorem]{Definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{question}[theorem]{Question}
+\newtheorem{remark}[theorem]{Remark}
+
+\title{Hyperbolicity of Augmented Links in the Thickened Torus}
+
+\author[Alice Kwon and Ying Hong Tham]{Alice Kwon and Ying Hong Tham}
 
 \begin{document}
-
-\title{Variation on a Variational Principle}
-\author{Alice Kwon}
-   \address{TODO SUNY Maritime address}
-    \email{TODO email}
-    \urladdr{TODO webpage}
-\author{Ying Hong Tham}
-   \address{Department of Mathematics, Stony Brook University, 
-            Stony Brook, NY 11794, USA}
-    \email{yinghong.tham@stonybrook.edu}
-    \urladdr{http://www.math.sunysb.edu/\textasciitilde yinghong/}
+\maketitle
 
 \begin{abstract}
-We prove that alternating links in the thickened torus remain hyperbolic
-after certain augmentations.
+For a hyperbolic link $K$ in the thickened torus, We show there is a decomposition of the complement
+of a link $L$, obtained from augmenting $K$, into torihedra. We further decompose 
+the torihedra into angled pyramids and finally angled tetrahedra. These fit into an angled structure 
+on a triangulation of the link complement, and thus by \cite{Casson-Rivin}, this shows
+that $L$ is hyperbolic.  
 \end{abstract}
-\maketitle
 
-\input{intro}
-\input{notation}
-\input{results}
+\section{Introduction}
+\label{s:intro}
+
+Given a twist reduced diagram of a link $K$, \emph{augmenting} is a process in
+which an unknotted circle component (augmentation) is added to one or more twist
+regions (a single crossing or a string of bigons) of $K$. The added circle
+component allows us to remove full twists at the twist region of $K$. If the
+twist region has an odd number of crossings then all but one crossing is
+removed, whereas if the twist region has an even number of crossings then all
+are removed. The newly obtained link is called an \emph{augmented link} and the
+newly obtained diagram is called an \emph{augmented link diagram}. See Figure
+\ref{fig:Augmentations}.
+
+Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in
+$\Sp^3$ the link $L$ obtained by augmenting $K$ is hyperbolic. In this paper we
+investigate if this statement holds for links in the thickened torus i.e. if $L$
+is a link obtained from augmenting a hyperbolic alternating link $K$ in the
+thickened torus. We define augmenting similarly for links in the thickened torus
+with their associated link diagram on $\torus \times \{0\}.$
+
+Menasco \cite{Menasco} showed there are decompositions of the complements of
+alternating links in $\Sp^3$ into two polyhedra, a top polyhedron and a bottom
+polyhedron.  For alternating links $K$ in the thickened torus, Champanerkar,
+Kofman and Purcell \cite{CKP2} showed that there is a decomposition of the
+complement of $K$ into objects called torihedra, which we think of as
+counterparts to Menasco's decomposition of links in $\Sp^3$ into polyhedra, for
+links in the thickened torus. Just like Menasco's decomposition, one obtains a
+top and a bottom torihedron.
+
+In \secref{s:auglinks} we show that for augmented
+links in the thickened torus one can also obtain a decomposition of the
+complement into a top and bottom torihedron.  In \secref{s:hyperbolicity}, we
+prove that many augmented alternating links in the thickened torus are
+hyperbolic.
+
+We point out that \cite{kwon2020fully}, the first author
+proved that \emph{fully} augmented links in the thickened torus
+are hyperbolic, so this paper can be seen as a generalization
+of that work.
+
+While revising this papaer,
+we learned that \cite{adams2021generalized}
+proves a generalization of our work here,
+showing hyperbolicity of generalized augmented links
+in an arbitrary thickened surface.
+We note that our approach, based on angle structures,
+is different from theirs, which is based on topological arguments.
+
+ \begin{figure}
+ \centering  
+ \begin{tabular}{cc}
+ \includegraphics [height=4cm]{augmentation1.png}&
+  \includegraphics [height=4cm]{augmentation2.png}\\
+  (a)&(b)
+  \end{tabular}
+ \caption{The left shows a pretzel knot before augmentation and the right shows after augmentation}
+ \label{fig:augmentationS3}
+ \end{figure}
+
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\section{Augmented Links}
+\label{s:auglinks}
+
+Champanerkar, Kofman and Purcell have studied alternating links in the thickened torus \cite{CKP2}. They define a link in the thickened torus as a quotient of a biperiodic alternating link as follows,
+
+\begin{define}
+\label{def:biperiodiclink}
+A \emph{biperiodic alternating link} $\mathcal{L}$ is an infinite link
+which has a projection onto
+$\R^2$ which is invariant under an action of a two dimensional lattice $\Lambda$
+by translations, such that $L=\mathcal{L}/\Lambda$ is an alternating link in
+$\torus \times I$, where $I = (-1,1)$, with the projection on $\torus \times \{0\}$.
+We call $L$ a link diagram in $\torus \times I$.   
+\end{define}
+
+\begin{remark}
+Since $\torus \times I \cong \Sp^3 - H$, where $H$ is a Hopf link. The complement $\torus \times I- L = \Sp^3 - (L \cup H)$.
+\end{remark}
+
+Champanerkar, Kofman and Purcell \cite{CKP2} extended the definition of prime links in $\Sp^3$ for links in $\torus \times I$ called weakly prime.
+
+ \begin{define} \label{def:weaklyprime}
+	 A diagram of a link $L$ is \emph{weakly prime} if whenever a disk is embedded in the diagram surface meets the diagram transversely in exactly two edges, then the disk contains a simple edge of the diagram and no crossings.
+\end{define}
+
+\begin{define}
+A \emph{twist region} in a link diagram $L=\mathcal{L}/\Lambda$ in $\torus
+\times I$, is the quotient of a twist region in the biperiodic link
+$\mathcal{L}$. %a string of bigons, or a single crossing in the diagram on the
+universal cover of $\torus \times I$ is called a .  A biperiodic link
+$\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on
+the plane that intersects $\mathcal{L}$ transversely in four points, with two
+points adjacent to one crossing and the other two points adjacent to another
+crossing, the simple closed curve bounds a subdiagram consisting of a (possibly
+empty) collection of bigons strung end to end between these crossings. We say
+$L$ is \emph{twist-reduced} if it is the quotient of a twist-reduced biperiodic
+link.  \end{define}
+
+Now we can define augmentation for a link in $\torus \times I$ the same way we
+define augmentation for links in $\Sp^3$. For a link in $\torus \times I$, the
+crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
+Let $L$ be a twist reduced diagram in $\torus \times I$, we define
+\emph{augmenting} as a process in which an unknotted circle component is added
+to one or more twist regions of $L$. See Figure \ref{fig:Augmentations}
+
+\begin{figure}
+\centering
+\begin{tabular}{cccc}
+\includegraphics[width=3cm]{fig1.png}&
+\includegraphics[width=3cm]{twist-augment.png}&
+\includegraphics[width=3cm]{fig-2.png}\\
+ % \includegraphics [width=3cm]{fal}\\
+A&B&C
+\end{tabular}
+	 \caption{A: The top right has an odd number of twists while the bottom left has
+	 an even number of twists. B: The picture of the link on the right after
+	 augmentation twist regions circled in red. C: The link with the twists
+	 removed.}
+\label{fig:Augmentations}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Torihedral Decomposition of Augmented Alternating Links in Thickened Torus}
+
+We present a method of decomposing an augmented link in the thickened torus into
+objects called ``torihedra'' as defined below. The idea is to combine methods of Menasco
+\cite{Menasco} and the use of crossing edges between each crossing of our link
+and Lackenby's ``cut-slice-flatten" method \cite{lackenby} on the augmentation
+sites.
+
+\begin{define}\cite{CKP2}
+\label{def:torihedron}
+A \emph{torihedron} $\sT$ is a cone on the torus, 
+i.e. $\torus \times [0,1]/(\torus \times \{1\})$, with a cellular graph
+$G = G(\sT)$ on $\torus \times \{0\}$.
+An \emph{ideal torihedron} is a torihedron with the
+vertices of $G$ and the vertex $\torus \times \{1\}$ removed. Hence, an ideal
+torihedron is homeomorphic to $\torus \times [0,1)$ with a finite set of points
+(ideal vertices) removed from $\torus \times \{0\}$.
+We refer to the vertex $\torus \times \{1\}$ as the cone point.
+\end{define}
+
+For visualization purposes, we typically draw the graph $G(\sT)$ of a
+torihedron from the perspective of the cone point $\torus \times \{1\}$.
+
+If the faces of $G(\sT)$ are disks,
+then $\sT$ can be decomposed into a union of pyramids,
+obtained by coning each face to the cone point of $\sT$.
+This also gives a decomposition of the corresponding ideal torihedron
+into ideal pyramids.
+We call these the \emph{pyramidal decompositions} of $\sT$ and its
+ideal version.
+
+\begin{prop}\label{p:tori_decomp}
+Let $L$ be an augmented link in $\torus \times I$.
+%Let $G(L)$ be a diagram of the link on $\torus \times \{0\}$.
+There is a decomposition of the complement,
+$(\torus \times I) - L$ into two ideal torihedra.
+\end{prop}
+
+\begin{proof}
+We will begin by assuming that there are no half twists. 
+Arrange the link diagram of $L$ in the following way: first place the added
+circle components perpendicular to the projection plane, $\torus
+\times \{0\}$ leaving the remaining part of the link parallel to the projection
+plane.  We now place a crossing edge on each crossing of the link so that for
+each crossing edge, one end of the edge lies on a bottom strand while the other
+end lies on a top strand as in Figure \ref{fig:crossingArc} left.
+
+\begin{figure} 
+\centering 
+\includegraphics[width=4cm]{crossingArc.png}
+\includegraphics[width=5cm]{crossingPush.png}
+\caption{Left: The black strands are
+part of the link and the red strand is the crossing edge. Right: The blue and
+red edges represent the split crossing edges and the shaded half disk is bounded
+by the crossing circle} 
+\label{fig:crossingArc} 
+\end{figure}
+
+\indent We view the link from the point at infinity from the top. We will push
+the top strand to the bottom strand, splitting the crossing edge into two
+identical edges as in Figure \ref{fig:crossingArc} right. We push the link
+components to infinity and stretch the crossing edge so that we have flattened
+the link onto $\torus \times \{0\}$ except for the crossing circles which will
+remain perpendicular to the projection plane.
+
+\indent Now place a disk on each crossing circle, so that the disk is bounded by
+the crossing circle. We can then cut $\torus \times I$ along $\torus \times \{0\}$ and
+focus on the top half, $\torus \times [0,1)$. We will follow the same method on the
+bottom half to obtain the second identical torihedron. The disk we place on each
+crossing circle is now cut in half. This half disk is now bounded by the
+projection plane and the semi-cricle arc of the crossing circle. We push down on
+the crossing circle and split the disk into two identical disks. We then push
+the arc of each crossing circle to infinity, collapsing them to ideal vertices.
+We obtain two triangular faces which represent the disk which look like a
+bow-tie as in Figure \ref{fig:falGluings}.
+
+\begin{figure}
+ \centering
+ \begin{tabular}{cc}
+ \includegraphics [width=8cm]{falGluing1.png}&
+ \includegraphics [width=7cm]{falGluing2.png}\\
+ (a)&(b)
+ \end{tabular}
+	\caption{(a) Gluing of bow-ties without half-twists
+	(b) Gluing with half-twists}
+ \label{fig:falGluings}
+ \end{figure}
+
+\indent We repeat the steps for the bottom half of $\torus \times I$, $\torus \times
+(-1,0]$. Then we get two torihedra. The graph of each will come from
+crossing edges and edges of the disk. Now, if there are half twists we will
+decompose the complement of the link the same way as if there are no half twists
+and we will identify the two bow-ties as in Figure \ref{fig:falGluings}.
+Finally,
+we obtain the complement of the link by gluing the two torihedra with the gluing
+information given by identifying crossing edges and triangles of the bow-tie. We
+glue the faces of the torihedra which do not correspond to a bow-tie with a
+$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
+\ref{fig:top-bottom} clockwise or counterclockwise.
+
+For future reference, we will denote the graph for the top and bottom
+torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
+where both graphs are viewed from the cone point of the top torihedron
+$\torus \times \{1\}$.
+Note that if $L = K$ is the non-augmented link,
+$\Gamma_T(L)$ is simply the link projection $K$,
+and in fact $\Gamma_T(K) = \Gamma_B(K)$.
+
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Figures \ref{fig:step_one} to \ref{fig:top-bottom} is an example which decomposes the link (C) of Figure
+\ref{fig:Augmentations}.
+
+\begin{figure}[h] 
+\centering
+\includegraphics[height=3cm]{fig-3.png}
+\includegraphics[height=3cm]{fig-4.png}
+	\caption{Each crossing circle bounds a twice-punctured disk}
+	\label{fig:step_one}
+\end{figure}
+
+%\vspace{-0.5cm} 
+\begin{figure}[h] 
+\centering 
+\includegraphics[height=3cm]{fig-5.png} 
+	\caption{We split the disk and collapse the arc of each
+ crossing circle to ideal vertices}
+	\label{fig:step_two}
+\end{figure}
+
+\begin{figure}[h] 
+\centering 
+\includegraphics[height=3cm]{fig-6.png} 
+\caption{Left: The crossing arc is the edge in red.
+Middle: Picture of splitting the crossing edge. Right: The link component is
+pushed off to infinity.}
+	\label{fig:step_three}
+\end{figure}
+
+\begin{figure}[h] 
+\centering 
+\includegraphics[height=3cm]{top-bottom.png} 
+	\caption{Left: The top torihedron. Right: The bottom torihdron with rotation for face gluing.} 
+\label{fig:top-bottom}
+\end{figure}
+
+\begin{definition}
+An \emph{angled torihedron} $(\sT, \theta_\bullet^*)$
+is a torihedron $\sT$ with
+an assignment $\theta_e^* \in [0,\pi]$
+such that for each vertex $v \in G(\sT)$,
+$\sum_{e \ni v} \theta_e^* = (\deg(v) - 2)\pi$.
+We also denote $\theta_e = \pi - \theta_e^*$,
+so $\sum_{e \ni v} \theta_e = 2\pi$;
+we refer to $\theta_e$ as the exterior angle
+and $\theta_e$ as the interior angle.
+
+We say $(\sT, \theta_\bullet^*)$ is \emph{degenerate}
+if $\theta_e^* = 0$ for some edge;
+we say it is \emph{non-degenerate} otherwise.
+\end{definition}
+
+One may ask for the pyramidal decomposition of a torihedron
+to ``respect" angles. The following definitions,
+in particular an ``angle splitting'', make sense of this.
+
+\begin{define}
+An \emph{angled ideal tetrahedron} is an ideal tetrahedron with an assignment of a dihedral angle
+to each edge, such that
+\begin{itemize}
+\item each dihedral angle is in $[0, \pi]$;
+\item for each tetrahedron, opposite edges have equal dihedral angles;
+\item the three distinct angles sum to $\pi$.
+\end{itemize}
+
+We say a angled ideal tetrahedron is \emph{degenerate} if
+one dihedral angle is 0; we say it is \emph{non-degenerate} otherwise.
+\end{define}
+
+\begin{define}
+A \emph{base-angled ideal pyramid}
+is a pyramid whose base is an $n$-gon, $n \geq 3$,
+and each boundary edge $e_i$ of the base face is assigned a dihedral angle
+$\alpha_i \geq 0$ such that the sum is $\sum \alpha_i = 2\pi$.
+The vertical edge $e_i'$ that meets $e_i$ and $e_{i+1}$
+is automatically assigned the dihedral angle $\pi - \alpha_i - \alpha_{i+1}$.
+
+We say a base-angled ideal pyramid is \emph{degenerate} if
+$\alpha_i = 0$ for some $i$; we say it is \emph{non-degenerate} otherwise.
+\end{define}
+
+Clearly, the dihedral angles of an ideal hyperbolic pyramid
+make it a base-angled ideal pyramid
+(with $\alpha_i = \vphi_{e_i}$);
+it is not hard to see that the converse is true:
+simply consider a circumsribed polygon such that the side $e_i$
+subtends an angle of $2\alpha_i$ at the center,
+and take the ideal hyperbolic pyramid over it in upper-half space.
+Also, an angled ideal tetrahedron is simply a base-angled ideal pyramid
+with base a triangle, and with no preferred face.
+
+\begin{definition}
+%TODO: this definition should come after base-angled pyramid
+An \emph{angle splitting} of an angled torihedron $(\sT,\theta_\bullet^*)$
+is a splitting of $\theta_e^* = \vphi_{\vec{e}} + \vphi_{\cev{e}}$
+for each edge $e$,
+such that for each face $f$,
+$\sum_{\vec{e} \in \del f} \vphi_{\vec{e}}^* = \pi$.
+
+Equivalently, an angle splitting is a decomposition of
+$\sT$ into base-angled pyramids,
+one for each face of $G(\sT)$, such that
+for each boundary edge $e$ of $\sT$,
+the dihedral angles from the two adjacent pyramids
+add to $\theta_e^*$.
+\end{definition}
+
+\begin{remark}
+These $\theta$'s are related to the $\theta$'s in
+\cite{BandS},
+and the $\vphi$'s are related to their ``coherent angle system''.
+\end{remark}
+
+%TODO remark on what splitting means in terms of ideal hyperbolic
+
+\begin{lemma}
+\label{l:pyramid_decomp}
+%Let $P_n$ be an ideal pyramid whose base is an $n$-gon and suppose,
+%\begin{itemize}
+%\item each boundary edge of the base face is assigned a dihedral angle $\alpha_i$ such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$;
+%\item we are given a decomposition of the base face into triangles by adding new edges. 
+%\end{itemize}
+Let $P_n$ be a base-angled ideal pyramid, and suppose we are given a
+decomposition of the base face into triangles by adding new edges.  One gets an
+obvious corresponding triangulation of $P_n$, where a new face is added for each
+new edge. Then there is an assignment of a dihedral angle to each edge of each
+ideal tetrahedron in this triangulation such that
+\begin{itemize}
+\item each tetrahedron is an angled ideal tetrahedron;
+\item the sum of dihedral angles around each new edge is $\pi$;
+\item the dihedral angles of the edges of the original base face are the same as
+	before.
+\end{itemize} 
+\end{lemma}
+
+\begin{proof}
+Induct on $n$; there is nothing to prove for the base case $n=3$.
+
+The proof is essentially given in Figure \ref{f:ideal_pyramid_arg}.
+
+\begin{figure}
+\includegraphics[height=5cm]{more_pictures/angle_split.png}
+\caption{Angle-splitting on a polygonal face of the graph}
+\label{f:ideal_pyramid_arg}
+\end{figure}
+
+Suppose the edges are labeled $e_i$,
+which goes between vertices $v_i$ and $v_{i+1}$,
+and suppose $e_i$ is assigned dihedral angle $\alpha_i$.
+Let $e'$ be a new edge addeed to the base face of $P_n$
+such that it separates the base face into a triangle and
+an $(n-1)$-gon;
+suppose the sides of the triangle are
+$e_i, e_{i+1}$, and $e'$.
+The new face corresponding to $e'$ separates $P_n$ into
+an ideal tetrahedron $T$ and an ideal pyramid $P_{n-1}$.
+We assign the dihedral angle of $\pi - \alpha_i - \alpha_{i+1}$
+to $e'$ in $T$, and assign $\alpha_i + \alpha_{i+1}$ to $e'$ in $P_{n-1}$.
+Clearly the sum of dihedral angles condition is satisfied
+in $T$ and $P_{n-1}$.
+It remains to check that the dihedral angles assigned to the vertical (non-base)
+edges are correct.
+For the vertical edge associated to $v_j$ for $j \neq i, i+2$,
+there is nothing to check;
+for $j = i$, the dihedral angles are
+$\pi - \alpha_i - (\pi - \alpha_i - \alpha_{i-1})$
+in $T$ and $\pi - \alpha_{i-1} - (\alpha_i + \alpha_{i+1})$ in $P_{n-1}$,
+which sum to $\pi - \alpha_i - \alpha_{i+1}$;
+it is similar for $j = i+2$.
+
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Hyperbolicity of Augmented Links}
+\label{s:hyperbolicity}
+Thurston introduced a method for finding the unique hyperbolic metric for a
+given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}. The idea
+was to triangulate the interior of $M$ into ideal tetrahedra and give those
+tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently
+in $M$. The shape parameter of a tetrahedron is described by the cross-ratio of
+its four vertices on the sphere at infinity. Thurston had written down a system
+of gluing equations with shape parameters whose solutions correspond to the
+complete hyperbolic metric on the interior of $M$. Casson and Rivin separated
+gluing equations into a linear and non-linear part \cite{Casson-Rivin}. Angle
+structures is the linear part of Thurston's gluing equations, and what we will
+use to attain hyperbolicity of complements of augmented links in the thickened
+torus.
+
+\begin{define}
+Let $M$ be an orientable 3-manifold with boundary consisting of tori. An angle
+structure on an ideal triangulation $\tau$ of $M$ is an assignment of a dihedral
+angle to each edge of each tetrahedron, such that
+\begin{itemize}
+\item each tetrahedron is a non-degenerate angled ideal tetrahedron,
+\item around each edge of $\tau$, the dihedral angles sum to $2\pi$.
+\end{itemize}
+\end{define}
+
+\begin{theorem}\cite{Casson-Rivin}\label{thm:Casson-Rivin}
+Let $M$ be a 3-manifold admitting an angle structure. Then $M$ is hyperbolic.
+\end{theorem}
+
+For a hyperbolic link $K$ in $\torus \times I$, we show
+that the resulting link obtained from augmenting $K$ is
+hyperbolic. The idea is to start with a graph from the torihedral decomposition
+of the link $K$ which will give us a graph on each torihedron with an angle
+assignment of
+$\pi/2$ for edge
+\cite{CKP2},
+the angled torihedra can be further decomposed into base-angled pyramids.
+By \prpref{p:tori_decomp},
+there is a torihedral decomposition of the complement of the augmented link $L$.
+Using those angles,
+we then assign angles to edges of these torihedra
+and decompose them into base-angled pyramids.
+These pyramids can be further decomposed into tetrahedra,
+thus obtaining an angle structure on a triangulation.
+In the Appendix, we show that this triangulation
+also has an angle structure that
+satisfies Thurston's gluing equations.
+
+\begin{define}
+We say an augmentation is \emph{right-augmented} if, when both strands are
+(locally) oriented such that they cross the augmentation disk in the same
+direction, the crossing is a positive right-handed half-twist.
+See Figure \ref{f:right_left_aug}.
+We say an augmentation is \emph{left-augmented} if it is not right-augmented.
+\end{define}
+
+\begin{figure}
+\includegraphics[width=5cm]{more_pictures/right_left_aug.png}
+\caption{R: right augmentation, L: left augmentation}
+\label{f:right_left_aug}
+\end{figure}
+
+We can recover $L$ from the link diagram of $K$
+together with labels at vertices indicating left- or right-augmentation.
+
+\begin{lemma}
+\label{l:2fe}
+Let $G$ be a 4-valent graph on $\torus$ with no bigons or self-loops.
+%and whose faces can be checkerboard colored.
+Then for any subset $F' \subseteq F$ of faces,
+\[
+	2\chi(F') \leq |E'|
+\]
+where $E' = \cup_{f \in F'} \del f$ is the set of edges
+that meets some face of $F'$,
+and $\chi(F') = \sum_{f\in F'} \chi(f)$ is the sum
+of the Euler characteristics of faces in $F'$.
+\end{lemma}
+
+\begin{figure}
+\includegraphics[width=11cm]{bigon_crush.png}
+\caption{Resolving internal vertex; eliminating bigons via ``crushing"}
+\label{f:bigon_crush}
+\end{figure}
+
+\begin{proof}
+We induct on $\chi(F')$ (over all possible such graphs $G$);
+for $F' = \emptyset$, there is nothing to prove.
+
+Call a vertex or edge \emph{interior} if it does not meet
+$F'' = F \backslash F'$.
+Suppose there is an interior vertex $v$.
+Make the modification as in Figure \ref{f:bigon_crush}
+(later we will choose which way to ``resolve'' the vertex).
+This decreases $\chi(F')$ by one and $|E'|$ by 2.
+However, this process may produce bigons;
+if it does, repeatedly eliminate bigons by either
+(1) performing the modification as in Figure \ref{f:bigon_crush}
+if the two vertices of the bigon are distinct,
+or (2) remove the bigon completely if the two vertices
+of the bigon are the same.
+Each of these steps also decreases $\chi(F')$ by one and $|E'|$ by 2
+(note in the second case, after removing the bigon,
+the operation merges two distinct faces or joins a face to itself;
+this adds an $S^1$, thus does not change the (total) euler characteristic
+of the two faces or the one face).
+
+We must check that this process terminates with a graph
+which satisfies the hypotheses set out in the lemma.
+It is clear that %checkboard colorability and
+4-valency is maintained
+at each step, and there will not be any bigons at the end.
+We need to ensure that eliminating bigons does not
+create self-loop edges.
+Here we specify how to choose which way to resolve the internal
+vertex $v$. If among the four faces touching $v$,
+one of them has greater than three sides (Case 1),
+then resolve $v$ so that this face is not merged;
+if all four faces are triangles (Case 2),
+simply resolve in an arbitrary manner.
+After the modification of the internal vertex,
+at most two bigons are created;
+eliminate those two bigons.
+Now we find that all bigons will be connected end-to-end
+(i.e. forming a single twist region) -
+this is because in Case 1, only one bigon was present after smoothing
+$v$, which would result in at most two bigons that would be connected;
+and if we were in Case 2, we find that the face between those
+eliminated bigons (coming from merging the two triangles across $v$)
+will become a bigon too,
+thus connecting the potential bigons on either ends.
+
+Therefore, one can eliminate bigons in an order so that
+they belong in one twist region;
+in particular, the (not necessarily distinct) faces on either side
+are not bigons,
+so eliminating the bigon does not produce a self-loop edge.
+
+Now suppose $G$ has no interior vertices.
+We perform some reductions.
+We remove all $f$ from $F'$ that have non-positive Euler characteristic,
+as doing so will not decrease $\chi(F')$ and will not increase $|E'|$.
+Now consider some $f\in F'$.
+If it has at least two boundary (i.e. non-interior) edges,
+we can remove $f$ from $F'$,
+which decreases $\chi(F')$ by 1 and $|E'|$ by at least 2.
+Thus we remove all such $f$.
+
+Now suppose $f\in F'$ has three contiguous interior edges
+$e_1,e_2,e_3$.
+(e.g. if $f$ has at least four sides).
+Let $v_1, v_2$ be the vertices between these three interior edges.
+Since $v_1$ is not interior,
+the face across $v_1$ from $f$ is not in $F'$;
+likewise with $v_2$.
+But this shows that the face across $e_2$ from $f$
+has two boundary edges, contradicting our reduction.
+%This would lead to the situation in \ref{},
+%showing that there is a face with at least
+%two boundary edges, contradicting our reduction.
+
+Thus, we now have a graph whose faces are triangles,
+and each face has exactly one boundary edge.
+Now the problem is solved with a simple counting argument:
+each $f$ corresponds to one boundary edge and two interior edges,
+but, since the interior edges are shared by two faces,
+they should count as half an edge; so
+\[
+ |E'| = \sum_{f\in F'} 1 + 1/2 + 1/2 = 2|F'| = 2\chi(F')
+\]
+and we get the desired result.
+\end{proof}
+
+The following theorem is quoted from \cite{BandS}
+(see also \cite{FF})
+
+\begin{theorem}[Feasible Flow Theorem]
+\label{t:feasible_flow}
+Let $(N,X)$ be a directed graph,
+with a \emph{lower capacity bound} $a_x$
+and \emph{upper capacity bound} $b_x$
+for each directed edge $x \in X$,
+with $-\infty \leq a_x \leq b_x \leq \infty$.
+A \emph{feasible flow} is a function $\vphi : X \to \RR$
+such that $\vphi_x \in [a_x, b_x]$ and
+Kirchhof's current law is satisfied
+(i.e. flow in = flow out at every vertex).
+
+A feasible flow exists if and only if,
+for every proper nonempty subset $N' \subset N$,
+\[
+\sum_{x \in ex(N')} b_x \geq \sum_{x \in in(N')} a_x
+\]
+where $ex(N'), in(N')$ refer to edges leaving,
+entering $N'$, respectively.
+\end{theorem}
+
+\begin{theorem}
+\label{t:auglink_hyp}
+Let $K$ be a weakly prime, alternating link whose diagram has no bigons.
+Let $L$ be a link obtained from augmenting $K$.
+Then $L$ is hyperbolic.
+\end{theorem}
+
+\begin{proof}
+By \cite[Theorem 7.5]{CKP2},
+(as discussed in \prpref{p:tori_decomp},)
+$\toruscomp{K}$ can be decomposed
+into two torihedra $\sT_T$ and $\sT_B$,
+whose graphs are $\Gamma_T(K), \Gamma_B(K)$ respectively;
+viewed from the top cone point $\torus \times \{1\}$,
+they are both the same as the projection graph of $K$.
+%which we denote by $\Gamma$.
+We make them non-degenerate angled torihedra by assigning $\theta^* = \pi/2$
+for all edges.
+
+We obtain an angle-splitting by applying the
+Feasible Flow theorem (\thmref{t:feasible_flow}) as follows:
+Consider the directed graph whose vertex set is
+$E \cup F \cup \{*\}$,
+where $E, F$ are the set of edges, faces of $\Gamma_T(K)$ respectively,
+%and $*$ is some abstract vertex.
+and there is a directed edge
+\begin{itemize}
+\item $* \to f$ for each face $f\in F$, with capacity interval
+	$[\pi, \infty)$,
+\item $f \to e$ for each edge $e \in \del f$,
+	with capacity interval $[\veps, \infty)$
+	for some $\veps>0$ to be set later,
+\item $e \to *$ for each edge $e$, with capacity interval
+	$(-\infty, \pi/2]$.
+\end{itemize}
+By \lemref{l:2fe}, $2|F'| = 2\chi(F') \leq |E'|$,
+and taking $\veps < \pi / |\text{max face size}|$,
+the feasible flow condition is satisfied,
+so a feasible flow exists.
+Since $2|F| = |E|$, the capacity interval restrictions
+on the flow at $*$ is sharp, so out-edges at $*$
+have flow $\pi$ and in-edges at $*$ have flow $\pi/2$.
+Then the flow $f \to e$ gives us $\vphi_{\vec{e}}$,
+where $f$ is the face to the left of $\vec{e}$.
+(We adapted this argument from \cite{BandS}).
+
+\begin{figure}
+\includegraphics[width=7cm]{more_pictures/horizontal_bowtie.png}
+\caption{Angle assignments on a bow-tie corresponding to an augmentation site}
+\label{f:bowtie_angles}
+\end{figure}
+
+By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
+obtained by gluing two torihedra $\sT_T(L),\sT_B(L)$
+with graphs $\Gamma_T(L),\Gamma_B(L)$.
+We make them degenerate angled torihedra by assigning $\theta^*$'s
+to edges of the bow-ties as in Figure \ref{f:bowtie_angles},
+and assign $\pi/2$ to all other edges.
+It is easy to check that upon gluing,
+each edge has sum of dihedral angles ($\theta^*$) equals $2\pi$.
+(This holds true even if they were glued assuming
+some augmentations had no half-twist; see \remref{r:nohalftwist}.)
+
+Furthermore, we can obtain an angle-splitting of $\sT_T(L)$
+(and similarly $\sT_B(L)$) by modifying the angle-splitting
+for $\sT_T(K)$;
+this is shown in Figure \ref{f:bowtie_angles2}.
+
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width = 5cm]{before_bowtie_angles.png}&
+\includegraphics[width = 5cm]{bowtie_angles.png}\\
+(a)&(b)
+\end{tabular}
+\caption{(a) Angles before augmentation (b) Angle splitting for bowtie corresponding to augmentation}
+\label{f:bowtie_angles2}
+\end{figure}
+
+Now we have a decomposition of the two torihedra into
+degenerate base-angled pyramids.
+However, we need the pyramids to be non-degenerate,
+so we first need to modify the angles and graph on the torihedra
+to make all $\theta^*$ nonzero.
+
+Consider a face $f$ of $\Gamma_T(L)$ that is not in a bow-tie.
+Suppose the corresponding face $\bar{f}$ of $\Gamma$,
+the projection graph (which is equal to $\Gamma_T(K)$),
+had vertices $v_1,\ldots,v_n$ in counter-clockwise order.
+We label the edges of $f$ by $e_{i,0}$, $e_{i,\pi}$, or $e_i$,
+depending on whether the $\theta^*$ is $0$, $\pi$, or $\pi/2$ respectively,
+with $i$ non-decreasing from 1 to $n$,
+adjacent edges having the same $i$ if and only if they
+belong to the same bow-tie.
+For sake of concreteness,
+suppose that if a vertex $v_i$ is right-augmented,
+then the augmentation circle intersects $\bar{f}$
+(everything is similar if it is left-augmented vertices' circles
+that intersect $\bar{f}$).
+In other words, locally, $f$ meets two of the edges of the bow-tie
+corresponding to a right-augmented vertex $v_i$
+(which would be labeled $e_{i,0}, e_{i,\pi}$ in counter-clockwise order),
+but only meets one of the edges of the bow-tie corresponding to
+a left-augmented vertex.
+
+Suppose, after cyclically reindexing, $v_1,\ldots,v_k$
+is a maximally contiguous subsequence of left-augmented vertices
+of $G(K)$ around the face $\bar{f}$;
+the edges around $f$ would start
+$e_{1,0}, e_{1,\pi}, e_{2,0}, e_{2,\pi}, \ldots$.
+We add new edges across $f$ as follows.
+(See Figure \ref{f:adding_edges};
+ignore the + and - signs for now.)
+
+First suppose $k=n$; then we do nothing.
+
+Next suppose there is only one such maximal contiguous subsequence.
+If $k = 1$, we add an edge that goes across
+$e_{1,0},e_{1,\pi},e_2$
+(in the sense that the new edge separates the edges of $f$ into two sets,
+one of them being those three edges;
+since $n\geq 3$, this edge is new).
+%If $k = 2$, we add edge across $e_{1,0},e_{1,\pi}$
+%and another edge across $e_{2,0},e_{2,\pi}$
+%(these two edges do not form a bigon because we've ruled out $k=n$).
+%(these two edges do not form a bigon because we've ruled out $k=n$).
+If $k \geq 2$,
+we add an edge across $e_{1,0},e_{1,\pi}$
+and another edge across $e_{2,0},e_{2,\pi},e_{3,0},\ldots,e_{k,\pi}$
+(these two edges do not form a bigon because we've ruled out $k=n$).
+%(again these two edges do not form a bigon).
+
+Finally, if there are multiple such maximal contiguous subsequences,
+we just add edges as above for each contiguous subsequence.
+The only caveat is that if the procedure calls to add a new edge
+that would form a bigon with the existing edges,
+we just do not add it.
+
+This way we obtain a new graph $\Gamma_T(L)'$, which defines a
+new torihedron $\sT_T(L)'$.
+We make $\sT_T(L)'$ angled using the angles from $\sT_T(L)$ for old edges,
+and putting $\pi$ for all new edges.
+
+\begin{figure}
+\includegraphics[width=5cm]{more_pictures/one_edge.png}
+%\includegraphics[width=5cm]{more_pictures/two_edge.png}
+\includegraphics[width=5cm]{more_pictures/two_edge_many.png}
+\caption{Red edge indicates an added edge to the graph to appropriately assign +/- labels which indicate 
+increasing/decreasing angles on the edge respectively.}
+\label{f:adding_edges}
+\end{figure}
+
+Now we deform the $\theta^*$ based on Figure \ref{f:adding_edges},
+increasing/decreasing by some small $\veps' > 0$ if the edge
+is labeled $+/-$.
+Note some edges may be labeled twice, in which case we perform
+both increasing/decreasing (e.g. if it is labeled $+$ and $-$,
+the $\theta^*$ is not changed).
+It is easy to see that the sum of $\theta^*$ around a vertex
+remains unchanged.
+Furthermore, all the edges with $\theta^*$ originally equal 0,
+i.e. all $e_{i,0}$'s,
+now have positive $\theta^*$,
+(it receives only one label $+$,
+because the other face it meets is a bow-tie).
+
+%Thus, we could attempt to apply the feasible flow theorem in a similar manner,
+%and obtain an angle-splitting for $\sT_T(L)'$, but 
+%TODO rephrase nicely.
+We can directly get an angle-splitting for $\sT_T(L)'$
+using the angle-splitting for $\sT_T(L)$.
+We reuse the $+/-$ assignments from Figure \ref{f:adding_edges}.
+For $e = e_{i,0}$, we increase $\vphi_{\vec{e}}, \vphi_{\cev{e}}$
+by $\veps'/2$ each; for $e = e_{i,\pi}$,
+we decrease them by $\veps'/2$ each.
+For other edges, we increase/decrease $\vphi_{\vec{e}}$ by $\veps'$,
+where $\vec{e}$ is the oriented edge corresponding to the side
+on which the $+/-$ sign appears in Figure \ref{f:adding_edges};
+so for example, if an edge $e$ receives both $+$ and $-$,
+then one of $\vphi_{\vec{e}},\vphi_{\cev{e}}$ increases
+while the other decreases, thus $\theta_e^*$ remains constant.
+
+Now we address $\sT_B(L)$.
+In the gluing of $\sT_T(L)$ to $\sT_B(L)$,
+non-bow-tie faces of $\Gamma_T(L)$ are identified with
+non-bow-tie faces of $\Gamma_B(L)$.
+Under this identification, we add the same edges to $\Gamma_B(L)$,
+thus obtaining the new torihedron $\sT_B(L)'$ with graph
+$\Gamma_B(L)'$.
+We perform the same deformations of $\theta^*$'s (or $\vphi$'s).
+
+We need to check that upon gluing $\sT_T(L)'$ to $\sT_B(L)'$,
+the sum of dihedral angles around each edge is still $2\pi$.
+This was clearly true before deforming, as the new edges of
+$\Gamma_T(L)'$ only gets identified with the unique
+corresponding edge of $\Gamma_B(L)'$, and they are both labeled
+with $\theta^* = \pi$.
+To see that the deformation does not change these sums,
+note that in the identification of faces of $\Gamma_T(L)'$
+to $\Gamma_B(L)'$,
+an edge with $\theta^*=0$ is identified with an edge with
+$\theta^*=\pi$,
+so an increase in the former would be conterbalanced by
+a decrease in the latter.
+It is also easy to see this is the case for the other edges.
+(Once again, a similar argument applies if $\sT_(L)'$
+and $\sT_B(L)'$ are glued assuming
+some augmentations had no half-twist; see \remref{r:nohalftwist}.)
+
+Finally, for each face of $\Gamma_T(L)'$ that has more than three sides,
+we arbitrarily decompose it into triangles
+and apply \lemref{l:pyramid_decomp}
+to obtain a triangulation of $\sT_T(L)'$ into non-degenerate angled tetrahedra;
+perform the corresponding decomposition for faces of
+$\Gamma_B(L)'$ and obtain a triangulation of $\sT_B(L)'$
+into non-degenerate angled tetrahedra.
+Upon gluing, this gives an angle structure on the triangulation
+of $\toruscomp{L}$
+\end{proof}
+
+\begin{remark}
+\label{r:nohalftwist}
+If the original link $K$ had some twist regions with at least one bigon,
+we may consider augmentations $L$ where all such twist regions
+are augmented, i.e. $L$ may have augmentations without half-twists.
+Then, as pointed out in proof of \thmref{t:auglink_hyp} above,
+the proof still works for $L$, showing that $L$ is also hyperbolic.
+\end{remark}
+
+\bibliographystyle{plain}
+\bibliography{references-ak}
 

### 2021-08-16 main.tex
fixes stuff

@@
 which an unknotted circle component (augmentation) is added to one or more twist
-regions (a single crossing or a string of bigons) of $K$. The added circle
+regions (a single crossing or a maximal string of bigons) of $K$. The added circle
 component allows us to remove full twists at the twist region of $K$. If the
@@
 removed, whereas if the twist region has an even number of crossings then all
-are removed. The newly obtained link is called an \emph{augmented link} and the
-newly obtained diagram is called an \emph{augmented link diagram}. See Figure
+are removed. We can remove full twists by a standard argument using a Dehn twist 
+on the complement of the crossing circle. The newly obtained link is called an 
+\emph{augmented link} and the newly obtained diagram is called an 
+\emph{augmented link diagram}. See Figure
 \ref{fig:Augmentations}.
@@
 Menasco \cite{Menasco} showed there are decompositions of the complements of
-alternating links in $\Sp^3$ into two polyhedra, a top polyhedron and a bottom
+alternating links in $\Sp^3$ into two topological polyhedra, a top polyhedron and a bottom
 polyhedron.  For alternating links $K$ in the thickened torus, Champanerkar,
@@
 
-While revising this papaer,
+While revising this paper,
 we learned that \cite{adams2021generalized}
@@
 $\torus \times I$, where $I = (-1,1)$, with the projection on $\torus \times \{0\}$.   
-We call $L$ a link diagram in $\torus \times I$.   
 \end{define}
@@
 \begin{define}
-A \emph{twist region} in a link diagram $L=\mathcal{L}/\Lambda$ in $\torus
+A \emph{twist region} in a link diagram of $L=\mathcal{L}/\Lambda$ in $\torus
 \times I$, is the quotient of a twist region in the biperiodic link
-$\mathcal{L}$. %a string of bigons, or a single crossing in the diagram on the
-universal cover of $\torus \times I$ is called a .  A biperiodic link
+$\mathcal{L}$. 
+%a string of bigons, or a single crossing in the diagram on the universal cover of $\torus \times I$ is called a .  
+A biperiodic link
 $\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on
-the plane that intersects $\mathcal{L}$ transversely in four points, with two
+the plane that intersects the diagram of $\mathcal{L}$ transversely in four points, with two
 points adjacent to one crossing and the other two points adjacent to another
@@
 empty) collection of bigons strung end to end between these crossings. We say
-$L$ is \emph{twist-reduced} if it is the quotient of a twist-reduced biperiodic
-link.  \end{define}
+the diagram of $L$ is \emph{twist-reduced} if it is the quotient of a twist-reduced biperiodic
+link diagram.  \end{define}
 
@@
 crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
-Let $L$ be a twist reduced diagram in $\torus \times I$, we define
+Let $D(L)$ be a twist reduced diagram of a link $L$ in $\torus \times I$, we define
 \emph{augmenting} as a process in which an unknotted circle component is added
-to one or more twist regions of $L$. See Figure \ref{fig:Augmentations}
+to one or more twist regions of $D(L)$. See Figure \ref{fig:Augmentations}
+
+\begin{remark}
+If $L$ is augmented at \emph{every} crossing/twist site we say $L$ is \emph{fully} augmented.
+\end{remark}
 
@@
 	 an even number of twists. B: The picture of the link on the right after
-	 augmentation twist regions circled in red. C: The link with the twists
+	 augmentation twist regions circled in red. C: The link with full twists
 	 removed.}
@@
 
-We present a method of decomposing an augmented link in the thickened torus into
-objects called ``torihedra'' as defined below. The idea is to combine methods of Menasco
+We present a method of decomposing an augmented link (not necessarily fully augmented) 
+in the thickened torus into
+objects called ``torihedra'' as defined below.  Decomposing alternating links in the thickened torus into 
+torihedra were first described in \cite{CKP2} then later used for fully augmented links in 
+the thickened torus in \cite{kwon2020fully}.
+The idea is to combine methods of Menasco
 \cite{Menasco} and the use of crossing edges between each crossing of our link
@@
 $G = G(\sT)$ on $\torus \times \{0\}$.
-An \emph{ideal torihedron} is a torihedron with the
+The \emph{ideal torihedron} $\sT^\circ$ is $\sT$ with the
 vertices of $G$ and the vertex $\torus \times \{1\}$ removed. Hence, an ideal
@@
 This also gives a decomposition of the corresponding ideal torihedron
-into ideal pyramids.
-We call these the \emph{pyramidal decompositions} of $\sT$ and its
-ideal version.
+$\sT^\circ$ into ideal pyramids.
+We call these the \emph{pyramidal decompositions} of $\sT$ and $\sT^\circ$.
 
@@
 we refer to $\theta_e$ as the exterior angle
-and $\theta_e$ as the interior angle.
+and $\theta_e^*$ as the interior angle. 
+For brevity, we write dihedral angle to mean 
+interior dihedral angle.
 
@@
 \begin{define}
-An \emph{angled ideal tetrahedron} is an ideal tetrahedron with an assignment of a dihedral angle
-to each edge, such that
+An \emph{angled ideal tetrahedron} is an ideal tetrahedron with an assignment of an
+dihedral angle to each edge, such that
 \begin{itemize}
@@
 \item for each tetrahedron, opposite edges have equal dihedral angles;
-\item the three distinct angles sum to $\pi$.
+\item the three distinct interior angles at edges incident to one vertex sum to $\pi$.
 \end{itemize}
 
-We say a angled ideal tetrahedron is \emph{degenerate} if
+We say an angled ideal tetrahedron is \emph{degenerate} if
 one dihedral angle is 0; we say it is \emph{non-degenerate} otherwise.
@@
 such that for each face $f$,
-$\sum_{\vec{e} \in \del f} \vphi_{\vec{e}}^* = \pi$.
+$\sum_{\vec{e} \in \del f} \vphi_{\vec{e}} = \pi$.
 
@@
 
-Suppose the edges are labeled $e_i$,
+Suppose the edges are labeled $e_i$, for an edge
 which goes between vertices $v_i$ and $v_{i+1}$,
@@
 \label{s:hyperbolicity}
-Thurston introduced a method for finding the unique hyperbolic metric for a
-given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}. The idea
-was to triangulate the interior of $M$ into ideal tetrahedra and give those
-tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently
-in $M$. The shape parameter of a tetrahedron is described by the cross-ratio of
-its four vertices on the sphere at infinity. Thurston had written down a system
-of gluing equations with shape parameters whose solutions correspond to the
-complete hyperbolic metric on the interior of $M$. Casson and Rivin separated
+Thurston introduced a method for finding the unique complete hyperbolic metric for a
+given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}. 
+%The idea
+%was to triangulate the interior of $M$ into ideal tetrahedra and give those
+%tetrahedra hyperbolic shapes (called shape parameters) that glue up coherently
+%in $M$. The shape parameter of a tetrahedron is described by the cross-ratio of
+%its four vertices on the sphere at infinity. 
+Thurston had written down a system
+of gluing and consistency equations which can be translated to 
+equations with angles for a triangulation of $M$ whose solutions correspond to the
+complete hyperbolic metric on the interior of $M$. Casson and Rivin separated Thurston's
 gluing equations into a linear and non-linear part \cite{Casson-Rivin}. Angle
@@
 
-\begin{theorem}\cite{Casson-Rivin}\label{thm:Casson-Rivin}
+\begin{theorem}\cite{TODO: find rivin's paper? should be in here https://arxiv.org/pdf/1004.0440.pdf}
 Let $M$ be a 3-manifold admitting an angle structure. Then $M$ is hyperbolic.
@@
 $\pi/2$ for edge
-\cite{CKP2},
-the angled torihedra can be further decomposed into base-angled pyramids.
+\cite{CKP2}.
 By \prpref{p:tori_decomp},
 there is a torihedral decomposition of the complement of the augmented link $L$.
-Using those angles,
-we then assign angles to edges of these torihedra
-and decompose them into base-angled pyramids.
-These pyramids can be further decomposed into tetrahedra,
-thus obtaining an angle structure on a triangulation.
-In the Appendix, we show that this triangulation
-also has an angle structure that
-satisfies Thurston's gluing equations.
+Using those angles from $K$,
+we then assign new angles locally to edges of torihedra from a torihedral 
+decomposition of $L$
+and decompose them into base-angled pyramids which can be decomposed 
+into tetrahedra, thus obtaining an angle structure on a triangulation.
 
@@
 We say an augmentation is \emph{right-augmented} if, when both strands are
-(locally) oriented such that they cross the augmentation disk in the same
-direction, the crossing is a positive right-handed half-twist.
+(locally) oriented so that they cross the augmentation disk in the same
+direction, the crossing between them is a positive right-handed half-twist.
 See Figure \ref{f:right_left_aug}.
@@
 We induct on $\chi(F')$  (over all possible such graphs $G$);
-for $F' = \emptyset$, there is nothing to prove.
+for $F' = \emptyset$ or $\chi(F') \leq 0$, there is nothing to prove.
 
@@
 We make them non-degenerate angled torihedra by assigning $\theta^* = \pi/2$
-for all edges.
+for all edges. Unlike in the case of alternating links or fully augmented links 
+in the thickened torus we cannot make all angles $\pi/2$. This is 
+because in our decomposition the vertices of the graph which
+defines our torihedra are not all four valent.
 
@@
 where $f$ is the face to the left of $\vec{e}$.
-(We adapted this argument from \cite{BandS}).
+(We adapted this argument from Lemma 3.4 of \cite{BandS}).
 
@@
 It is easy to check that upon gluing,
-each edge has sum of dihedral angles ($\theta^*$) equals $2\pi$.
+each edge has sum of dihedral angles ($\theta^*$) that is equal to $2\pi$.
 (This holds true even if they were glued assuming

### 2021-08-17 main.tex
gets rid of the pesky lemma 3.4

@@
 for each edge $e$,
+where $\vec{e},\cev{e}$ are the two orientations
+on $e$,
 such that for each face $f$,
-$\sum_{\vec{e} \in \del f} \vphi_{\vec{e}} = \pi$.
+$\sum_{\vec{e} \in \del f} \vphi_{\vec{e}} = \pi$,
+where $\vec{e} \in \del f$ is the edge in the boundary of $f$
+taken with outward orientation.
 
@@
 add to $\theta_e^*$.
+
+We also say that $\vphi_\bullet$ is an angle-splitting
+of the edge-labeled graph $(G(\sT), \theta_\bullet^*)$.
 \end{definition}
@@
 
-\begin{lemma}
-\label{l:2fe}
-Let $G$ be a 4-valent graph on $\torus$ with no bigons or self-loops.
-%and whose faces can be checkerboard colored.
-Then for any subset $F' \subseteq F$ of faces,
-\[
-	2\chi(F') \leq |E'|
-\]
-where $E' = \cup_{f \in F'} \del f$ is the set of edges
-that meets some face of $F'$,
-and $\chi(F') = \sum_{f\in F'} \chi(f)$ is the sum
-of the Euler characteristics of faces in $F'$.
-\end{lemma}
+We need the following theorem,
+adapted from \cite[Theorem 4]{BandS},
+specialized to genus 1 surfaces:
 
-\begin{figure}
-\includegraphics[width=11cm]{bigon_crush.png}
-\caption{Resolving internal vertex; eliminating bigons via ``crushing"}
-\label{f:bigon_crush}
-\end{figure}
+\begin{theorem}{\cite[Theorem 4]{BandS}}
+Let $\Gamma = (V,E)$ be a graph on the torus,
+and let $\Gamma^* = (F,E^*)$ be the dual graph,
+with $E^*$ being naturally identified with $E$.
+Let $\theta_\bullet \in (0,\pi)^E$
+be a function on the set of edges $E$
+that sums to $2\pi$ around each vertex of $V$.
 
-\begin{proof}
-We induct on $\chi(F')$  (over all possible such graphs $G$);
-for $F' = \emptyset$ or $\chi(F') \leq 0$, there is nothing to prove.
+There exists an angle-splitting of $(\Gamma,\theta_\bullet)$
+if and only if the following
+``cocycle condition'' is satisfied:
 
-Call a vertex or edge \emph{interior} if it does not meet
-$F'' = F \backslash F'$.
-Suppose there is an interior vertex $v$.
-Make the modification as in Figure \ref{f:bigon_crush}
-(later we will choose which way to ``resolve'' the vertex).
-This decreases $\chi(F')$ by one and $|E'|$ by 2.
-However, this process may produce bigons;
-if it does, repeatedly eliminate bigons by either
-(1) performing the modification as in Figure \ref{f:bigon_crush}
-if the two vertices of the bigon are distinct,
-or (2) remove the bigon completely if the two vertices
-of the bigon are the same.
-Each of these steps also decreases $\chi(F')$ by one and $|E'|$ by 2
-(note in the second case, after removing the bigon,
-the operation merges two distinct faces or joins a face to itself;
-this adds an $S^1$, thus does not change the (total) euler characteristic
-of the two faces or the one face).
+\begin{quotation}
+Suppose we cut the torus along a subset of edges in the dual graph
+$\Gamma^*$, obtaining one or more pieces;
+Then for any piece that is a disc,
+the sum of $\theta_\bullet$ over the edges in the boundary
+of the piece is at least $2\pi$,
+with equality if and only if the piece
+contains exactly one vertex of $\Gamma$.
+\end{quotation}
 
-We must check that this process terminates with a graph
-which satisfies the hypotheses set out in the lemma.
-It is clear that %checkboard colorability and
-4-valency is maintained
-at each step, and there will not be any bigons at the end.
-We need to ensure that eliminating bigons does not
-create self-loop edges.
-Here we specify how to choose which way to resolve the internal
-vertex $v$. If among the four faces touching $v$,
-one of them has greater than three sides (Case 1),
-then resolve $v$ so that this face is not merged;
-if all four faces are triangles (Case 2),
-simply resolve in an arbitrary manner.
-After the modification of the internal vertex,
-at most two bigons are created;
-eliminate those two bigons.
-Now we find that all bigons will be connected end-to-end
-(i.e. forming a single twist region) -
-this is because in Case 1, only one bigon was present after smoothing
-$v$, which would result in at most two bigons that would be connected;
-and if we were in Case 2, we find that the face between those
-eliminated bigons (coming from merging the two triangles across $v$)
-will become a bigon too,
-thus connecting the potential bigons on either ends.
+\label{t:bs-thm4}
+\end{theorem}
 
-Therefore, one can eliminate bigons in an order so that
-they belong in one twist region;
-in particular, the (not necessarily distinct) faces on either side
-are not bigons,
-so eliminating the bigon does not produce a self-loop edge.
-
-Now suppose $G$ has no interior vertices.
-We perform some reductions.
-We remove all $f$ from $F'$ that have non-positive Euler characteristic,
-as doing so will not decrease $\chi(F')$ and will not increase $|E'|$.
-Now consider some $f\in F'$.
-If it has at least two boundary (i.e. non-interior) edges,
-we can remove $f$ from $F'$,
-which decreases $\chi(F')$ by 1 and $|E'|$ by at least 2.
-Thus we remove all such $f$.
-
-Now suppose $f\in F'$ has three contiguous interior edges
-$e_1,e_2,e_3$.
-(e.g. if $f$ has at least four sides).
-Let $v_1, v_2$ be the vertices between these three interior edges.
-Since $v_1$ is not interior,
-the face across $v_1$ from $f$ is not in $F'$;
-likewise with $v_2$.
-But this shows that the face across $e_2$ from $f$
-has two boundary edges, contradicting our reduction.
-%This would lead to the situation in \ref{},
-%showing that there is a face with at least
-%two boundary edges, contradicting our reduction.
-
-Thus, we now have a graph whose faces are triangles,
-and each face has exactly one boundary edge.
-Now the problem is solved with a simple counting argument:
-each $f$ corresponds to one boundary edge and two interior edges,
-but, since the interior edges are shared by two faces,
-they should count as half an edge; so
-\[
- |E'| = \sum_{f\in F'} 1 + 1/2 + 1/2 = 2|F'| = 2\chi(F')
-\]
-and we get the desired result.
-\end{proof}
-
-The following theorem is quoted from \cite{BandS}
-(see also \cite{FF})
-
-\begin{theorem}[Feasible Flow Theorem]
-\label{t:feasible_flow}
-Let $(N,X)$ be a directed graph,
-with a \emph{lower capacity bound} $a_x$
-and \emph{upper capacity bound} $b_x$
-for each directed edge $x \in X$,
-with $-\infty \leq a_x \leq b_x \leq \infty$.
-A \emph{feasible flow} is a function $\vphi : X \to \RR$
-such that $\vphi_x \in [a_x, b_x]$ and
-Kirchhof's current law is satisfied
-(i.e. flow in = flow out at every vertex).
-
-A feasible flow exists if and only if,
-for every proper nonempty subset $N' \subset N$,
-\[
-\sum_{x \in ex(N')} b_x \geq \sum_{x \in in(N')} a_x
-\]
-where $ex(N'), in(N')$ refer to edges leaving,
-entering $N'$, respectively.
-\end{theorem}
+The original theorem \cite[Theorem 4]{BandS}
+proves that a circle pattern combinatorially equivalent to $\Gamma$
+exists; a circle pattern naturally yields
+an angle-splitting (which they call a coherent angle system).
 
@@
 \label{t:auglink_hyp}
-Let $K$ be a weakly prime, alternating link whose diagram has no bigons.
+Let $K$ be a weakly prime, alternating link
+in the thickened torus
+whose diagram has no bigons.
 Let $L$ be a link obtained from augmenting $K$.
@@
 into two torihedra $\sT_T$ and $\sT_B$,
-whose graphs are $\Gamma_T(K), \Gamma_B(K)$ respectively;
+with $\sT_T$ meeting the top cone point $\torus \times \{1\}$
+and $\sT_B$ meeting the bottom cone point $\torus \times \{-1\}$.
+We denote their graphs by $\Gamma_T(K), \Gamma_B(K)$ respectively;
 viewed from the top cone point $\torus \times \{1\}$,
-they are both the same as the projection graph of $K$.
+both graphs are the same as the projection graph of $K$.
 %which we denote by $\Gamma$.
 We make them non-degenerate angled torihedra by assigning $\theta^* = \pi/2$
-for all edges. Unlike in the case of alternating links or fully augmented links 
-in the thickened torus we cannot make all angles $\pi/2$. This is 
-because in our decomposition the vertices of the graph which
-defines our torihedra are not all four valent.
+for all edges.
+%%Unlike in the case of alternating links or fully augmented links 
+%%in the thickened torus we cannot make all angles $\pi/2$. This is 
+%%because in our decomposition the vertices of the graph which
+%%defines our torihedra are not all four valent.
 
-We obtain an angle-splitting by applying the
-Feasible Flow theorem (\thmref{t:feasible_flow}) as follows:
-Consider the directed graph whose vertex set is
-$E \cup F \cup \{*\}$,
-where $E, F$ are the set of edges, faces of $\Gamma_T(K)$ respectively,
-%and $*$ is some abstract vertex.
-and there is a directed edge
-\begin{itemize}
-\item $* \to f$ for each face $f\in F$, with capacity interval
-	$[\pi, \infty)$,
-\item $f \to e$ for each edge $e \in \del f$,
-	with capacity interval $[\veps, \infty)$
-	for some $\veps>0$ to be set later,
-\item $e \to *$ for each edge $e$, with capacity interval
-	$(-\infty, \pi/2]$.
-\end{itemize}
-By \lemref{l:2fe}, $2|F'| = 2\chi(F') \leq |E'|$,
-and taking $\veps < \pi / |\text{max face size}|$,
-the feasible flow condition is satisfied,
-so a feasible flow exists.
-Since $2|F| = |E|$, the capacity interval restrictions
-on the flow at $*$ is sharp, so out-edges at $*$
-have flow $\pi$ and in-edges at $*$ have flow $\pi/2$.
-Then the flow $f \to e$ gives us $\vphi_{\vec{e}}$,
-where $f$ is the face to the left of $\vec{e}$.
-(We adapted this argument from Lemma 3.4 of \cite{BandS}).
+Using the fact that $K$ is weakly prime,
+it is not hard to see that the ``cocycle condition''
+of \thmref{t:bs-thm4} are satisfied,
 

### 2021-08-18 main.tex
made some minor changes, clarifying the exposition

@@
 \newcommand{\sT}{{\mathcal{T}}}
+\newcommand{\cD}{{\mathcal{D}}}
+\newcommand{\cL}{{\mathcal{L}}}
 
@@
 
-Champanerkar, Kofman and Purcell have studied alternating links in the thickened torus \cite{CKP2}. They define a link in the thickened torus as a quotient of a biperiodic alternating link as follows,
+TODO Notation section: $I = (-1,1)$.
+
+Champanerkar, Kofman and Purcell have studied alternating links in the thickened
+torus \cite{CKP2}. They define a link in the thickened torus as a quotient of a
+biperiodic alternating link as follows:
 
@@
 \label{def:biperiodiclink}
-A \emph{biperiodic alternating link} $\mathcal{L}$ is an infinite link
-which has a projection onto
-$\R^2$ which is invariant under an action of a two dimensional lattice $\Lambda$
-by translations, such that $L=\mathcal{L}/\Lambda$ is an alternating link in
-$\torus \times I$, where $I = (-1,1)$, with the projection on $\torus \times \{0\}$.   
+A \emph{biperiodic alternating link} $\cL$ is an infinite link
+in $\R^2 \times I$ with a link diagram $\cD \subset \R^2$
+such that $\cL$ and $\cD$ are
+invariant under the action of a two dimensional lattice $\Lambda$
+on $\R^2$ by translations.
+
+The quotient $L=\mathcal{L}/\Lambda$ is an alternating link in
+$\torus \times I$,
+whose projection onto $\torus \times \{0\} = \R^2 \times \{0\} /\Lambda$
+is an alternating link diagram $\cD/\Lambda$.
 \end{define}
+%%\begin{define}
+%%\label{def:biperiodiclink}
+%%A \emph{biperiodic alternating link} $\mathcal{L}$ is an infinite link
+%%which has a projection onto
+%%$\R^2$ which is invariant under an action of a two dimensional lattice $\Lambda$
+%%by translations, such that $L=\mathcal{L}/\Lambda$ is an alternating link in
+%%$\torus \times I$, where $I = (-1,1)$, with the projection on $\torus \times \{0\}$.
+%%\end{define}
 
 \begin{remark}
-Since $\torus \times I \cong \Sp^3 - H$, where $H$ is a Hopf link. The complement $\torus \times I- L = \Sp^3 - (L \cup H)$.
+Since $\torus \times I \cong \Sp^3 - H$, where $H$ is a Hopf link.
+The complement $\torus \times I- L = \Sp^3 - (L \cup H)$.
 \end{remark}
 
-Champanerkar, Kofman and Purcell \cite{CKP2} extended the definition of prime links in $\Sp^3$ for links in $\torus \times I$ called weakly prime.
+Champanerkar, Kofman and Purcell \cite{CKP2} extended
+the definition of prime links in $\Sp^3$
+for links in $\torus \times I$ called weakly prime.
 
 \begin{define} \label{def:weaklyprime}
-	 A diagram of a link $L$ is \emph{weakly prime} if whenever a disk is embedded in the diagram surface meets the diagram transversely in exactly two edges, then the disk contains a simple edge of the diagram and no crossings.
+A diagram of a link $L$ is \emph{weakly prime}
+if whenever a disk is embedded in the diagram surface
+meets the diagram transversely in exactly two edges,
+then the disk contains a simple edge of the diagram and no crossings.
 \end{define}
@@
 Now we can define augmentation for a link in $\torus \times I$ the same way we
-define augmentation for links in $\Sp^3$. For a link in $\torus \times I$, the
+define augmentation for links in $\Sp^3$:
+For a link in $\torus \times I$, the
 crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
@@
 to one or more twist regions of $D(L)$. See Figure \ref{fig:Augmentations}
+
+\begin{definition}
+Let $D(L)$ be a twist reduced diagram of a link $L$ in $\torus \times I$, we define
+\emph{augmenting} as a process in which an unknotted circle component is added
+to one or more twist regions of $D(L)$. See Figure \ref{fig:Augmentations}
+
+We say $L$ is \emph{fully} augmented
+if $L$ is augmented at \emph{every} crossing/twist site,
+\label{d:augmentation}
+\end{definition}
 
@@
 A \emph{torihedron} $\sT$ is a cone on the torus, 
-i.e. $\torus \times [0,1]/(\torus \times \{1\})$, with a cellular graph
+i.e. $\torus \times [0,1]/(\torus \times \{1\})$, with a
+(TODO define cellular; later say ``if faces are disks'') cellular graph
 $G = G(\sT)$ on $\torus \times \{0\}$.
@@
 (ideal vertices) removed from $\torus \times \{0\}$.
-We refer to the vertex $\torus \times \{1\}$ as the cone point.
+We refer to the vertex $\torus \times \{1\}$ as the \emph{cone point}
+of $\sT$.
 \end{define}
@@
 \includegraphics[width=7cm]{more_pictures/horizontal_bowtie.png}
-\caption{Angle assignments on a bow-tie corresponding to an augmentation site}
+\caption{Assignments of $\theta^*$ to edges of a bow-tie
+	corresponding to an augmentation site}
 \label{f:bowtie_angles}
@@
 \end{tabular}
-\caption{(a) Angles before augmentation (b) Angle splitting for bowtie corresponding to augmentation}
+\caption{(a) Angle splitting before augmentation (b) Angle splitting for bowtie corresponding to augmentation}
 \label{f:bowtie_angles2}
@@
 We make $\sT_T(L)'$ angled using the angles from $\sT_T(L)$ for old edges,
-and putting $\pi$ for all new edges.
+and putting $\pi$ for all new edges TODO make clear it's the red edges that is
+new.
 
@@
 It is also easy to see this is the case for the other edges.
-(Once again, a similar argument applies if $\sT_(L)'$
+(Once again, a similar argument applies if $\sT_T(L)'$
 and $\sT_B(L)'$ are glued assuming

### 2021-08-19 main.tex
definition of cellular, included it in hypothesis of theorem

@@
 }
-\newcommand{\Sp}{{\rm{S}}}
+\newcommand{\Sp}{{S}}
 \newcommand{\C}{\mathbb{C}}
@@
 The quotient $L=\mathcal{L}/\Lambda$ is an alternating link in
-$\torus \times I$,
+the thickened torus $\torus \times I$,
 whose projection onto $\torus \times \{0\} = \R^2 \times \{0\} /\Lambda$
@@
 \end{define}
-%%\begin{define}
-%%\label{def:biperiodiclink}
-%%A \emph{biperiodic alternating link} $\mathcal{L}$ is an infinite link
-%%which has a projection onto
-%%$\R^2$ which is invariant under an action of a two dimensional lattice $\Lambda$
-%%by translations, such that $L=\mathcal{L}/\Lambda$ is an alternating link in
-%%$\torus \times I$, where $I = (-1,1)$, with the projection on $\torus \times \{0\}$.
-%%\end{define}
+
+We refer to $\torus \times \{0\}$ as the \emph{projection plane}.
 
@@
 \begin{define} \label{def:weaklyprime}
-A diagram of a link $L$ is \emph{weakly prime}
-if whenever a disk is embedded in the diagram surface
+A diagram $D \subset \torus$
+of a link $L$ in the thickened torus $\torus \times I$
+is \emph{weakly prime}
+if whenever a disk is embedded in $\torus$
 meets the diagram transversely in exactly two edges,
@@
 $\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on
-the plane that intersects the diagram of $\mathcal{L}$ transversely in four points, with two
+the plane that intersects the diagram of $\mathcal{L}$
+transversely in four points, with two
 points adjacent to one crossing and the other two points adjacent to another
@@
 empty) collection of bigons strung end to end between these crossings. We say
-the diagram of $L$ is \emph{twist-reduced} if it is the quotient of a twist-reduced biperiodic
-link diagram.  \end{define}
+the diagram of $L$ is \emph{twist-reduced}
+if it is the quotient of a twist-reduced biperiodic
+link diagram.
+\end{define}
 
@@
 define augmentation for links in $\Sp^3$:
-For a link in $\torus \times I$, the
-crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
-Let $D(L)$ be a twist reduced diagram of a link $L$ in $\torus \times I$, we define
-\emph{augmenting} as a process in which an unknotted circle component is added
-to one or more twist regions of $D(L)$. See Figure \ref{fig:Augmentations}
+%For a link in $\torus \times I$, the
+%crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
+%Let $D(L)$ be a twist reduced diagram of a link $L$ in $\torus \times I$, we define
+%\emph{augmenting} as a process in which an unknotted circle component is added
+%to one or more twist regions of $D(L)$. See Figure \ref{fig:Augmentations}
 
 \begin{definition}
-Let $D(L)$ be a twist reduced diagram of a link $L$ in $\torus \times I$, we define
-\emph{augmenting} as a process in which an unknotted circle component is added
-to one or more twist regions of $D(L)$. See Figure \ref{fig:Augmentations}
-
+Let $D(K)$ be a twist reduced diagram of a link $K$ in $\torus \times I$, we define
+\emph{augmenting} as a process in which an unknotted circle component,
+called a \emph{crossing circle}, is added
+to one or more twist regions of $D(K)$ (see Figure \ref{fig:Augmentations});
+we call the resulting link $L$ an \emph{augmented link obtained from $K$}.
 We say $L$ is \emph{fully} augmented
-if $L$ is augmented at \emph{every} crossing/twist site,
+if $L$ is obtained by augmenting
+$K$ at \emph{every} crossing/twist site.
 \label{d:augmentation}
@@
 
-\begin{remark}
-If $L$ is augmented at \emph{every} crossing/twist site we say $L$ is \emph{fully} augmented.
-\end{remark}
+\begin{definition}
+A graph $G = (V,E)$ on the torus is \emph{cellular}
+if its complement is a collection of open disks.
+\label{d:cellular}
+\end{definition}
+
+%We say that a link diagram in the thickened torus is
+%\emph{cellular}.
+
+%%\begin{remark}
+%%If $L$ is augmented at \emph{every} crossing/twist site we say $L$ is \emph{fully} augmented.
+%%\end{remark}
 
@@
 
-We present a method of decomposing an augmented link (not necessarily fully augmented) 
-in the thickened torus into
-objects called ``torihedra'' as defined below.  Decomposing alternating links in the thickened torus into 
-torihedra were first described in \cite{CKP2} then later used for fully augmented links in 
+We present a method of decomposing an augmented link
+(not necessarily fully augmented) in the thickened torus into
+objects called ``torihedra'' as defined below.
+Decomposing alternating links in the thickened torus into 
+torihedra were first described in \cite{CKP2},
+then later used for fully augmented links in 
 the thickened torus in \cite{kwon2020fully}.
 The idea is to combine methods of Menasco
-\cite{Menasco} and the use of crossing edges between each crossing of our link
-and Lackenby's ``cut-slice-flatten" method \cite{lackenby} on the augmentation
+\cite{Menasco} and the use of crossing edges
+between each crossing of our link
+and Lackenby's ``cut-slice-flatten" method \cite{lackenby}
+on the augmentation
 sites.
@@
 A \emph{torihedron} $\sT$ is a cone on the torus, 
-i.e. $\torus \times [0,1]/(\torus \times \{1\})$, with a
-(TODO define cellular; later say ``if faces are disks'') cellular graph
+i.e. $\torus \times [0,1]/(\torus \times \{1\})$, with a cellular graph
 $G = G(\sT)$ on $\torus \times \{0\}$.
@@
 \begin{prop}\label{p:tori_decomp}
-Let $L$ be an augmented link in $\torus \times I$.
+Let $K$ be an alternating link in the thickened torus,
+and let $L$ be an augmented link obtained from $K$.
 %Let $G(L)$ be a diagram of the link on $\torus \times \{0\}$.
@@
 We will begin by assuming that there are no half twists.
-Arrange the link diagram of $L$ in the following way: first place the added
-circle components perpendicular to the projection plane, $\torus
-\times \{0\}$ leaving the remaining part of the link parallel to the projection
-plane.  We now place a crossing edge on each crossing of the link so that for
-each crossing edge, one end of the edge lies on a bottom strand while the other
-end lies on a top strand as in Figure \ref{fig:crossingArc} left.
+Let $L = K \cup C$, with $C$ being the collection of crossing circles.
+%Arrange the link diagram of $L$ in the following way:
+Arrange $L$ in the following way:
+place the circle components in $C$ perpendicular to
+the projection plane $\torus \times \{0\}$,
+and leave the remaining part of the link $K \subseteq L$
+lying in the projection plane (except at crossings).
+We now place a \emph{crossing edge} at each crossing of the original link $K$,
+connecting the top and bottom strands at the crossing
+(see Figure \ref{fig:crossingArc} left).
+%so that for each crossing edge,
+%one end of the edge lies on a bottom strand while the other
+%end lies on a top strand as in Figure \ref{fig:crossingArc} left.
 
@@
 
-\indent We view the link from the point at infinity from the top. We will push
+We view the link from the point at infinity from the top. We will push
 the top strand to the bottom strand, splitting the crossing edge into two
@@
 
-\indent Now place a disk on each crossing circle, so that the disk is bounded by
-the crossing circle. We can then cut $\torus \times I$ along $\torus \times \{0\}$ and
-focus on the top half, $\torus \times [0,1)$. We will follow the same method on the
-bottom half to obtain the second identical torihedron. The disk we place on each
-crossing circle is now cut in half. This half disk is now bounded by the
-projection plane and the semi-cricle arc of the crossing circle. We push down on
-the crossing circle and split the disk into two identical disks. We then push
-the arc of each crossing circle to infinity, collapsing them to ideal vertices.
+%Now place a disk on each crossing circle, so that the disk is bounded by
+%the crossing circle.
+Now for each crossing circle $c$, consider a spanning disk $B_c$;
+$B_c$ intersects the projection plane $\torus \times \{0\}$
+along the red segments in Figure \ref{fig:falGluings},
+which consists of three edges.
+We then cut $\torus \times I$ along $\torus \times \{0\}$ and
+focus on the top half, $\torus \times [0,1)$.
+(We will follow the same method on the
+bottom half to obtain the second identical torihedron.)
+The spanning disks we placed for each crossing circle are now cut in half
+along the red segment.
+Each half of the disk is now bounded by the
+projection plane and the semi-circle arc of the crossing circle.
+We push down on the crossing circle and split the disk into
+two identical disks.
+We then push the arc of each crossing circle to infinity,
+collapsing them to ideal vertices.
 We obtain two triangular faces which represent the disk which look like a
-bow-tie as in Figure \ref{fig:falGluings}.
+bow-tie as in Figure \ref{fig:falGluings} (a).
 
@@
 
-\indent We repeat the steps for the bottom half of $\torus \times I$, $\torus \times
+We repeat the steps for the bottom half of $\torus \times I$, $\torus \times
 (-1,0]$. Then we get two torihedra. The graph of each will come from
-crossing edges and edges of the disk. Now, if there are half twists we will
-decompose the complement of the link the same way as if there are no half twists
-and we will identify the two bow-ties as in Figure \ref{fig:falGluings}.
+crossing edges and edges from crossing circles.
+Now, if there are half twists,
+we decompose the complement of the link the same way
+(as if there are no half twists)
+but we identify the two bow-ties as in Figure \ref{fig:falGluings} (b).
 Finally,
@@
 Note that if $L = K$ is the non-augmented link,
-$\Gamma_T(L)$ is simply the link projection $K$,
+$\Gamma_T(L)$ is simply the link projection of $K$,
 and in fact $\Gamma_T(K) = \Gamma_B(K)$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Figures \ref{fig:step_one} to \ref{fig:top-bottom} is an example which decomposes the link (C) of Figure
+The Figures \ref{fig:step_one} to \ref{fig:top-bottom}
+depict an example which decomposes the link (C) of Figure
 \ref{fig:Augmentations}.
@@
 in the thickened torus
-whose diagram has no bigons.
+whose diagram is cellular and has no bigons.
 Let $L$ be a link obtained from augmenting $K$.

### 2021-08-20 main.tex
trying to make the torihedron decomp part clearer..

@@
 \begin{abstract}
-For a hyperbolic link $K$ in the thickened torus, We show there is a decomposition of the complement
-of a link $L$, obtained from augmenting $K$, into torihedra. We further decompose 
-the torihedra into angled pyramids and finally angled tetrahedra. These fit into an angled structure 
-on a triangulation of the link complement, and thus by \cite{Casson-Rivin}, this shows
+For a hyperbolic link $K$ in the thickened torus,
+we show there is a decomposition of the complement of a link $L$,
+obtained from augmenting $K$, into torihedra. We further decompose 
+the torihedra into angled pyramids and finally angled tetrahedra.
+These fit into an angled structure on a triangulation of the link complement,
+and thus by \cite{Casson-Rivin}, this shows
 that $L$ is hyperbolic.  
@@
 \begin{definition}
-Let $D(K)$ be a twist reduced diagram of a link $K$ in $\torus \times I$, we define
+Let $D(K)$ be a twist reduced diagram of a link $K$ in $\torus \times I$.
+We define
 \emph{augmenting} as a process in which an unknotted circle component,
-called a \emph{crossing circle}, is added
-to one or more twist regions of $D(K)$ (see Figure \ref{fig:Augmentations});
+called a \emph{crossing circle},
+is added to one or more twist regions of $D(K)$
+(see Figure \ref{fig:Augmentations});
 we call the resulting link $L$ an \emph{augmented link obtained from $K$}.
-We say $L$ is \emph{fully} augmented
-if $L$ is obtained by augmenting
+We say $L$ is \emph{fully} augmented if $L$ is obtained by augmenting
 $K$ at \emph{every} crossing/twist site.
@@
 \end{definition}
+
+As pointed out in the introduction,
+after augmenting a twist region,
+a standard Dehn twist argument allows us to remove
+a full twist (that is, two bigons).
+We say an augmentation has a \emph{half twist}
+if at least one of the augmented twist regions
+has an odd number of bigons.
 
@@
 torihedron from the perspective of the cone point $\torus \times \{1\}$.
+Note however that later we will be dealing with
+``top'' and ``bottom'' torihedra that are glued together
+along their torus boundary faces;
+to avoid confusion, we will visualize the graphs of both torihedra
+from the perspective of the cone point of the ``top'' torihedron.
 
@@
 We call these the \emph{pyramidal decompositions} of $\sT$ and $\sT^\circ$.
+
+\begin{definition}
+Let $G$ be a graph with no self-loops on the torus.
+
+\label{d:diagram-bowtie}
+\end{definition}
 
@@
 \begin{proof}
-We will begin by assuming that there are no half twists.
+We will begin by assuming that $L$ has no half twists.
 Let $L = K \cup C$, with $C$ being the collection of crossing circles.
@@
 
-We view the link from the point at infinity from the top. We will push
-the top strand to the bottom strand, splitting the crossing edge into two
-identical edges as in Figure \ref{fig:crossingArc} right. We push the link
+Next we construct the graph that will define the ``top'' torihedron.
+We view the link from the point at infinity from the top end
+($\torus \times \{1\}$) of the thickened torus.
+Push the top strand to the bottom strand,
+splitting the crossing edge into two
+identical edges and spreading them apart
+as in Figure \ref{fig:crossingArc} right.
+We push the link
 components to infinity and stretch the crossing edge so that we have flattened
-the link onto $\torus \times \{0\}$ except for the crossing circles which will
-remain perpendicular to the projection plane.
+the link onto $\torus \times \{0\}$ except for the crossing circles,
+which remains perpendicular to the projection plane.
 
@@
 
-\begin{theorem}\cite{TODO: find rivin's paper? should be in here https://arxiv.org/pdf/1004.0440.pdf}
+%\cite{TODO: find rivin's paper? should be in here https://arxiv.org/pdf/1004.0440.pdf}
+\begin{theorem}\cite[Theorem 1.1]{FG-angles}
 Let $M$ be a 3-manifold admitting an angle structure. Then $M$ is hyperbolic.
@@
 Then $L$ is hyperbolic.
+
+More generally, if $K$ is as above with a twist reduced diagram
+containing bigons,
+and $L$ is obtained by augmenting $K$
+at every twist region with at least one bigon
+(and possibly other crossings),
+then $L$ is hyperbolic.
 \end{theorem}
@@
 \begin{proof}
+Let us first consider the case when $K$ did not have bigons.
+
 By \cite[Theorem 7.5]{CKP2},
@@
 it is not hard to see that the ``cocycle condition''
-of \thmref{t:bs-thm4} are satisfied,
+of \thmref{t:bs-thm4} is satisfied.
 
@@
 (This holds true even if they were glued assuming
-some augmentations had no half-twist; see \remref{r:nohalftwist}.)
+some augmentations had no half-twist;
+see end of proof where we deal with $K$ having bigons.)
+%\remref{r:nohalftwist}.)
 
@@
 and $\sT_B(L)'$ are glued assuming
-some augmentations had no half-twist; see \remref{r:nohalftwist}.)
+some augmentations had no half-twist;
+see end of proof where we deal with $K$ having bigons.)
+%see \remref{r:nohalftwist}.)
 
@@
 of $\toruscomp{L}$
-\end{proof}
 
-\begin{remark}
-\label{r:nohalftwist}
+Now let us consider $K$ with bigons.
+Let $K'$ be the link obtained from $K$ by replacing
+each twist region of $K$ by a single appropriate crossing.
+Let $L'$ be the link obtained from augmenting $K'$
+by exactly the same crossing circles.
+The top and bottom torihedra $\sT_T(L'),\sT_B(L')$
+are the same as $\sT_T(L),\sT_B(L)$;
+however, the gluing differs slightly:
+for twist regions of $K$ that have an even number of bigons,
+the gluing of $\sT_T(L')$ to $\sT_B(L')$
+should be using Figure \ref{fig:falGluings} (a) (not (b)).
+As remarked throughout the proof,
+all the arguments carry through verbatim.
+
+%Then the only difference in the arguments
+%is that, for twist regions of $K$ that have an even number of bigons,
+%the
+
+%\begin{remark}
+%\label{r:nohalftwist}
 If the original link $K$ had some twist regions with at least one bigon,
@@
 the proof still works for $L$, showing that $L$ is also hyperbolic.
-\end{remark}
+%\end{remark}
+
+\end{proof}
 

### 2021-08-21 main.tex
fixed up the torihedral decomposition to make half-twist stuff clearer

@@
 
-Given a twist reduced diagram of a link $K$, \emph{augmenting} is a process in
+Given a twist-reduced diagram of a link $K$, \emph{augmenting} is a process in
 which an unknotted circle component (augmentation) is added to one or more twist
-regions (a single crossing or a maximal string of bigons) of $K$. The added circle
-component allows us to remove full twists at the twist region of $K$. If the
-twist region has an odd number of crossings then all but one crossing is
-removed, whereas if the twist region has an even number of crossings then all
-are removed. We can remove full twists by a standard argument using a Dehn twist 
-on the complement of the crossing circle. The newly obtained link is called an 
+regions (a single crossing or a maximal string of bigons) of $K$.
+%%By a standard argument using a Dehn twist
+%%on the complement of the crossing circle,
+%%the added circle component allows us to remove full twists
+%%(i.e. pairs of bigons)
+%%at the twist region of $K$
+%%while keeping the link complement the same.
+%%If the twist region has an odd number of crossings,
+%%then all but one crossing is removed,
+%%whereas if the twist region has an even number of crossings,
+%%then all are removed.
+%We can remove full twists by a standard argument using a Dehn twist 
+%on the complement of the crossing circle.
+The newly obtained link is called an 
 \emph{augmented link} and the newly obtained diagram is called an 
@@
 
-Menasco \cite{Menasco} showed there are decompositions of the complements of
-alternating links in $\Sp^3$ into two topological polyhedra, a top polyhedron and a bottom
-polyhedron.  For alternating links $K$ in the thickened torus, Champanerkar,
-Kofman and Purcell \cite{CKP2} showed that there is a decomposition of the
+Menasco \cite{Menasco} showed that there are decompositions
+of the complements of alternating links in $\Sp^3$
+into two topological polyhedra,
+a top polyhedron and a bottom polyhedron.
+For alternating links $K$ in the thickened torus,
+Champanerkar, Kofman and Purcell \cite{CKP2}
+showed that there is a decomposition of the
 complement of $K$ into objects called torihedra, which we think of as
-counterparts to Menasco's decomposition of links in $\Sp^3$ into polyhedra, for
-links in the thickened torus. Just like Menasco's decomposition, one obtains a
-top and a bottom torihedron.
+counterparts to Menasco's decomposition % of links in $\Sp^3$ into polyhedra,
+for links in the thickened torus;
+just like Menasco's decomposition, one obtains a top and a bottom torihedron.
 
 In \secref{s:auglinks} we show that for augmented
-links in the thickened torus one can also obtain a decomposition of the
-complement into a top and bottom torihedron.  In \secref{s:hyperbolicity}, we
-prove that many augmented alternating links in the thickened torus are
-hyperbolic.
+links in the thickened torus (not necessarily fully augmented),
+one can also obtain a decomposition of the
+complement into a top and bottom torihedron.
+In \secref{s:hyperbolicity}, we prove that
+many augmented alternating links in the thickened torus are hyperbolic.
 
@@
 
-While revising this paper,
-we learned that \cite{adams2021generalized}
+While revising this paper, we learned that \cite{adams2021generalized}
 proves a generalization of our work here,
@@
 \begin{tabular}{cc}
- \includegraphics [height=4cm]{augmentation1.png}&
-  \includegraphics [height=4cm]{augmentation2.png}\\
-  (a)&(b)
+\includegraphics[height=4cm]{augmentation1.png}
+\;\;\;\;
+& \includegraphics[height=4cm]{augmentation2.png}
+\\
+(a)
+& (b)
 \end{tabular}
- \caption{The left shows a pretzel knot before augmentation and the right shows after augmentation}
+\caption{(a) pretzel knot before augmentation
+(b) pretzel knot after augmentation;
+second diagram shows
+removal of full twists in the augmented twist regions.}
 \label{fig:augmentationS3}
@@
 %crossing circles are added to the diagram projected onto $\torus \times \{0\}$.
-%Let $D(L)$ be a twist reduced diagram of a link $L$ in $\torus \times I$, we define
+%Let $D(L)$ be a twist-reduced diagram of a link $L$ in $\torus \times I$, we define
 %\emph{augmenting} as a process in which an unknotted circle component is added
@@
 \begin{definition}
-Let $D(K)$ be a twist reduced diagram of a link $K$ in $\torus \times I$.
+Let $D(K)$ be a twist-reduced diagram of a link $K$ in $\torus \times I$.
 We define
@@
 a full twist (that is, two bigons).
+
+\begin{definition}
 We say an augmentation has a \emph{half twist}
@@
 has an odd number of bigons.
+\label{d:half-twist}
+\end{definition}
 
@@
 Let $G$ be a graph with no self-loops on the torus.
-
+TODO definition of adding a bow-tie
 \label{d:diagram-bowtie}
@@
 and leave the remaining part of the link $K \subseteq L$
-lying in the projection plane (except at crossings).
+lying in the projection plane (except at crossings of $K$).
+Thus, the projection of $L$ onto the projection plane
+will be a diagram $D(K)$ of $K$
+together with line segments corresponding to crossing circles.
+(We demand that $D(K)$ be alternating and twist-reduced.)
+As discussed before, we may remove full twists (i.e. pairs of bigons)
+from the twist regions of $K$ that are augmented in $L$,
+and since $L$ is assumed to have no half twists,
+the two edges of $D(K)$ that go through a crossing circle
+do not meet (see Figure \ref{fig:Augmentations} C).
+From now on, we will take $K$ to be this modified link
+(with full twists removed).
+
 We now place a \emph{crossing edge} at each crossing of the original link $K$,
 connecting the top and bottom strands at the crossing
-(see Figure \ref{fig:crossingArc} left).
+(see Figure \ref{fig:crossingArc} (a)).
 %so that for each crossing edge,
 %one end of the edge lies on a bottom strand while the other
-%end lies on a top strand as in Figure \ref{fig:crossingArc} left.
+%end lies on a top strand as in Figure \ref{fig:crossingArc} (a).
 
@@
 \centering 
+\begin{tabular}{cc}
 \includegraphics[width=4cm]{crossingArc.png}
-\includegraphics[width=5cm]{crossingPush.png}
-\caption{Left: The black strands are
-part of the link and the red strand is the crossing edge. Right: The blue and
+& \includegraphics[width=5cm]{crossingPush.png}
+\\
+(a)
+& (b)
+\end{tabular}
+\caption{(a) The black strands are
+part of the link and the red strand is the crossing edge.
+(b) The blue and
 red edges represent the split crossing edges and the shaded half disk is bounded
@@
 ($\torus \times \{1\}$) of the thickened torus.
-Push the top strand to the bottom strand,
+At each crossing of $K$,
+push the top strand towards the bottom strand,
 splitting the crossing edge into two
 identical edges and spreading them apart
-as in Figure \ref{fig:crossingArc} right.
-We push the link
-components to infinity and stretch the crossing edge so that we have flattened
-the link onto $\torus \times \{0\}$ except for the crossing circles,
-which remains perpendicular to the projection plane.
+as in Figure \ref{fig:crossingArc} (b).
+%We push the link
+%components to infinity and stretch the crossing edge so that we have flattened
+%the link onto $\torus \times \{0\}$ except for the crossing circles,
+%which remains perpendicular to the projection plane.
 
@@
 projection plane and the semi-circle arc of the crossing circle.
-We push down on the crossing circle and split the disk into
-two identical disks.
+We push down on the crossing circle and split the half-disk into
+two identical half-disks.
 We then push the arc of each crossing circle to infinity,
 collapsing them to ideal vertices.
-We obtain two triangular faces which represent the disk which look like a
+We obtain two triangular faces which represent the half-disk which look like a
 bow-tie as in Figure \ref{fig:falGluings} (a).
+See Figures \ref{fig:step_one} to \ref{fig:top-bottom}
+for an example.
 
@@
 
+The crossing edges and edges from spanning disks of crossing circles
+form the graph of the top ideal torihedron.
 We repeat the steps for the bottom half of $\torus \times I$, $\torus \times
-(-1,0]$. Then we get two torihedra. The graph of each will come from
-crossing edges and edges from crossing circles.
-Now, if there are half twists,
-we decompose the complement of the link the same way
-(as if there are no half twists)
-but we identify the two bow-ties as in Figure \ref{fig:falGluings} (b).
-Finally,
-we obtain the complement of the link by gluing the two torihedra with the gluing
+(-1,0]$. Thus we get two ideal torihedra.
+%The graph of each will come from
+%crossing edges and edges from spanning disks of crossing circles.
+
+We obtain the complement of $L$ by gluing the two torihedra with the gluing
 information given by identifying crossing edges and triangles of the bow-tie. We
@@
 \ref{fig:top-bottom} clockwise or counterclockwise.
+
+Now, if $L$ has half-twists,
+we apply the constructions above to $L'$,
+which is the link obtained from $L$ by removing all half-twists
+(replacing them with parallel strands).
+The complement of $L$ is again obtained by
+gluing the torihedra together all the same,
+except that at the bow-ties coming from twist regions with a half-twist,
+they are glued as in Figure \ref{fig:falGluings} (b).
+%we decompose the complement of the link the same way
+%(as if there are no half twists)
+%but we identify the two bow-ties as in Figure \ref{fig:falGluings} (b).
+%Finally,
 
@@
 and in fact $\Gamma_T(K) = \Gamma_B(K)$.
-
 \end{proof}
@@
 \caption{Left: The crossing arc is the edge in red.
-Middle: Picture of splitting the crossing edge. Right: The link component is
-pushed off to infinity.}
+Middle: Picture of splitting the crossing edge.
+Right: The link components are pushed off to infinity.}
 	\label{fig:step_three}
@@
 \includegraphics[height=3cm]{top-bottom.png} 
-	\caption{Left: The top torihedron. Right: The bottom torihdron with rotation for face gluing.} 
+	\caption{Left: The top torihedron.
+	Right: The bottom torihdron with rotation indicating face gluing;
+	TODO shouldn't it be rotating other way.} 
 \label{fig:top-bottom}
@@
 
-More generally, if $K$ is as above with a twist reduced diagram
+More generally, if $K$ is as above with a twist-reduced diagram
 containing bigons,

### 2021-08-23 main.tex
added the bow-tie modification of graphs; added a more concise description of the top and bottom torihedra for augmented link, makes it easier to justify some angle stuff later.

@@
 \begin{define}
-A \emph{twist region} in a link diagram of $L=\mathcal{L}/\Lambda$ in $\torus
+Recall that a \emph{twist region}
+in a link diagram is a maximal sequence of vertices
+such that consecutive vertices are two vertices of a bigon face,
+and consecutive bigons meet only at a vertex (not an edge).
+\footnote{There is an ambiguity of ``maximality'' in this definition:
+for example, if a vertex of a link diagram meets exactly one bigon,
+it can be considered as part of a twist region of length 2
+(given by that bigon),
+or it can be considered as part of a twist region of length 1,
+as there are no bigons in the other ``direction''.
+It should be clear which ``direction'' a twist region is going
+when we deal with augmentations later.
+}
+For links in the thickened torus,
+a \emph{twist region} in a link diagram of $L=\mathcal{L}/\Lambda$ in $\torus
 \times I$, is the quotient of a twist region in the biperiodic link
 $\mathcal{L}$.
-%a string of bigons, or a single crossing in the diagram on the universal cover of $\torus \times I$ is called a .  
+
 A biperiodic link
@@
 \end{define}
+
+We note that when a link diagram is cellular
+(Definition \ref{d:cellular}),
+a twist region in the torus cannot be a cycle;
+otherwise, the face adjacent to the twist region would be an annulus.
 
@@
 if at least one of the augmented twist regions
-has an odd number of bigons.
+has an odd number of vertices (i.e. even number of bigons).
 \label{d:half-twist}
@@
 \cite{Menasco} and the use of crossing edges
-between each crossing of our link
+between (TODO for?) each crossing of our link
 and Lackenby's ``cut-slice-flatten" method \cite{lackenby}
@@
 \begin{definition}
-Let $G$ be a graph with no self-loops on the torus.
-TODO definition of adding a bow-tie
+Let $G$ be a graph on the torus.
+Let $v$ be a vertex and $e,e'$ be distinct edges that meet $v$.
+A \emph{left (resp. right) bow-tie modification to $v,e,e'$}
+is the process of removing $v,e,e'$ and adding in a ``bow-tie''
+as in Figure \ref{TODO} (a) (resp. (b)).
+We call the TODO long edges, the TODO short edges,
+and TODO diagonal edges.
+TODO in figure caption, left bow-tie modification so-called because
+the triangular face appears to the left of the long edges;
+also note that left/right conincide with Figure \ref{f:right_left_aug}
 \label{d:diagram-bowtie}
@@
 
+\begin{define}
+We say a twist region is \emph{right-augmented} if, when both strands are
+(locally) oriented so that they cross the augmentation disk in the same
+direction, the crossing is a positive right-handed half-twist.
+We say a twist is \emph{left-augmented} if it is not right-augmented.
+See Figure \ref{f:right_left_aug}.
+\end{define}
+
+\begin{figure}
+\includegraphics[width=5cm]{more_pictures/right_left_aug.png}
+\caption{R: right augmentation, L: left augmentation}
+\label{f:right_left_aug}
+\end{figure}
+
+We can recover $L$ from the link diagram of $K$
+together with labels at vertices indicating left- or right-augmentation.
+
 \begin{prop}\label{p:tori_decomp}
-Let $K$ be an alternating link in the thickened torus,
+Let $K$ be an alternating link in the thickened torus
+with a cellular link diagram,
 and let $L$ be an augmented link obtained from $K$.
@@
 There is a decomposition of the complement,
-$(\torus \times I) - L$ into two ideal torihedra.
+$(\torus \times I) - L$, into two ideal torihedra.
 \end{prop}
@@
 \begin{proof}
+We first give a description of the topological operations
+that give the torihedral decomposition;
+this will justify the 
+more concise description purely in terms of link diagrams
+which we present at the end.
+
 We will begin by assuming that $L$ has no half twists.
@@
 
-We now place a \emph{crossing edge} at each crossing of the original link $K$,
+We now place a \emph{crossing edge} at each crossing of $K$,
 connecting the top and bottom strands at the crossing
@@
 and in fact $\Gamma_T(K) = \Gamma_B(K)$.
+
+As promised, we give a description of (the graphs of) the torihedra
+in terms of link diagrams of $K$ and $L$.
+Let $D = D(K)$ be the link diagram of $K$,
+and let $D'$ be the graph obtained from $D$
+by collapsing each augmented twist region of $K$ to a vertex.
+It is clear that $D'$ is the link diagram of a link $K'$
+obtained from $K$ by removing half-twists from each augmented twist region
+until one crossing remains.
+Let $v_t$ denote a vertex of $D'$ corresponding to
+an augmented twist region of $K$,
+and let $v_c$ denote a vertex of $D'$ corresponding to
+a crossing of $K$ not in an augmented twist region.
+
+Orient the edges of $D'$ to point from an undercrossing
+to an overcrossing.
+Label the two outgoing edges at vertex $v$
+(which corresponds to a crossing or a twist region)
+by $e_v^{(1)}, e_v^{(2)}$ (in arbitrary order).
+For each left- (resp. right-) augmented twist region $t$,
+we perform a left (resp. right) bow-tie modification to
+$v_t, e_{v_t}^{(1)}, e_{v_t}^{(2)}$.
+
+The resulting graph is the graph $\Gamma_T(L)$
+of the top torihedron.
+If we had oriented the edges of $D'$ the other way,
+and subsequently performed the same operations,
+we would obtain $\Gamma_B(L)$ the graph of the bottom torihedron.
+
+The non-bow-tie faces of $\Gamma_T(L)$ and $\Gamma_B(L)$
+naturally correspond
+(as the bow-tie modification procedure does not remove faces)
+and are glued together.
 \end{proof}
@@
 	Right: The bottom torihdron with rotation indicating face gluing;
-	TODO shouldn't it be rotating other way.} 
+	TODO shouldn't it be rotating other way?} 
 \label{fig:top-bottom}
@@
 is a torihedron $\sT$ with
-an assignment $\theta_e^* \in [0,\pi]$
+an assignment of an \emph{interior dihedral angle}
+$\theta_e^* \in [0,\pi]$ to each edge $e$ of $G(\sT)$
 such that for each vertex $v \in G(\sT)$,
@@
 so $\sum_{e \ni v} \theta_e = 2\pi$;
-we refer to $\theta_e$ as the exterior angle
-and $\theta_e^*$ as the interior angle. 
+we refer to $\theta_e$ as the \emph{exterior dihedral angle}.
+%and $\theta_e^*$ as the interior angle. 
 For brevity, we write dihedral angle to mean 
@@
 \begin{define}
-An \emph{angled ideal tetrahedron} is an ideal tetrahedron with an assignment of an
-dihedral angle to each edge, such that
+An \emph{angled ideal tetrahedron} is an ideal tetrahedron
+with an assignment of an
+interior dihedral angle $\theta_e^*$ to each edge $e$, such that
 \begin{itemize}
@@
 and each boundary edge $e_i$ of the base face is assigned a dihedral angle
-$\alpha_i \geq 0$ such that the sum is $\sum \alpha_i = 2\pi$.
+$\alpha_i \geq 0$ such that their sum is $\sum \alpha_i = \pi$.
 The vertical edge $e_i'$ that meets $e_i$ and $e_{i+1}$
@@
 An \emph{angle splitting} of an angled torihedron $(\sT,\theta_\bullet^*)$
-is a splitting of $\theta_e^* = \vphi_{\vec{e}} + \vphi_{\cev{e}}$
-for each edge $e$,
-where $\vec{e},\cev{e}$ are the two orientations
-on $e$,
-such that for each face $f$,
+is an assignment of an angle $\vphi_{\vec{e}}$ to each
+oriented edge $\vec{e}$, such that
+
+\begin{itemize}
+\item for each edge $e$,
+$\theta_e^* = \vphi_{\vec{e}} + \vphi_{\cev{e}}$,
+where $\cev{e}$ is the opposite orientation on $e$,
+\item for each face $f$,
 $\sum_{\vec{e} \in \del f} \vphi_{\vec{e}} = \pi$,
@@
 taken with outward orientation.
+\end{itemize}
 
@@
 of the edge-labeled graph $(G(\sT), \theta_\bullet^*)$.
+
+We say that an angle-splitting is \emph{degenerate}
+if $\vphi_{\vec{e}} = 0$ for some oriented edge $\vec{e}$;
+it is \emph{non-degenerate} otherwise.
 \end{definition}
@@
 \begin{remark}
-These $\theta$'s are related to the $\theta$'s in
+These $\theta$'s are the same as the $\theta$'s in
 \cite{BandS},
-and the $\vphi$'s are related to their ``coherent angle system''.
+and angle-splittings $\vphi_\bullet$'s
+are the same as their ``coherent angle system''.
 \end{remark}
@@
 \end{itemize} 
+Moreover, if $P_n$ is non-degenerate,
+then the resulting angled tetrahedra are also non-degenerate.
 \end{lemma}
@@
 The proof is essentially given in Figure \ref{f:ideal_pyramid_arg}.
+We spell it out here in words.
 
@@
 
+Non-degeneracy of the resulting angled tetrahedra
+follows easily from the observation that the angles
+assigned to each side of a new edge is simply the sum
+of the angles of original edges on the other side.
 \end{proof}
@@
 \label{s:hyperbolicity}
-Thurston introduced a method for finding the unique complete hyperbolic metric for a
-given 3-manifold $M$ with boundary consisting of tori \cite{Thurston}. 
+Thurston introduced a method for finding the
+unique complete hyperbolic metric for a given 3-manifold $M$
+with boundary consisting of tori \cite{Thurston}. 
 %The idea
@@
 %its four vertices on the sphere at infinity. 
-Thurston had written down a system
-of gluing and consistency equations which can be translated to 
-equations with angles for a triangulation of $M$ whose solutions correspond to the
-complete hyperbolic metric on the interior of $M$. Casson and Rivin separated Thurston's
-gluing equations into a linear and non-linear part \cite{Casson-Rivin}. Angle
-structures is the linear part of Thurston's gluing equations, and what we will
-use to attain hyperbolicity of complements of augmented links in the thickened
-torus.
+Thurston wrote down a system of gluing and consistency equations
+which can be translated to equations involving
+angles for a triangulation of $M$ whose solutions correspond to the
+complete hyperbolic metric on the interior of $M$.
+Casson and Rivin separated Thurston's
+gluing equations into a linear and non-linear part \cite{Casson-Rivin}.
+Angle structures are solutions to the linear part of
+Thurston's gluing equations;
+we will use them to attain hyperbolicity of complements
+of augmented links in the thickened torus.
 
@@
 %\cite{TODO: find rivin's paper? should be in here https://arxiv.org/pdf/1004.0440.pdf}
+
 \begin{theorem}\cite[Theorem 1.1]{FG-angles}
-Let $M$ be a 3-manifold admitting an angle structure. Then $M$ is hyperbolic.
+Let $M$ be a 3-manifold with a triangulation that admits an angle structure.
+Then $M$ is hyperbolic.
 \end{theorem}
@@
 For a hyperbolic link $K$ in $\torus \times I$, we show
-that the resulting link obtained from augmenting $K$ is
-hyperbolic. The idea is to start with a graph from the torihedral decomposition
+that the link $L$ obtained from augmenting $K$ is hyperbolic.
+The idea is to start with a graph from the torihedral decomposition
 of the link $K$ which will give us a graph on each torihedron with an angle
-assignment of
-$\pi/2$ for edge
-\cite{CKP2}.
+assignment of $\pi/2$ to each edge \cite{CKP2}.
 By \prpref{p:tori_decomp},
@@
 into tetrahedra, thus obtaining an angle structure on a triangulation.
-
-\begin{define}
-We say an augmentation is \emph{right-augmented} if, when both strands are
-(locally) oriented so that they cross the augmentation disk in the same
-direction, the crossing between them is a positive right-handed half-twist.
-See Figure \ref{f:right_left_aug}.
-We say an augmentation is \emph{left-augmented} if it is not right-augmented.
-\end{define}
-
-\begin{figure}
-\includegraphics[width=5cm]{more_pictures/right_left_aug.png}
-\caption{R: right augmentation, L: left augmentation}
-\label{f:right_left_aug}
-\end{figure}
-
-We can recover $L$ from the link diagram of $K$
-together with labels at vertices indicating left- or right-augmentation.
 

### 2021-08-24 main.tex
moved description of torihedral decomp in terms of link diagrams into a definition; cleared up proof of main theorm

@@
 \newcommand{\lemref}[1]{Lemma \ref{#1}}
+\newcommand{\defref}[1]{Definition \ref{#1}}
 \newcommand{\figref}[1]{Figure \ref{#1}}
@@
 We can recover $L$ from the link diagram of $K$
-together with labels at vertices indicating left- or right-augmentation.
+together with labels at twist regions indicating left- or right-augmentation.
+
+\begin{definition}
+\label{d:tori-decomp-graph}
+Let $L$ be a link obtained from augmenting an alternating link $K$
+with a cellular link diagram $D = D(K)$.
+We define the \emph{top/bottom bow-tie graph of $L$} as follows.
+
+%Let $D = D(K)$ be the link diagram of $K$,
+Let $D'$ be the graph obtained from $D$
+by collapsing each augmented twist region of $K$ to a vertex.
+Clearly, $D'$ is the link diagram of a link $K'$
+obtained from $K$ by removing half-twists from each augmented twist region
+until one crossing remains.
+Let $v_t$ denote a vertex of $D'$ corresponding to
+an augmented twist region of $K$,
+and let $v_c$ denote a vertex of $D'$ corresponding to
+a crossing of $K$ not in an augmented twist region.
+
+Orient the edges of $D'$ to point from an undercrossing
+to an overcrossing.
+Label the two outgoing edges at vertex $v$
+(which corresponds to a crossing or a twist region)
+by $e_v^{(1)}, e_v^{(2)}$ (in arbitrary order).
+For each left- (resp. right-) augmented twist region $t$,
+we perform a left (resp. right) bow-tie modification to
+$v_t, e_{v_t}^{(1)}, e_{v_t}^{(2)}$.
+
+We call the resulting graph the \emph{top bow-tie graph of $L$},
+denoted by $\Gamma_T(L)$.
+If we had oriented the edges of $D'$ the other way,
+and subsequently performed the same operations,
+we obtain another graph,
+which we call the \emph{bottom bow-tie graph of $L$},
+denoted by $\Gamma_B(L)$.
+\hfill $\triangle$
+\end{definition}
+
+Note that the non-bow-tie faces of $\Gamma_T(L)$ and $\Gamma_B(L)$
+are naturally identified with the faces of $D'$
+(as the bow-tie modification procedure does not remove faces).
 
@@
 There is a decomposition of the complement,
-$(\torus \times I) - L$, into two ideal torihedra.
+$(\torus \times I) - L$, into two ideal torihedra;
+the graphs of the torihedra are $\Gamma_T(L)$ and $\Gamma_B(L)$.
 \end{prop}
@@
 \begin{proof}
-We first give a description of the topological operations
-that give the torihedral decomposition;
-this will justify the 
-more concise description purely in terms of link diagrams
-which we present at the end.
+%As mentioned before, we will be combining
+%Menasco's method using crossing edges at each crossing
+%and Lackenby's ``cut-slice-flatten'' method
+%on augmentation sites.
+
+%We give a description of the topological operations
+%that give the torihedral decomposition;
+%this will justify the 
+%more concise description purely in terms of link diagrams
+%which we present in Remark \ref{r:tori-decomp-graph}.
 
@@
 form the graph of the top ideal torihedron.
-We repeat the steps for the bottom half of $\torus \times I$, $\torus \times
-(-1,0]$. Thus we get two ideal torihedra.
+It is not hard to see that this graph is $\Gamma_T(L)$.
+We repeat similar steps for the bottom half of $\torus \times I$,
+$\torus \times (-1,0]$
+(note we should be pushing the bottom strands up towards the top strand).
+It is also easy to see that this graph is $\Gamma_B(L)$
+(from the same perspective, not from the perspective of the bottom end
+$\torus \times \{-1\}$).
+Thus we get two ideal torihedra.
 %The graph of each will come from
@@
 We obtain the complement of $L$ by gluing the two torihedra with the gluing
-information given by identifying crossing edges and triangles of the bow-tie. We
-glue the faces of the torihedra which do not correspond to a bow-tie with a
-$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
-\ref{fig:top-bottom} clockwise or counterclockwise.
+information given by identifying crossing edges and triangles of the bow-tie.
+As observed before, the non-bow-tie faces of $\Gamma_T(L),\Gamma_B(L)$
+naturally pair up, and we glue them accordingly
+(there is a ``$2\pi/n$'' twist when gluing these faces,
+where $n$ is the number of sides of each face as in Figure
+\ref{fig:top-bottom} clockwise or counterclockwise).
+The bow-tie triangular faces are glued up according to
+\figref{fig:falGluings} (a).
+%We glue the faces of the torihedra which do not correspond to a bow-tie with a
+%$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
+%\ref{fig:top-bottom} clockwise or counterclockwise.
 
@@
 
-For future reference, we will denote the graph for the top and bottom
-torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
-where both graphs are viewed from the cone point of the top torihedron
-$\torus \times \{1\}$.
-Note that if $L = K$ is the non-augmented link,
-$\Gamma_T(L)$ is simply the link projection of $K$,
-and in fact $\Gamma_T(K) = \Gamma_B(K)$.
-
-As promised, we give a description of (the graphs of) the torihedra
-in terms of link diagrams of $K$ and $L$.
-Let $D = D(K)$ be the link diagram of $K$,
-and let $D'$ be the graph obtained from $D$
-by collapsing each augmented twist region of $K$ to a vertex.
-It is clear that $D'$ is the link diagram of a link $K'$
-obtained from $K$ by removing half-twists from each augmented twist region
-until one crossing remains.
-Let $v_t$ denote a vertex of $D'$ corresponding to
-an augmented twist region of $K$,
-and let $v_c$ denote a vertex of $D'$ corresponding to
-a crossing of $K$ not in an augmented twist region.
-
-Orient the edges of $D'$ to point from an undercrossing
-to an overcrossing.
-Label the two outgoing edges at vertex $v$
-(which corresponds to a crossing or a twist region)
-by $e_v^{(1)}, e_v^{(2)}$ (in arbitrary order).
-For each left- (resp. right-) augmented twist region $t$,
-we perform a left (resp. right) bow-tie modification to
-$v_t, e_{v_t}^{(1)}, e_{v_t}^{(2)}$.
-
-The resulting graph is the graph $\Gamma_T(L)$
-of the top torihedron.
-If we had oriented the edges of $D'$ the other way,
-and subsequently performed the same operations,
-we would obtain $\Gamma_B(L)$ the graph of the bottom torihedron.
-
-The non-bow-tie faces of $\Gamma_T(L)$ and $\Gamma_B(L)$
-naturally correspond
-(as the bow-tie modification procedure does not remove faces)
-and are glued together.
+%%For future reference, we will denote the graph for the top and bottom
+%%torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
+%%where both graphs are viewed from the cone point of the top torihedron
+%%$\torus \times \{1\}$.
+%%Note that if $L = K$ is the non-augmented link,
+%%$\Gamma_T(L)$ is simply the link projection of $K$,
+%%and in fact $\Gamma_T(K) = \Gamma_B(K)$.
 \end{proof}
@@
 %TODO: this definition should come after base-angled pyramid
-An \emph{angle splitting} of an angled torihedron $(\sT,\theta_\bullet^*)$
+An \emph{angle-splitting} of an angled torihedron $(\sT,\theta_\bullet^*)$
 is an assignment of an angle $\vphi_{\vec{e}}$ to each
@@
 
-Equivalently, an angle splitting is a decomposition of
+Equivalently, an angle-splitting is a decomposition of
 $\sT$ into base-angled pyramids,
-one for each face of $G(\sT)$, such that
-for each boundary edge $e$ of $\sT$,
-the dihedral angles from the two adjacent pyramids
-add to $\theta_e^*$.
+one for each face $F$ of $G(\sT)$, such that
+the interior dihedral of the edge $\vec{e} \in \del F$
+is $\vphi_{\vec{e}}$.
+%for each boundary edge $e$ of $\sT$,
+%the dihedral angles from the two adjacent pyramids
+%add to $\theta_e^*$.
 
@@
 Let $\Gamma = (V,E)$ be a graph on the torus,
-and let $\Gamma^* = (F,E^*)$ be the dual graph,
-with $E^*$ being naturally identified with $E$.
-Let $\theta_\bullet \in (0,\pi)^E$
+and let $\check{\Gamma} = (F,\check{E})$ be the dual graph,
+with $\check{E}$ being naturally identified with $E$.
+%Let $\theta_\bullet \in (0,\pi)^E$
+Let $f \in (0,\pi)^E$
 be a function on the set of edges $E$
-that sums to $2\pi$ around each vertex of $V$.
-
-There exists an angle-splitting of $(\Gamma,\theta_\bullet)$
+that sums to $2\pi$ around each vertex of $V$;
+let $f^*(e) = \pi - f(e)$.
+
+There exists a non-degenerate
+%angle-splitting of $(\Gamma,\theta_\bullet)$
+angle-splitting of $(\Gamma,f^*)$
 if and only if the following
@@
 Suppose we cut the torus along a subset of edges in the dual graph
-$\Gamma^*$, obtaining one or more pieces;
+$\check{\Gamma}$, obtaining one or more pieces;
 Then for any piece that is a disc,
-the sum of $\theta_\bullet$ over the edges in the boundary
+the sum of $f$ over the edges in the boundary
 of the piece is at least $2\pi$,
@@
 and $L$ is obtained by augmenting $K$
-at every twist region with at least one bigon
-(and possibly other crossings),
+such that every twist region with at least one bigon is augmented,
+%(and possibly other crossings),
 then $L$ is hyperbolic.
@@
 \begin{proof}
-Let us first consider the case when $K$ did not have bigons.
-
-By \cite[Theorem 7.5]{CKP2},
-(as discussed in \prpref{p:tori_decomp},)
-$\toruscomp{K}$ can be decomposed
-into two torihedra $\sT_T$ and $\sT_B$,
-with $\sT_T$ meeting the top cone point $\torus \times \{1\}$
-and $\sT_B$ meeting the bottom cone point $\torus \times \{-1\}$.
-We denote their graphs by $\Gamma_T(K), \Gamma_B(K)$ respectively;
-viewed from the top cone point $\torus \times \{1\}$,
-both graphs are the same as the projection graph of $K$.
-%which we denote by $\Gamma$.
-We make them non-degenerate angled torihedra by assigning $\theta^* = \pi/2$
-for all edges.
-%%Unlike in the case of alternating links or fully augmented links 
-%%in the thickened torus we cannot make all angles $\pi/2$. This is 
-%%because in our decomposition the vertices of the graph which
-%%defines our torihedra are not all four valent.
-
-Using the fact that $K$ is weakly prime,
-it is not hard to see that the ``cocycle condition''
-of \thmref{t:bs-thm4} is satisfied.
-
-\begin{figure}
-\includegraphics[width=7cm]{more_pictures/horizontal_bowtie.png}
-\caption{Assignments of $\theta^*$ to edges of a bow-tie
-	corresponding to an augmentation site}
-\label{f:bowtie_angles}
-\end{figure}
-
+%Let us first consider the case when $K$ did not have bigons.
 By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
@@
 with graphs $\Gamma_T(L),\Gamma_B(L)$.
-We make them degenerate angled torihedra by assigning $\theta^*$'s
-to edges of the bow-ties as in Figure \ref{f:bowtie_angles},
-and assign $\pi/2$ to all other edges.
-It is easy to check that upon gluing,
-each edge has sum of dihedral angles ($\theta^*$) that is equal to $2\pi$.
-(This holds true even if they were glued assuming
-some augmentations had no half-twist;
-see end of proof where we deal with $K$ having bigons.)
-%\remref{r:nohalftwist}.)
-
-Furthermore, we can obtain an angle-splitting of $\sT_T(L)$
-(and similarly $\sT_B(L)$) by modifying the angle-splitting
-for $\sT_T(K)$;
-this is shown in Figure \ref{f:bowtie_angles2}.
-
-\begin{figure}
-\begin{tabular}{cc}
-\includegraphics[width = 5cm]{before_bowtie_angles.png}&
-\includegraphics[width = 5cm]{bowtie_angles.png}\\
-(a)&(b)
-\end{tabular}
-\caption{(a) Angle splitting before augmentation (b) Angle splitting for bowtie corresponding to augmentation}
-\label{f:bowtie_angles2}
-\end{figure}
+
+Recall that $\Gamma_T(L),\Gamma_B(L)$ are
+obtained by bow-tie modifications of the diagram $D'$
+of a link $K'$
+(see \defref{d:tori-decomp-graph}).
+Assign to each edge $e$ of $D'$ the angle $\theta_e = \pi/2$
+(so that $\theta_e^* = \pi/2$).
+Using the fact that $K'$ is weakly prime
+(which easily follows from $K$ being weakly prime),
+it is not hard to see that the ``cocycle condition''
+of \thmref{t:bs-thm4} is satisfied by this assignment.
+Thus, there exists a non-degenerate angle-splitting
+$\vphi_\bullet$ of $(D',\theta_\bullet^*)$.
+%Recall from the proof of \prpref{p:tori_decomp}
+%that the two graphs $\Gamma_T(L),\Gamma_B(L)$
+%can be obtained by modifying the link diagram of $K$:
+%we take $K'$ to be the link that agrees with $K$ everywhere
+%except each augmented twist region has only one crossing,
+%and $\Gamma_T(L),\Gamma_B(L)$ are
+
+Now we perform the bow-tie modifications to obtain
+$\Gamma_T(L),\Gamma_B(L)$.
+For each step (i.e. each bow-tie modification),
+we show how to modify the $\theta^*$ assignments
+and how to get angle-splittings.
+Say we perform such a modification
+at some vertex $v$ and two edges $e^{(1)},e^{(2)}$.
+We assign new $\theta_\bullet^*$ angles to
+the resulting bow-tie modification graph
+as in \figref{f:bowtie_angles}.
+Note that the sum of $\theta$ (not $\theta^*$)
+around each vertex is still $2\pi$.
+\figref{f:bowtie_angles2} shows an angle-splitting
+of this assignment.
+TODO perhaps these figures need some tidying up
+
+It is straightforward to check that
+upon gluing the top and bottom torihedra,
+the sum of interior dihedral angles $\theta^*$
+around each edge is $2\pi$;
+crossing edges have $\theta^* = \pi/2$,
+and appear four times, twice in each torihedron,
+while for bow-tie edges,
+simply check for half-twist and non-half-twist cases
+separately.
 
@@
 Consider a face $f$ of $\Gamma_T(L)$ that is not in a bow-tie.
-Suppose the corresponding face $\bar{f}$ of $\Gamma$,
-the projection graph (which is equal to $\Gamma_T(K)$),
+Suppose the corresponding face $\bar{f}$ of $D'$
 had vertices $v_1,\ldots,v_n$ in counter-clockwise order.
@@
 Upon gluing, this gives an angle structure on the triangulation
-of $\toruscomp{L}$
-
-Now let us consider $K$ with bigons.
-Let $K'$ be the link obtained from $K$ by replacing
-each twist region of $K$ by a single appropriate crossing.
-Let $L'$ be the link obtained from augmenting $K'$
-by exactly the same crossing circles.
-The top and bottom torihedra $\sT_T(L'),\sT_B(L')$
-are the same as $\sT_T(L),\sT_B(L)$;
-however, the gluing differs slightly:
-for twist regions of $K$ that have an even number of bigons,
-the gluing of $\sT_T(L')$ to $\sT_B(L')$
-should be using Figure \ref{fig:falGluings} (a) (not (b)).
-As remarked throughout the proof,
-all the arguments carry through verbatim.
-
-%Then the only difference in the arguments
-%is that, for twist regions of $K$ that have an even number of bigons,
-%the
-
-%\begin{remark}
-%\label{r:nohalftwist}
-If the original link $K$ had some twist regions with at least one bigon,
-we may consider augmentations $L$ where all such twist regions
-are augmented, i.e. $L$ may have augmentations without half-twists.
-Then, as pointed out in proof of \thmref{t:auglink_hyp} above,
-the proof still works for $L$, showing that $L$ is also hyperbolic.
-%\end{remark}
-
+of $\toruscomp{L}$.
+Thus, $L$ is hyperbolic.
 \end{proof}

### 2021-08-24 main.tex
put back the figures in proof

@@
 Assign to each edge $e$ of $D'$ the angle $\theta_e = \pi/2$
-(so that $\theta_e^* = \pi/2$).
+(so that $\theta_e^* = \pi/2$ too).
 Using the fact that $K'$ is weakly prime
@@
 TODO perhaps these figures need some tidying up
+
+\begin{figure}
+\includegraphics[width=7cm]{more_pictures/horizontal_bowtie.png}
+\caption{Assignments of $\theta^*$ to edges of a bow-tie
+	corresponding to an augmentation site}
+\label{f:bowtie_angles}
+\end{figure}
+
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width = 5cm]{before_bowtie_angles.png}&
+\includegraphics[width = 5cm]{bowtie_angles.png}\\
+(a)&(b)
+\end{tabular}
+\caption{(a) Angle splitting before augmentation (b) Angle splitting for bowtie corresponding to augmentation}
+\label{f:bowtie_angles2}
+\end{figure}
 
@@
 We add new edges across $f$ as follows.
-(See Figure \ref{f:adding_edges};
+(See \figref{f:adding_edges};
 ignore the + and - signs for now.)
+
+\begin{figure}
+\includegraphics[width=5cm]{more_pictures/one_edge.png}
+%\includegraphics[width=5cm]{more_pictures/two_edge.png}
+\includegraphics[width=5cm]{more_pictures/two_edge_many.png}
+\caption{Red edge indicates an added edge to the graph to appropriately assign +/- labels which indicate 
+increasing/decreasing angles on the edge respectively.}
+\label{f:adding_edges}
+\end{figure}
 

### 2021-08-25 main.tex
fixed proof, need to do some diagrams

@@
 \newtheorem{example}[theorem]{Example}
+\newtheorem{convention}[theorem]{Convention}
 
@@
 \newtheorem{remark}[theorem]{Remark}
+
+\newcommand{\cm}{,\linebreak[1]}
 
@@
 and consecutive bigons meet only at a vertex (not an edge).
-\footnote{There is an ambiguity of ``maximality'' in this definition:
-for example, if a vertex of a link diagram meets exactly one bigon,
-it can be considered as part of a twist region of length 2
-(given by that bigon),
-or it can be considered as part of a twist region of length 1,
-as there are no bigons in the other ``direction''.
-It should be clear which ``direction'' a twist region is going
-when we deal with augmentations later.
-}
+We say that the \emph{direction} of a twist region
+is the pair of faces (possibly the same face)
+that are across from the bigons at the end;
+if a twist region consists of only one vertex,
+a direction is a pair of opposite faces (again, possibly the same face)
+meeting at the crossing.
+%%\footnote{There is an ambiguity of ``maximality'' in this definition:
+%%for example, if a vertex of a link diagram meets exactly one bigon,
+%%it can be considered as part of a twist region of length 2
+%%(given by that bigon),
+%%or it can be considered as part of a twist region of length 1,
+%%as there are no bigons in the other ``direction''.
+%%It should be clear which ``direction'' a twist region is going
+%%when we deal with augmentations later.
+%%}
+
 For links in the thickened torus,
@@
 where $\vec{e} \in \del f$ is the edge in the boundary of $f$
-taken with outward orientation.
+taken with outward-orientation
+(see Convention \ref{cvn:ornt-edge}).
 \end{itemize}
@@
 \end{definition}
+
+\begin{convention}
+The outward-orientation on the boundary of a face
+is the orientation such that the face is to the left of the boundary.
+An assignment/label on an oriented edge $\vec{e}$
+(for example, $\vphi_{\vec{e}}$)
+will usually be drawn to the left of that edge.
+\label{cvn:ornt-edge}
+\end{convention}
 
@@
 \caption{Assignments of $\theta^*$ to edges of a bow-tie
-	corresponding to an augmentation site}
+	corresponding to an augmentation site;
+	the edges labeled $\pi$ are the long edges,
+	the edges labeled 0 are the short edges,
+	the edges labeled $\pi/2$ are the diagonal edges}
 \label{f:bowtie_angles}
@@
 Now we have a decomposition of the two torihedra into
-degenerate base-angled pyramids.
-However, we need the pyramids to be non-degenerate,
-so we first need to modify the angles and graph on the torihedra
-to make all $\theta^*$ nonzero.
-
-Consider a face $f$ of $\Gamma_T(L)$ that is not in a bow-tie.
+degenerate base-angled pyramids
+(recall that that means that some of the
+interior dihedral angles $\theta^*$ are 0),
+but we need the pyramids to be non-degenerate,
+so we need to modify the graph on the torihedra
+and the angle assignments to make all $\theta^*$ nonzero.
+
+We first modify the graphs on the torihedra by adding edges
+to them for some extra ``flexibility''.
+Consider a face $f$ of $\Gamma_T(L)$ that is not from a bow-tie.
 Suppose the corresponding face $\bar{f}$ of $D'$
 had vertices $v_1,\ldots,v_n$ in counter-clockwise order.
+Note that $f$ may meet a vertex twice,
+but we label each occurence with its own index.
 We label the edges of $f$ by $e_{i,0}$, $e_{i,\pi}$, or $e_i$,
-depending on whether the $\theta^*$ is $0$, $\pi$, or $\pi/2$ respectively,
-with $i$ non-decreasing from 1 to $n$,
-adjacent edges having the same $i$ if and only if they
-belong to the same bow-tie.
-For sake of concreteness,
-suppose that if a vertex $v_i$ is right-augmented,
-then the augmentation circle intersects $\bar{f}$
-(everything is similar if it is left-augmented vertices' circles
-that intersect $\bar{f}$).
-In other words, locally, $f$ meets two of the edges of the bow-tie
-corresponding to a right-augmented vertex $v_i$
-(which would be labeled $e_{i,0}, e_{i,\pi}$ in counter-clockwise order),
-but only meets one of the edges of the bow-tie corresponding to
-a left-augmented vertex.
+depending on whether the $\theta^*$ of that edges
+is $0$, $\pi$, or $\pi/2$ respectively.
+%with $i$ non-decreasing from 1 to $n$,
+%so that adjacent edges having the same $i$ if and only if they
+%belong to the same bow-tie.
+More precisely, for a vertex $v_i$ corresponding to a crossing
+of $K$ that is not augmented,
+we label $e_{v_i}^{(.)}$ by $e_i$
+(here $e_{v_i}^{(.)}$ is $e_{v_i}^{(1)}$ or $e_{v_i}^{(2)}$,
+whichever meets $\bar{f}$; see \defref{d:tori-decomp-graph}).
+For a vertex $v_i$ that corresponds to a twist region of $K$,
+if the direction of the twist region is towards $\bar{f}$,
+then $f$ meets a diagonal edge of the bow-tie corresponding to $v_i$,
+and we label it $e_i$;
+if not, then $f$ meets a short and long edge of the corresponding bow-tie,
+and we label them by $e_{i,0}$ and $e_{i,\pi}$,
+respectively.
+
+If $\bar{f}$ does not have vertices of the latter kind,
+i.e. if $f$ does not meet short or long edges,
+then we will not modify $f$.
+So assume that $\bar{f}$ does have such a vertex,
+and suppose it is left-augmented
+(the other case is treated similarly).
+Then for all left-augmented vertices $v_i$ of $\bar{f}$,
+$f$ would meet the short,long edges $e_{i,0},e_{i,\pi}$,
+while for all right-augmented vertices,
+$f$ would meet the diagonal edges.
+In particular,
+the edges $e_{i,0}, e_{i,\pi}$ always appear in counter-clockwise order),
 
@@
 is a maximally contiguous subsequence of left-augmented vertices
-of $G(K)$ around the face $\bar{f}$;
+of $D'$ around $\bar{f}$;
 the edges around $f$ would start
-$e_{1,0}, e_{1,\pi}, e_{2,0}, e_{2,\pi}, \ldots$.
-We add new edges across $f$ as follows.
-(See \figref{f:adding_edges};
-ignore the + and - signs for now.)
-
-\begin{figure}
-\includegraphics[width=5cm]{more_pictures/one_edge.png}
-%\includegraphics[width=5cm]{more_pictures/two_edge.png}
-\includegraphics[width=5cm]{more_pictures/two_edge_many.png}
-\caption{Red edge indicates an added edge to the graph to appropriately assign +/- labels which indicate 
-increasing/decreasing angles on the edge respectively.}
-\label{f:adding_edges}
-\end{figure}
-
-First suppose $k=n$; then we do nothing.
-
-Next suppose there is only one such maximal contiguous subsequence.
-If $k = 1$, we add an edge that goes across
-$e_{1,0},e_{1,\pi},e_2$
+$e_{1,0} \cm e_{1,\pi} \cm e_{2,0} \cm e_{2,\pi} \cm \ldots
+	\cm e_{k,0} \cm e_{k,\pi} \cm \ldots$.
+We add new edges across $f$ as follows
+(see \figref{f:adding_edges};
+ignore the + and - signs for now.):
+
+\begin{itemize}
+\item \textbf{Case $k=n$:} (i.e. every vertex of $\bar{f}$ is left-augmented.)
+In this case, we do nothing.
+
+\item \textbf{Case: There is only one such maximal contiguous subsequence:}
+
+\textbf{Subcase: $k=1$:}
+We add an edge that goes across $e_{1,0},e_{1,\pi},e_2$
 (in the sense that the new edge separates the edges of $f$ into two sets,
@@
 %(these two edges do not form a bigon because we've ruled out $k=n$).
-If $k \geq 2$,
-we add an edge across $e_{1,0},e_{1,\pi}$
+
+\textbf{Subcase: $k \geq 2$:}
+We add an edge across $e_{1,0},e_{1,\pi}$
 and another edge across $e_{2,0},e_{2,\pi},e_{3,0},\ldots,e_{k,\pi}$
@@
 
-Finally, if there are multiple such maximal contiguous subsequences,
-we just add edges as above for each contiguous subsequence.
-The only caveat is that if the procedure calls to add a new edge
-that would form a bigon with the existing edges,
-we just do not add it.
-
-This way we obtain a new graph $\Gamma_T(L)'$, which defines a
-new torihedron $\sT_T(L)'$.
-We make $\sT_T(L)'$ angled using the angles from $\sT_T(L)$ for old edges,
-and putting $\pi$ for all new edges TODO make clear it's the red edges that is
-new.
+\textbf{Case: There are multiple such maximal contiguous subsequences.}
+We just add edges as in the previous case for each contiguous subsequence,
+except one special case: when the edges of $f$ are exactly
+$e_{1,0},e_{1,\pi},e_2,e_{3,0},e_{3,\pi},e_4$,
+we add only one edge separating the first three edges from the other three.
+(This prevents formation of a bigon.)
+\end{itemize}
 
@@
 \includegraphics[width=5cm]{more_pictures/two_edge_many.png}
-\caption{Red edge indicates an added edge to the graph to appropriately assign +/- labels which indicate 
-increasing/decreasing angles on the edge respectively.}
+\caption{TODO change this. Red edge indicates an added edge to $\Gamma_T(L)$;
+the +/- labels indicate whether to
+increase/decrease $\theta^*$ and $\vphi$.}
 \label{f:adding_edges}
@@
 
-Now we deform the $\theta^*$ based on Figure \ref{f:adding_edges},
-increasing/decreasing by some small $\veps' > 0$ if the edge
-is labeled $+/-$.
-Note some edges may be labeled twice, in which case we perform
-both increasing/decreasing (e.g. if it is labeled $+$ and $-$,
-the $\theta^*$ is not changed).
-It is easy to see that the sum of $\theta^*$ around a vertex
-remains unchanged.
-Furthermore, all the edges with $\theta^*$ originally equal 0,
-i.e. all $e_{i,0}$'s,
-now have positive $\theta^*$,
-(it receives only one label $+$,
-because the other face it meets is a bow-tie).
-
-%Thus, we could attempt to apply the feasible flow theorem in a similar manner,
-%and obtain an angle-splitting for $\sT_T(L)'$, but 
-%TODO rephrase nicely.
-We can directly get an angle-splitting for $\sT_T(L)'$
-using the angle-splitting for $\sT_T(L)$.
-We reuse the $+/-$ assignments from Figure \ref{f:adding_edges}.
-For $e = e_{i,0}$, we increase $\vphi_{\vec{e}}, \vphi_{\cev{e}}$
-by $\veps'/2$ each; for $e = e_{i,\pi}$,
-we decrease them by $\veps'/2$ each.
-For other edges, we increase/decrease $\vphi_{\vec{e}}$ by $\veps'$,
-where $\vec{e}$ is the oriented edge corresponding to the side
-on which the $+/-$ sign appears in Figure \ref{f:adding_edges};
-so for example, if an edge $e$ receives both $+$ and $-$,
-then one of $\vphi_{\vec{e}},\vphi_{\cev{e}}$ increases
-while the other decreases, thus $\theta_e^*$ remains constant.
-
-Now we address $\sT_B(L)$.
-In the gluing of $\sT_T(L)$ to $\sT_B(L)$,
-non-bow-tie faces of $\Gamma_T(L)$ are identified with
-non-bow-tie faces of $\Gamma_B(L)$.
-Under this identification, we add the same edges to $\Gamma_B(L)$,
-thus obtaining the new torihedron $\sT_B(L)'$ with graph
-$\Gamma_B(L)'$.
-We perform the same deformations of $\theta^*$'s (or $\vphi$'s).
-
-We need to check that upon gluing $\sT_T(L)'$ to $\sT_B(L)'$,
-the sum of dihedral angles around each edge is still $2\pi$.
-This was clearly true before deforming, as the new edges of
-$\Gamma_T(L)'$ only gets identified with the unique
-corresponding edge of $\Gamma_B(L)'$, and they are both labeled
-with $\theta^* = \pi$.
-To see that the deformation does not change these sums,
-note that in the identification of faces of $\Gamma_T(L)'$
-to $\Gamma_B(L)'$,
-an edge with $\theta^*=0$ is identified with an edge with
-$\theta^*=\pi$,
-so an increase in the former would be conterbalanced by
-a decrease in the latter.
-It is also easy to see this is the case for the other edges.
-(Once again, a similar argument applies if $\sT_T(L)'$
-and $\sT_B(L)'$ are glued assuming
-some augmentations had no half-twist;
-see end of proof where we deal with $K$ having bigons.)
-%see \remref{r:nohalftwist}.)
-
-Finally, for each face of $\Gamma_T(L)'$ that has more than three sides,
+This way we obtain a new graph $\Gamma_T'$, which defines a
+new torihedron $\sT_T'$.
+We make $\sT_T'$ angled using the angles from $\sT_T(L)$ for old edges,
+and putting $\theta^* = \pi$ for all new edges.
+
+We can get an angle-splitting for $(\Gamma_T',\theta^*)$,
+using the angle-splitting for $\Gamma_T(L)$ for old edges,
+and for a new edge $e$ that cuts through some face $f$ of $\Gamma_T(L)$,
+we assign $\vphi_{\vec{e}} = \sum \vphi_{\vec{e'}}$,
+where the sum is over all the edges $\vec{e'} \in \del f$
+that on the other side of $\vec{e}$.
+It is easy to see that the new assignments are all non-zero
+(follows from non-degeneracy of the angle-splitting on $D'$).
+
+Now fix some small $\veps > 0$.
+Let $\vphi_{\vec{e}}' = \vphi_{\vec{e}} + x \cdot \veps$,
+where $x$ is the label on $\vec{e}$ (0 if unlabeled).
+Let $\theta_e'^* = \vphi_{\vec{e}}' + \vphi_{\cev{e}}'$.
+It is easy to check that the sum of $\theta'*$
+around each vertex is the same as for $\theta^*$,
+so it defines an angled torihedron $(\sT_T',\theta'^*)$.
+It is also easy to check that for each face of $\Gamma_T'$,
+the $+/-$ labels cancel out,
+so $\vphi'$ is an angle-splitting of it.
+Furthermore, all shorts edges
+(which are the only edges with $\vphi_{\vec{e}} = 0$)
+have a $+1$ label on each side,
+so $\vphi'$ is non-degenerate.
+
+Now we perform the same operations for the bottom torihedron,
+adding new edges to $\Gamma_B(L)$ to get $\Gamma_B'$
+in the same manner;
+note that left and right augmentations are switched,
+so that the order of $e_{i,0},e_{i,\pi}$ are switched.
+Thus all the $+/-$ labels in \figref{f:adding_edges}
+should have switched signs.
+We also get a nondegerate angle-splitting $\vphi'$
+of an angled torihedron $(\sT_B',\theta'^*)$.
+
+It is easy to see that, under the gluing of
+$\sT_T(L)$ to $\sT_B(L)$,
+the new edges added to $\Gamma_T(L)$
+are glued to the new edges added to $\Gamma_B(L)$.
+As noted before, upon gluing $\sT_T(L)$ to $\sT_B(L)$
+the sum of exterior dihedral angles $\theta^*$ around each edge
+is $2\pi$.
+This clearly remains true after adding the new edges
+(they're label $\pi$ on each torihedron).
+It is also eashy to check that the $+/-$ labels get canceled out.
+Thus, upon gluing $\sT_T'$ to $\sT_B'$,
+the sum of new exterior dihedral angles $\theta'^*$ around each edge
+is $2\pi$.
+
+Finally, we obtain a triangulation with an angle structure as follows.
+For each face of $\Gamma_T'$ that has more than three sides,
 we arbitrarily decompose it into triangles
 and apply \lemref{l:pyramid_decomp}
-to obtain a triangulation of $\sT_T(L)'$ into non-degenerate angled tetrahedra;
+to obtain a triangulation of $\sT_T'$ into non-degenerate angled tetrahedra;
 perform the corresponding decomposition for faces of
-$\Gamma_B(L)'$ and obtain a triangulation of $\sT_B(L)'$
+$\Gamma_B'$ and obtain a triangulation of $\sT_B'$
 into non-degenerate angled tetrahedra.
-Upon gluing, this gives an angle structure on the triangulation
-of $\toruscomp{L}$.
+These triangulations glue up into a triangulation of $\toruscomp{L}$
+with an angle structure.
 Thus, $L$ is hyperbolic.
@@
 \end{document}
+
+%%Figures for easy look up
+
+%augmenting twist regions
+%\label{fig:Augmentations}
+
+%left right augmentations
+%\label{f:right_left_aug}
+
+%crossing edge, Menasco thing
+%\label{fig:crossingArc}
+
+%cut-slice-flatten, bow-ties, gluing
+%\label{fig:falGluings}
+
+%definition of the torihedral decomp graph
+%\label{d:tori-decomp-graph}
+
+%assignments of theta^*
+%\label{f:bowtie_angles}
+
+%assigment of +/- labels
+%\label{f:adding_edges}

### 2021-08-27 main.tex
drawing diagrams..

@@
 %\usepackage[all,cmtip]{xy} 
-%\usepackage{tikz}
+%\usepackage{mystyle}
+
+%%%%%%%%%%%%%%%%%% Tikz %%%%%%%%%
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+\usetikzlibrary{shapes.multipart} %% for multiple lines in node (must have align=center)
+\usetikzlibrary{calc}
+\usetikzlibrary{scopes}
+\usetikzlibrary{math}
+\usetikzlibrary{decorations.markings,decorations.pathreplacing}
+\usetikzlibrary{fadings}
 \usepackage{tikz-cd}
-%\usepackage{mystyle}
+
+\setlength{\textwidth}{\paperwidth}
+\addtolength{\textwidth}{-2in}
+\setlength{\textheight}{\paperheight}
+\addtolength{\textheight}{-2in}
+\calclayout
+
+\tikzset{
+every picture/.style={line width=0.8pt, >=stealth,
+                       baseline=-3pt,label distance=-3pt},
+%%%%%%%%%%  Node styles
+emptynode/.style={circle,minimum size=0pt, inner sep=0pt, outer
+sep=0},
+dotnode/.style={fill=black,circle,minimum size=2.5pt, inner sep=1pt, outer
+sep=0},
+small_dotnode/.style={fill=black,circle,minimum size=2pt, inner sep=0pt, outer
+sep=0},
+morphism/.style={fill=white,circle,draw,thin, inner sep=1pt, minimum size=15pt,
+                 scale=0.8},
+small_morphism/.style={fill=white,circle,draw,thin,inner sep=1pt,
+                       minimum size=10pt, scale=0.8},
+ellipse_morphism/.style args={#1}{fill=white,circle,draw,thin,inner sep=1pt,
+                       minimum size=5pt, scale=0.8,
+												ellipse, draw, rotate=#1},
+%note that ellipse stretches based on the text inside, so put \;\;\; in label
+coupon/.style={draw,thin, inner sep=1pt, minimum size=18pt,scale=0.8},
+semi_morphism/.style args={#1,#2}{
+                  fill=white,semicircle,draw,thin, inner sep=1pt, scale=0.8,
+                  shape border rotate=#1,
+                  label={#1-90:#2}},
+%%can only rotate semi_morphisms by right angles tho
+%%%% different line styles:
+regular/.style={densely dashed}, %% for the regular color, i.e. sum d_i
+edge/.style={very thick, draw=green, text=black},
+overline/.style={preaction={draw,line width=2mm,white,-}},
+thin_overline/.style={preaction={draw,line width=#1 mm,white,-}},
+thin_overline/.default=2,
+thick_overline/.style={preaction={draw,line width=3mm,white,-}},
+really_thick/.style={line width=3mm, gray},
+%drinfeld center/.style={>=stealth,green!60!black, double
+%distance=1pt,text=black},
+boundary/.style={thick,  draw=blue, text=black},
+%arrow_decoration={markings, mark=at position 0.5 with {\arrow{>}}}
+ribbon/.style={line width=1.5mm, postaction={draw,line width=1mm,white}},
+ribbon_u/.style args={#1,#2}{line width=#1mm, postaction={draw,line width=#2mm,white}},
+%use line width=0.4pt for thin lines to point to things
+%%%%%%% Fill styles %%%%%%%%%%%%%%%
+cell/.style={fill=black!10},
+subgraph/.style={fill=black!30},
+%%%%%%% Mid-path arrows
+midarrow/.style={postaction={decorate},
+                 decoration={
+                    markings,% switch on markings
+                    mark=at position #1 with {\arrow{>}},
+                 }},
+midarrow/.default=0.5,
+%%%%% Mid-path arrow but reverse
+midarrow_rev/.style={postaction={decorate},
+                 decoration={
+                    markings,% switch on markings
+                    mark=at position #1 with {\arrow{<}},
+                 }},
+midarrow_rev/.default=0.5,
+%%%%% for the flowchart; need align=center to allow multiline in node
+block/.style={rectangle, rounded corners, text centered, draw=black, align=center}
+}
+
+%% style for flow chart blocks
+\tikzstyle{block} = [rectangle, rounded corners, text centered, draw=black, align=center]
+
+%% for shading with gradients
+\tikzfading[name=fade inside, inner color=transparent!80, outer
+color=transparent!10]
+
+%%%end tikz stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\begin{tikzpicture}
+\node[emptynode] (a) at (-0.9,-0.3) {};
+\node[dotnode] (b) at (-0.3,-0.1) {};
+\node[dotnode] (c) at (0.3,0.1) {};
+\node[emptynode] (d) at (0.9,0.3) {};
+%% two strands going out back
+\draw (b) -- +(150:1cm);
+\draw (c) -- +(150:1cm);
+%% the ellipse; draw top arc, then fill, then bottom arc
+\draw[thin_overline={1}] (a) -- (b) -- (c) -- (d)
+	.. controls +(90:0.8cm) and +(90:0.8cm) .. (a);
+\draw[fill, opacity=0.2] (a) -- (d)
+	.. controls +(90:0.8cm) and +(90:0.8cm) .. (a);
+\draw (a) -- (d)
+	.. controls +(-90:0.8cm) and +(-90:0.8cm) .. (a);
+%% two strands coming out front with twist
+%\draw (b) -- +(-30:2cm); %\draw (c) -- +(-30:2cm);
+\draw[thin_overline={1}] (c)
+	.. controls +(-30:0.5cm) and +(150:0.5cm) .. (0.9,-0.8);
+\draw[thin_overline={1}] (b)
+	.. controls +(-30:0.5cm) and +(150:0.5cm) .. (1.5,-0.6);
+\end{tikzpicture}
+
+\comment{
+
 \section{Introduction}
@@
 We label the edges of $f$ by $e_{i,0}$, $e_{i,\pi}$, or $e_i$,
-depending on whether the $\theta^*$ of that edges
+depending on whether the $\theta^*$ of that edge
 is $0$, $\pi$, or $\pi/2$ respectively.
@@
 So assume that $\bar{f}$ does have such a vertex,
-and suppose it is left-augmented
+and suppose it is right-augmented
 (the other case is treated similarly).
-Then for all left-augmented vertices $v_i$ of $\bar{f}$,
+Then for all right-augmented vertices $v_i$ of $\bar{f}$,
 $f$ would meet the short,long edges $e_{i,0},e_{i,\pi}$,
-while for all right-augmented vertices,
+while for all left-augmented vertices,
 $f$ would meet the diagonal edges.
 In particular,
-the edges $e_{i,0}, e_{i,\pi}$ always appear in counter-clockwise order),
+the edges $e_{i,0}, e_{i,\pi}$ always appear in counter-clockwise order.
 
 Suppose, after cyclically reindexing, $v_1,\ldots,v_k$
-is a maximally contiguous subsequence of left-augmented vertices
+is a maximally contiguous subsequence of right-augmented vertices
 of $D'$ around $\bar{f}$;
@@
 \begin{itemize}
-\item \textbf{Case $k=n$:} (i.e. every vertex of $\bar{f}$ is left-augmented.)
+\item \textbf{Case $k=n$:} (i.e. every vertex of $\bar{f}$ is right-augmented.)
 In this case, we do nothing.
@@
 
+}
+
 \end{document}

### 2021-09-01 main.tex
more figures
putting the figures back in context
diagram for bow-tie-modifications
diagram for crossing edges

@@
 
+%% colors
+\definecolor{light-gray}{gray}{0.9}
+\definecolor{med-gray}{gray}{0.6}
+
 %%%end tikz stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%% \comment{
+
 \begin{abstract}
@@
 \end{abstract}
-
-\begin{tikzpicture}
-\node[emptynode] (a) at (-0.9,-0.3) {};
-\node[dotnode] (b) at (-0.3,-0.1) {};
-\node[dotnode] (c) at (0.3,0.1) {};
-\node[emptynode] (d) at (0.9,0.3) {};
-%% two strands going out back
-\draw (b) -- +(150:1cm);
-\draw (c) -- +(150:1cm);
-%% the ellipse; draw top arc, then fill, then bottom arc
-\draw[thin_overline={1}] (a) -- (b) -- (c) -- (d)
-	.. controls +(90:0.8cm) and +(90:0.8cm) .. (a);
-\draw[fill, opacity=0.2] (a) -- (d)
-	.. controls +(90:0.8cm) and +(90:0.8cm) .. (a);
-\draw (a) -- (d)
-	.. controls +(-90:0.8cm) and +(-90:0.8cm) .. (a);
-%% two strands coming out front with twist
-%\draw (b) -- +(-30:2cm); %\draw (c) -- +(-30:2cm);
-\draw[thin_overline={1}] (c)
-	.. controls +(-30:0.5cm) and +(150:0.5cm) .. (0.9,-0.8);
-\draw[thin_overline={1}] (b)
-	.. controls +(-30:0.5cm) and +(150:0.5cm) .. (1.5,-0.6);
-\end{tikzpicture}
-
-\comment{
 
@@
 meeting at the crossing.
+We say that a twist region consisting of only one vertex
+is \emph{trivial}.
 %%\footnote{There is an ambiguity of ``maximality'' in this definition:
@@
 as in Figure \ref{TODO} (a) (resp. (b)).
-We call the TODO long edges, the TODO short edges,
-and TODO diagonal edges.
+We call the TODO \emph{long} edges, the TODO \emph{short} edges,
+and TODO \emph{diagonal} edges,
+and we call the new triangular faces the \emph{bow-tie faces}.
 TODO in figure caption, left bow-tie modification so-called because
@@
 also note that left/right conincide with Figure \ref{f:right_left_aug}
+
+\begin{figure}[ht]
+\input{bow-tie-modification.tikz}
+\caption{Bow-tie modifications}
+\label{f:bow-tie-modification}
+\end{figure}
+
 \label{d:diagram-bowtie}
@@
 \end{define}
-
-\begin{figure}
-\includegraphics[width=5cm]{more_pictures/right_left_aug.png}
-\caption{R: right augmentation, L: left augmentation}
-\label{f:right_left_aug}
-\end{figure}
 
@@
 denoted by $\Gamma_B(L)$.
-\hfill $\triangle$
+%\hfill $\triangle$
 \end{definition}
+
+\begin{figure}[ht]
+\input{torihedra-graphs.tikz}
+\caption{Constructing the top and bottom bow-tie graphs,
+using bow-tie modifications}
+\label{f:tori-decomp-graph}
+\end{figure}
 
@@
 together with line segments corresponding to crossing circles.
-(We demand that $D(K)$ be alternating and twist-reduced.)
+%(We demand that $D(K)$ be alternating and twist-reduced.)
 As discussed before, we may remove full twists (i.e. pairs of bigons)
@@
 connecting the top and bottom strands at the crossing
-(see Figure \ref{fig:crossingArc} (a)).
+(see \figref{f:crossing-edges}).
+%(see Figure \ref{fig:crossingArc} (a)).
 %so that for each crossing edge,
@@
 \begin{figure} 
-\centering 
-\begin{tabular}{cc}
-\includegraphics[width=4cm]{crossingArc.png}
-& \includegraphics[width=5cm]{crossingPush.png}
-\\
-(a)
-& (b)
-\end{tabular}
-\caption{(a) The black strands are
-part of the link and the red strand is the crossing edge.
-(b) The blue and
-red edges represent the split crossing edges and the shaded half disk is bounded
-by the crossing circle} 
-\label{fig:crossingArc} 
+\input{fig-crossing-edges.tikz}
+\label{f:crossing-edges}
+\caption{Splitting and flattening crossing edges.}
+%\centering 
+%\begin{tabular}{cc}
+%\includegraphics[width=4cm]{crossingArc.png}
+%& \includegraphics[width=5cm]{crossingPush.png}
+%\\
+%(a)
+%& (b)
+%\end{tabular}
+%\caption{(a) The black strands are
+%part of the link and the red strand is the crossing edge.
+%(b) The blue and
+%red edges represent the split crossing edges and the shaded half disk is bounded
+%by the crossing circle} 
+%\label{fig:crossingArc} 
 \end{figure}
@@
 splitting the crossing edge into two
-identical edges and spreading them apart
-as in Figure \ref{fig:crossingArc} (b).
+identical edges and spreading them apart as in
+\figref{f:crossing-edges}.
+%Figure \ref{fig:crossingArc}.
+% (b).
 %We push the link
@@
 
+\begin{figure}[ht]
+\input{cut-slice-flatten.tikz}
+\caption{Removing half-twists from augmented twist-regions}
+\label{f:cut-slice-flatten}
+\end{figure}
+
 \begin{figure}
@@
 \end{figure}
+
+\begin{remark}
+We note that our main \thmref{t:auglink_hyp}
+requires that all non-trivial twist regions be augmented,
+but \prpref{p:tori_decomp} does not require it.
+\label{r:unnecessary-augment-bigon}
+\end{remark}
 
@@
 angle-splitting of $(\Gamma,f^*)$
-if and only if the following
-``cocycle condition'' is satisfied:
+if and only if the following is satisfied:
 
@@
 (which easily follows from $K$ being weakly prime),
-it is not hard to see that the ``cocycle condition''
+it is not hard to see that the condition on cocycles
 of \thmref{t:bs-thm4} is satisfied by this assignment.
@@
 
-It is straightforward to check that
-upon gluing the top and bottom torihedra,
+We check that upon gluing the top and bottom torihedra,
 the sum of interior dihedral angles $\theta^*$
-around each edge is $2\pi$;
+around each edge is $2\pi$:
 crossing edges have $\theta^* = \pi/2$,
@@
 degenerate base-angled pyramids
-(recall that that means that some of the
-interior dihedral angles $\theta^*$ are 0),
-but we need the pyramids to be non-degenerate,
-so we need to modify the graph on the torihedra
-and the angle assignments to make all $\theta^*$ nonzero.
+(recall that that means some of the
+interior dihedral angles $\theta^*$ are 0);
+since we need the pyramids to be non-degenerate,
+we modify the graph on the torihedra
+and the angle assignments to make all $\theta^*$ nonzero
+as follows.
 
@@
 \begin{figure}
-\includegraphics[width=5cm]{more_pictures/one_edge.png}
-%\includegraphics[width=5cm]{more_pictures/two_edge.png}
-\includegraphics[width=5cm]{more_pictures/two_edge_many.png}
-\caption{TODO change this. Red edge indicates an added edge to $\Gamma_T(L)$;
-the +/- labels indicate whether to
-increase/decrease $\theta^*$ and $\vphi$.}
+\input{fig-add-edges.tikz}
+\caption{Adding edges to non-bow-tie faces;
+the $+/-$ labels are short for $+1/-1$.}
+%edge indicates an added edge to $\Gamma_T(L)$;
+%indicate whether to
+%increase/decrease $\vphi$ (and $\theta^*$)
 \label{f:adding_edges}
@@
 Let $\theta_e'^* = \vphi_{\vec{e}}' + \vphi_{\cev{e}}'$.
-It is easy to check that the sum of $\theta'*$
+It is easy to check that the sum of $\theta'^*$
 around each vertex is the same as for $\theta^*$,
 so it defines an angled torihedron $(\sT_T',\theta'^*)$.
-It is also easy to check that for each face of $\Gamma_T'$,
-the $+/-$ labels cancel out,
-so $\vphi'$ is an angle-splitting of it.
+For each face of $\Gamma_T'$, the $+/-$ labels
+on the inner side of boundary edges cancel out:
+for bow-tie faces, the short edge gets a $+1$ and the long edge
+gets $-1$, while for non-bow-tie faces,
+it is clear from \figref{f:adding_edges}.
+Hence, $\vphi'$ is an angle-splitting of $(\sT_T',\theta'^*)$.
 Furthermore, all shorts edges
@@
 
-It is easy to see that, under the gluing of
+By construction, under the gluing of
 $\sT_T(L)$ to $\sT_B(L)$,
 the new edges added to $\Gamma_T(L)$
-are glued to the new edges added to $\Gamma_B(L)$.
+are glued to the new edges added to $\Gamma_B(L)$,
+since they are added by the same procedure.
 As noted before, upon gluing $\sT_T(L)$ to $\sT_B(L)$
@@
 (they're label $\pi$ on each torihedron).
-It is also eashy to check that the $+/-$ labels get canceled out.
+Again by construction,
+the $+/-$ labels coming from the top and bottom diagrams get canceled out.
 Thus, upon gluing $\sT_T'$ to $\sT_B'$,
@@
 
-}
+%%% comment }
 
@@
 %\label{fig:crossingArc} 
+%\label{f:crossing-edges}.
 

### 2021-09-01 main.tex
added more nice diagrams

@@
 \begin{figure}[ht]
-\input{bow-tie-modification.tikz}
+\input{fig-bow-tie-modification.tikz}
 \caption{Bow-tie modifications}
@@
 \begin{figure}[ht]
-\input{torihedra-graphs.tikz}
+\input{fig-torihedra-graphs.tikz}
 \caption{Constructing the top and bottom bow-tie graphs,
@@
 
-Next we construct the graph that will define the ``top'' torihedron.
+Next we construct the graph that will define the torihedra.
 We view the link from the point at infinity from the top end
@@
 %the crossing circle.
-Now for each crossing circle $c$, consider a spanning disk $B_c$;
-$B_c$ intersects the projection plane $\torus \times \{0\}$
-along the red segments in Figure \ref{fig:falGluings},
-which consists of three edges.
-We then cut $\torus \times I$ along $\torus \times \{0\}$ and
-focus on the top half, $\torus \times [0,1)$.
-(We will follow the same method on the
-bottom half to obtain the second identical torihedron.)
-The spanning disks we placed for each crossing circle are now cut in half
-along the red segment.
-Each half of the disk is now bounded by the
-projection plane and the semi-circle arc of the crossing circle.
-We push down on the crossing circle and split the half-disk into
-two identical half-disks.
-We then push the arc of each crossing circle to infinity,
-collapsing them to ideal vertices.
-We obtain two triangular faces which represent the half-disk which look like a
-bow-tie as in Figure \ref{fig:falGluings} (a).
-See Figures \ref{fig:step_one} to \ref{fig:top-bottom}
-for an example.
+Now for each crossing circle $c$, consider a spanning
+(twice-punctured) disk $B_c$.
+The following operations are depicted in \figref{f:cut-slice-flatten}.
+$B_c$ intersects the projection plane $\torus \times \{0\}$,
+cutting $B_c$ into two pieces $B_c^+,B_c^-$,
+each being an ideal triangle.
+We then slice along the disk $B_c$, turning it into two copies,
+$B_c^{(1)},B_c^{(2)}$ (in no particular order);
+each copy $B_c^{(j)}$ is also cut horizontally into two pieces,
+$B_c^{(j),+},B_c^{(j),-}$.
+We untwist all crossings in the twist region
+which $c$ encircles,
+rotating $B_c^{(j)}$ by $180^\circ$ for each crossing.
+Then we flatten the disks;
+the crossing circle is shrunk to a point,
+as it is at infinity.
 
 \begin{figure}[ht]
-\input{cut-slice-flatten.tikz}
-\caption{Removing half-twists from augmented twist-regions}
+\input{fig-cut-slice-flatten.tikz}
+\caption{Cut-slice-flatten}
 \label{f:cut-slice-flatten}
@@
 
-\begin{figure}
-\centering
-\begin{tabular}{cc}
-\includegraphics [width=8cm]{falGluing1.png}&
-\includegraphics [width=7cm]{falGluing2.png}\\
-(a)&(b)
-\end{tabular}
-\caption{(a) Gluing of bow-ties without half-twists
-(b) Gluing with half-twists}
-\label{fig:falGluings}
-\end{figure}
+%%We cut $\torus \times I$ along $\torus \times \{0\}$ and
+%%focus on the top half, $\torus \times [0,1)$.
+%%(We will follow the same method on the
+%%bottom half to obtain the second identical torihedron.)
+%%The spanning disks we placed for each crossing circle are now
+%%cut in half along the red segment.
+%%Each half of the disk is now bounded by the
+%%projection plane and the semi-circle arc of the crossing circle.
+%%We push down on the crossing circle and split the half-disk into
+%%two identical half-disks.
+%%We then push the arc of each crossing circle to infinity,
+%%collapsing them to ideal vertices.
+%%We obtain two triangular faces which represent the half-disk which look like a
+%%bow-tie as in Figure \ref{fig:falGluings} (a).
+%%See Figures \ref{fig:step_one} to \ref{fig:top-bottom}
+%%for an example.
+%%
+%%
+%%\begin{figure}
+%%\centering
+%%\begin{tabular}{cc}
+%%\includegraphics [width=8cm]{falGluing1.png}&
+%%\includegraphics [width=7cm]{falGluing2.png}\\
+%%(a)&(b)
+%%\end{tabular}
+%%\caption{(a) Gluing of bow-ties without half-twists
+%%(b) Gluing with half-twists}
+%%\label{fig:falGluings}
+%%\end{figure}
 
@@
 $\check{\Gamma}$, obtaining one or more pieces;
-Then for any piece that is a disc,
+Then for any piece that is a disk,
 the sum of $f$ over the edges in the boundary

### 2021-09-02 main.tex
finish fixing prop on tori decomp

@@
 midarrow_rev/.default=0.5,
+%%%%% Mid-path arrow but thin
+midarrow_thin/.style={postaction={decorate},
+                 decoration={
+                    markings,% switch on markings
+                    mark=at position #1 with {\arrow{Classical TikZ
+											Rightarrow[length=2pt]}},
+                 }},
+midarrow_thin/.default=0.5,
 %%%%% for the flowchart; need align=center to allow multiline in node
@@
 A \emph{left (resp. right) bow-tie modification to $v,e,e'$}
-is the process of removing $v,e,e'$ and adding in a ``bow-tie''
-as in Figure \ref{TODO} (a) (resp. (b)).
-We call the TODO \emph{long} edges, the TODO \emph{short} edges,
-and TODO \emph{diagonal} edges,
-and we call the new triangular faces the \emph{bow-tie faces}.
-TODO in figure caption, left bow-tie modification so-called because
-the triangular face appears to the left of the long edges;
-also note that left/right conincide with Figure \ref{f:right_left_aug}
+is the process of removing $v,e,e'$ and adding in
+a pair of triangular faces, which we refer to as a ``bow-tie''
+(see \figref{f:bow-tie-modification}).
+%as in Figure \ref{TODO} (a) (resp. (b)).
+The edges of the bow-tie are of three types;
+\emph{diagonal} edges, which do not touch $v$,
+\emph{long} edges, which are ``parallel'' to the original edges $e,e'$,
+and \emph{short} edges, which connect $v$ to the two new vertices.
+We call the new triangular faces the \emph{bow-tie faces}.
 
@@
 (locally) oriented so that they cross the augmentation disk in the same
-direction, the crossing is a positive right-handed half-twist.
+direction, the crossing is a right-handed half-twist.
 We say a twist is \emph{left-augmented} if it is not right-augmented.
-See Figure \ref{f:right_left_aug}.
+(See \figref{f:bow-tie-modification}).
 \end{define}
@@
 %\hfill $\triangle$
+
+Note that the non-bow-tie faces of $\Gamma_T(L)$ and $\Gamma_B(L)$
+are naturally identified with the faces of $D'$
+(as the bow-tie modification procedure does not remove faces).
 \end{definition}
@@
 \end{figure}
-
-Note that the non-bow-tie faces of $\Gamma_T(L)$ and $\Gamma_B(L)$
-are naturally identified with the faces of $D'$
-(as the bow-tie modification procedure does not remove faces).
 
@@
 \begin{proof}
-%As mentioned before, we will be combining
-%Menasco's method using crossing edges at each crossing
-%and Lackenby's ``cut-slice-flatten'' method
-%on augmentation sites.
-
-%We give a description of the topological operations
-%that give the torihedral decomposition;
-%this will justify the 
-%more concise description purely in terms of link diagrams
-%which we present in Remark \ref{r:tori-decomp-graph}.
-
-We will begin by assuming that $L$ has no half twists.
+As mentioned before, we will be combining
+Menasco's method using crossing edges at each crossing
+and Lackenby's ``cut-slice-flatten'' method
+on augmentation sites.
+
+%We will begin by assuming that $L$ has no half twists.
 Let $L = K \cup C$, with $C$ being the collection of crossing circles.
-%Arrange the link diagram of $L$ in the following way:
 Arrange $L$ in the following way:
@@
 %(We demand that $D(K)$ be alternating and twist-reduced.)
-As discussed before, we may remove full twists (i.e. pairs of bigons)
-from the twist regions of $K$ that are augmented in $L$,
-and since $L$ is assumed to have no half twists,
-the two edges of $D(K)$ that go through a crossing circle
-do not meet (see Figure \ref{fig:Augmentations} C).
-From now on, we will take $K$ to be this modified link
-(with full twists removed).
+%As discussed before, we may remove full twists (i.e. pairs of bigons)
+%from the twist regions of $K$ that are augmented in $L$,
+%and since $L$ is assumed to have no half twists,
+%the two edges of $D(K)$ that go through a crossing circle
+%do not meet (see \figref{fig:Augmentations} C).
+%From now on, we will take $K$ to be this modified link
+%(with full twists removed).
 
@@
 (see \figref{f:crossing-edges}).
+We also three horizontal edges for each crossing circle
+(see \figref{f:cut-slice-flatten}, leftmost diagram).
 %(see Figure \ref{fig:crossingArc} (a)).
@@
 
-Next we construct the graph that will define the torihedra.
-We view the link from the point at infinity from the top end
+%Next we construct the graph that will define the torihedra.
+View the link from the point at infinity from the top end
 ($\torus \times \{1\}$) of the thickened torus.
@@
 \figref{f:crossing-edges}.
+Note that after this operation, the link (which is no longer a link)
+for both top and bottom look the same,
+but a crossing edge associated to a crossing
+is pushed in different directions;
+this contributes to a ``$2\pi/n$'' twist
+when gluing back the faces of the top and bottom torihedra.
 %Figure \ref{fig:crossingArc}.
@@
 \input{fig-cut-slice-flatten.tikz}
-\caption{Cut-slice-flatten}
+\caption{Cut-slice-flatten;
+the even and odd refer to the number of crossings
+in that twist region
+(we only draw one crossing in the first diagram);
+the top and bottom graphs are glued back,
+gray face to gray face, white face to white face;
+note that the graph does not depend on the
+parity of the number of crossings, but the gluing is different}
 \label{f:cut-slice-flatten}
 \end{figure}
+
+Finally, we shrink all remaining segments of the link $L$
+to ideal vertices.
+It is easy to see that the top and bottom graphs
+are exactly $\Gamma_T(L)$ and $\Gamma_B(L)$ from
+\defref{d:tori-decomp-graph}.
+To recover the link complement,
+we glue bow-tie to bow-tie as described in \figref{f:cut-slice-flatten},
+and glue each non-bow-tie face to its natural counterpart
+(see \defref{d:tori-decomp-graph}),
+with a ``$2\pi/n$'' twist as discussed before.
 
@@
 
-The crossing edges and edges from spanning disks of crossing circles
-form the graph of the top ideal torihedron.
-It is not hard to see that this graph is $\Gamma_T(L)$.
-We repeat similar steps for the bottom half of $\torus \times I$,
-$\torus \times (-1,0]$
-(note we should be pushing the bottom strands up towards the top strand).
-It is also easy to see that this graph is $\Gamma_B(L)$
-(from the same perspective, not from the perspective of the bottom end
-$\torus \times \{-1\}$).
-Thus we get two ideal torihedra.
-%The graph of each will come from
-%crossing edges and edges from spanning disks of crossing circles.
-
-We obtain the complement of $L$ by gluing the two torihedra with the gluing
-information given by identifying crossing edges and triangles of the bow-tie.
-As observed before, the non-bow-tie faces of $\Gamma_T(L),\Gamma_B(L)$
-naturally pair up, and we glue them accordingly
-(there is a ``$2\pi/n$'' twist when gluing these faces,
-where $n$ is the number of sides of each face as in Figure
-\ref{fig:top-bottom} clockwise or counterclockwise).
-The bow-tie triangular faces are glued up according to
-\figref{fig:falGluings} (a).
-%We glue the faces of the torihedra which do not correspond to a bow-tie with a
-%$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
-%\ref{fig:top-bottom} clockwise or counterclockwise.
-
-Now, if $L$ has half-twists,
-we apply the constructions above to $L'$,
-which is the link obtained from $L$ by removing all half-twists
-(replacing them with parallel strands).
-The complement of $L$ is again obtained by
-gluing the torihedra together all the same,
-except that at the bow-ties coming from twist regions with a half-twist,
-they are glued as in Figure \ref{fig:falGluings} (b).
-%we decompose the complement of the link the same way
-%(as if there are no half twists)
-%but we identify the two bow-ties as in Figure \ref{fig:falGluings} (b).
-%Finally,
-
-%%For future reference, we will denote the graph for the top and bottom
-%%torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
-%%where both graphs are viewed from the cone point of the top torihedron
-%%$\torus \times \{1\}$.
-%%Note that if $L = K$ is the non-augmented link,
-%%$\Gamma_T(L)$ is simply the link projection of $K$,
-%%and in fact $\Gamma_T(K) = \Gamma_B(K)$.
+%%The crossing edges and edges from spanning disks of crossing circles
+%%form the graph of the top ideal torihedron.
+%%It is not hard to see that this graph is $\Gamma_T(L)$.
+%%We repeat similar steps for the bottom half of $\torus \times I$,
+%%$\torus \times (-1,0]$
+%%(note we should be pushing the bottom strands up towards the top strand).
+%%It is also easy to see that this graph is $\Gamma_B(L)$
+%%(from the same perspective, not from the perspective of the bottom end
+%%$\torus \times \{-1\}$).
+%%Thus we get two ideal torihedra.
+%%%The graph of each will come from
+%%%crossing edges and edges from spanning disks of crossing circles.
+%%
+%%
+%%We obtain the complement of $L$ by gluing the two torihedra with the gluing
+%%information given by identifying crossing edges and triangles of the bow-tie.
+%%As observed before, the non-bow-tie faces of $\Gamma_T(L),\Gamma_B(L)$
+%%naturally pair up, and we glue them accordingly
+%%(there is a ``$2\pi/n$'' twist when gluing these faces,
+%%where $n$ is the number of sides of each face as in Figure
+%%\ref{fig:top-bottom} clockwise or counterclockwise).
+%%The bow-tie triangular faces are glued up according to
+%%\figref{fig:falGluings} (a).
+%%%We glue the faces of the torihedra which do not correspond to a bow-tie with a
+%%%$2\pi/n$ twist where $n$ is the number of sides of each face as in Figure
+%%%\ref{fig:top-bottom} clockwise or counterclockwise.
+%%
+%%
+%%Now, if $L$ has half-twists,
+%%we apply the constructions above to $L'$,
+%%which is the link obtained from $L$ by removing all half-twists
+%%(replacing them with parallel strands).
+%%The complement of $L$ is again obtained by
+%%gluing the torihedra together all the same,
+%%except that at the bow-ties coming from twist regions with a half-twist,
+%%they are glued as in Figure \ref{fig:falGluings} (b).
+%%%we decompose the complement of the link the same way
+%%%(as if there are no half twists)
+%%%but we identify the two bow-ties as in Figure \ref{fig:falGluings} (b).
+%%%Finally,
+%%
+%%
+%%%%For future reference, we will denote the graph for the top and bottom
+%%%%torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively,
+%%%%where both graphs are viewed from the cone point of the top torihedron
+%%%%$\torus \times \{1\}$.
+%%%%Note that if $L = K$ is the non-augmented link,
+%%%%$\Gamma_T(L)$ is simply the link projection of $K$,
+%%%%and in fact $\Gamma_T(K) = \Gamma_B(K)$.
 \end{proof}

### 2021-09-04 main.tex
flipped the arrows on that figure

@@
 
-TODO Notation section: $I = (-1,1)$.
+We denote $I = (-1,1)$.
 
@@
 the thickened torus in \cite{kwon2020fully}.
-The idea is to combine methods of Menasco
-\cite{Menasco} and the use of crossing edges
-between (TODO for?) each crossing of our link
+The idea is to combine methods of Menasco \cite{Menasco}
+and the use of crossing edges at each crossing of our link
 and Lackenby's ``cut-slice-flatten" method \cite{lackenby}
-on the augmentation
-sites.
+on the augmentation sites.
 
@@
 \caption{Left: The crossing arc is the edge in red.
-Middle: Picture of splitting the crossing edge.
-Right: The link components are pushed off to infinity.}
+Middle: Picture of splitting the crossing edge
+and bow-ties.
+Right: The link components are pushed off to infinity
+(diagrammatically, they are shrunk to points).}
 	\label{fig:step_three}
@@
 \label{fig:top-bottom}
+\end{figure}
+
+\begin{figure}[h] 
+\centering 
+\includegraphics[height=3cm]{top-bottom-flippedarrows.png} 
+	\caption{Left: The top torihedron.
+	Right: The bottom torihdron with rotation indicating face gluing;
+	TODO should it be like that?} 
+\label{fig:top-bottom-flippedarrows}
 \end{figure}
@@
 of this assignment.
-TODO perhaps these figures need some tidying up
 
@@
 \caption{Assignments of $\theta^*$ to edges of a bow-tie
-	corresponding to an augmentation site;
-	the edges labeled $\pi$ are the long edges,
-	the edges labeled 0 are the short edges,
-	the edges labeled $\pi/2$ are the diagonal edges}
+	corresponding to a left augmentation site;
+	the long edges are assigned $\pi$,
+	the short edges are assigned 0,
+	and the diagonal edges are assigned $\pi/2$
+	(same for a right augmentation).
+	}
 \label{f:bowtie_angles}
@@
 \end{tabular}
-\caption{(a) Angle splitting before augmentation (b) Angle splitting for bowtie corresponding to augmentation}
+\caption{(a) Angle splitting before augmentation 
+(b) Angle splitting for bowtie corresponding to
+left bow-tie modification/augmentation;
+similar for right bow-tie modification/augmentation}
 \label{f:bowtie_angles2}

### 2021-09-04 main.tex
made some final changes

@@
 The Figures \ref{fig:step_one} to \ref{fig:top-bottom}
-depict an example which decomposes the link (C) of Figure
-\ref{fig:Augmentations}.
+depict an example which decomposes the link (C) of
+\figref{fig:Augmentations}.
 
@@
 \includegraphics[height=3cm]{fig-4.png}
-	\caption{Each crossing circle bounds a twice-punctured disk}
+	\caption{Each crossing circle bounds a twice-punctured disk;
+	the rightmost figure shows half of the disk.}
 	\label{fig:step_one}
@@
 	\caption{We split the disk and collapse the arc of each
- crossing circle to ideal vertices}
+ crossing circle to ideal vertices;
+ the leftmost figure shows the view from the top
+ of a half disk being spread apart.}
 	\label{fig:step_two}
@@
 \centering 
-\includegraphics[height=3cm]{top-bottom.png} 
-	\caption{Left: The top torihedron.
-	Right: The bottom torihdron with rotation indicating face gluing;
-	TODO shouldn't it be rotating other way?} 
-\label{fig:top-bottom}
-\end{figure}
-
-\begin{figure}[h] 
-\centering 
 \includegraphics[height=3cm]{top-bottom-flippedarrows.png} 
 	\caption{Left: The top torihedron.
-	Right: The bottom torihdron with rotation indicating face gluing;
-	TODO should it be like that?} 
-\label{fig:top-bottom-flippedarrows}
+	Right: The bottom torihdron with rotation indicating face gluing}
+\label{fig:top-bottom}
 \end{figure}
@@
 
+\begin{samepage}
 \begin{define}
@@
 \end{define}
+\end{samepage}
 
@@
 \begin{theorem}\cite[Theorem 1.1]{FG-angles}
+\label{t:hyperbolic-angle-str}
 Let $M$ be a 3-manifold with a triangulation that admits an angle structure.
@@
 (b) Angle splitting for bowtie corresponding to
-left bow-tie modification/augmentation;
-similar for right bow-tie modification/augmentation}
+left bow-tie modification/augmentation.
+For right bow-tie modification/augmentation,
+just flip both diagrams (a) and (b) horizontally.}
 \label{f:bowtie_angles2}
@@
 
-\textbf{Subcase: $k=1$:}
+\begin{itemize}
+\item \textbf{Subcase: $k=1$:}
 We add an edge that goes across $e_{1,0},e_{1,\pi},e_2$
@@
 
-\textbf{Subcase: $k \geq 2$:}
+\item \textbf{Subcase: $k \geq 2$:}
 We add an edge across $e_{1,0},e_{1,\pi}$
@@
 %(again these two edges do not form a bigon).
-
-\textbf{Case: There are multiple such maximal contiguous subsequences.}
+\end{itemize}
+
+\item \textbf{Case: There are multiple such maximal contiguous subsequences.}
 We just add edges as in the previous case for each contiguous subsequence,
@@
 \caption{Adding edges to non-bow-tie faces;
-the $+/-$ labels are short for $+1/-1$.}
+the $+,-$ labels are short for $+1,-1$ respectively.}
 %edge indicates an added edge to $\Gamma_T(L)$;
@@
 using the angle-splitting for $\Gamma_T(L)$ for old edges,
-and for a new edge $e$ that cuts through some face $f$ of $\Gamma_T(L)$,
+and for a new edge $e$ (as in \figref{f:adding_edges})
+that cuts through some face $f$ of $\Gamma_T(L)$,
 we assign $\vphi_{\vec{e}} = \sum \vphi_{\vec{e'}}$,
@@
 that on the other side of $\vec{e}$.
-It is easy to see that the new assignments are all non-zero
-(follows from non-degeneracy of the angle-splitting on $D'$).
+By non-degeneracy of the angle-splitting on $D'$,
+these assignments to the new edges are all non-zero
 
@@
 with an angle structure.
-Thus, $L$ is hyperbolic.
+Thus, by \thmref{t:hyperbolic-angle-str},
+$L$ is hyperbolic.
 \end{proof}

### 2021-09-04 ms.tex
final version submitted to arxiv

--- 2021-09-04 main.tex
@@
 	\caption{Left: The top torihedron.
-	Right: The bottom torihdron with rotation indicating face gluing}
+	Right: The bottom torihedron with rotation indicating face gluing}
 \label{fig:top-bottom}
@@
 it is not hard to see that the converse is true:
-simply consider a circumsribed polygon such that the side $e_i$
+simply consider a circumscribed polygon such that the side $e_i$
 subtends an angle of $2\alpha_i$ at the center,
@@
 \begin{figure}
-\includegraphics[height=5cm]{more_pictures/angle_split.png}
+\includegraphics[height=5cm]{angle_split.png}
 \caption{Angle-splitting on a polygonal face of the graph}
@@
 and suppose $e_i$ is assigned dihedral angle $\alpha_i$.
-Let $e'$ be a new edge addeed to the base face of $P_n$
+Let $e'$ be a new edge added to the base face of $P_n$
 such that it separates the base face into a triangle and
@@
 \begin{figure}
-\includegraphics[width=7cm]{more_pictures/horizontal_bowtie.png}
+\includegraphics[width=7cm]{horizontal_bowtie.png}
 \caption{Assignments of $\theta^*$ to edges of a bow-tie
@@
 Note that $f$ may meet a vertex twice,
-but we label each occurence with its own index.
+but we label each occurrence with its own index.
 We label the edges of $f$ by $e_{i,0}$, $e_{i,\pi}$, or $e_i$,
@@
 should have switched signs.
-We also get a nondegerate angle-splitting $\vphi'$
+We also get a non-degenerate angle-splitting $\vphi'$
 of an angled torihedron $(\sT_B',\theta'^*)$.

### 2022-04-06 main.tex
address main concerns of reviewer, left with errata to fix

@@
 and consecutive bigons meet only at a vertex (not an edge).
+
+TODO terrible defn.
+
 We say that the \emph{direction} of a twist region
@@
 There is a decomposition of the complement,
-$(\torus \times I) - L$, into two ideal torihedra;
-the graphs of the torihedra are $\Gamma_T(L)$ and $\Gamma_B(L)$.
+$(\torus \times I) - L$, into two ideal torihedra.
+
+Moreover, the graphs of the torihedra are
+the top and bottom bow-tie graphs from
+\defref{d:tori-decomp-graph},
+$\Gamma_T(L)$ and $\Gamma_B(L)$,
+respectively.
+
+We call this the
+\emph{torihedral decomposition of
+the link complement of $L$ in the thickened torus}.
 \end{prop}
@@
 
+TODO rephrase to more careful.
+
 For a hyperbolic link $K$ in $\torus \times I$, we show
@@
 and $L$ is obtained by augmenting $K$
-such that every twist region with at least one bigon is augmented,
+such that for every twist region with at least one bigon,
+either the twist region is augmented,
+or each vertex of the twist region is augmented
+in the other direction,
+or both.
 %(and possibly other crossings),
@@
 \end{theorem}
+
+% awkward attempts to address necessity of bigon condition
+% in main theorem
+%\begin{remark}
+%In the torihedral decomposition of $L$
+%(as in \prpref{p:tori_decomp}),
+%a string of bigons would
+%produce bow-tie graphs whose total number 
+%of edges identified is greater than 4 
+%
+%
+%We put restrictions on bigons for the following reason.
+%Recall from \prpref{p:tori_decomp} that
+%a link complement is obtained from identifying
+%certain collections of edges from the top and bottom torihedra.
+%When there are non-augmented bigons,
+%some of these collections would not be 
+%\end{remark}
 
@@
 (so that $\theta_e^* = \pi/2$ too).
+This assignment has the property that
+the sum of dihedral angles around each identified edge
+(in the complement of $K'$) is $2\pi$.
+This can be achieved because of the hypotheses on bigons
+in our theorem statement.
+
 Using the fact that $K'$ is weakly prime
@@
 
+\begin{remark}
+Note that for our definition of augmentation,
+we exclude the case where
+an unknotted circle component is added around
+two parallel strands that do not meet at a crossing.
+In particular, this implies that
+a non-weakly prime link cannot become weakly prime
+under augmentation.
+
+If we have an augmentation around two such parallel strands,
+we may consider the related link
+where those two strands have a full twist;
+the hyperbolicity is unaltered, and
+\thmref{t:auglink_hyp} would apply.
+\end{remark}
+
 \bibliographystyle{plain}

### 2022-04-16 main.tex
made better twist region defn

@@
 
-We point out that \cite{kwon2020fully}, the first author
+We point out that in \cite{kwon2020fully}, the first author
 proved that \emph{fully} augmented links in the thickened torus
@@
 Recall that a \emph{twist region}
-in a link diagram is a maximal sequence of vertices
+in a link diagram in the plane is a maximal sequence of vertices
 such that consecutive vertices are two vertices of a bigon face,
-and consecutive bigons meet only at a vertex (not an edge).
-
-TODO terrible defn.
-
-We say that the \emph{direction} of a twist region
-is the pair of faces (possibly the same face)
-that are across from the bigons at the end;
-if a twist region consists of only one vertex,
-a direction is a pair of opposite faces (again, possibly the same face)
-meeting at the crossing.
-We say that a twist region consisting of only one vertex
-is \emph{trivial}.
-%%\footnote{There is an ambiguity of ``maximality'' in this definition:
-%%for example, if a vertex of a link diagram meets exactly one bigon,
-%%it can be considered as part of a twist region of length 2
-%%(given by that bigon),
-%%or it can be considered as part of a twist region of length 1,
-%%as there are no bigons in the other ``direction''.
-%%It should be clear which ``direction'' a twist region is going
-%%when we deal with augmentations later.
-%%}
+and consecutive bigons meet at exactly one vertex.
+The \emph{length} of the twist region is the number of bigons.
+
+We say a single vertex $v$ is a \emph{trivial twist region}
+(or \emph{twist region of length 0})
+if, for some cyclical ordering $f_1,f_2,f_3,f_4$
+of the four faces adjacent to $v$,
+$f_1,f_3$ are not bigons.
+Note that if all four faces are not bigons,
+then we think of $v$ as being a trivial twist region in two ways,
+and in this sense, every vertex is part of exactly
+two twist regions.
+%
+%We say that the \emph{direction} of a twist region
+%is the pair of faces (possibly the same face)
+%that are across from the bigons at the end;
+%if a twist region consists of only one vertex,
+%a direction is a pair of opposite faces (again, possibly the same face)
+%meeting at the crossing.
+%We say that a twist region consisting of only one vertex
+%is \emph{trivial}.
 
@@
 $\mathcal{L}$. 
-
-A biperiodic link
-$\mathcal{L}$ is called \emph{twist-reduced} if for any simple closed curve on
+\end{define}
+
+\begin{define}
+A biperiodic link $\mathcal{L}$ is called \emph{twist-reduced}
+if for any simple closed curve on
 the plane that intersects the diagram of $\mathcal{L}$
-transversely in four points, with two
-points adjacent to one crossing and the other two points adjacent to another
-crossing, the simple closed curve bounds a subdiagram consisting of a (possibly
-empty) collection of bigons strung end to end between these crossings. We say
-the diagram of $L$ is \emph{twist-reduced}
-if it is the quotient of a twist-reduced biperiodic
-link diagram.
+transversely in four points,
+with two points adjacent to one crossing
+and the other two points adjacent to another crossing,
+the simple closed curve bounds a subdiagram consisting of
+a collection of bigons strung end to end between these crossings.
+We say the diagram of $L$ is \emph{twist-reduced}
+if it is the quotient of a twist-reduced biperiodic link diagram.
 \end{define}
-
-We note that when a link diagram is cellular
-(Definition \ref{d:cellular}),
-a twist region in the torus cannot be a cycle;
-otherwise, the face adjacent to the twist region would be an annulus.
 
@@
 we call the resulting link $L$ an \emph{augmented link obtained from $K$}.
-We say $L$ is \emph{fully} augmented if $L$ is obtained by augmenting
+We say $L$ is \emph{fully augmented} if $L$ is obtained by augmenting
 $K$ at \emph{every} crossing/twist site.
@@
 \end{definition}
+
+We note that when a link diagram is cellular,
+a twist region in the torus cannot be a cycle;
+otherwise, the face adjacent to the twist region would
+have non-trivial homology.
 
@@
 
-If the faces of $G(\sT)$ are disks,
-then $\sT$ can be decomposed into a union of pyramids,
-obtained by coning each face to the cone point of $\sT$.
+Since the faces of $G(\sT)$ are disks,
+$\sT$ can be decomposed into a union of pyramids,
+where each pyramid is obtained by coning a face of $G(\sT)$
+to the cone point of $\sT$.
 This also gives a decomposition of the corresponding ideal torihedron
@@
 Let $v$ be a vertex and $e,e'$ be distinct edges that meet $v$.
-A \emph{left (resp. right) bow-tie modification to $v,e,e'$}
+A \emph{bow-tie modification to $v,e,e'$}
 is the process of removing $v,e,e'$ and adding in
-a pair of triangular faces, which we refer to as a ``bow-tie''
-(see \figref{f:bow-tie-modification}).
-%as in Figure \ref{TODO} (a) (resp. (b)).
+a pair of triangular faces, which we refer to as
+\emph{bow-tie faces} or a \emph{bow-tie}
+(see Figure \ref{f:bow-tie-modification},
+\ref{f:bow-tie-modification-general}).
 The edges of the bow-tie are of three types;
@@
 \emph{long} edges, which are ``parallel'' to the original edges $e,e'$,
-and \emph{short} edges, which connect $v$ to the two new vertices.
-We call the new triangular faces the \emph{bow-tie faces}.
+and \emph{short} edges.
+%, which connect $v$ to the two new vertices.
+%We call the new triangular faces the \emph{bow-tie faces}.
+A bow-tie modification is a \emph{left} bow-tie modification
+if, traveling from $v$ out along $e$ and $e'$,
+the diagonal faces appear to the left of $e$ and $e'$,
+respectively;
+likewise for \emph{right} bow-tie modifications.
 
@@
 \input{fig-bow-tie-modification.tikz}
-\caption{Bow-tie modifications}
+\caption{Bow-tie modifications and its relation to torihedra}
 \label{f:bow-tie-modification}
@@
 
+\begin{figure}[ht]
+\input{fig-bow-tie-modification-general.tikz}
+\caption{Another example of (left) bow-tie modification}
+\label{f:bow-tie-modification-general}
+\end{figure}
+
 \label{d:diagram-bowtie}
@@
 \begin{define}
-We say a twist region is \emph{right-augmented} if, when both strands are
-(locally) oriented so that they cross the augmentation disk in the same
-direction, the crossing is a right-handed half-twist.
+We say a twist region is \emph{right-augmented} if,
+when both strands are (locally) oriented
+so that they cross the augmentation disk in the same direction,
+the crossing is a right-handed half-twist.
 We say a twist is \emph{left-augmented} if it is not right-augmented.
@@
 We define the \emph{top/bottom bow-tie graph of $L$} as follows.
+(See \figref{f:tori-decomp-graph} for illustrations.)
 
@@
 (see \figref{f:cut-slice-flatten}, leftmost diagram).
-%(see Figure \ref{fig:crossingArc} (a)).
-%so that for each crossing edge,
-%one end of the edge lies on a bottom strand while the other
-%end lies on a top strand as in Figure \ref{fig:crossingArc} (a).
 
@@
 \input{fig-crossing-edges.tikz}
+\caption{Splitting and flattening crossing edges.}
 \label{f:crossing-edges}
-\caption{Splitting and flattening crossing edges.}
-%\centering 
-%\begin{tabular}{cc}
-%\includegraphics[width=4cm]{crossingArc.png}
-%& \includegraphics[width=5cm]{crossingPush.png}
-%\\
-%(a)
-%& (b)
-%\end{tabular}
-%\caption{(a) The black strands are
-%part of the link and the red strand is the crossing edge.
-%(b) The blue and
-%red edges represent the split crossing edges and the shaded half disk is bounded
-%by the crossing circle} 
-%\label{fig:crossingArc} 
 \end{figure}
 
-%Next we construct the graph that will define the torihedra.
 View the link from the point at infinity from the top end
@@
 is pushed in different directions;
-this contributes to a ``$2\pi/n$'' twist
+this contributes to a ``$2\pi/n$ twist''
 when gluing back the faces of the top and bottom torihedra.
-%Figure \ref{fig:crossingArc}.
-% (b).
-%We push the link
-%components to infinity and stretch the crossing edge so that we have flattened
-%the link onto $\torus \times \{0\}$ except for the crossing circles,
-%which remains perpendicular to the projection plane.
-
-%Now place a disk on each crossing circle, so that the disk is bounded by
-%the crossing circle.
+
 Now for each crossing circle $c$, consider a spanning
@@
 in the other direction,
-or both.
+or both,
 %(and possibly other crossings),
@@
 we modify the graph on the torihedra
-and the angle assignments to make all $\theta^*$ nonzero
+and the angle assignments to make all $\theta^*$ non-zero
 as follows.
@@
 Then for all right-augmented vertices $v_i$ of $\bar{f}$,
-$f$ would meet the short,long edges $e_{i,0},e_{i,\pi}$,
+$f$ would meet the short, long edges $e_{i,0},e_{i,\pi}$,
 while for all left-augmented vertices,
@@
 By non-degeneracy of the angle-splitting on $D'$,
-these assignments to the new edges are all non-zero
+these assignments to the new edges are all non-zero.
 

### 2022-04-17 main.tex
finished remarks on extending use case of Theorem.

@@
 We say $L$ is \emph{fully augmented} if $L$ is obtained by augmenting
-$K$ at \emph{every} crossing/twist site.
+$K$ at \emph{every} crossing/twist region.
 \label{d:augmentation}
@@
 and $L$ is obtained by augmenting $K$
-such that for every twist region with at least one bigon,
-either the twist region is augmented,
-or each vertex of the twist region is augmented
-in the other direction,
-or both,
-%(and possibly other crossings),
+such that for every twist region with at least one bigon
+is augmented,
 then $L$ is hyperbolic.
@@
 
-% awkward attempts to address necessity of bigon condition
-% in main theorem
-%\begin{remark}
-%In the torihedral decomposition of $L$
-%(as in \prpref{p:tori_decomp}),
-%a string of bigons would
-%produce bow-tie graphs whose total number 
-%of edges identified is greater than 4 
-%
-%
-%We put restrictions on bigons for the following reason.
-%Recall from \prpref{p:tori_decomp} that
-%a link complement is obtained from identifying
-%certain collections of edges from the top and bottom torihedra.
-%When there are non-augmented bigons,
-%some of these collections would not be 
-%\end{remark}
-
 \begin{proof}
-%Let us first consider the case when $K$ did not have bigons.
 By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
@@
 For a vertex $v_i$ that corresponds to a twist region of $K$,
-if the direction of the twist region is towards $\bar{f}$,
+if the crossing circle ``faces'' $f$,
+%if the direction of the twist region is towards $\bar{f}$,
 then $f$ meets a diagonal edge of the bow-tie corresponding to $v_i$,
-and we label it $e_i$;
-if not, then $f$ meets a short and long edge of the corresponding bow-tie,
+and we label it $e_i$
+(for example if $f$ is the top left face
+in \figref{f:bowtie_angles2} (a));
+if not, then $f$ meets a short and long edge
+of the corresponding bow-tie,
 and we label them by $e_{i,0}$ and $e_{i,\pi}$,
-respectively.
+respectively
+(for example if $f$ is the top right face
+in \figref{f:bowtie_angles2} (b)).
 
@@
 (see \figref{f:adding_edges};
-ignore the + and - signs for now.):
+ignore the + and - signs for now):
 
@@
 where the sum is over all the edges $\vec{e'} \in \del f$
-that on the other side of $\vec{e}$.
+on the other side of $\vec{e}$.
 By non-degeneracy of the angle-splitting on $D'$,
@@
 Let $\vphi_{\vec{e}}' = \vphi_{\vec{e}} + x \cdot \veps$,
-where $x$ is the label on $\vec{e}$ (0 if unlabeled).
+where $x$ is the label
+(in \figref{f:adding_edges}) on $\vec{e}$
+(set $x=0$ if unlabeled).
 Let $\theta_e'^* = \vphi_{\vec{e}}' + \vphi_{\cev{e}}'$.
-It is easy to check that the sum of $\theta'^*$
-around each vertex is the same as for $\theta^*$,
-so it defines an angled torihedron $(\sT_T',\theta'^*)$.
+It is easy to check that the sum of labels
+% $\theta'^*$
+around each vertex is 0,
+hence $\theta'^*$
+%the same as for $\theta^*$,
+defines an angled torihedron $(\sT_T',\theta'^*)$.
 For each face of $\Gamma_T'$, the $+/-$ labels
@@
 This clearly remains true after adding the new edges
-(they're label $\pi$ on each torihedron).
+(they're labeled $\pi$ on each torihedron).
 Again by construction,
@@
 Thus, upon gluing $\sT_T'$ to $\sT_B'$,
-the sum of new exterior dihedral angles $\theta'^*$ around each edge
-is $2\pi$.
+the sum of new exterior dihedral angles $\theta'^*$
+around each edge is still $2\pi$.
 
@@
 \begin{remark}
-Note that for our definition of augmentation,
-we exclude the case where
-an unknotted circle component is added around
-two parallel strands that do not meet at a crossing.
-In particular, this implies that
-a non-weakly prime link cannot become weakly prime
-under augmentation.
-
-If we have an augmentation around two such parallel strands,
-we may consider the related link
-where those two strands have a full twist;
-the hyperbolicity is unaltered, and
-\thmref{t:auglink_hyp} would apply.
+By applying \thmref{t:auglink_hyp} judiciously,
+one may prove hyperbolicity of augmented links
+that do not satisfy its hypotheses as stated.
+
+%Note that for our definition of augmentation,
+%we exclude the case where
+%an unknotted circle component is added around
+%two parallel strands that do not meet at a crossing.
+%In particular, this implies that
+%a non-weakly prime link cannot become weakly prime
+%under augmentation.
+
+%If we have an augmentation around two such parallel strands,
+Say we have a link $K$ that satisfies
+the stricter hypotheses of \thmref{t:auglink_hyp}
+(no bigons).
+Consider a crossing circle $C$ around two parallel strands
+that do not meet at a crossing.
+The addition of $C$ to $K$ is not an augmentation
+as in \defref{d:augmentation},
+and so \thmref{t:auglink_hyp} does not directly apply.
+However, we may consider the related link $K"$
+where those two strands have a full twist,
+so that the addition of $C$ to $K"$ is an augmentation.
+Now \thmref{auglink_hyp} applies to $K" \cup C$,
+and thus $K \cup C$ is also hyperbolic.
+
+Note that augmenting in the sense of \defref{d:augmentation}
+will not turn a non-weakly prime link into a weakly prime link,
+but the above extended notion of augmenting might.
+
+Another way to squeeze more out of \thmref{t:auglink_hyp}
+is to consider augmenting twist regions
+in the ``transverse direction''.
+That is, suppose $K$ has only one twist region $T$,
+which is left-handed,
+but we perform a right-handed augmentation
+at each vertex of $T$
+(instead of the usual left-handed augmentation which is
+one of the hypotheses of \thmref{t:auglink_hyp}).
+Consider the link $K"$ where each vertex of $T$
+is replaced by a right-handed twist region of length 2
+(two bigons).
+Then the twist region $T$ ``is'' no longer a twist region
+in $K"$, and we may freely apply \thmref{t:auglink_hyp})
+and conclude that the ``transversely augmented'' $K$
+is hyperbolic.
 \end{remark}

### 2022-04-17 main.tex
just tidied up a bit, removed an internal todo

@@
 \begin{definition}
-%TODO: this definition should come after base-angled pyramid
 An \emph{angle-splitting} of an angled torihedron $(\sT,\theta_\bullet^*)$
@@
 
-%TODO remark on what splitting means in terms of ideal hyperbolic
-
 \begin{lemma}
 \label{l:pyramid_decomp}
-%Let $P_n$ be an ideal pyramid whose base is an $n$-gon and suppose,
-%\begin{itemize}
-%\item each boundary edge of the base face is assigned a dihedral angle $\alpha_i$ such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$;
-%\item we are given a decomposition of the base face into triangles by adding new edges. 
-%\end{itemize}
 Let $P_n$ be a base-angled ideal pyramid, and suppose we are given a
@@
 Angle structures are solutions to the linear part of
-Thurston's gluing equations;
-we will use them to attain hyperbolicity of complements
-of augmented links in the thickened torus.
+Thurston's gluing equations.
+By \thmref{t:hyperbolic-angle-str}
+(\cite[Theorem 1.1]{FG-angles}),
+to prove hyperbolicity of a link complement,
+it suffices to find an angle structure
+on a triangulation of the link complement.
+%we will use them to attain hyperbolicity of complements
+%of augmented links in the thickened torus.
 
 \begin{define}
-Let $M$ be an orientable 3-manifold with boundary consisting of tori. An angle
-structure on an ideal triangulation $\tau$ of $M$ is an assignment of a dihedral
-angle to each edge of each tetrahedron, such that
+Let $M$ be an orientable 3-manifold with boundary consisting of tori.
+An angle structure on an ideal triangulation $\tau$ of $M$
+is an assignment of a dihedral angle to each edge
+of each tetrahedron, such that
 \begin{itemize}
@@
 \end{theorem}
-
-TODO rephrase to more careful.
 
